---
title: "Florida 16S diversity analysis"
author: "Nicola G. Kriefall"
date: "12/1/21"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
editor_options: 
  chunk_output_type: console
---

# Setup

## Packages

```{r}
library(phyloseq)
library(cowplot)
library(ggplot2)
library(nlme)
library(emmeans)
library("Rmisc")
library("bestNormalize")


library(car)
library(multcomp)

library(car)
library("dplyr")

#home
setwd("~/nicfall@bu.edu - Google Drive/My Drive/Flirma/flirma_networks/fl_16s/02.diversity")

#work
#setwd("~/Library/CloudStorage/GoogleDrive-nicfall@bu.edu/My Drive/Flirma/flirma_networks/fl_16s/02.diversity")
```

## Read in data

Be careful, I tried different data inputs [i.e. not rare, or rare]

```{r}
ps.clean1 <- readRDS("../01.generate_asv_table/flpub.ps.lulu.trim.clean.rds")
ps.clean2 <- subset_samples(ps.clean1,site_zone!="FALSE"&site!="UK3")
ps.clean <- prune_taxa(taxa_sums(ps.clean2)>0,ps.clean2)
ps.clean #7017 taxa and 314 samples

samdf <- data.frame(ps.clean@sam_data)
table(samdf$site_zone)

```

## Calculate metrics

[Notes from phyloseq author](https://rdrr.io/bioc/phyloseq/man/estimate_richness.html)
Visualize alpha-diversity - Should be done on raw, untrimmed dataset

```{r generate div metrics, eval=F}
df <- data.frame(estimate_richness(ps.clean, split=TRUE, measures=c("Shannon","InvSimpson","Observed")))

df$sample_num <- rownames(df)
df$sample_num <- sub("X","",df$sample_num)
rownames(df) <- df$sample_num
df.div <- merge(df,samdf,by="sample_num") #add sample data

#shannon diversity divided by species richness
##aka pielou's evenness
##can also do this function: microbiome::evenness()
df.div$even <- df.div$Shannon/(log(df.div$Observed))
#write.csv(df.div,file="fl16s.23.df.diversity.trim.csv")

# ##reorder the time points
# df.div$time <- factor(df.div$time, levels = c("Pre","Irma","Post"))
# df.div$zone <- as.factor(df.div$zone)
# 
# #separate species
# df.div.rad <- subset(df.div,spp=="srad")
# df.div.sid <- subset(df.div,spp=="ssid")
```

# Analyzing alpha metrics

## Re-read in data, skipping the two sections above

```{r re-read in *start here*}
#df.div <- read.csv("fl16s.df.diversity.csv")
#df.div <- read.csv("fl16s.23.df.diversity.rare.csv")

table(df.div$site_zone)
df.div %>%
  filter(spp=="ssid") %>%
  summarise(sd.obs=sd(Observed), av.obs=mean(Observed))
#     sd.obs   av.obs
# 1 45.87478 75.80447

df.div %>%
  filter(spp=="srad") %>%
  summarise(sd.obs=sd(Observed), av.obs=mean(Observed))
#     sd.obs   av.obs
# 1 52.62415 106.8593

df.div$zone <- as.factor(df.div$zone)
df.div$time <- factor(df.div$time,levels=c("Pre","Irma","Post"))

#separate species
df.div.rad1 <- subset(df.div,spp=="srad")
##for rads, taking out UK1 because it makes the stats uneven
df.div.rad <- subset(df.div.rad1,site!="UK1")

df.div.sid <- subset(df.div,spp=="ssid")
```

## Shannon{.tabset}

### Sids vs. rads

```{r}
ggplot(df.div,aes(x=spp,y=Shannon))+
  geom_boxplot()

wilcox.test(Shannon~spp,data=df.div)
#super sig
```

### Shannon sids plot(s)

```{r}
ggplot(df.div.sid,aes(x=time,y=Shannon,fill=time,color=time,shape=site))+
  geom_jitter(position = position_jitterdodge())+
  facet_grid(.~zone)+
  geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  theme_cowplot()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  ggtitle("S. siderea")+
  scale_shape_manual(values=c(0,2,3),name="Site")+
  ylab("Shannon diversity")+
  xlab("Time point")+
  guides(color="none",fill="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))
  #scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+

#ggsave(gg.sh.sids.yr,file="gg.sids.shannon.pdf",width=3.5,height=4)

### dots & error bars
df.div.sid.shan.se <- summarySE(df.div.sid,measurevar="Shannon",groupvars=c("time","site","zone"))

ggplot(df.div.sid.shan.se,aes(x=time,y=Shannon,color=time,shape=site))+
  geom_jitter(data=df.div.sid,position = position_jitterdodge(),alpha=0.3)+
  facet_grid(.~zone)+
  geom_errorbar(aes(ymin=Shannon-se,ymax=Shannon+se),position=position_dodge(0.5),width=0.2)+
  #geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  geom_point(position=position_dodge(0.5),fill="white")+
  theme_cowplot()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(25,22,24),name="Site")

```

### Shannon rads plot(s)

```{r}
ggplot(df.div.rad,aes(x=time,y=Shannon,fill=time,color=time,shape=site))+
  geom_jitter(position = position_jitterdodge())+
  facet_grid(.~zone)+
  geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  theme_cowplot()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  ggtitle("S. radians")+
  scale_shape_manual(values=c(0,2,3),name="Site")+
  ylab("Shannon diversity")+
  xlab("Time point")+
  guides(color="none",fill="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))
  #scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+

#ggsave(gg.sh.rads.yr,file="gg.rads.shannon.pdf",width=3.5,height=4)

### dots & error bars
df.div.rad.shan.se <- summarySE(df.div.rad,measurevar="Shannon",groupvars=c("time","site","zone"))

ggplot(df.div.rad.shan.se,aes(x=time,y=Shannon,color=time,shape=site))+
  geom_jitter(data=df.div.rad,position = position_jitterdodge(),alpha=0.3)+
  facet_grid(.~zone)+
  geom_errorbar(aes(ymin=Shannon-se,ymax=Shannon+se),position=position_dodge(0.5),width=0.2)+
  #geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  geom_point(position=position_dodge(0.5),fill="white")+
  theme_cowplot()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(25,24),name="Site")
```

### Shannon sids stats

```{r}
shapiro.test(log(df.div.sid$Shannon))
shapiro.test(df.div.sid$Shannon)
#df.div.sid$sh.norm <- bestNormalize(df.div.sid$Shannon)$x.t
#shapiro.test(df.div.sid$sh.norm)
#leveneTest(Shannon~time*site*zone,data=df.div.sid)

sid.a1 <- aov(Shannon~time*site/zone,data=df.div.sid)
summary(sid.a1)
TukeyHSD(sid.a1)

#DunnettTest(df.div.sid$Shannon, df.div.sid$time)

emmip(sid.a1,  ~ time | site:zone)

emmeans(sid.a1, ~time|site/zone)

with(df.div.sid, table(time, site, zone))


#I think I'm going with this one:
lme.shan.sid <- lme(Shannon ~ time*zone,
              random = ~ 1|site,
              data=df.div.sid)

summary(lme.shan.sid)
anova(lme.shan.sid)
#             numDF denDF  F-value p-value
# (Intercept)     1   171 851.9163  <.0001
# time            2   171   1.2950  0.2766
# zone            1   171   0.0939  0.7596
# time:zone       2   171   3.1316  0.0462

shapiro.test(residuals(lme.shan.sid))
qqnorm(residuals(lme.shan.sid))
qqline(residuals(lme.shan.sid), col="red")
plot(lme.shan.sid)

#qqnorm(my.lme, ~ranef(., level=1)) #one per random level if I understand this site correctly:
#https://stats.stackexchange.com/questions/77891/checking-assumptions-lmer-lme-mixed-models-in-r

### posthoc things ###
emmeans(lme.shan.sid, list(pairwise ~ time:zone), adjust = "none")
#nada

#following Bonferroni explanation down at the bottom of this page:
#http://rstudio-pubs-static.s3.amazonaws.com/5832_87bb0ddcaa9d49d59e1998bc7438a297.html
#from google: Bonferroni correction, divide the critical P value (α) by the number of comparisons being made. For example, if 10 hypotheses are being tested, the new critical P value would be α/10. 

##I'm interested in:
 # Pre Inshore - Pre Offshore     -0.5576 0.302 171  -1.847  0.0664
 # Irma Inshore - Irma Offshore    0.2557 0.283 171   0.904  0.3672
 # Post Inshore - Post Offshore    0.4519 0.310 171   1.458  0.1466

##none significant 

##also:
##inshore
# Pre Inshore - Irma Inshore     -0.0645 0.290 171  -0.223  0.8241
# Pre Inshore - Post Inshore     -0.3330 0.305 171  -1.093  0.2761
# Irma Inshore - Post Inshore    -0.2684 0.298 171  -0.901  0.3691

##nada
##offshore
# Pre Offshore - Irma Offshore    0.7488 0.295 171   2.537  0.0121
# Pre Offshore - Post Offshore    0.6765 0.307 171   2.204  0.0289
# Irma Offshore - Post Offshore  -0.0723 0.295 171  -0.245  0.8069
##Pre different from offshore Irma at 0.017 level
```

### Shannon rads stats

```{r}
shapiro.test(df.div.rad$Shannon)
shapiro.test(log(df.div.rad$Shannon))
df.div.rad$sh.norm <- bestNormalize(df.div.rad$Shannon)$x.t
shapiro.test(df.div.rad$sh.norm)
#leveneTest(Shannon~time*site*zone,data=df.div.rad)

lme.shan.rad <- lme(Shannon ~ time*zone,
              random = ~ 1|site,
              data=df.div.rad)

summary(lme.shan.rad)
anova(lme.shan.rad)
#             numDF denDF   F-value p-value
# (Intercept)     1   101 262.22447  <.0001
# time            2   101  35.05105  <.0001
# zone            1   101   0.45971  0.4993
# time:zone       2   101   1.29843  0.2775

shapiro.test(residuals(lme.shan.rad))
qqnorm(residuals(lme.shan.rad))
qqline(residuals(lme.shan.rad), col="red")
plot(lme.shan.rad)

#qqnorm(my.lme, ~ranef(., level=1)) #one per random level if I understand this site correctly:
#https://stats.stackexchange.com/questions/77891/checking-assumptions-lmer-lme-mixed-models-in-r

### posthoc things ###
emmeans(lme.shan.rad, list(pairwise ~ time:zone), adjust = "none")

#following Bonferroni explanation down at the bottom of this page:
#http://rstudio-pubs-static.s3.amazonaws.com/5832_87bb0ddcaa9d49d59e1998bc7438a297.html
#from google: Bonferroni correction, divide the critical P value (α) by the number of comparisons being made. For example, if 10 hypotheses are being tested, the new critical P value would be α/10. 

##I'm interested in:
 # Pre Inshore - Pre Offshore     -0.0615 0.364 101  -0.169  0.8661
 # Irma Inshore - Irma Offshore   -0.5729 0.358 101  -1.601  0.1126
 # Post Inshore - Post Offshore    0.2654 0.389 101   0.683  0.4963

##none significant 

##also:
##inshore
#  Pre Inshore - Irma Inshore      0.9423 0.368 101   2.558  0.0120
#  Pre Inshore - Post Inshore      2.0300 0.368 101   5.509  <.0001*
#  Irma Inshore - Post Inshore     1.0877 0.358 101   3.038  0.0030*
# 
# ##offshore
#  Pre Offshore - Irma Offshore    0.4309 0.353 101   1.219  0.2257
#  Pre Offshore - Post Offshore    2.3570 0.384 101   6.131  <.0001*
#  Irma Offshore - Post Offshore   1.9260 0.389 101   4.956  <.0001*

#stars indicate < 0.0055 level 
```

## ASV richness{.tabset}

### Sids vs. rads

```{r}
ggplot(df.div,aes(x=spp,y=Observed))+
  geom_boxplot()

wilcox.test(Observed~spp,data=df.div)
#super sig
```

### Shannon sids plot(s)

```{r}
ggplot(df.div.sid,aes(x=time,y=Observed,fill=time,color=time,shape=site))+
  geom_jitter(position = position_jitterdodge())+
  facet_grid(.~zone)+
  geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  theme_cowplot()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  ggtitle("S. siderea")+
  scale_shape_manual(values=c(0,2,3),name="Site")+
  ylab("Observed diversity")+
  xlab("Time point")+
  guides(color="none",fill="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))
  #scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+

#ggsave(gg.sh.sids.yr,file="gg.sids.Observed.pdf",width=3.5,height=4)
```

### Observed rads plot(s)

```{r}
ggplot(df.div.rad,aes(x=time,y=Observed,fill=time,color=time,shape=site))+
  geom_jitter(position = position_jitterdodge())+
  facet_grid(.~zone)+
  geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  theme_cowplot()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  ggtitle("S. radians")+
  scale_shape_manual(values=c(0,2,3),name="Site")+
  ylab("Observed diversity")+
  xlab("Time point")+
  guides(color="none",fill="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))
  #scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+

#ggsave(gg.sh.rads.yr,file="gg.rads.Observed.pdf",width=3.5,height=4)
```

### Stats all together

#### Running Observed things

```{r}
#df.div.sid$sh.norm <- bestNormalize(df.div.sid$Observed)$x.t
#shapiro.test(df.div.sid$sh.norm)
#leveneTest(Observed~time*site*zone,data=df.div.sid)
##normalization didn't help for anova

##following nested info here: https://rpubs.com/MarkusLoew/198899
#my.aov <- aov(Observed ~ time*site*zone + Error(site_zone),data = df.div.sid)
#summary(my.aov)
# 
#my.aov <- aov(Observed ~ time*site*zone,data = df.div.sid)
#summary(my.aov)
library(bestNormalize)
bestNormalize(df.div.sid$Observed)
#orderNorm
df.div.sid$obs.norm <- bestNormalize(df.div.sid$Observed)$x.t

sid.lme <- lme(obs.norm ~ time*zone,
              random = ~ 1|site,
              data=df.div.sid)

summary(sid.lme)
anova(sid.lme)
#             numDF denDF   F-value p-value
# (Intercept)     1   158 101.23247  <.0001
# time            2   158   0.61265  0.5432
# zone            1   158   1.85535  0.1751
# time:zone       2   158   6.38755  0.0021
##sig interaction of time by zone
#that was untransformed

##ordernorm transformed:
#             numDF denDF  F-value p-value
# (Intercept)     1   158 0.000001  0.9993
# time            2   158 0.317864  0.7282
# zone            1   158 0.034675  0.8525
# time:zone       2   158 4.928669  0.0084 *

shapiro.test(residuals(sid.lme)) #very good after norm
qqnorm(residuals(sid.lme))
qqline(residuals(sid.lme), col="red")
#could almost not be worse before transformation

#plot(predict(sid.lme), residuals(sid.lme))
plot(sid.lme)

qqnorm(sid.lme, ~ranef(., level=1)) #one per random level if I understand this site correctly:
#https://stats.stackexchange.com/questions/77891/checking-assumptions-lmer-lme-mixed-models-in-r

##comparing fixed effects vs. random effects
model.fixed = gls(obs.norm ~ time*zone,
                  data=df.div.sid,
                  method="REML")

anova(sid.lme,
      model.fixed)

hist(residuals(sid.lme),
     col="darkgray")
#gorg

plot(fitted(sid.lme),
     residuals(sid.lme)) 

library("emmeans")
### posthoc things ###
emmeans(sid.lme, list(pairwise ~ time), adjust = "none")
#nada

emmeans(sid.lme, list(pairwise ~ time:zone), adjust = "tukey")

#following Bonferroni explanation down at the bottom of this page:
#http://rstudio-pubs-static.s3.amazonaws.com/5832_87bb0ddcaa9d49d59e1998bc7438a297.html
#from google: Bonferroni correction, divide the critical P value (α) by the number of comparisons being made. For example, if 10 hypotheses are being tested, the new critical P value would be α/10. 

##I'm interested in:
 # Pre Inshore - Pre Offshore     -0.6765 0.258 158  -2.620  0.0097 *
 # Irma Inshore - Irma Offshore    0.3828 0.244 158   1.570  0.1184
 # Post Inshore - Post Offshore    0.2264 0.302 158   0.750  0.4542
##pre in vs. off is different, nothing else
 
##also:
##inshore
 # Pre Inshore - Irma Inshore     -0.4263 0.250 158  -1.707  0.0898 ns
 # Pre Inshore - Post Inshore     -0.2997 0.288 158  -1.040  0.2998 ns
 # Irma Inshore - Post Inshore     0.1265 0.285 158   0.445  0.6572 ns
##nada
 
##offshore
 #  Pre Offshore - Irma Offshore    0.6330 0.252 158   2.507  0.0132 *
 # Pre Offshore - Post Offshore    0.6032 0.273 158   2.206  0.0288
 # Irma Offshore - Post Offshore  -0.0299 0.264 158  -0.113  0.9099
##pre vs. Irma different, that's it
```

### Observed rads

```{r Observed rads}
gg.sh.rads.yr <- ggplot(df.div.rad,aes(x=time,y=Observed,fill=time,color=time,shape=zone))+
  facet_grid(site~.)+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Observed index")+
  xlab("Time point")+
  ylim(0,7.6)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
  
gg.sh.rads.yr

#ggsave(gg.sh.rads.yr,file="gg.sha.rads.year.pdf",width=3.5,height=4)
```

### Observed rads stats

```{r}
#diagnostic plots didn't look great below, normalizing 
bestNormalize(df.div.rad$Observed)
#orderNorm Transformation with 133 nonmissing obs and no ties 
df.div.rad$obs.norm <- bestNormalize(df.div.rad$Observed)$x.t

#df.div.rad$sh.log <- log(df.div.rad$Observed)
rad.lme <- lme(obs.norm ~ time*zone,
              random = ~ 1|site,
              data=df.div.rad)

summary(rad.lme)
anova(rad.lme)
#             numDF denDF  F-value p-value
# (Intercept)     1   125 744.2085  <.0001
# time            2   125  47.2367  <.0001
# zone            1   125   1.0613  0.3049
# time:zone       2   125   1.3763  0.2563
##time is very very significant - post goes way down which is weird

##after normalizing:
#             numDF denDF  F-value p-value
# (Intercept)     1   125  0.08199  0.7751
# time            2   125 39.53644  <.0001
# zone            1   125  2.85579  0.0935
# time:zone       2   125  2.28306  0.1062
#different in terms of numbers, not differnt in terms of level of significance

shapiro.test(residuals(rad.lme))
qqnorm(residuals(rad.lme))
qqline(residuals(rad.lme), col="red")

#plot(predict(rad.lme), reraduals(rad.lme))
plot(rad.lme)

qqnorm(rad.lme, ~ranef(., level=1)) #one per random level if I understand this site correctly:
##https://stats.stackexchange.com/questions/77891/checking-assumptions-lmer-lme-mixed-models-in-r

##comparing fixed effects vs. random effects
model.fixed = gls(obs.norm ~ time*zone,
                  data=df.div.rad,
                  method="REML")

anova(rad.lme,
      model.fixed)

hist(residuals(rad.lme),
     col="darkgray")

plot(fitted(rad.lme),
     residuals(rad.lme)) 

### posthoc things ###
emmeans(rad.lme, list(pairwise ~ time), adjust = "none")
##all different:
# $`pairwise differences of time`
#  1           estimate    SE  df t.ratio p.value
#  Pre - Irma     0.690 0.156 125   4.428  <.0001
#  Pre - Post     1.553 0.178 125   8.726  <.0001
#  Irma - Post    0.863 0.182 125   4.745  <.0001

emmeans(rad.lme, list(pairwise ~ time:zone), adjust = "none")

#following Bonferroni explanation down at the bottom of this page:
#http://rstudio-pubs-static.s3.amazonaws.com/5832_87bb0ddcaa9d49d59e1998bc7438a297.html
#from google: Bonferroni correction, divide the critical P value (α) by the number of comparisons being made. For example, if 10 hypotheses are being tested, the new critical P value would be α/10. 

##I'm interested in:
 # Pre Inshore - Pre Offshore     -0.5469 0.204 125  -2.678  0.0084 *
 # Irma Inshore - Irma Offshore   -0.0577 0.233 125  -0.248  0.8047
 # Post Inshore - Post Offshore    0.1217 0.278 125   0.438  0.6621
##in vs. off was different during pre, not super interesting

##also:
##inshore
 # Pre Inshore - Irma Inshore      0.4456 0.214 125   2.083  0.0393
 # Pre Inshore - Post Inshore      1.2190 0.243 125   5.019  <.0001
 # Irma Inshore - Post Inshore     0.7734 0.245 125   3.161  0.0020
##post different than both, although pre vs. irma was almost there :/ 

##offshore
 # Pre Offshore - Irma Offshore    0.9349 0.225 125   4.155  0.0001 *
 # Pre Offshore - Post Offshore    1.8876 0.253 125   7.473  <.0001 *
 # Irma Offshore - Post Offshore   0.9527 0.268 125   3.552  0.0005 *
##all different!
```

## Evenness{.tabset}

### Sids vs. rads

```{r}
ggplot(df.div,aes(x=spp,y=even))+
  geom_boxplot()
#rads way more even
wilcox.test(even~spp,data=df.div)
#super sig
```

### Even sids plot(s)

```{r}
ggplot(df.div.sid,aes(x=time,y=even,fill=time,color=time,shape=site))+
  geom_jitter(position = position_jitterdodge())+
  facet_grid(.~zone)+
  geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  theme_cowplot()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  ggtitle("S. siderea")+
  scale_shape_manual(values=c(0,2,3),name="Site")+
  ylab("Evenness")+
  xlab("Time point")+
  guides(color="none",fill="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))
  #scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+

#ggsave(gg.sh.sids.yr,file="gg.sids.even.pdf",width=3.5,height=4)
```

### Even rads plot(s)

```{r}
ggplot(df.div.rad,aes(x=time,y=even,fill=time,color=time,shape=site))+
  geom_jitter(position = position_jitterdodge())+
  facet_grid(.~zone)+
  geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  theme_cowplot()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  ggtitle("S. radians")+
  scale_shape_manual(values=c(0,2,3),name="Site")+
  ylab("Evenness")+
  xlab("Time point")+
  guides(color="none",fill="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))
  #scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+

#ggsave(gg.sh.rads.yr,file="gg.rads.even.pdf",width=3.5,height=4)
```

# Stats even

For the chapter

```{r}
lmer.sid <- lmer(even ~ time*zone +
(1|site), data = df.div.sid)

Anova(lmer.sid, test = "F")
#                F Df Df.res  Pr(>F)  
# time      3.5726  2 158.52 0.03037 *
# zone      0.1093  1 158.09 0.74140  
# time:zone 1.5674  2 158.34 0.21181  

emmeans(lmer.sid, list(pairwise ~ time), adjust = "bonf")
 # Pre - Irma    0.0660 0.0342 158   1.930  0.1663
 # Pre - Post    0.0953 0.0382 158   2.494  0.0410 #pre v post sig
 # Irma - Post   0.0293 0.0374 159   0.783  1.0000

emmeans(lmer.sid, list(pairwise ~ time:zone), adjust = "none")


# 1                             estimate     SE  df t.ratio p.value
#  Pre Inshore - Irma Inshore      0.0188 0.0481 158   0.390  0.6968
#  Pre Inshore - Post Inshore      0.0331 0.0555 158   0.596  0.5518
#  Pre Inshore - Pre Offshore     -0.0593 0.0496 158  -1.194  0.2342
#  Pre Inshore - Irma Offshore     0.0539 0.0477 158   1.131  0.2599
#  Pre Inshore - Post Offshore     0.0982 0.0518 158   1.896  0.0597
#  Irma Inshore - Post Inshore     0.0143 0.0550 159   0.261  0.7948
#  Irma Inshore - Pre Offshore    -0.0781 0.0489 158  -1.595  0.1128
#  Irma Inshore - Irma Offshore    0.0351 0.0469 158   0.750  0.4546
#  Irma Inshore - Post Offshore    0.0794 0.0510 158   1.556  0.1217
#  Post Inshore - Pre Offshore    -0.0924 0.0562 158  -1.643  0.1023
#  Post Inshore - Irma Offshore    0.0208 0.0546 159   0.381  0.7034
#  Post Inshore - Post Offshore    0.0651 0.0581 159   1.120  0.2644
#  Pre Offshore - Irma Offshore    0.1132 0.0486 158   2.330  0.0211
#  Pre Offshore - Post Offshore    0.1575 0.0526 158   2.996  0.0032
#  Irma Offshore - Post Offshore   0.0443 0.0507 158   0.873  0.3839

##same results as with nlme

```

## Different iteration

```{r}
#bestNormalize(df.div.sid$even)
#orderNorm
#df.div.sid$obs.norm <- bestNormalize(df.div.sid$even)$x.t

sid.lme <- lme(even ~ time*zone,
              random = ~ 1|site,
              data=df.div.sid)

#summary(sid.lme)
anova(sid.lme)
#             numDF denDF   F-value p-value
# (Intercept)     1   158 1599.5912  <.0001
# time            2   158    3.6315  0.0287 *
# zone            1   158    0.1099  0.7407
# time:zone       2   158    1.5692  0.2114
##untransformed

##ordernorm transformed:
shapiro.test(residuals(sid.lme)) #very good
qqnorm(residuals(sid.lme))
qqline(residuals(sid.lme), col="red")

#plot(predict(sid.lme), residuals(sid.lme))
plot(sid.lme)

qqnorm(sid.lme, ~ranef(., level=1)) #one per random level if I understand this site correctly:
#https://stats.stackexchange.com/questions/77891/checking-assumptions-lmer-lme-mixed-models-in-r

##comparing fixed effects vs. random effects
model.fixed = gls(even ~ time*zone,
                  data=df.div.sid,
                  method="REML")

anova(sid.lme,
      model.fixed)

hist(residuals(sid.lme),
     col="darkgray")
#gorg

plot(fitted(sid.lme),
     residuals(sid.lme)) 

### posthoc things ###
emmeans(sid.lme, list(pairwise ~ time), adjust = "bonf")
# $`pairwise differences of time`
#  1           estimate     SE  df t.ratio p.value
 # Pre - Irma    0.0660 0.0341 158   1.933  0.1651
 # Pre - Post    0.0953 0.0382 158   2.496  0.0408 *
 # Irma - Post   0.0293 0.0373 158   0.786  1.0000

emmeans(sid.lme, list(pairwise ~ time:zone), adjust = "tukey")

#following Bonferroni explanation down at the bottom of this page:
#http://rstudio-pubs-static.s3.amazonaws.com/5832_87bb0ddcaa9d49d59e1998bc7438a297.html
#from google: Bonferroni correction, divide the critical P value (α) by the number of comparisons being made. For example, if 10 hypotheses are being tested, the new critical P value would be α/10. 

##I'm interested in:
 # Pre Inshore - Pre Offshore     -0.0593 0.0496 158  -1.194  0.2341
 # Irma Inshore - Irma Offshore    0.0351 0.0469 158   0.750  0.4545
 # Post Inshore - Post Offshore    0.0651 0.0580 158   1.122  0.2634
##nada

##also:
##inshore
 # Pre Inshore - Irma Inshore      0.0188 0.0480 158   0.391  0.6964
 # Pre Inshore - Post Inshore      0.0331 0.0554 158   0.597  0.5511
 # Irma Inshore - Post Inshore     0.0143 0.0547 158   0.262  0.7939
#nada 

##offshore
 # Pre Offshore - Irma Offshore    0.1132 0.0485 158   2.332  0.0210 ns with multcomp
 # Pre Offshore - Post Offshore    0.1575 0.0525 158   2.997  0.0032 *
 # Irma Offshore - Post Offshore   0.0443 0.0507 158   0.874  0.3835
##Irma & post not different, others are
#maybe season?
```

### even rads

```{r even rads}
gg.sh.rads.yr <- ggplot(df.div.rad,aes(x=time,y=even,fill=time,color=time,shape=zone))+
  facet_grid(site~.)+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("even index")+
  xlab("Time point")+
  ylim(0,7.6)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
  
gg.sh.rads.yr

#ggsave(gg.sh.rads.yr,file="gg.sha.rads.year.pdf",width=3.5,height=4)
```

### even rads stats

```{r}
#diagnostic plots didn't look great below, normalizing 
bestNormalize(df.div.rad$even)
#orderNorm Transformation with 133 nonmissing obs and no ties 
df.div.rad$eve.norm <- bestNormalize(df.div.rad$even)$x.t

#df.div.rad$sh.log <- log(df.div.rad$even)
rad.lme <- lme(eve.norm ~ time*zone,
              random = ~ 1|site,
              data=df.div.rad)

summary(rad.lme)
anova(rad.lme)
#             numDF denDF  F-value p-value
# (Intercept)     1   125 744.2085  <.0001
# time            2   125  47.2367  <.0001
# zone            1   125   1.0613  0.3049
# time:zone       2   125   1.3763  0.2563
##time is very very significant - post goes way down which is weird

##after normalizing:
#             numDF denDF  F-value p-value
# (Intercept)     1   125  0.08199  0.7751
# time            2   125 39.53644  <.0001
# zone            1   125  2.85579  0.0935
# time:zone       2   125  2.28306  0.1062
#different in terms of numbers, not differnt in terms of level of significance

shapiro.test(residuals(rad.lme))
qqnorm(residuals(rad.lme))
qqline(residuals(rad.lme), col="red")

#plot(predict(rad.lme), reraduals(rad.lme))
plot(rad.lme)

qqnorm(rad.lme, ~ranef(., level=1)) #one per random level if I understand this site correctly:
##https://stats.stackexchange.com/questions/77891/checking-assumptions-lmer-lme-mixed-models-in-r

##comparing fixed effects vs. random effects
model.fixed = gls(even ~ time*zone,
                  data=df.div.rad,
                  method="REML")

anova(rad.lme,
      model.fixed)

hist(residuals(rad.lme),
     col="darkgray")

plot(fitted(rad.lme),
     residuals(rad.lme)) 

### posthoc things ###
emmeans(rad.lme, list(pairwise ~ time), adjust = "tukey")
##all different:
# $`pairwise differences of time`
#  1           estimate    SE  df t.ratio p.value
#  Pre - Irma     0.690 0.156 125   4.428  <.0001
#  Pre - Post     1.553 0.178 125   8.726  <.0001
#  Irma - Post    0.863 0.182 125   4.745  <.0001

emmeans(rad.lme, list(pairwise ~ time:zone), adjust = "tukey")

#following Bonferroni explanation down at the bottom of this page:
#http://rstudio-pubs-static.s3.amazonaws.com/5832_87bb0ddcaa9d49d59e1998bc7438a297.html
#from google: Bonferroni correction, divide the critical P value (α) by the number of comparisons being made. For example, if 10 hypotheses are being tested, the new critical P value would be α/10. 

##I'm interested in:
 # Pre Inshore - Pre Offshore     -0.5469 0.204 125  -2.678  0.0084
 # Irma Inshore - Irma Offshore   -0.0577 0.233 125  -0.248  0.8047
 # Post Inshore - Post Offshore    0.1217 0.278 125   0.438  0.6621
##in vs. off was different during pre, not super interesting

##also:
##inshore
 # Pre Inshore - Irma Inshore      0.4456 0.214 125   2.083  0.0393 
 # Pre Inshore - Post Inshore      1.2190 0.243 125   5.019  <.0001
 # Irma Inshore - Post Inshore     0.7734 0.245 125   3.161  0.0020
##post different than both, although pre vs. irma was almost there :/ 

##offshore
 # Pre Offshore - Irma Offshore    0.9349 0.225 125   4.155  0.0001
 # Pre Offshore - Post Offshore    1.8876 0.253 125   7.473  <.0001
 # Irma Offshore - Post Offshore   0.9527 0.268 125   3.552  0.0005
##all different!
```

# Jaccard

```{r}
#library("devtools")
#devtools::install_github("kylebittinger/usedist")
#library("usedist")
library(reshape2)

ps.sid <- subset_samples(ps.clean,spp=="ssid")
ps.sid.in <- subset_samples(ps.clean,zone=="Inshore")
ps.sid.in.pre.irm <- subset_samples(ps.sid.in,time=="Pre"|time=="Irma")
ps.sid.in.pre.pos <- subset_samples(ps.sid.in,time=="Pre"|time=="Post")
ps.sid.in.irm.pos <- subset_samples(ps.sid.in,time=="Irma"|time=="Post")

sam.pre <- subset(samdf,time=="Pre")
sams.pre <- c(sam.pre$sample_num)

sam.irm <- subset(samdf,time=="Irma")
sams.irm <- c(sam.irm$sample_num)

sam.pos <- subset(samdf,time=="Post")
sams.pos <- c(sam.pos$sample_num)

dist.sid.in.pre.irm <- distance(ps.sid.in.pre.irm, "jaccard", binary = TRUE) # vegdist jaccard
dist.sid.in.pre.pos <- distance(ps.sid.in.pre.pos, "jaccard", binary = TRUE) # vegdist jaccard
dist.sid.in.irm.pos <- distance(ps.sid.in.irm.pos, "jaccard", binary = TRUE) # vegdist jaccard

df.sid.in.pre.irm <- melt(as.matrix(dist.sid.in.pre.irm), varnames = c("row", "col"))
df.sid.in.pre.pos <- melt(as.matrix(dist.sid.in.pre.pos), varnames = c("row", "col"))
df.sid.in.irm.pos <- melt(as.matrix(dist.sid.in.irm.pos), varnames = c("row", "col"))

df.sid.in.pre.irm2 <- df.sid.in.pre.irm[df.sid.in.pre.irm$col %in% c(sams.pre),]
df.sid.in.pre.irm3 <- df.sid.in.pre.irm2[df.sid.in.pre.irm2$row %in% c(sams.irm),]

df.sid.in.pre.irm3.se <- summarySE(data=df.sid.in.pre.irm3,measurevar="value")

df.sid.in.pre.pos2 <- df.sid.in.pre.pos[df.sid.in.pre.pos$col %in% c(sams.pre),]
df.sid.in.pre.pos3 <- df.sid.in.pre.pos2[df.sid.in.pre.pos2$row %in% c(sams.pos),]

df.sid.in.pre.pos3.se <- summarySE(data=df.sid.in.pre.pos3,measurevar="value")

df.sid.in.irm.pos2 <- df.sid.in.irm.pos[df.sid.in.irm.pos$col %in% c(sams.irm),]
df.sid.in.irm.pos3 <- df.sid.in.irm.pos2[df.sid.in.irm.pos2$row %in% c(sams.pos),]

df.sid.in.irm.pos3.se <- summarySE(data=df.sid.in.irm.pos3,measurevar="value")

df.sid.in <- rbind(df.sid.in.pre.irm3.se,df.sid.in.pre.pos3.se,df.sid.in.irm.pos3.se)
df.sid.in$.id <- c("pre.irm","pre.pos","irm.pos")

#ggplot(df.sid.in,aes(x=.id,y=value))+
#  geom_point()

df.sid.in.pre.irm3$comp <- rep("Pre_Irma",nrow(df.sid.in.pre.irm3))
df.sid.in.pre.irm3$zone <- rep("inshore",nrow(df.sid.in.pre.irm3))

df.sid.in.pre.pos3$comp <- rep("Pre_Post",nrow(df.sid.in.pre.pos3))
df.sid.in.pre.pos3$zone <- rep("inshore",nrow(df.sid.in.pre.pos3))

df.sid.in.irm.pos3$comp <- rep("Irma_Post",nrow(df.sid.in.irm.pos3))
df.sid.in.irm.pos3$zone <- rep("inshore",nrow(df.sid.in.irm.pos3))

### offshore ###
ps.sid.off <- subset_samples(ps.clean,zone=="Offshore")
ps.sid.off.pre.irm <- subset_samples(ps.sid.off,time=="Pre"|time=="Irma")
ps.sid.off.pre.pos <- subset_samples(ps.sid.off,time=="Pre"|time=="Post")
ps.sid.off.irm.pos <- subset_samples(ps.sid.off,time=="Irma"|time=="Post")

dist.sid.off.pre.irm <- distance(ps.sid.off.pre.irm, "jaccard", binary = TRUE) # vegdist jaccard
dist.sid.off.pre.pos <- distance(ps.sid.off.pre.pos, "jaccard", binary = TRUE) # vegdist jaccard
dist.sid.off.irm.pos <- distance(ps.sid.off.irm.pos, "jaccard", binary = TRUE) # vegdist jaccard

df.sid.off.pre.irm <- melt(as.matrix(dist.sid.off.pre.irm), varnames = c("row", "col"))
df.sid.off.pre.pos <- melt(as.matrix(dist.sid.off.pre.pos), varnames = c("row", "col"))
df.sid.off.irm.pos <- melt(as.matrix(dist.sid.off.irm.pos), varnames = c("row", "col"))

df.sid.off.pre.irm2 <- df.sid.off.pre.irm[df.sid.off.pre.irm$col %in% c(sams.pre),]
df.sid.off.pre.irm3 <- df.sid.off.pre.irm2[df.sid.off.pre.irm2$row %in% c(sams.irm),]

df.sid.off.pre.irm3.se <- summarySE(data=df.sid.off.pre.irm3,measurevar="value")

df.sid.off.pre.pos2 <- df.sid.off.pre.pos[df.sid.off.pre.pos$col %in% c(sams.pre),]
df.sid.off.pre.pos3 <- df.sid.off.pre.pos2[df.sid.off.pre.pos2$row %in% c(sams.pos),]

df.sid.off.pre.pos3.se <- summarySE(data=df.sid.off.pre.pos3,measurevar="value")

df.sid.off.irm.pos2 <- df.sid.off.irm.pos[df.sid.off.irm.pos$col %in% c(sams.irm),]
df.sid.off.irm.pos3 <- df.sid.off.irm.pos2[df.sid.off.irm.pos2$row %in% c(sams.pos),]

df.sid.off.irm.pos3.se <- summarySE(data=df.sid.off.irm.pos3,measurevar="value")

#df.sid.off <- rbind(df.sid.off.pre.irm3.se,df.sid.off.pre.pos3.se,df.sid.off.irm.pos3.se)
#df.sid.off$.id <- c("pre.irm","pre.pos","irm.pos")

#ggplot(df.sid.off,aes(x=.id,y=value))+
#  geom_point()

df.sid.off.pre.irm3$comp <- rep("Pre_Irma",nrow(df.sid.off.pre.irm3))
df.sid.off.pre.irm3$zone <- rep("Offshore",nrow(df.sid.off.pre.irm3))

df.sid.off.pre.pos3$comp <- rep("Pre_Post",nrow(df.sid.off.pre.pos3))
df.sid.off.pre.pos3$zone <- rep("Offshore",nrow(df.sid.off.pre.pos3))

df.sid.off.irm.pos3$comp <- rep("Irma_Post",nrow(df.sid.off.irm.pos3))
df.sid.off.irm.pos3$zone <- rep("Offshore",nrow(df.sid.off.irm.pos3))


df.sid.all <- rbind(df.sid.in.pre.irm3,df.sid.in.pre.pos3,df.sid.in.irm.pos3,df.sid.off.pre.irm3,df.sid.off.pre.pos3,df.sid.off.irm.pos3)

ggplot(df.sid.all,aes(x=comp,y=value))+
  geom_boxplot()+
  facet_wrap(~zone)

a1 <- aov(value~comp*zone,data=df.sid.all)
TukeyHSD(a1)

sid.lme <- lme(value ~ time*zone,
              random = ~ 1|site,
              data=df.sid.all)


df <- data.frame(estimate_richness(ps.clean, split=TRUE, measures=c("Shannon","InvSimpson","Observed")))

df$sample_num <- rownames(df)
df$sample_num <- sub("X","",df$sample_num)
rownames(df) <- df$sample_num
df.div <- merge(df,samdf,by="sample_num") #add sample data

#shannon diversity divided by species richness
##aka pielou's evenness
##can also do this function: microbiome::evenness()
df.div$even <- df.div$Shannon/(log(df.div$Observed))
#write.csv(df.div,file="fl16s.df.diversity.csv")
#write.csv(df.div,file="fl16s.df.diversity_rare.csv")

##reorder the time points
df.div$time <- factor(df.div$time, levels = c("Pre","Irma","Post"))
df.div$zone <- as.factor(df.div$zone)

#separate species
df.div.rad <- subset(df.div,spp=="srad")
df.div.sid <- subset(df.div,spp=="ssid")
```



