---
title: "Florida 16S diversity analysis"
author: "Nicola G. Kriefall"
date: "12/1/21"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
---

# Setup

## Packages

```{r}
library(cowplot)
library(ggplot2)
library(phyloseq)
library("Rmisc")

#home
#setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks_master/fl_16s/02.diversity")

#work
setwd("~/nicfall@bu.edu - Google Drive/My Drive/Flirma/flirma_networks_master/fl_16s/02.diversity")
```

## Read in data

Be careful, I tried different data inputs here

```{r}
#ps.cleaner <- readRDS("~/Google Drive (nicfall@bu.edu)/Flirma/flirma_networks_master/fl_16s/01.generate_asv_table/fl16s.ps.cleaner.clr.rd3.rds")
#ps.cleaner <- ps.cleaner <- readRDS("../01.generate_asv_table/fl16s.ps.cleaner.rd3.rds")
#ps.clean <- subset_samples(ps.cleaner,site!="UK3")

ps.rare <- readRDS("../01.generate_asv_table/ps.rare.rd3.6500.rds")
ps.clean <- subset_samples(ps.rare,site!="UK3")

# ps.clean1 <- readRDS("../01.generate_asv_table/fl16s.ps.cleaner.rd3_newvars.rds")
# ps.clean <- subset_samples(ps.clean1,site!="UK3")

samdf <- data.frame(ps.clean@sam_data)
```

## Calculate metrics

[Notes from phyloseq author](https://rdrr.io/bioc/phyloseq/man/estimate_richness.html)
Visualize alpha-diversity - Should be done on raw, untrimmed dataset

```{r generate div metrics}
df <- data.frame(estimate_richness(ps.clean, split=TRUE, measures=c("Shannon","InvSimpson","Observed")))

df$sample_num <- rownames(df)
df$sample_num <- sub("X","",df$sample_num)
rownames(df) <- df$sample_num 
df.div <- merge(df,samdf,by="sample_num") #add sample data

#shannon diversity divided by species richness
df.div$even <- df.div$Shannon/(log(df.div$Observed))
#write.csv(df.div,file="fl16s.df.diversity_rare6500.csv")

##reorder the time points
df.div$time <- factor(df.div$time, levels = c("Pre","Irma","Post"))

#separate species
df.div.rad <- subset(df.div,spp=="srad")
df.div.sid <- subset(df.div,spp=="ssid")
```

Re-read in data, skipping the two sections above

```{r}
df.div <- read.csv("fl16s.df.diversity_edits.csv")

df.div$time <- factor(df.div$time, levels = c("Pre","Irma","Post"))

#separate species
df.div.rad <- subset(df.div,spp=="srad")
df.div.sid <- subset(df.div,spp=="ssid")
```

# Analyzing alpha metrics

## Shannon sids {.tabset}

```{r}
gg.sh.sids.yr <- ggplot(df.div.sid,aes(x=time,y=Shannon,fill=time,color=time,shape=zone))+
  facet_grid(site~.)+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Shannon index")+
  xlab("Timepoint")+
  ylim(0,6.7)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. siderea")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")
gg.sh.sids.yr

#ggsave(gg.sh.sids.yr,file="gg.sha.sids.year.pdf",width=3.5,height=4)
```

### Shannon sids stats - zone

```{r shannon sids rz}
shapiro.test(df.div.sid$Shannon) #good

# a.sha <- aov(Shannon~time*site*zone*,data=df.div.sid)
# summary(a.sha)
# 
# TukeyHSD(a.sha)

# within site & year
df.div.sid.15 <- subset(df.div.sid,time=="Pre")
df.div.sid.17 <- subset(df.div.sid,time=="Irma")
df.div.sid.18 <- subset(df.div.sid,time=="Post")

#LK1
df.div.sid.15.lk1 <- subset(df.div.sid.15,site=="LK1")
df.div.sid.17.lk1 <- subset(df.div.sid.17,site=="LK1")
df.div.sid.18.lk1 <- subset(df.div.sid.18,site=="LK1")

wilcox.test(Shannon~zone,data=df.div.sid.15.lk1)#p < 0.001***
wilcox.test(Shannon~zone,data=df.div.sid.17.lk1)#ns
wilcox.test(Shannon~zone,data=df.div.sid.18.lk1)#ns

#UK1
df.div.sid.15.uk1 <- subset(df.div.sid.15,site=="UK1")
df.div.sid.17.uk1 <- subset(df.div.sid.17,site=="UK1")
df.div.sid.18.uk1 <- subset(df.div.sid.18,site=="UK1")

wilcox.test(Shannon~zone,data=df.div.sid.15.uk1)#ns
wilcox.test(Shannon~zone,data=df.div.sid.17.uk1)#p = 0.089 .
wilcox.test(Shannon~zone,data=df.div.sid.18.uk1)#p = 0.053 .

#UK2
df.div.15.uk2 <- subset(df.div.sid.15,site=="UK2")
df.div.17.uk2 <- subset(df.div.sid.17,site=="UK2")
df.div.18.uk2 <- subset(df.div.sid.18,site=="UK2")

wilcox.test(Shannon~zone,data=df.div.15.uk2)#ns
wilcox.test(Shannon~zone,data=df.div.17.uk2)#ns
wilcox.test(Shannon~zone,data=df.div.18.uk2)#p = 0.09 .
```

### Shannon sids stats - time 

```{r stats sids by year}
df.div.sid.lk1 <- subset(df.div.sid,site=="LK1")
df.div.sid.uk1 <- subset(df.div.sid,site=="UK1")
df.div.sid.uk2 <- subset(df.div.sid,site=="UK2")

df.div.sid.lk1.in <- subset(df.div.sid.lk1,zone=="Inshore")
df.div.sid.lk1.off <- subset(df.div.sid.lk1,zone=="Offshore")

df.div.sid.uk1.in <- subset(df.div.sid.uk1,zone=="Inshore")
df.div.sid.uk1.off <- subset(df.div.sid.uk1,zone=="Offshore")

df.div.sid.uk2.in <- subset(df.div.sid.uk2,zone=="Inshore")
df.div.sid.uk2.off <- subset(df.div.sid.uk2,zone=="Offshore")

pairwise.wilcox.test(df.div.sid.lk1.in$Shannon, df.div.sid.lk1.in$time, p.adjust.method = "BH")
pairwise.wilcox.test(df.div.sid.lk1.off$Shannon, df.div.sid.lk1.off$time, p.adjust.method = "BH")
#      Pre    Irma  
# Irma 0.0029 -     
# Post 0.0472 0.4470

pairwise.wilcox.test(df.div.sid.uk1.in$Shannon, df.div.sid.uk1.in$time, p.adjust.method = "BH")
pairwise.wilcox.test(df.div.sid.uk1.off$Shannon, df.div.sid.uk1.off$time, p.adjust.method = "BH")
#ns

pairwise.wilcox.test(df.div.sid.uk2.in$Shannon, df.div.sid.uk2.in$time, p.adjust.method = "BH")
pairwise.wilcox.test(df.div.sid.uk2.off$Shannon, df.div.sid.uk2.off$time, p.adjust.method = "BH")
#ns
```

### Shannon rads plot

```{r shannon rads}
gg.sh.rads.yr <- ggplot(df.div.rad,aes(x=time,y=Shannon,fill=time,color=time,shape=zone))+
  facet_grid(site~.)+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Shannon index")+
  xlab("Timepoint")+
  ylim(0,7.5)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")
gg.sh.rads.yr

#ggsave(gg.sh.rads.yr,file="gg.sha.rads.year.pdf",width=3.5,height=4)
```

### Shannon rads stats

### Shannon rads stats - zone

```{r shannon rads rz}
shapiro.test(df.div.rad$Shannon) #good

# a.sha <- aov(Shannon~time*site*zone*,data=df.div.rad)
# summary(a.sha)
# 
# TukeyHSD(a.sha)

# within site & year
df.div.rad.15 <- subset(df.div.rad,time=="Pre")
df.div.rad.17 <- subset(df.div.rad,time=="Irma")
df.div.rad.18 <- subset(df.div.rad,time=="Post")

#LK1
df.div.rad.15.lk1 <- subset(df.div.rad.15,site=="LK1")
df.div.rad.17.lk1 <- subset(df.div.rad.17,site=="LK1")
df.div.rad.18.lk1 <- subset(df.div.rad.18,site=="LK1")

wilcox.test(Shannon~zone,data=df.div.rad.15.lk1)#p < 0.05*
# data:  Shannon by zone
# W = 20, p-value = 0.04347
wilcox.test(Shannon~zone,data=df.div.rad.17.lk1)#ns
wilcox.test(Shannon~zone,data=df.div.rad.18.lk1)#ns

#UK1
df.div.rad.15.uk1 <- subset(df.div.rad.15,site=="UK1")
df.div.rad.17.uk1 <- subset(df.div.rad.17,site=="UK1")
df.div.rad.18.uk1 <- subset(df.div.rad.18,site=="UK1")

wilcox.test(Shannon~zone,data=df.div.rad.15.uk1)#p = 0.089 .
# data:  Shannon by zone
# W = 27, p-value = 0.08921
#wilcox.test(Shannon~zone,data=df.div.rad.17.uk1)#can't do, missing data
#wilcox.test(Shannon~zone,data=df.div.rad.18.uk1)#can't do, missing data

#UK2
df.div.15.uk2 <- subset(df.div.rad.15,site=="UK2")
df.div.17.uk2 <- subset(df.div.rad.17,site=="UK2")
df.div.18.uk2 <- subset(df.div.rad.18,site=="UK2")

wilcox.test(Shannon~zone,data=df.div.15.uk2)#ns
wilcox.test(Shannon~zone,data=df.div.17.uk2)#p < 0.05 *
# data:  Shannon by zone
# W = 12, p-value = 0.01061
wilcox.test(Shannon~zone,data=df.div.18.uk2)#ns
```

### Shannon rads stats - time 

```{r stats rads by year}
df.div.rad.lk1 <- subset(df.div.rad,site=="LK1")
df.div.rad.uk1 <- subset(df.div.rad,site=="UK1")
df.div.rad.uk2 <- subset(df.div.rad,site=="UK2")

df.div.rad.lk1.in <- subset(df.div.rad.lk1,zone=="Inshore")
df.div.rad.lk1.off <- subset(df.div.rad.lk1,zone=="Offshore")

df.div.rad.uk1.in <- subset(df.div.rad.uk1,zone=="Inshore")
df.div.rad.uk1.off <- subset(df.div.rad.uk1,zone=="Offshore")

df.div.rad.uk2.in <- subset(df.div.rad.uk2,zone=="Inshore")
df.div.rad.uk2.off <- subset(df.div.rad.uk2,zone=="Offshore")

pairwise.wilcox.test(df.div.rad.lk1.in$Shannon, df.div.rad.lk1.in$time, p.adjust.method = "BH")
#      Pre    Irma  
# Irma 0.8421 -     
# Post 0.0028 0.0019
pairwise.wilcox.test(df.div.rad.lk1.off$Shannon, df.div.rad.lk1.off$time, p.adjust.method = "BH")
#      Pre     Irma   
# Irma 0.01340 -      
# Post 0.00031 0.03301

pairwise.wilcox.test(df.div.rad.uk1.in$Shannon, df.div.rad.uk1.in$time, p.adjust.method = "BH") #ns
pairwise.wilcox.test(df.div.rad.uk1.off$Shannon, df.div.rad.uk1.off$time, p.adjust.method = "BH") #ns

pairwise.wilcox.test(df.div.rad.uk2.in$Shannon, df.div.rad.uk2.in$time, p.adjust.method = "BH")
#      Pre    Irma  
# Irma 0.0030 -     
# Post 0.0046 0.9682
pairwise.wilcox.test(df.div.rad.uk2.off$Shannon, df.div.rad.uk2.off$time, p.adjust.method = "BH")
#     Pre    Irma  
# Irma 0.2110 -     
# Post 0.0037 0.0079
```

## Observed

### Observed sids - by zone

```{r}
gg.ob.sids.yr <- ggplot(df.div.sid,aes(x=time,y=Observed,fill=time,color=time,shape=zone))+
  facet_grid(site~.,scales="free_y")+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("ASV richness")+
  xlab("Timepoint")+
  ylim(0,1000)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. siderea")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")
gg.ob.sids.yr

gg.ob.sids.zone <- ggplot(df.div.sid,aes(x=zone,y=Observed,color=zone,shape=zone,fill=zone))+
  #ylim(0,1000)+
  facet_grid(time~site,scales="free_y")+
  geom_jitter(alpha=0.6)+
  geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  ylab("ASV richness")+
  xlab("Zone")+
  theme_bw()+
  scale_color_manual(values=c("#3BBA76","#453882"))+
  scale_fill_manual(values=c("#3BBA76","#453882"))+
  scale_shape_manual(values=c(16,18))+
  theme(legend.position="none",plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. siderea")+
  xlab("Reef zone")
gg.ob.sids.zone
#ggsave("gg.obs.sids.year.pdf",width=3)
```

### Observed sids - by time

```{r}
gg.ob.sids.yr <- ggplot(df.div.sid,aes(x=time,y=Observed,color=time,shape=zone,fill=time))+
  ylim(0,1000)+
  facet_grid(zone~site,scales="free_y")+
  geom_jitter(alpha=0.8)+
  geom_boxplot(outlier.shape=NA,color="black",alpha=0.5)+
  ylab("ASV richness")+
  xlab("Timepoint")+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(16,18))+
  theme(legend.position="none",plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. siderea")
gg.ob.sids.yr

ggsave(gg.ob.sids.yr,file="gg.obs.sids.year.pdf",width=4,height=4)
```

### Observed sids stats - zone

```{r shannon rz}
#shapiro.test(log(df.div.sid$Observed)) #good

#LK1
wilcox.test(Observed~zone,data=df.div.sid.15.lk1)
#W = 7, p-value = 0.00219 *
wilcox.test(Observed~zone,data=df.div.sid.17.lk1)
#W = 70, p-value = 0.04347 *
wilcox.test(Observed~zone,data=df.div.sid.18.lk1) #ns 

#UK1
wilcox.test(Observed~zone,data=df.div.sid.15.uk1) #ns
wilcox.test(Observed~zone,data=df.div.sid.17.uk1) #ns
wilcox.test(Observed~zone,data=df.div.sid.18.uk1) #ns

#UK2
wilcox.test(Observed~zone,data=df.div.15.uk2) #ns
wilcox.test(Observed~zone,data=df.div.17.uk2) #ns
wilcox.test(Observed~zone,data=df.div.18.uk2) #ns
```

### Observed sids stats - time 

```{r stats by year}
df.div.sid.lk1 <- subset(df.div.sid,site=="LK1")
df.div.sid.uk1 <- subset(df.div.sid,site=="UK1")
df.div.sid.uk2 <- subset(df.div.sid,site=="UK2")

df.div.sid.lk1.in <- subset(df.div.sid.lk1,zone=="Inshore")
df.div.sid.lk1.off <- subset(df.div.sid.lk1,zone=="Offshore")

df.div.sid.uk1.in <- subset(df.div.sid.uk1,zone=="Inshore")
df.div.sid.uk1.off <- subset(df.div.sid.uk1,zone=="Offshore")

df.div.sid.uk2.in <- subset(df.div.sid.uk2,zone=="Inshore")
df.div.sid.uk2.off <- subset(df.div.sid.uk2,zone=="Offshore")

pairwise.wilcox.test(df.div.sid.lk1.in$Shannon, df.div.sid.lk1.in$time, p.adjust.method = "BH")
pairwise.wilcox.test(df.div.sid.lk1.off$Shannon, df.div.sid.lk1.off$time, p.adjust.method = "BH")
#      Pre    Irma  
# Irma 0.0029 -     
# Post 0.0472 0.4470

pairwise.wilcox.test(df.div.sid.uk1.in$Shannon, df.div.sid.uk1.in$time, p.adjust.method = "BH")
pairwise.wilcox.test(df.div.sid.uk1.off$Shannon, df.div.sid.uk1.off$time, p.adjust.method = "BH")
#ns

pairwise.wilcox.test(df.div.sid.uk2.in$Shannon, df.div.sid.uk2.in$time, p.adjust.method = "BH")
pairwise.wilcox.test(df.div.sid.uk2.off$Shannon, df.div.sid.uk2.off$time, p.adjust.method = "BH")
#ns
```

## Evenness

```{r}


```




