---
title: "Florida 16S diversity analysis"
author: "Nicola G. Kriefall"
date: "12/1/21"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
---

# Setup

## Packages

```{r}
library(cowplot)
library(ggplot2)
library(phyloseq)
library("Rmisc")
library(car)

#home
#setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_16s/02.diversity")

#work
setwd("/Volumes/GoogleDrive-104519233854090018057/My Drive/Flirma/flirma_networks/fl_16s/02.diversity")
```

## Read in data

Be careful, I tried different data inputs [i.e. not rare, or rare]

```{r}
ps.clean <- readRDS("../01.generate_asv_table/ps.cleanest.less.rds")

#ps.clean <- readRDS("../01.generate_asv_table/ps.cleanest.rare6000.rds")

samdf <- data.frame(ps.clean@sam_data)
```

## Calculate metrics

[Notes from phyloseq author](https://rdrr.io/bioc/phyloseq/man/estimate_richness.html)
Visualize alpha-diversity - Should be done on raw, untrimmed dataset

```{r generate div metrics, eval=F}
df <- data.frame(estimate_richness(ps.clean, split=TRUE, measures=c("Shannon","InvSimpson","Observed")))

df$sample_num <- rownames(df)
df$sample_num <- sub("X","",df$sample_num)
rownames(df) <- df$sample_num
df.div <- merge(df,samdf,by="sample_num") #add sample data

#shannon diversity divided by species richness
df.div$even <- df.div$Shannon/(log(df.div$Observed))
#write.csv(df.div,file="fl16s.df.diversity.csv")
#write.csv(df.div,file="fl16s.df.diversity_rare.csv")

##reorder the time points
df.div$time <- factor(df.div$time, levels = c("Pre","Irma","Post"))
df.div$zone <- as.factor(df.div$zone)

#separate species
df.div.rad <- subset(df.div,spp=="srad")
df.div.sid <- subset(df.div,spp=="ssid")
```

Re-read in data, skipping the two sections above

```{r re-read in *start here*}
df.div <- read.csv("fl16s.df.diversity.csv")
#df.div <- read.csv("fl16s.df.diversity_rare.csv")

df.div$zone <- as.factor(df.div$zone)
df.div$time <- factor(df.div$time,levels=c("Pre","Irma","Post"))

#separate species
df.div.rad <- subset(df.div,spp=="srad")
df.div.sid <- subset(df.div,spp=="ssid")
```

More subsetting for stuff below

```{r more & more subsetting sids}
# within site & year
df.div.sid.15 <- subset(df.div.sid,time=="Pre")
df.div.sid.17 <- subset(df.div.sid,time=="Irma")
df.div.sid.18 <- subset(df.div.sid,time=="Post")

df.div.sid.15.lk1 <- subset(df.div.sid.15,site=="LK1")
df.div.sid.17.lk1 <- subset(df.div.sid.17,site=="LK1")
df.div.sid.18.lk1 <- subset(df.div.sid.18,site=="LK1")

df.div.sid.15.uk1 <- subset(df.div.sid.15,site=="UK1")
df.div.sid.17.uk1 <- subset(df.div.sid.17,site=="UK1")
df.div.sid.18.uk1 <- subset(df.div.sid.18,site=="UK1")

df.div.sid.15.uk2 <- subset(df.div.sid.15,site=="UK2")
df.div.sid.17.uk2 <- subset(df.div.sid.17,site=="UK2")
df.div.sid.18.uk2 <- subset(df.div.sid.18,site=="UK2")

#by time
df.div.sid.lk1 <- subset(df.div.sid,site=="LK1")
df.div.sid.uk1 <- subset(df.div.sid,site=="UK1")
df.div.sid.uk2 <- subset(df.div.sid,site=="UK2")

df.div.sid.lk1.in <- subset(df.div.sid.lk1,zone=="Inshore")
df.div.sid.lk1.off <- subset(df.div.sid.lk1,zone=="Offshore")

df.div.sid.uk1.in <- subset(df.div.sid.uk1,zone=="Inshore")
df.div.sid.uk1.off <- subset(df.div.sid.uk1,zone=="Offshore")

df.div.sid.uk2.in <- subset(df.div.sid.uk2,zone=="Inshore")
df.div.sid.uk2.off <- subset(df.div.sid.uk2,zone=="Offshore")
```

Subsetting rads

```{r more & more subsetting rads}
# within site & year
df.div.rad.15 <- subset(df.div.rad,time=="Pre")
df.div.rad.17 <- subset(df.div.rad,time=="Irma")
df.div.rad.18 <- subset(df.div.rad,time=="Post")

#LK1
df.div.rad.15.lk1 <- subset(df.div.rad.15,site=="LK1")
df.div.rad.17.lk1 <- subset(df.div.rad.17,site=="LK1")
df.div.rad.18.lk1 <- subset(df.div.rad.18,site=="LK1")

df.div.rad.15.uk1 <- subset(df.div.rad.15,site=="UK1")
df.div.rad.17.uk1 <- subset(df.div.rad.17,site=="UK1")
df.div.rad.18.uk1 <- subset(df.div.rad.18,site=="UK1")

df.div.rad.15.uk2 <- subset(df.div.rad.15,site=="UK2")
df.div.rad.17.uk2 <- subset(df.div.rad.17,site=="UK2")
df.div.rad.18.uk2 <- subset(df.div.rad.18,site=="UK2")

#now by time
df.div.rad.lk1 <- subset(df.div.rad,site=="LK1")
df.div.rad.uk1 <- subset(df.div.rad,site=="UK1")
df.div.rad.uk2 <- subset(df.div.rad,site=="UK2")

df.div.rad.lk1.in <- subset(df.div.rad.lk1,zone=="Inshore")
df.div.rad.lk1.off <- subset(df.div.rad.lk1,zone=="Offshore")

df.div.rad.uk1.in <- subset(df.div.rad.uk1,zone=="Inshore")
df.div.rad.uk1.off <- subset(df.div.rad.uk1,zone=="Offshore")

df.div.rad.uk2.in <- subset(df.div.rad.uk2,zone=="Inshore")
df.div.rad.uk2.off <- subset(df.div.rad.uk2,zone=="Offshore")
```

# Analyzing alpha metrics

## Shannon sids {.tabset}

```{r}
gg.sh.sids.yr <- ggplot(df.div.sid,aes(x=time,y=Shannon,fill=time,color=time,shape=zone))+
  facet_grid(site~.)+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Shannon index")+
  xlab("Time point")+
  ylim(0,6.7)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. siderea")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
gg.sh.sids.yr

#ggsave(gg.sh.sids.yr,file="gg.sids.shannon.pdf",width=3.5,height=4)
```

### Shannon sids stats - zone

```{r shannon sids rz}
#LOWER KEYS 1
#are they sig different across reef zones?
wilcox.test(Shannon~zone,data=df.div.sid.15.lk1)#p < 0.001***
#still same sig level when rarefied
wilcox.test(Shannon~zone,data=df.div.sid.17.lk1)#p < 0.1 .
#not rare:
# W = 102, p-value = 0.08873
#trend lost with rarefaction
# W = 63, p-value = 0.1564
wilcox.test(Shannon~zone,data=df.div.sid.18.lk1)#ns, rare or not

#UPPER KEYS 1
wilcox.test(Shannon~zone,data=df.div.sid.15.uk1)#ns, rare or not
wilcox.test(Shannon~zone,data=df.div.sid.17.uk1)#trend when rare
#W = 102, p-value = 0.08873
wilcox.test(Shannon~zone,data=df.div.sid.18.uk1)#ns, rare or not

#UPPER KEYS 2
wilcox.test(Shannon~zone,data=df.div.sid.15.uk2)#ns, rare or not
wilcox.test(Shannon~zone,data=df.div.sid.17.uk2)#ns, rare or not
wilcox.test(Shannon~zone,data=df.div.sid.18.uk2)#ns, rare or not
```

### Shannon sids stats - time 

```{r stats sids by year}
pairwise.wilcox.test(df.div.sid.lk1.in$Shannon, df.div.sid.lk1.in$time, p.adjust.method = "BH")
#      Pre   Irma 
# Irma 0.278 -    
# Post 0.041 0.047
#RAREFIED STATS:
#      Pre   Irma 
# Irma 0.278 -    
# Post 0.047 0.047
pairwise.wilcox.test(df.div.sid.lk1.off$Shannon, df.div.sid.lk1.off$time, p.adjust.method = "BH")
#REGULAR STATS:
#      Pre    Irma  
# Irma 0.0029 -     
# Post 0.0823 0.6009
#RAREFIED STATS:
#      Pre    Irma  
# Irma 0.0029 -     
# Post 0.0823 0.5362

pairwise.wilcox.test(df.div.sid.uk1.in$Shannon, df.div.sid.uk1.in$time, p.adjust.method = "BH")
#      Pre   Irma 
# Irma 0.512 -    
# Post 0.038 0.479
#RAREFIED STATS
#      Pre   Irma 
# Irma 0.605 -    
# Post 0.038 0.479
pairwise.wilcox.test(df.div.sid.uk1.off$Shannon, df.div.sid.uk1.off$time, p.adjust.method = "BH")
#ns, rare or not

pairwise.wilcox.test(df.div.sid.uk2.in$Shannon, df.div.sid.uk2.in$time, p.adjust.method = "BH")
#ns, rare or not
pairwise.wilcox.test(df.div.sid.uk2.off$Shannon, df.div.sid.uk2.off$time, p.adjust.method = "BH")
#ns, rare or not
```

## Shannon rads{.tabset}

```{r shannon rads}
gg.sh.rads.yr <- ggplot(df.div.rad,aes(x=time,y=Shannon,fill=time,color=time,shape=zone))+
  facet_grid(site~.)+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Shannon index")+
  xlab("Time point")+
  ylim(0,7.6)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
  
gg.sh.rads.yr

#ggsave(gg.sh.rads.yr,file="gg.sha.rads.year.pdf",width=3.5,height=4)
```

### Shannon rads stats - zone

```{r shannon rads rz}
#LK1
wilcox.test(Shannon~zone,data=df.div.rad.15.lk1)#p < 0.05*
# data:  Shannon by zone
# W = 20, p-value = 0.04347
wilcox.test(Shannon~zone,data=df.div.rad.17.lk1)#ns
wilcox.test(Shannon~zone,data=df.div.rad.18.lk1)#ns

#UK1
wilcox.test(Shannon~zone,data=df.div.rad.15.uk1)#p = 0.089 .
# data:  Shannon by zone
# W = 27, p-value = 0.08921
#same trend with rare
#wilcox.test(Shannon~zone,data=df.div.rad.17.uk1)#can't do, missing data
#wilcox.test(Shannon~zone,data=df.div.rad.18.uk1)#can't do, missing data

#UK2
wilcox.test(Shannon~zone,data=df.div.rad.15.uk2)#ns
wilcox.test(Shannon~zone,data=df.div.rad.17.uk2)#p < 0.05 *
# data:  Shannon by zone
# W = 11, p-value = 0.01522
#same with rare
wilcox.test(Shannon~zone,data=df.div.rad.18.uk2)#ns
```

### Shannon rads stats - time 

```{r stats rads by year}
pairwise.wilcox.test(df.div.rad.lk1.in$Shannon, df.div.rad.lk1.in$time, p.adjust.method = "BH")
#      Pre    Irma  
# Irma 0.8421 -     
# Post 0.0028 0.0019
#same with rare
pairwise.wilcox.test(df.div.rad.lk1.off$Shannon, df.div.rad.lk1.off$time, p.adjust.method = "BH")
#      Pre     Irma   
# Irma 0.01340 -      
# Post 0.00031 0.03301
#same with rare
pairwise.wilcox.test(df.div.rad.uk1.in$Shannon, df.div.rad.uk1.in$time, p.adjust.method = "BH") #ns
#pairwise.wilcox.test(df.div.rad.uk1.off$Shannon, df.div.rad.uk1.off$time, p.adjust.method = "BH") #not available

pairwise.wilcox.test(df.div.rad.uk2.in$Shannon, df.div.rad.uk2.in$time, p.adjust.method = "BH")
#      Pre    Irma  
# Irma 0.0030 -     
# Post 0.0046 0.9682
#same with rare
pairwise.wilcox.test(df.div.rad.uk2.off$Shannon, df.div.rad.uk2.off$time, p.adjust.method = "BH")
#     Pre    Irma  
# Irma 0.2110 -     
# Post 0.0037 0.0079
#same with rare
```

## Richness sids

```{r}
gg.ob.sid.yr <- ggplot(df.div.sid,aes(x=time,y=Observed,fill=time,color=time,shape=zone))+
  facet_grid(site~.)+  
  #facet_grid(site~.,scales="free_y")+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("ASV richness")+
  xlab("Time point")+
  ylim(-100,1100)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. siderea")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
  
gg.ob.sid.yr

#ggsave(gg.ob.sid.yr,file="gg.sids.rich.pdf",width=3.5,height=4)
```

### Observed sids stats - zone

```{r sids obs rz stats}
#LOWER KEYS 1
#are they sig different across reef zones?
wilcox.test(Observed~zone,data=df.div.sid.15.lk1)#p < 0.01**
#W = 7, p-value = 0.00219
#rare: W = 7, p-value = 0.0009743
wilcox.test(Observed~zone,data=df.div.sid.17.lk1) #p < 0.05*
#W = 70, p-value = 0.04347
#rare: same
wilcox.test(Observed~zone,data=df.div.sid.18.lk1)#ns, rare or not

#UPPER KEYS 1
wilcox.test(Observed~zone,data=df.div.sid.15.uk1)#ns, rare or not
wilcox.test(Observed~zone,data=df.div.sid.17.uk1)#ns, rare or not
wilcox.test(Observed~zone,data=df.div.sid.18.uk1)#ns, rare or not

#UPPER KEYS 2
wilcox.test(Observed~zone,data=df.div.sid.15.uk2)#ns, rare or not
wilcox.test(Observed~zone,data=df.div.sid.17.uk2)#ns, rare or not
wilcox.test(Observed~zone,data=df.div.sid.18.uk2)#ns, rare or not
```

### Observed sids stats - time 

```{r sids obs time stats}
pairwise.wilcox.test(df.div.sid.lk1.in$Observed, df.div.sid.lk1.in$time, p.adjust.method = "BH")
#      Pre   Irma 
# Irma 0.037 -    
# Post 0.591 0.035
#same level with rarefaction
pairwise.wilcox.test(df.div.sid.lk1.off$Observed, df.div.sid.lk1.off$time, p.adjust.method = "BH")
#      Pre   Irma 
# Irma 0.012 -    
# Post 0.063 0.417
#same with rare

pairwise.wilcox.test(df.div.sid.uk1.in$Observed, df.div.sid.uk1.in$time, p.adjust.method = "BH") #ns, rare or not
pairwise.wilcox.test(df.div.sid.uk1.off$Observed, df.div.sid.uk1.off$time, p.adjust.method = "BH") #ns, rare or not

pairwise.wilcox.test(df.div.sid.uk2.in$Observed, df.div.sid.uk2.in$time, p.adjust.method = "BH") #ns, rare or not
pairwise.wilcox.test(df.div.sid.uk2.off$Observed, df.div.sid.uk2.off$time, p.adjust.method = "BH") #ns, rare or not
```

## Richness rads {.tabset}

```{r}
gg.ob.rad.yr <- ggplot(df.div.rad,aes(x=time,y=Observed,fill=time,color=time,shape=zone))+
  facet_grid(site~.)+  
  #facet_grid(site~.,scales="free_y")+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("ASV richness")+
  xlab("Time point")+
  ylim(-200,2200)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
  
gg.ob.rad.yr

#ggsave(gg.ob.rad.yr,file="gg.rads.rich.pdf",width=3.5,height=4)
```

### Observed rads stats - zone

```{r rads obs rz stats}
#LOWER KEYS 1
#are they sig different across reef zones?
wilcox.test(Observed~zone,data=df.div.rad.15.lk1) #p < 0.05*
#W = 14, p-value = 0.01013
#sig rare
wilcox.test(Observed~zone,data=df.div.rad.17.lk1) 
#ns rare or not
wilcox.test(Observed~zone,data=df.div.rad.18.lk1)
#ns rare or not

#UPPER KEYS 1
wilcox.test(Observed~zone,data=df.div.rad.15.uk1)
#ns rare
#wilcox.test(Observed~zone,data=df.div.rad.17.uk1)
#not available
#wilcox.test(Observed~zone,data=df.div.rad.18.uk1)
#not available

#UPPER KEYS 2
wilcox.test(Observed~zone,data=df.div.rad.15.uk2)
#p = 0.08 not rare
#p = 0.06 rare
wilcox.test(Observed~zone,data=df.div.rad.17.uk2) #p < 0.01**
#W = 8, p-value = 0.005512
#p = 0.01 rare
wilcox.test(Observed~zone,data=df.div.rad.18.uk2)
#ns rare or not
```

### Observed rads stats - time 

```{r rads obs time stats}
pairwise.wilcox.test(df.div.rad.lk1.in$Observed, df.div.rad.lk1.in$time, p.adjust.method = "BH")
#      Pre    Irma  
# Irma 0.6038 -     
# Post 0.0037 0.0037
#same with rare
pairwise.wilcox.test(df.div.rad.lk1.off$Observed, df.div.rad.lk1.off$time, p.adjust.method = "BH")
#      Pre     Irma   
# Irma 0.00073 -      
# Post 0.00031 0.00967
#same with rare

pairwise.wilcox.test(df.div.rad.uk1.in$Observed, df.div.rad.uk1.in$time, p.adjust.method = "BH") 
#ns
#pairwise.wilcox.test(df.div.rad.uk1.off$Observed, df.div.rad.uk1.off$time, p.adjust.method = "BH") 
#not available

pairwise.wilcox.test(df.div.rad.uk2.in$Observed, df.div.rad.uk2.in$time, p.adjust.method = "BH") 
#      Pre    Irma  
# Irma 0.0044 -     
# Post 0.0017 0.8148
#same with rare
pairwise.wilcox.test(df.div.rad.uk2.off$Observed, df.div.rad.uk2.off$time, p.adjust.method = "BH") 
#      Pre    Irma  
# Irma 0.0947 -     
# Post 0.0012 0.0050
#same with rare
```

## Evenness sids

```{r evenness plot sids}
gg.ev.sid.yr <- ggplot(df.div.sid,aes(x=time,y=even,fill=time,color=time,shape=zone))+
  facet_grid(site~zone)+  
  #facet_grid(site~.,scales="free_y")+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Bacterial community evenness")+
  xlab("Time point")+
  ylim(0,1.05)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. siderea")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none",alpha="none",shape="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
gg.ev.sid.yr  

#ggsave(gg.ev.sid.yr,file="gg.sids.even.new.pdf",width=2.5,height=4)
```

### Evenness sids stats - zone

```{r sids even rz stats}
#LOWER KEYS 1
#are they sig different across reef zones?
wilcox.test(even~zone,data=df.div.sid.15.lk1) #p < 0.001***
#W = 5, p-value = 0.0004114
wilcox.test(even~zone,data=df.div.sid.17.lk1) #ns
wilcox.test(even~zone,data=df.div.sid.18.lk1) #ns

#UPPER KEYS 1
wilcox.test(even~zone,data=df.div.sid.15.uk1)#ns, rare or not
wilcox.test(even~zone,data=df.div.sid.17.uk1)#ns, rare or not
wilcox.test(even~zone,data=df.div.sid.18.uk1)#ns, rare or not

#UPPER KEYS 2
wilcox.test(even~zone,data=df.div.sid.15.uk2)#ns, rare or not
wilcox.test(even~zone,data=df.div.sid.17.uk2)#ns, rare or not
wilcox.test(even~zone,data=df.div.sid.18.uk2)#ns, rare or not
```

### Evenness sids stats - time 

```{r sids even time stats}
pairwise.wilcox.test(df.div.sid.lk1.in$even, df.div.sid.lk1.in$time, p.adjust.method = "BH")
#      Pre   Irma 
# Irma 0.400 -    
# Post 0.041 0.063
pairwise.wilcox.test(df.div.sid.lk1.off$even, df.div.sid.lk1.off$time, p.adjust.method = "BH")
#      Pre   Irma 
# Irma 0.009 -    
# Post 0.705 0.740

pairwise.wilcox.test(df.div.sid.uk1.in$even, df.div.sid.uk1.in$time, p.adjust.method = "BH") 
#      Pre   Irma 
# Irma 0.872 -    
# Post 0.014 0.029
pairwise.wilcox.test(df.div.sid.uk1.off$even, df.div.sid.uk1.off$time, p.adjust.method = "BH") #ns

pairwise.wilcox.test(df.div.sid.uk2.in$even, df.div.sid.uk2.in$time, p.adjust.method = "BH") #ns
pairwise.wilcox.test(df.div.sid.uk2.off$even, df.div.sid.uk2.off$time, p.adjust.method = "BH") #ns
```

## Richness rads {.tabset}

```{r}
gg.ev.rad.yr <- ggplot(df.div.rad,aes(x=time,y=even,fill=time,color=time,shape=zone))+
  facet_grid(site~zone)+  
  #facet_grid(site~.,scales="free_y")+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab(" ")+
  xlab("Time point")+
  ylim(0,1.05)+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none",alpha="none",shape="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
  
gg.ev.rad.yr

ggsave(gg.ev.rad.yr,file="gg.rads.even.new.pdf",width=2.5,height=4)
```

### Evenness rads stats - zone

```{r rads eve rz stats}
#LOWER KEYS 1
wilcox.test(even~zone,data=df.div.rad.15.lk1) #ns
wilcox.test(even~zone,data=df.div.rad.17.lk1) #ns
wilcox.test(even~zone,data=df.div.rad.18.lk1) #ns

#UPPER KEYS 1
wilcox.test(even~zone,data=df.div.rad.15.uk1) #ns
#wilcox.test(even~zone,data=df.div.rad.17.uk1)
#not available
#wilcox.test(even~zone,data=df.div.rad.18.uk1)
#not available

#UPPER KEYS 2
wilcox.test(even~zone,data=df.div.rad.15.uk2) #ns
wilcox.test(even~zone,data=df.div.rad.17.uk2) #p < 0.05*
#W = 10, p-value = 0.01111
wilcox.test(even~zone,data=df.div.rad.18.uk2) #ns
```

### even rads stats - time 

```{r rads even time stats}
pairwise.wilcox.test(df.div.rad.lk1.in$even, df.div.rad.lk1.in$time, p.adjust.method = "BH")
#      Pre    Irma  
# Irma 0.4470 -     
# Post 0.0167 0.0092
pairwise.wilcox.test(df.div.rad.lk1.off$even, df.div.rad.lk1.off$time, p.adjust.method = "BH")
#      Pre     Irma   
# Irma 0.09452 -      
# Post 0.00062 0.10880

pairwise.wilcox.test(df.div.rad.uk1.in$even, df.div.rad.uk1.in$time, p.adjust.method = "BH") 
#ns
#pairwise.wilcox.test(df.div.rad.uk1.off$even, df.div.rad.uk1.off$time, p.adjust.method = "BH") 
#not available

pairwise.wilcox.test(df.div.rad.uk2.in$even, df.div.rad.uk2.in$time, p.adjust.method = "BH") 
#      Pre    Irma  
# Irma 0.0089 -     
# Post 0.0889 1.0000
pairwise.wilcox.test(df.div.rad.uk2.off$even, df.div.rad.uk2.off$time, p.adjust.method = "BH") 
#     Pre    Irma  
# Irma 0.4470 -     
# Post 0.0059 0.0079
```





