---
title: "Florida 16s community composition"
author: "Nicola G. Kriefall"
date: "12/7/2021"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
---

# Setup

```{r packages composition}
# library(rlang)
# library(dplyr)
# library(stats)
# #library(MCMC.OTU)
# #install.packages("remotes")
# #remotes::install_github("Jtrachsel/funfuns")
# library("funfuns")
```

```{r packages used composition}
library(stringr)
library(ggpubr)
library(vegan)
library(cowplot)
library(ggplot2)
library(tidyverse)
```

Read in data

```{r read in data}
setwd("~/nicfall@bu.edu - Google Drive/My Drive/Flirma/flirma_networks_master/fl_16s/03.comm_comp")

#ps.clean <- readRDS("../01.generate_asv_table/fl16s.ps.cleaner.rd3_newvars.rds")

#made these below:
ps.fam <- readRDS("ps.asvsnamed.fam.RDS")
ps.cla <- readRDS("ps.asvsnamed.cla.RDS")
ps.clean <- readRDS("ps.asvsnamed.clean.RDS")
```

Rename ASVs to be more informative

(ran once then skip)

```{r rename ASVs}
#tax <- as.data.frame(ps.rare@tax_table@.Data)
#tax <- as.data.frame(ps.rare@tax_table@.Data)
tax <- as.data.frame(ps.clean@tax_table@.Data)
#tax <- as.data.frame(ps.norm@tax_table@.Data)

tax.clean <- data.frame(row.names = row.names(tax),
                        Kingdom = str_replace(tax[,1], "D_0__",""),
                        Phylum = str_replace(tax[,2], "D_1__",""),
                        Class = str_replace(tax[,3], "D_2__",""),
                        Order = str_replace(tax[,4], "D_3__",""),
                        Family = str_replace(tax[,5], "D_4__",""),
                        Genus = str_replace(tax[,6], "D_5__",""),
                        Species = str_replace(tax[,7], "D_6__",""),
                        stringsAsFactors = FALSE)
tax.clean[is.na(tax.clean)] <- ""

for (i in 1:7){ tax.clean[,i] <- as.character(tax.clean[,i])}
####### Fill holes in the tax table
tax.clean[is.na(tax.clean)] <- ""
for (i in 1:nrow(tax.clean)){
  if (tax.clean[i,2] == ""){
    kingdom <- paste("Kingdom_", tax.clean[i,1], sep = "")
    tax.clean[i, 2:7] <- kingdom
  } else if (tax.clean[i,3] == ""){
    phylum <- paste("Phylum_", tax.clean[i,2], sep = "")
    tax.clean[i, 3:7] <- phylum
  } else if (tax.clean[i,4] == ""){
    class <- paste("Class_", tax.clean[i,3], sep = "")
    tax.clean[i, 4:7] <- class
  } else if (tax.clean[i,5] == ""){
    order <- paste("Order_", tax.clean[i,4], sep = "")
    tax.clean[i, 5:7] <- order
  } else if (tax.clean[i,6] == ""){
    family <- paste("Family_", tax.clean[i,5], sep = "")
    tax.clean[i, 6:7] <- family
  } else if (tax.clean[i,7] == ""){
    tax.clean$Species[i] <- paste("Genus",tax.clean$Genus[i], sep = "_")
  }
}

tax_table(ps.clean) <- as.matrix(tax.clean)

#ps.clean.gen <- tax_glom(ps.clean,"Genus")
#ps.otu.gen <- data.frame(ps.clean.gen@otu_table)
#sum(colSums(ps.otu.gen))

#ps.clean.gen.wayless <- prune_taxa(taxa_sums(ps.clean.gen) < 72605, ps.clean.gen) 

#family
ps.clean.fam <- tax_glom(ps.clean,"Family")
ps.clean.fam.no0 <- prune_taxa(taxa_sums(ps.clean.fam) > 0, ps.clean.fam) 

#class
ps.clean.cla <- tax_glom(ps.clean,"Class")
ps.clean.cla.no0 <- prune_taxa(taxa_sums(ps.clean.cla) > 0, ps.clean.cla) 

#ps.otu.fam <- data.frame(ps.clean.fam@otu_table)
#sum(colSums(ps.otu.gen))

#ps.clean.gen.wayless <- prune_taxa(taxa_sums(ps.clean.gen) < 72605, ps.clean.gen) 
# sum(colSums(ps.otu))
# ps.clean.less <- prune_taxa(taxa_sums(ps.clean) > 64914, ps.clean) 
```

Saving

```{r save renamed files, eval=FALSE}
# saveRDS(ps.clean.fam.no0,"ps.asvsnamed.fam.RDS")
# saveRDS(ps.clean.cla.no0,"ps.asvsnamed.cla.RDS")
# saveRDS(ps.clean,"ps.asvsnamed.clean.RDS")
```

# Pcoa {.tabset}

Subset samples

```{r}
##option to clr transform here or not
ps.clr <-  microbiome::transform(ps.clean,"clr")
ps.temp <- subset_samples(ps.clr,site!="UK3")

##other option
#ps.temp <- subset_samples(ps.clean,site!="UK3")

ps.clean.sid <- subset_samples(ps.temp,spp=="ssid")

#time
ps.clean.sid.pre <- subset_samples(ps.clean.sid,time=="Pre")
ps.clean.sid.irm <- subset_samples(ps.clean.sid,time=="Irma")
ps.clean.sid.pos <- subset_samples(ps.clean.sid,time=="Post")

#sites & time
ps.clean.sid.pre.lk1 <- subset_samples(ps.clean.sid.pre,site=="LK1")
ps.clean.sid.pre.uk1 <- subset_samples(ps.clean.sid.pre,site=="UK1")
ps.clean.sid.pre.uk2 <- subset_samples(ps.clean.sid.pre,site=="UK2")

ps.clean.sid.irm.lk1 <- subset_samples(ps.clean.sid.irm,site=="LK1")
ps.clean.sid.irm.uk1 <- subset_samples(ps.clean.sid.irm,site=="UK1")
ps.clean.sid.irm.uk2 <- subset_samples(ps.clean.sid.irm,site=="UK2")

ps.clean.sid.pos.lk1 <- subset_samples(ps.clean.sid.pos,site=="LK1")
ps.clean.sid.pos.uk1 <- subset_samples(ps.clean.sid.pos,site=="UK1")
ps.clean.sid.pos.uk2 <- subset_samples(ps.clean.sid.pos,site=="UK2")

#radians
ps.clean.rad <- subset_samples(ps.temp,spp=="srad")

#time
ps.clean.rad.pre <- subset_samples(ps.clean.rad,time=="Pre")
ps.clean.rad.irm <- subset_samples(ps.clean.rad,time=="Irma")
ps.clean.rad.pos <- subset_samples(ps.clean.rad,time=="Post")

#sites & time
ps.clean.rad.pre.lk1 <- subset_samples(ps.clean.rad.pre,site=="LK1")
ps.clean.rad.pre.uk1 <- subset_samples(ps.clean.rad.pre,site=="UK1")
ps.clean.rad.pre.uk2 <- subset_samples(ps.clean.rad.pre,site=="UK2")

ps.clean.rad.irm.lk1 <- subset_samples(ps.clean.rad.irm,site=="LK1")
ps.clean.rad.irm.uk1 <- subset_samples(ps.clean.rad.irm,site=="UK1")
ps.clean.rad.irm.uk2 <- subset_samples(ps.clean.rad.irm,site=="UK2")

ps.clean.rad.pos.lk1 <- subset_samples(ps.clean.rad.pos,site=="LK1")
#ps.clean.rad.pos.uk1 <- subset_samples(ps.clean.rad.pos,site=="UK1")
ps.clean.rad.pos.uk2 <- subset_samples(ps.clean.rad.pos,site=="UK2")
```

## CLR

### Sids

#### All data

```{r}
ord.clean.sid <- ordinate(ps.clean.sid, "PCoA", "euclidean")

gg.clean.sid <- plot_ordination(ps.clean.sid, ord.clean.sid,color="time",shape="zone",axes=c(1,2))+
  stat_ellipse()+
  theme_cowplot()
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  #ggtitle("S. siderea")+
  #facet_wrap(time~site)
gg.clean.sid
```

#### LK1

```{r}
ps.clean.sid.lk1 <- subset_samples(ps.clean.sid,site=="LK1")

ord.clean.sid.lk1 <- ordinate(ps.clean.sid.lk1, "PCoA", "euclidean")

gg.clean.sid.lk1 <- plot_ordination(ps.clean.sid.lk1, ord.clean.sid.lk1,color="time",shape="zone",axes=c(1,2))+
  stat_ellipse()+
  theme_cowplot()
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  #ggtitle("S. siderea")+
  #facet_wrap(time~site)
gg.clean.sid.lk1
```

```{r}
ord.clean.sid.pre.lk1 <- ordinate(ps.clean.sid.pre.lk1, "PCoA", "euclidean")

gg.clean.sid.pre.lk1 <- plot_ordination(ps.clean.sid.pre.lk1, ord.clean.sid.pre.lk1,color="zone",shape="zone",axes=c(1,2))+
  stat_ellipse()+
  theme_cowplot()+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  #ggtitle("S. siderea")+
  facet_wrap(time~site)
gg.clean.sid.pre.lk1

ord.clean.sid.irm.lk1 <- ordinate(ps.clean.sid.irm.lk1, "PCoA", "euclidean")

gg.clean.sid.irm.lk1 <- plot_ordination(ps.clean.sid.irm.lk1, ord.clean.sid.irm.lk1,color="zone",shape="zone",axes=c(1,2))+
  stat_ellipse()+
  theme_cowplot()+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  #ggtitle("S. siderea")+
  facet_wrap(time~site)
gg.clean.sid.irm.lk1

ord.clean.sid.pos.lk1 <- ordinate(ps.clean.sid.pos.lk1, "PCoA", "euclidean")

gg.clean.sid.pos.lk1 <- plot_ordination(ps.clean.sid.pos.lk1, ord.clean.sid.pos.lk1,color="zone",shape="zone",axes=c(1,2))+
  stat_ellipse()+
  theme_cowplot()+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  #ggtitle("S. siderea")+
  facet_wrap(time~site)
gg.clean.sid.pos.lk1

gg.sid <- ggarrange(gg.clean.sid.pre.lk1,gg.clean.sid.irm.lk1,gg.clean.sid.pos.lk1,nrow=1,common.legend=T,legend="right")
annotate_figure(gg.sid, fig.lab="S. siderea - CLR transformed",fig.lab.face = "bold")
```

### Rads

```{r}
ps.clean.rad.pre.lk1.clr <- microbiome::transform(ps.clean.rad.pre.lk1,"clr")
ord.clean.rad.pre.lk1.clr <- ordinate(ps.clean.rad.pre.lk1.clr, "PCoA", "euclidean")

gg.clean.rad.pre.lk1.clr <- plot_ordination(ps.clean.rad.pre.lk1.clr, ord.clean.rad.pre.lk1.clr,color="zone",shape="zone",axes=c(1,2))+
  stat_ellipse()+
  theme_cowplot()+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  #ggtitle("S. raderea")+
  facet_wrap(time~site)
gg.clean.rad.pre.lk1.clr

ps.clean.rad.irm.lk1.clr <- microbiome::transform(ps.clean.rad.irm.lk1,"clr")
ord.clean.rad.irm.lk1.clr <- ordinate(ps.clean.rad.irm.lk1.clr, "PCoA", "euclidean")

gg.clean.rad.irm.lk1.clr <- plot_ordination(ps.clean.rad.irm.lk1.clr, ord.clean.rad.irm.lk1.clr,color="zone",shape="zone",axes=c(1,2))+
  stat_ellipse()+
  theme_cowplot()+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  #ggtitle("S. raderea")+
  facet_wrap(time~site)
gg.clean.rad.irm.lk1.clr

ps.clean.rad.pos.lk1.clr <- microbiome::transform(ps.clean.rad.pos.lk1,"clr")
ord.clean.rad.pos.lk1.clr <- ordinate(ps.clean.rad.pos.lk1.clr, "PCoA", "euclidean")

gg.clean.rad.pos.lk1.clr <- plot_ordination(ps.clean.rad.pos.lk1.clr, ord.clean.rad.pos.lk1.clr,color="zone",shape="zone",axes=c(1,2))+
  stat_ellipse()+
  theme_cowplot()+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  #ggtitle("S. raderea")+
  facet_wrap(time~site)
gg.clean.rad.pos.lk1.clr

ggarrange(gg.clean.rad.pre.lk1.clr,gg.clean.rad.irm.lk1.clr,gg.clean.rad.pos.lk1.clr,nrow=1,common.legend=T,legend="right")+
  ggtitle("S. radians")
```

## Relative abundance

```{r}
ps.clean.rel <- transform_sample_counts(ps.clean, function(x) x / sum(x))

ord.rel <- ordinate(ps.clean.rel, "NMDS", "bray")

gg.clean.rel <- plot_ordination(ps.clean.rel, ord.rel,color="time",shape="time",axes=c(1,2))+
  stat_ellipse()+
  theme_cowplot()+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  ggtitle("Relative abundance")+
  facet_wrap(~spp)
gg.clean.rel

p3 = plot_ordination(ps.clean.rel, ord.rel, type="biplot", color="Phylum", shape="year", title="biplot")
p3

```

# Core vs. accessory

## Core

```{r packages core, echo=FALSE}
#BiocManager::install("microbiome")
#remotes::install_github("r-lib/rlang")
library(microbiome)
```

```{r core}
pseq.core <- core(ps.norm, detection = 0, prevalence = .5)
pseq.core #3 taxa

#saving
#core.tax <- data.frame(pseq.core@tax_table)
#write.csv(core.tax,"core.taxa.csv")

ps_glom <- tax_glom(pseq.core, "Genus")
#ps0 <- transform_sample_counts(ps_glom, function(x) x / sum(x))
ps1 <- merge_samples(ps_glom, "site_zone")
#ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))

plot_bar(ps1, fill="Genus")+
  geom_bar(stat="identity")+
  theme_cowplot()+
  scale_fill_brewer(palette="BrBG")+
  facet_wrap(~year)
#ggsave(file="core.bar.pdf",width=8)

#plot_ordination(pseq.core,ordination="")
plot_ordination(pseq.core,ordinate(pseq.core,"PCoA", "bray"),color="site", shape="site")+
  stat_ellipse()+
  theme_cowplot()+
  scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")

#by site
ps.core.mnw <- subset_samples(pseq.core,site=="MNW")
ps.core.mse <- subset_samples(pseq.core,site=="MSE")
ps.core.tnw <- subset_samples(pseq.core,site=="TNW")

plot_ordination(ps.core.mnw,ordinate(ps.core.mnw,"PCoA", "bray"),color="zone", shape="zone")+
  stat_ellipse()+
  theme_cowplot()#+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")
```

```{r calculate core abundance}
# calculating core abundances #
core.sqs <- tax_table(pseq.core)
core.sqs.ids <- row.names(core.sqs)
core.sqs.ids

ps.rare.trim.rel <- transform_sample_counts(ps.rare.trim, function(x) x / sum(x))
seq.rare.rel <- data.frame(otu_table(ps.rare.trim.rel))
tax.core <- tax_table(ps.rare.trim.rel)

seq.core <- seq.rare.rel %>% select(c(core.sqs.ids))
core.rel <- data.frame(colMeans(seq.core))

total.rel <- data.frame(colMeans(seq.rare.rel))
total.rel.ordered <- data.frame(total.rel[order(-total.rel$colMeans.seq.rare.rel.),,drop=FALSE])
```

Core stats

```{r core stats}
seq.core <- data.frame(otu_table(pseq.core))

dist.core <- vegdist(seq.core)
samdf.core <- data.frame(sample_data(pseq.core))
row.names(samdf.core)==row.names(seq.core)

bet.all <- betadisper(dist.core,samdf.core$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

bet.all <- betadisper(dist.core,samdf.core$site)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

adonis(seq.core ~ site, data=samdf.core, permutations=999)
adonis(seq.core ~ site/zone, data=samdf.core, permutations=999)
adonis(seq.core ~ zone, strata=samdf.core$site,data=samdf.core, permutations=999)

pairwise.adonis(seq.core, factors = samdf.core$site, permutations = 999)
#MNW only marginally different than TNW surprisingly

#### by site - MNW ####
seq.core.mnw <- data.frame(otu_table(ps.core.mnw))

dist.core.mnw <- vegdist(seq.core.mnw)
samdf.core.mnw <- data.frame(sample_data(ps.core.mnw))
row.names(samdf.core.mnw)==row.names(seq.core.mnw)

bet.all <- betadisper(dist.core.mnw,samdf.core.mnw$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

adonis(seq.core.mnw ~ zone,data=samdf.core.mnw, permutations=999)
#not sig
```

## Accessory

```{r accessory, eval=FALSE}
ps.rare.trim.otu <- data.frame(ps.rare.trim@otu_table)
core.tax <- data.frame(pseq.core@tax_table)
core.ids <- c(rownames(core.tax))
ps.rare.trim.acc.otu <- ps.rare.trim.otu[,!colnames(ps.rare.trim.otu) %in% core.ids ]
row.names(samdf) <- samdf$id

#remake phyloseq object
ps.acc <- phyloseq(otu_table(ps.rare.trim.acc.otu, taxa_are_rows=FALSE), 
                         sample_data(samdf), 
                         tax_table(taxa2))
ps.acc #214 taxa accessory

plot_ordination(ps.acc,ordinate(ps.acc,"PCoA", "bray"),color="site", shape="site")+
  stat_ellipse()+
  theme_cowplot()+
  scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")
#ggsave(file="pcoa.acc.all.pdf")

#by site
ps.acc.mnw <- subset_samples(ps.acc,site=="MNW")
ps.acc.mse <- subset_samples(ps.acc,site=="MSE")
ps.acc.tnw <- subset_samples(ps.acc,site=="TNW")

gg.pcoa.acc.mnw <- plot_ordination(ps.acc.mnw,ordinate(ps.acc.mnw,"PCoA", "bray"),color="zone", shape="zone")+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))

gg.pcoa.acc.mse <- plot_ordination(ps.acc.mse,ordinate(ps.acc.mse,"PCoA", "bray"),color="zone", shape="zone")+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))

gg.pcoa.acc.tnw <- plot_ordination(ps.acc.tnw,ordinate(ps.acc.tnw,"PCoA", "bray"),color="zone", shape="zone")+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))

ggarrange(gg.pcoa.acc.mnw,gg.pcoa.acc.mse,gg.pcoa.acc.tnw,nrow=1,common.legend=T,legend="right")
#ggsave("pcoa.acc.zone.pdf",width=11,height=3)

#### by site - MNW ####
seq.acc.mnw <- data.frame(otu_table(ps.acc.mnw))

dist.acc.mnw <- vegdist(seq.acc.mnw)
samdf.acc.mnw <- data.frame(sample_data(ps.acc.mnw))
row.names(samdf.acc.mnw)==row.names(seq.acc.mnw)

bet.all <- betadisper(dist.acc.mnw,samdf.acc.mnw$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

adonis(seq.acc.mnw ~ zone,data=samdf.acc.mnw, permutations=999)
# Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)   
# zone       1    0.7993 0.79929  2.1125 0.07514  0.002 **
# Residuals 26    9.8374 0.37836         0.92486          
# Total     27   10.6367                 1.00000          
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

#### by site - MSE ####
seq.acc.mse <- data.frame(otu_table(ps.acc.mse))

dist.acc.mse <- vegdist(seq.acc.mse)
samdf.acc.mse <- data.frame(sample_data(ps.acc.mse))
row.names(samdf.acc.mse)==row.names(seq.acc.mse)

bet.all <- betadisper(dist.acc.mse,samdf.acc.mse$zone)
anova(bet.all)
plot(bet.all) 
# Df   Sum Sq   Mean Sq F value  Pr(>F)  
# Groups     1 0.021763 0.0217633  4.5724 0.04169 *
# Residuals 27 0.128513 0.0047597                  
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

adonis(seq.acc.mse ~ zone,data=samdf.acc.mse, permutations=999)
# Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)   
# zone       1    0.8113 0.81126  2.2489 0.07689  0.004 **
# Residuals 27    9.7400 0.36074         0.92311          
# Total     28   10.5513                 1.00000 

#### by site - TNW ####
seq.acc.tnw <- data.frame(otu_table(ps.acc.tnw))

dist.acc.tnw <- vegdist(seq.acc.tnw)
samdf.acc.tnw <- data.frame(sample_data(ps.acc.tnw))
row.names(samdf.acc.tnw)==row.names(seq.acc.tnw)

bet.all <- betadisper(dist.acc.tnw,samdf.acc.tnw$zone)
anova(bet.all)
plot(bet.all) #ns                

adonis(seq.acc.tnw ~ zone,data=samdf.acc.tnw, permutations=999)
#  Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)   
# zone       1    0.8429 0.84287  2.2735 0.08336  0.002 **
# Residuals 25    9.2685 0.37074         0.91664          
# Total     26   10.1113                 1.00000          
```

# Bar plots [needs fixing] {.tabset}

## All, by Phylum

```{r bar plot phylum}
ps.clean.rel <- transform_sample_counts(ps.clean, function(x) x / sum(x))

ps.all.tab <- psmelt(ps.clean.rel)%>%
  filter(!is.na(Abundance))%>%
  group_by(year,site,zone,Phylum,OTU)%>%
  summarize_at("Abundance",mean)

ps.all.tab$year <- factor(ps.all.tab$year,levels=c("Pre","Irma","Post"))
#ps.all.tab.more <- subset(ps.all.tab,Abundance>0.01)

#toggling .more in or not
gg.bar.all.phy <- ggplot(ps.all.tab,aes(x=year,y=Abundance,fill=Phylum))+
  geom_bar(stat="identity")+
  theme_cowplot()+
  #theme(legend.position="none")+
  xlab('Reef zone')+  
  facet_grid(zone~site)

gg.bar.all.phy
ggsave(gg.bar.all.phy,file="bac.bar.all.phy.pdf",width=10,height=5.5)
```

## All, by family

```{r bar plot family}
ps.clean.rel <- transform_sample_counts(ps.clean, function(x) x / sum(x))

ps.all.tab <- psmelt(ps.clean.rel)%>%
  filter(!is.na(Abundance))%>%
  group_by(year,site,zone,Family,OTU)%>%
  summarize_at("Abundance",mean)

ps.all.tab.more <- subset(ps.all.tab,Abundance>0.01)
ps.all.tab.more$year <- factor(ps.all.tab.more$year,levels=c("Pre","Irma","Post"))

gg.bar.all.fam <- ggplot(ps.all.tab.more,aes(x=year,y=Abundance,fill=Family))+
  geom_bar(stat="identity")+
  theme_cowplot()+
  #theme(legend.position="none")+
  xlab('Reef zone')+  
  facet_grid(zone~site)

gg.bar.all.fam
ggsave(gg.bar.all.fam,file="bac.bar.all.fam.pdf",width=10,height=5.5)
```

## All, by class

```{r bar plot class}
ps.clean.rel <- transform_sample_counts(ps.clean, function(x) x / sum(x))

ps.all.tab <- psmelt(ps.clean.rel)%>%
  filter(!is.na(Abundance))%>%
  group_by(year,site,zone,Class,OTU)%>%
  summarize_at("Abundance",mean)

ps.all.tab$year <- factor(ps.all.tab$year,levels=c("Pre","Irma","Post"))
ps.all.tab.more <- subset(ps.all.tab,Abundance>0.01)

#toggling .more in or not
gg.bar.all.cla <- ggplot(ps.all.tab.more,aes(x=year,y=Abundance,fill=Class))+
  geom_bar(stat="identity")+
  theme_cowplot()+
  #theme(legend.position="none")+
  xlab('Reef zone')+  
  facet_grid(zone~site)

gg.bar.all.cla
ggsave(gg.bar.all.cla,file="bac.bar.all.cla.pdf",width=10,height=5.5)
```

```{r bar plot fam}
ps.clean.fam.rel <- transform_sample_counts(ps.clean.fam, function(x) x / sum(x))

ps.all.tab <- psmelt(ps.clean.fam.rel)%>%
  filter(!is.na(Abundance))%>%
  group_by(year,site,zone,Family)%>%
  summarize_at("Abundance",mean)

ps.all.tab.more <- subset(ps.all.tab,Abundance>0.01)
ps.all.tab.more$year <- factor(ps.all.tab.more$year,levels=c("Pre","Irma","Post"))

gg.bar.all.fam <- ggplot(ps.all.tab.more,aes(x=year,y=Abundance,fill=Family))+
  geom_bar(stat="identity")+
  theme_cowplot()+
  #theme(legend.position="none")+
  xlab('Reef zone')+  
  facet_grid(zone~site)

gg.bar.all.fam 
#ggsave(gg.bar.all,file="bac.bar.all.pdf",height=4)
```

# PCOA plots

## Plots - year {.tabset}

```{r rel abun}
#ps.clean.rel <- transform_sample_counts(ps.clean, function(x) x / sum(x))

ps.clean.rel <- transform_sample_counts(ps.clean.lk1.fam.no0, function(x) x / sum(x))
ord.rel <- ordinate(ps.clean.rel, "PCoA", "bray")
gg.clean.rel <- plot_ordination(ps.clean.rel, ord.rel,color="year",shape="year",axes=c(1,3))+
  #stat_ellipse()+
  theme_cowplot()+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  ggtitle("Relative abundance")+
  facet_wrap(~spp)
gg.clean.rel

p3 = plot_ordination(ps.clean.rel, ord.rel, type="biplot", color="Phylum", shape="year", title="biplot")
p3
```

```{r rel abun genus > 1%}
ps.clean.rel <- transform_sample_counts(ps.clean.gen.wayless, function(x) x / sum(x))
ord.rel <- ordinate(ps.clean.rel, "PCoA", "jaccard")
gg.clean.rel <- plot_ordination(ps.clean.rel, ord.rel,color="year", shape="year")+
  stat_ellipse()+
  theme_cowplot()+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  xlab("Axis 1 (44.1%)")+
  ylab("Axis 2 (23%)")+
  ggtitle("Relative abundance")+
  facet_wrap(~site)
gg.clean.rel

p3 = plot_ordination(ps.clean.rel, ord.rel, type="biplot", color="Phylum", shape="year", title="biplot")
p3
```

```{r rel abun fam}

ps.clean.rel <- transform_sample_counts(ps.clean, function(x) x / sum(x))
ord.rel <- ordinate(ps.clean.rel, "PCoA", "bray")
gg.clean.rel <- plot_ordination(ps.clean.rel, ord.rel,color="year", shape="year",axes=2:3)+
  stat_ellipse()+
  theme_cowplot()+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  ggtitle("Relative abundance")+
  facet_grid(zone~site)+
  scale_color_manual(values=c("#F8850F","#AE305C","#781C6D"))
gg.clean.rel

ggsave(gg.clean.rel,file="pca.all.2:3.pdf")

p3 = plot_ordination(ps.clean.rel, ord.rel, type="biplot", color="Phylum", shape="year", title="biplot")
p3
```

### Rarefied

```{r site rare}
library(ggplot2)



ord.rare <- ordinate(ps.rare, "PCoA", "bray")
gg.rare <- plot_ordination(ps.rare, ord.rare,color="year", shape="year",axes=2:3)+
  stat_ellipse()+
  facet_wrap(~site)
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")
gg.rare

ps.norm.gen <- tax_glom(ps.norm,"Genus")
ord.norm.gen <- ordinate(ps.norm.gen, "PCoA", "bray")

gg.norm.gen <- plot_ordination(ps.norm.gen, ord.norm.gen,color="year", shape="year")+
  stat_ellipse()+
  theme_cowplot()
gg.norm.gen

ps.norm.fam <- tax_glom(ps.norm,"Family")
ord.norm.fam <- ordinate(ps.norm.fam, "PCoA", "bray")

gg.norm.gen <- plot_ordination(ps.norm.gen, ord.norm.gen,color="year", shape="year")+
  stat_ellipse()+
  theme_cowplot()
gg.norm.gen
```

```{r site rarefied}
ord <- ordinate(ps.norm, "PCoA", "bray")
gg.norm <- plot_ordination(ps.norm, ord,color="year", shape="year",axes=2:3)+
  stat_ellipse()+
  theme_cowplot()
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")
gg.norm

ps.norm.gen <- tax_glom(ps.norm,"Genus")
ord.norm.gen <- ordinate(ps.norm.gen, "PCoA", "bray")

gg.norm.gen <- plot_ordination(ps.norm.gen, ord.norm.gen,color="year", shape="year")+
  stat_ellipse()+
  theme_cowplot()
gg.norm.gen

ps.norm.fam <- tax_glom(ps.norm,"Family")
ord.norm.fam <- ordinate(ps.norm.fam, "PCoA", "bray")

p3 = plot_ordination(ps.norm.fam, ord.norm.fam, type="biplot", color="Family", shape="year", title="biplot")
p3

gg.norm.gen <- plot_ordination(ps.norm.fam, ord.norm.fam,color="year", shape="year",axes=2:3)+
  stat_ellipse()#+
  theme_cowplot()
gg.norm.gen
```

Network

```{r NETWORK}
set.seed(711L)

ps.clean.lk1 <- subset_samples(ps.clean,site=="LK1")
ps.clean.lk1.pre <- subset_samples(ps.clean.lk1,year=="Pre")
ps.clean.lk1.irm <- subset_samples(ps.clean.lk1,year=="Irma")
ps.clean.lk1.pos <- subset_samples(ps.clean.lk1,year=="Post")

plot_net(ps.clean.lk1.pre,color="zone",shape="zone")
plot_net(ps.clean.lk1.irm,color="zone",shape="zone")
plot_net(ps.clean.lk1.pos,color="zone",shape="zone")

###sum by fam

ps.clean.fam <- tax_glom(ps.clean,"Family")

ps.clean.pre <- subset_samples(ps.clean.fam,year=="Pre")
ps.clean.pre.no0 <- prune_taxa(taxa_sums(ps.clean.pre)>0,ps.clean.pre)
ps.clean.pre.set <- make_network(ps.clean.pre.no0,type="taxa",max.dist=0.5)
plot_network(ps.clean.pre.set,ps.clean.pre)

#most simple
plot_net(ps.clean,color="year",shape="site")

ps.clean.pre <- subset_samples(ps.clean.fam,year=="Pre")
plot_net(ps.clean.pre,color="zone",shape="zone")

ps.clean.irm <- subset_samples(ps.clean,year=="Irma")
plot_net(ps.clean.irm,color="zone",shape="zone")

ps.clean.pos <- subset_samples(ps.clean,year=="Post")
plot_net(ps.clean.pos,color="zone",shape="zone")

#fam networks by site
ps.clean.fam.pre <- subset_samples(ps.clean.fam,year=="Pre")
ps.clean.fam.pre.lk1 <- subset_samples(ps.clean.fam.pre,site=="LK1")
ps.clean.fam.pre.lk1 <- prune_taxa(taxa_sums(ps.clean.fam.pre.lk1)>0,ps.clean.fam.pre.lk1)

ps.clean.fam.irm <- subset_samples(ps.clean.fam,year=="Irma")
ps.clean.fam.irm.lk1 <- subset_samples(ps.clean.fam.irm,site=="LK1")
ps.clean.fam.irm.lk1 <- prune_taxa(taxa_sums(ps.clean.fam.irm.lk1)>0,ps.clean.fam.irm.lk1)

ps.clean.fam.pos <- subset_samples(ps.clean.fam,year=="Post")
ps.clean.fam.pos.lk1 <- subset_samples(ps.clean.fam.pos,site=="LK1")
ps.clean.fam.pos.lk1 <- prune_taxa(taxa_sums(ps.clean.fam.pos.lk1)>0,ps.clean.fam.pos.lk1)

net.pre.lk1 <- plot_net(ps.clean.fam.pre.lk1,color="zone",shape="zone")+
  ggtitle("A. Pre")
net.pre.lk1
net.irm.lk1 <- plot_net(ps.clean.fam.irm.lk1,color="zone",shape="zone")+
  ggtitle("B. Irma")
net.pos.lk1 <- plot_net(ps.clean.fam.pos.lk1,color="zone",shape="zone")+
  ggtitle("C. Post")

ggarrange(net.pre.lk1,net.irm.lk1,net.pos.lk1,common.legend=TRUE,nrow=1,legend.position="right")
ggsave("gg.nets.new.fam.pdf",width=10)

net.pre.lk1 <- plot_net(ps.clean.fam.pre.lk1,color="zone",shape="zone")+
  ggtitle("A. Pre")
net.pre.lk1
net.irm.lk1 <- plot_net(ps.clean.fam.irm.lk1,color="zone",shape="zone")+
  ggtitle("B. Irma")
net.pos.lk1 <- plot_net(ps.clean.fam.pos.lk1,color="zone",shape="zone")+
  ggtitle("C. Post")

ggarrange(net.pre.lk1,net.irm.lk1,net.pos.lk1,common.legend=TRUE,nrow=1,legend.position="right")
ggsave("gg.nets.new.fam.pdf",width=10)

net.pre.lk1 <- plot_net(ps.clean.fam.pre.lk1,type="taxa",color="Phylum")+
  ggtitle("A. Pre")
net.pre.lk1
net.irm.lk1 <- plot_net(ps.clean.fam.irm.lk1,type="taxa",color="Phylum")+
  ggtitle("B. Irma")
net.pos.lk1 <- plot_net(ps.clean.fam.pos.lk1,type="taxa",color="Phylum")+
  ggtitle("C. Post")

ggarrange(net.pre.lk1,net.irm.lk1,net.pos.lk1,nrow=1)

ps.clean.fam.pre.lk1.in <- subset_samples(ps.clean.fam.pre.lk1,zone=="Inshore")
ps.clean.fam.pre.lk1.off <- subset_samples(ps.clean.fam.pre.lk1,zone=="Offshore")

ps.clean.fam.irm.lk1.in <- subset_samples(ps.clean.fam.irm.lk1,zone=="Inshore")
ps.clean.fam.irm.lk1.off <- subset_samples(ps.clean.fam.irm.lk1,zone=="Offshore")

ps.clean.fam.pos.lk1.in <- subset_samples(ps.clean.fam.pos.lk1,zone=="Inshore")
ps.clean.fam.pos.lk1.off <- subset_samples(ps.clean.fam.pos.lk1,zone=="Offshore")

# ps.clean.fam.pre.lk1.in.set <- make_network(ps.clean.fam.pre.lk1.in,type="taxa",max.dist=0.5)
# plot_network(ps.clean.fam.pre.lk1.in.set,ps.clean.fam.pre.lk1.in,point_label="Family")

net.pre.lk1.in <- plot_net(ps.clean.fam.pre.lk1.in,type="taxa",color="Phylum")+
  ggtitle("A. Pre - Inshore")
net.pre.lk1.in
net.pre.lk1.off <- plot_net(ps.clean.fam.pre.lk1.off,type="taxa",color="Phylum")+
  ggtitle("A. Pre - Offshore")
net.pre.lk1.off

net.irm.lk1.in <- plot_net(ps.clean.fam.irm.lk1.in,type="taxa",color="Phylum")+
  ggtitle("A. Irma - Inshore")
net.irm.lk1.in
net.irm.lk1.off <- plot_net(ps.clean.fam.irm.lk1.off,type="taxa",color="Phylum")+
  ggtitle("A. Irma - Offshore")
net.irm.lk1.off

net.pos.lk1.in <- plot_net(ps.clean.fam.pos.lk1.in,type="taxa",color="Phylum")+
  ggtitle("A. Post - Inshore")
net.pos.lk1.in
net.pos.lk1.off <- plot_net(ps.clean.fam.pos.lk1.off,type="taxa",color="Phylum")+
  ggtitle("A. Post - Offshore")
net.pos.lk1.off

ggarrange(net.pre.lk1.in,net.pre.lk1.off,net.irm.lk1.in,net.irm.lk1.off,net.pos.lk1.in,net.pos.lk1.off,nrow=2,ncol=3,common.legend=FALSE)

net.irm.lk1 <- plot_net(ps.clean.fam.irm.lk1,color="zone",shape="zone")+
  ggtitle("B. Irma")
net.pos.lk1 <- plot_net(ps.clean.fam.pos.lk1,color="zone",shape="zone")+
  ggtitle("C. Post")
```

Stats

Help on adonis (here)[https://thebiobucket.blogspot.com/2011/04/assumptions-for-permanova-with-adonis.html#more]

```{r stats site rare}
seq.rare <- data.frame(otu_table(ps.rare.trim))

dist.rare <- vegdist(seq.rare)
samdf.rare <- data.frame(sample_data(ps.rare.trim))
row.names(samdf.rare)==row.names(seq.rare)

bet.all <- betadisper(dist.rare,samdf.rare$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

bet.all <- betadisper(dist.rare,samdf.rare$site)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

adonis(seq.rare ~ site, data=samdf.rare, permutations=999)
adonis(seq.rare ~ site/zone, data=samdf.rare, permutations=999)
adonis(seq.rare ~ zone, strata=samdf.rare$site,data=samdf.rare, permutations=999)

pairwise.adonis(seq.rare, factors = samdf.rare$site, permutations = 999)
#all significantly different
```

### Relative abundance

```{r sites rel abun}
ps.trim.rel <- transform_sample_counts(ps.trim, function(x) x / sum(x))
ord.rel <- ordinate(ps.trim.rel, "PCoA", "bray")
gg.pcoa.site <- plot_ordination(ps.trim.rel, ord.rel,color="site", shape="site")+
  stat_ellipse()+
  theme_cowplot()+
  scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  scale_shape_manual(name="Site",values=c(8,4,9))+
  xlab("Axis 1 (44.1%)")+
  ylab("Axis 2 (23%)")+
  ggtitle("Relative abundance")
gg.pcoa.site
```

Stats

```{r stats site rel}
seq.trim <- data.frame(otu_table(ps.trim.rel))

dist.trim <- vegdist(seq.trim)
samdf.trim <- data.frame(sample_data(ps.trim))
row.names(samdf.trim)==row.names(seq.trim)

bet.all <- betadisper(dist.trim,samdf.trim$zone)
anova(bet.all)
#permutest(bet.all, pairwise = FALSE, permutations = 999)
plot(bet.all) #very much overlap, not sig

bet.all <- betadisper(dist.trim,samdf.trim$site)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

adonis(seq.trim ~ site, data=samdf.trim, permutations=999)
adonis(seq.trim ~ site/zone, data=samdf.trim, permutations=999)
adonis(seq.trim ~ zone, strata=samdf.trim$site,data=samdf.trim, permutations=999)

pairwise.adonis(seq.trim, factors = samdf.trim$site, permutations = 999)
#all significantly different
```

### Plot - both

They look super similar

```{r ggarrange pcoas}
ggarrange(gg.pcoa.site.rare,gg.pcoa.site,labels="AUTO",common.legend=TRUE,legend="right")
```

## Plots - reef zones{.tabset} 

```{r subset data}
ps.mnw.rel <- subset_samples(ps.trim.rel,site=="MNW")
ps.mnw <- subset_samples(ps.rare.trim,site=="MNW")

ps.mse.rel <- subset_samples(ps.trim.rel,site=="MSE")
ps.mse <- subset_samples(ps.rare.trim,site=="MSE")

ps.tnw.rel <- subset_samples(ps.trim.rel,site=="TNW")
ps.tnw <- subset_samples(ps.rare.trim,site=="TNW")
```

### Mo'orea NW

Relative abundance - appears total overlap

```{r mnw rel}
ord.mnw.rel <- ordinate(ps.mnw.rel, "PCoA", "bray")
gg.mnw.rel <- plot_ordination(ps.mnw.rel, ord.mnw.rel,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Mo'orea NW")+
  xlab("Axis 1 (38.8%)")+
  ylab("Axis 2 (29.8%)")+
  theme(axis.text=element_text(size=10))
gg.mnw.rel
```

Stats

```{r stats mnw rel}
seq.mnw.rel <- data.frame(otu_table(ps.mnw.rel))
samdf.mnw.rel <- data.frame(sample_data(ps.mnw.rel))
row.names(samdf.mnw.rel)==row.names(seq.mnw.rel)

dist.mnw.rel <- vegdist(seq.mnw.rel)
bet.mnw.rel <- betadisper(dist.mnw.rel,samdf.mnw.rel$zone,bias.adjust = TRUE,type="median")
anova(bet.mnw.rel) #not sig
#permutest(bet.mnw.rel, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.mnw.rel)

adonis(seq.mnw.rel ~ zone, data=samdf.mnw.rel, permutations=999) #not sig
```

Rarefied

Slightly less overlap - but maybe still non-significant? 

```{r mnw rare}
ord.mnw <- ordinate(ps.mnw, "PCoA", "bray")
gg.mnw <- plot_ordination(ps.mnw, ord.mnw,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Mo'orea NW")+
  xlab("Axis 1 (38.9%)")+
  ylab("Axis 2 (30.4%)")+
  theme(axis.text=element_text(size=10))
gg.mnw
```

Stats

```{r stats mnw rare}
seq.mnw.rare <- data.frame(otu_table(ps.mnw))
samdf.mnw.rare <- data.frame(sample_data(ps.mnw))
row.names(samdf.mnw.rare)==row.names(seq.mnw.rare)

dist.mnw.rare <- vegdist(seq.mnw.rare)
bet.mnw.rare <- betadisper(dist.mnw.rare,samdf.mnw.rare$zone,bias.adjust = TRUE,type="median")
anova(bet.mnw.rare) #not sig
#permutest(bet.mnw.rare, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.mnw.rare)

adonis(seq.mnw.rare ~ zone, data=samdf.mnw.rare, permutations=999) #not sig
```

### Mo'orea SE

Relative abundance - appears to separate more than MNW

```{r mse rel}
ord.mse.rel <- ordinate(ps.mse.rel, "PCoA", "bray")
gg.mse.rel <- plot_ordination(ps.mse.rel, ord.mse.rel,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Mo'orea SE")+
  xlab("Axis 1 (39.6%)")+
  ylab("Axis 2 (27.2%)")+
  theme(axis.text=element_text(size=10))
gg.mse.rel
```

Stats

```{r stats mse rel}
seq.mse.rel <- data.frame(otu_table(ps.mse.rel))
samdf.mse.rel <- data.frame(sample_data(ps.mse.rel))
row.names(samdf.mse.rel)==row.names(seq.mse.rel)

dist.mse.rel <- vegdist(seq.mse.rel)
bet.mse.rel <- betadisper(dist.mse.rel,samdf.mse.rel$zone,bias.adjust = TRUE,type="median")
anova(bet.mse.rel) #not sig
#permutest(bet.mse.rel, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.mse.rel)

adonis(seq.mse.rel ~ zone, data=samdf.mse.rel, permutations=999) #p < 0.01**
```

Rarefied

Equivalent

```{r mse rare}
ord.mse <- ordinate(ps.mse, "PCoA", "bray")
gg.mse <- plot_ordination(ps.mse, ord.mse,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Mo'orea SE")+
  xlab("Axis 1 (38.1%)")+
  ylab("Axis 2 (27.8%)")+
  theme(axis.text=element_text(size=10))
gg.mse
```

Stats

Same story

```{r stats mse rare}
seq.mse.rare <- data.frame(otu_table(ps.mse))
samdf.mse.rare <- data.frame(sample_data(ps.mse))
row.names(samdf.mse.rare)==row.names(seq.mse.rare)

dist.mse.rare <- vegdist(seq.mse.rare)
bet.mse.rare <- betadisper(dist.mse.rare,samdf.mse.rare$zone,bias.adjust = TRUE,type="median")
anova(bet.mse.rare) #not sig
#permutest(bet.mse.rare, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.mse.rare)

adonis(seq.mse.rare ~ zone, data=samdf.mse.rare, permutations=999) #p < 0.01**
```

### Tahiti NW

Relative abundance - looks very silly

```{r tnw rel}
ord.tnw.rel <- ordinate(ps.tnw.rel, "PCoA", "bray")
gg.tnw.rel <- plot_ordination(ps.tnw.rel, ord.tnw.rel,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Tahiti NW")+
  #xlab("Axis 1 (60.2%)")+
  #ylab("Axis 2 (9.7%)")+
  theme(axis.text=element_text(size=10))
gg.tnw.rel
```

Stats

```{r stats tnw rel}
seq.tnw.rel <- data.frame(otu_table(ps.tnw.rel))
samdf.tnw.rel <- data.frame(sample_data(ps.tnw.rel))
row.names(samdf.tnw.rel)==row.names(seq.tnw.rel)

dist.tnw.rel <- vegdist(seq.tnw.rel)
bet.tnw.rel <- betadisper(dist.tnw.rel,samdf.tnw.rel$zone,bias.adjust = TRUE,type="median")
anova(bet.tnw.rel) #p < 0.05*
#permutest(bet.tnw.rel, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.tnw.rel)

adonis(seq.tnw.rel ~ zone, data=samdf.tnw.rel, permutations=999) #p < 0.01**
```

Rarefied

Equivalent

```{r tnw rare}
ord.tnw <- ordinate(ps.tnw, "PCoA", "bray")
gg.tnw <- plot_ordination(ps.tnw, ord.tnw,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Tahiti NW")+
  xlab("Axis 1 (59.4%)")+
  ylab("Axis 2 (10.8%)")+
  theme(axis.text=element_text(size=10))
gg.tnw
```

Stats

```{r stats tnw rare}
seq.tnw.rare <- data.frame(otu_table(ps.tnw))
samdf.tnw.rare <- data.frame(sample_data(ps.tnw))
row.names(samdf.tnw.rare)==row.names(seq.tnw.rare)

dist.tnw.rare <- vegdist(seq.tnw.rare)
bet.tnw.rare <- betadisper(dist.tnw.rare,samdf.tnw.rare$zone,bias.adjust = TRUE,type="median")
anova(bet.tnw.rare) #p < 0.01**
permutest(bet.tnw.rare, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.tnw.rare)

adonis(seq.tnw.rare ~ zone, data=samdf.tnw.rare, permutations=999) #p < 0.01**
```

## Summary

- No differences in results between relative abundance & rarefied plots/stats
- Pairwise adonis significant between all three sites
- Adonis significant across reef zones at TNW & MSE, but not MNW
- Beta dispersion not significantly different except between TNW F & B (can definitely see it)

Relative abundance

```{r panels rel}
ggarrange(gg.mnw.rel,gg.mse.rel,gg.tnw.rel,nrow=1,common.legend=TRUE,legend="right",labels="AUTO")
```

Rarefied

```{r panels rare}
ggarrange(gg.mnw,gg.mse,gg.tnw,nrow=1,common.legend=TRUE,legend="right",labels=c("(a)","(b)","(c)"))
#ggsave("16s.pcoa.pdf",height=2.5,width=8)
```

# ANCOM

Tutorial [here](https://github.com/FrederickHuangLin/ANCOM)

## Setup

```{r ancom packages}
library(readr)
library(tidyverse)
#library(dplyr)
library(nlme)
#install.packages('compositions')
library(compositions)
source("/Volumes/GoogleDrive/My Drive/Moorea_revisions/mr16s_revised/analysis/scripts/ancom_v2.1.R")

setwd("/Volumes/GoogleDrive/My Drive/Moorea_revisions/mr16s_revised/analysis/03.community_comp")
```

```{r ancom all, eval=FALSE}
otu_data_unt <- data.frame(ps.trim@otu_table)
otu_data<- data.frame(t(otu_data_unt))
#might need to make the sample names an actual row yet, not sure

meta_data = data.frame(ps.trim@sam_data)
meta_data = meta_data %>% rename(Sample.ID = id)

# Step 1: Data preprocessing

feature_table = otu_data; sample_var = "Sample.ID"; group_var = NULL
out_cut = 0.05; zero_cut = 0.90; lib_cut = 1000; neg_lb = FALSE
prepro = feature_table_pre_process(feature_table, meta_data, sample_var, group_var, 
                                   out_cut, zero_cut, lib_cut, neg_lb)
feature_table = prepro$feature_table # Preprocessed feature table
meta_data = prepro$meta_data # Preprocessed metadata
struc_zero = prepro$structure_zeros # Structural zero info

# Step 2: ANCOM

main_var = "zone"; p_adj_method = "BH"; alpha = 0.05
adj_formula = NULL; rand_formula = "~ 1 | site"

res.all = ANCOM(feature_table, meta_data, struc_zero, main_var, p_adj_method, 
            alpha, adj_formula, rand_formula)

#saveRDS(res.mnw,file="ancom.res.mnw.RDS")

# Step 3: Volcano Plot

# Number of taxa except structural zeros
n_taxa = ifelse(is.null(struc_zero), nrow(feature_table), sum(apply(struc_zero, 1, sum) == 0))
# Cutoff values for declaring differentially abundant taxa
cut_off = c(0.9 * (n_taxa -1), 0.8 * (n_taxa -1), 0.7 * (n_taxa -1), 0.6 * (n_taxa -1))
names(cut_off) = c("detected_0.9", "detected_0.8", "detected_0.7", "detected_0.6")

# Annotation data
dat_ann = data.frame(x = min(res.all$fig$data$x), y = cut_off["detected_0.7"], label = "W[0.7]")

fig = res.all$fig +  
  geom_hline(yintercept = cut_off["detected_0.7"], linetype = "dashed") + 
  geom_text(data = dat_ann, aes(x = x, y = y, label = label), 
            size = 4, vjust = -0.5, hjust = 0, color = "orange", parse = TRUE)
fig  
```

## ANCOM by site{.tabset}

Note: shouldn't be done on rarefied according to authors

Ran these three chunks once, then loading in data below

### MNW

```{r ancom mnw, eval=FALSE}
ps.mnw <- subset_samples(ps.trim,site=="MNW")

otu_data_unt <- data.frame(ps.mnw@otu_table)
otu_data<- data.frame(t(otu_data_unt))
#might need to make the sample names an actual row yet, not sure

meta_data = data.frame(ps.mnw@sam_data)
meta_data = meta_data %>% rename(Sample.ID = id)

# Step 1: Data preprocessing

feature_table = otu_data; sample_var = "Sample.ID"; group_var = NULL
out_cut = 0.05; zero_cut = 0.90; lib_cut = 1000; neg_lb = FALSE
prepro = feature_table_pre_process(feature_table, meta_data, sample_var, group_var, 
                                   out_cut, zero_cut, lib_cut, neg_lb)
feature_table = prepro$feature_table # Preprocessed feature table
meta_data = prepro$meta_data # Preprocessed metadata
struc_zero = prepro$structure_zeros # Structural zero info

# Step 2: ANCOM

main_var = "zone"; p_adj_method = "BH"; alpha = 0.05
adj_formula = NULL; rand_formula = NULL

res.mnw = ANCOM(feature_table, meta_data, struc_zero, main_var, p_adj_method, 
            alpha, adj_formula, rand_formula)

#saveRDS(res.mnw,file="ancom.res.mnw.RDS")

# Step 3: Volcano Plot

# Number of taxa except structural zeros
n_taxa = ifelse(is.null(struc_zero), nrow(feature_table), sum(apply(struc_zero, 1, sum) == 0))
# Cutoff values for declaring differentially abundant taxa
cut_off = c(0.9 * (n_taxa -1), 0.8 * (n_taxa -1), 0.7 * (n_taxa -1), 0.6 * (n_taxa -1))
names(cut_off) = c("detected_0.9", "detected_0.8", "detected_0.7", "detected_0.6")

# Annotation data
dat_ann = data.frame(x = min(res.mnw$fig$data$x), y = cut_off["detected_0.7"], label = "W[0.7]")

fig = res.mnw$fig +  
  geom_hline(yintercept = cut_off["detected_0.7"], linetype = "dashed") + 
  geom_text(data = dat_ann, aes(x = x, y = y, label = label), 
            size = 4, vjust = -0.5, hjust = 0, color = "orange", parse = TRUE)
fig  
```

### MSE

```{r ancom mse, eval=FALSE}
ps.mse <- subset_samples(ps.trim,site=="MSE")

otu_data_unt <- data.frame(ps.mse@otu_table)
otu_data<- data.frame(t(otu_data_unt))
#might need to make the sample names an actual row yet, not sure

meta_data = data.frame(ps.mse@sam_data)
meta_data = meta_data %>% rename(Sample.ID = id)

# Step 1: Data preprocessing

feature_table = otu_data; sample_var = "Sample.ID"; group_var = NULL
out_cut = 0.05; zero_cut = 0.90; lib_cut = 1000; neg_lb = FALSE
prepro = feature_table_pre_process(feature_table, meta_data, sample_var, group_var, 
                                   out_cut, zero_cut, lib_cut, neg_lb)
feature_table = prepro$feature_table # Preprocessed feature table
meta_data = prepro$meta_data # Preprocessed metadata
struc_zero = prepro$structure_zeros # Structural zero info

# Step 2: ANCOM

main_var = "zone"; p_adj_method = "BH"; alpha = 0.05
adj_formula = NULL; rand_formula = NULL

res.mse = ANCOM(feature_table, meta_data, struc_zero, main_var, p_adj_method, 
            alpha, adj_formula, rand_formula)

#saveRDS(res.mse,file="ancom.res.mse.RDS")

# Step 3: Volcano Plot

# Number of taxa except structural zeros
n_taxa = ifelse(is.null(struc_zero), nrow(feature_table), sum(apply(struc_zero, 1, sum) == 0))
# Cutoff values for declaring differentially abundant taxa
cut_off = c(0.9 * (n_taxa -1), 0.8 * (n_taxa -1), 0.7 * (n_taxa -1), 0.6 * (n_taxa -1))
names(cut_off) = c("detected_0.9", "detected_0.8", "detected_0.7", "detected_0.6")

# Annotation data
dat_ann = data.frame(x = min(res.mse$fig$data$x), y = cut_off["detected_0.7"], label = "W[0.7]")

fig = res.mse$fig +  
  geom_hline(yintercept = cut_off["detected_0.7"], linetype = "dashed") + 
  geom_text(data = dat_ann, aes(x = x, y = y, label = label), 
            size = 4, vjust = -0.5, hjust = 0, color = "orange", parse = TRUE)
fig  
```

### TNW

```{r ancom tnw, eval=FALSE}
ps.tnw <- subset_samples(ps.trim,site=="TNW")

otu_data_unt <- data.frame(ps.tnw@otu_table)
otu_data<- data.frame(t(otu_data_unt))
#might need to make the sample names an actual row yet, not sure

meta_data = data.frame(ps.tnw@sam_data)
meta_data = meta_data %>% rename(Sample.ID = id)

# Step 1: Data preprocessing

feature_table = otu_data; sample_var = "Sample.ID"; group_var = NULL
out_cut = 0.05; zero_cut = 0.90; lib_cut = 1000; neg_lb = FALSE
prepro = feature_table_pre_process(feature_table, meta_data, sample_var, group_var, 
                                   out_cut, zero_cut, lib_cut, neg_lb)
feature_table = prepro$feature_table # Preprocessed feature table
meta_data = prepro$meta_data # Preprocessed metadata
struc_zero = prepro$structure_zeros # Structural zero info

# Step 2: ANCOM

main_var = "zone"; p_adj_method = "BH"; alpha = 0.05
adj_formula = NULL; rand_formula = NULL

res.tnw = ANCOM(feature_table, meta_data, struc_zero, main_var, p_adj_method, 
            alpha, adj_formula, rand_formula)

#saveRDS(res.tnw,file="ancom.res.tnw.RDS")

# Step 3: Volcano Plot

# Number of taxa except structural zeros
n_taxa = ifelse(is.null(struc_zero), nrow(feature_table), sum(apply(struc_zero, 1, sum) == 0))
# Cutoff values for declaring differentially abundant taxa
cut_off = c(0.9 * (n_taxa -1), 0.8 * (n_taxa -1), 0.7 * (n_taxa -1), 0.6 * (n_taxa -1))
names(cut_off) = c("detected_0.9", "detected_0.8", "detected_0.7", "detected_0.6")

# Annotation data
dat_ann = data.frame(x = min(res.tnw$fig$data$x), y = cut_off["detected_0.7"], label = "W[0.7]")

fig = res.tnw$fig +  
  geom_hline(yintercept = cut_off["detected_0.7"], linetype = "dashed") + 
  geom_text(data = dat_ann, aes(x = x, y = y, label = label), 
            size = 4, vjust = -0.5, hjust = 0, color = "orange", parse = TRUE)
fig  
```

## Synthesizing ANCOM results

Re-read in data

```{r load ancom results}
res.mnw <- readRDS("ancom.res.mnw.RDS")
res.mse <- readRDS("ancom.res.mse.RDS")
res.tnw <- readRDS("ancom.res.tnw.RDS")
```

Which ones are 'significant'

```{r subset out files}
mnw.out <- res.mnw$out
mnw.out.sig <- mnw.out[mnw.out$detected_0.6==TRUE,]
#1

mse.out <- res.mse$out
mse.out.sig <- mse.out[mse.out$detected_0.6==TRUE,]
#8

tnw.out <- res.tnw$out
tnw.out.sig <- tnw.out[tnw.out$detected_0.6==TRUE,]
#4
```

Subset the sig ones in phyloseq

```{r}
want.mnw <- c(mnw.out.sig$taxa_id)
want.mse <- c(mse.out.sig$taxa_id)
want.tnw <- c(tnw.out.sig$taxa_id)

want <- c(want.mnw,want.mse,want.tnw)

ps.sig.taxa <- subset_taxa(ps.rare.trim,row.names(ps.trim@tax_table) %in% want)
#37 & 13 are in there twice

#looks so cool!
plot_bar(ps.sig.taxa,x="site_zone",y="Abundance",fill="Genus")+
  facet_wrap(~Genus,scales="free")

#ggsave("sig.genus.abun.pdf",width=11)
```

Heat map attempts

```{r}
library("microbiomeutilities")
library("viridis")

ps.sig.mnw <- subset_samples(ps.sig.taxa,site=="MNW")

ps.sig.mnw.sz <- merge_samples(ps.sig.mnw,"site_zone")

ps.sig.mnw.sz@sam_data$zone <- c("A","B")

heat.sig.mnw <- plot_taxa_heatmap(ps.sig.mnw.sz,
  subset.top=14,                               
  VariableA = "zone",
  heatcolors=colorRampPalette(colors=c(viridis_pal(direction=-1,option="D")(32)))(30),
  #heatcolors = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  transformation = "log10",
  cluster_cols=F,
  cluster_rows=F
)
#pdf: 3 x 4 in

ps.sig.mse <- subset_samples(ps.sig.taxa,site=="MSE")

ps.sig.mse.sz <- merge_samples(ps.sig.mse,"site_zone")

ps.sig.mse.sz@sam_data$zone <- c("A","B")

heat.sig.mse <- plot_taxa_heatmap(ps.sig.mse.sz,
  subset.top=14,                               
  VariableA = "zone",
  heatcolors=colorRampPalette(colors=c(viridis_pal(direction=-1,option="D")(32)))(30),
  #heatcolors = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  transformation = "log10",
  cluster_cols=F,
  cluster_rows=F
)

ps.sig.tnw <- subset_samples(ps.sig.taxa,site=="TNW")

ps.sig.tnw.sz <- merge_samples(ps.sig.tnw,"site_zone")

ps.sig.tnw.sz@sam_data$zone <- c("A","B")

heat.sig.tnw <- plot_taxa_heatmap(ps.sig.tnw.sz,
  subset.top=14,                               
  VariableA = "zone",
  heatcolors=colorRampPalette(colors=c(viridis_pal(direction=-1,option="D")(32)))(30),
  #heatcolors = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  transformation = "log10",
  cluster_cols=F,
  cluster_rows=F
)
```

```{r messy crap, eval=FALSE}




heat.sig <- plot_taxa_heatmap(ps.sig.taxa,
  subset.top=14,                               
  VariableA = "zone",
  heatcolors = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  transformation = "log10",
  cluster_cols=T
)

ps.sz <- merge_samples(ps.rare.trim, "site_zone")

ps.sig.taxa.sz <- subset_taxa(ps.sz,row.names(ps.sz@tax_table) %in% want)
#37 & 13 are in there twice

ps.sig.taxa.sz@sam_data$zone <- c("A","B","A","B","A","B")

heat.sig <- plot_taxa_heatmap(ps.sig.taxa.sz,
  subset.top=14,                               
  VariableA = "zone",
  heatcolors = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  transformation = "Z-OTU",
  cluster_cols=F
)

```

# Heat maps!

```{r}
#evtools::install_github("microsud/microbiomeutilities")
library("microbiomeutilities")

#package doesn't like the sq level
taxa.tab <- as.data.frame(ps.trim@tax_table)
taxa.tab.nosq <- as.matrix(taxa.tab[,1:7])
seq.trim.tab <- as.data.frame(ps.trim@otu_table)

rownames(samdf) <- samdf$id

ps.trim.nosq <- phyloseq(otu_table(seq.trim.tab, taxa_are_rows=FALSE), 
                         sample_data(samdf), 
                         tax_table(taxa.tab.nosq))



library(RColorBrewer)

heat.sample <- plot_taxa_heatmap(ps.trim.nosq,
  subset.top=223,                               
  VariableA = "site",
  heatcolors = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  transformation = "log10",
  cluster_cols=T
)

ps.trim.nosq.mnw <- subset_samples(ps.trim.nosq,site=="MNW")

heat.mnw <- plot_taxa_heatmap(ps.trim.nosq.mnw,
  subset.top = 20,
  VariableA = "zone",
  heatcolors = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  transformation = "log10",
  cluster_cols=T
)

ps.trim.nosq.mse <- subset_samples(ps.trim.nosq,site=="MSE")

heat.mse <- plot_taxa_heatmap(ps.trim.nosq.mse,
  subset.top = 20,
  VariableA = "zone",
  heatcolors=colorRampPalette(colors=c(viridis_pal(direction=-1,option="D")(32)))(30),
  #heatcolors = colorRampPalette(brewer.pal(n = 7, name = "Purples"))(100),#took out rev() here
  transformation = "log10",
  cluster_cols=T
)

ps.sz <- merge_samples(ps.rare.trim, "site_zone")

ps.sz@sam_data$zone <- c("A","B","A","B","A","B")

heat.all.sz <- plot_taxa_heatmap(ps.sz,
  subset.top=20,                               
  VariableA = "zone",
  heatcolors = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  transformation = "Z-OTU",
  cluster_cols=F
)
```






