---
title: "fl16s_networks"
author: "Nicola Kriefall"
date: "06/03/2022"
output: html_document
---

# Setup

## Load libraries

```{r libraries}
library("devtools")
library("stringr")
#install_github("zdk123/SpiecEasi")
#library(SpiecEasi)
#library(igraph)
#library(vegan)
#library(Matrix)
#library(reshape2)
#library(plyr)
library(dplyr)
library(gridExtra)
library(grid)
#library(microbiome)
library(phyloseq)

setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_16s/05.networks")
```

### Extra function

```{r extra 'not in' function}
#extra function
# load in the following function
'%!in%' <- function(x,y) {
!('%in%'(x,y))
}
# END
```

## Read in & process data

Ran following section once, saved, then skipped other times

```{r, eval=F}
ps.clean <- readRDS("../01.generate_asv_table/ps.cleanest.less.rds")

tax <- as.data.frame(ps.clean@tax_table@.Data)

tax.clean <- data.frame(row.names = row.names(tax),
                        Kingdom = str_replace(tax[,1], "D_0__",""),
                        Phylum = str_replace(tax[,2], "D_1__",""),
                        Class = str_replace(tax[,3], "D_2__",""),
                        Order = str_replace(tax[,4], "D_3__",""),
                        Family = str_replace(tax[,5], "D_4__",""),
                        Genus = str_replace(tax[,6], "D_5__",""),
                        Species = str_replace(tax[,7], "D_6__",""),
                        stringsAsFactors = FALSE)
tax.clean[is.na(tax.clean)] <- ""

for (i in 1:7){ tax.clean[,i] <- as.character(tax.clean[,i])}
####### Fill holes in the tax table
tax.clean[is.na(tax.clean)] <- ""
for (i in 1:nrow(tax.clean)){
  if (tax.clean[i,2] == ""){
    kingdom <- paste("Kingdom_", tax.clean[i,1], sep = "")
    tax.clean[i, 2:7] <- kingdom
  } else if (tax.clean[i,3] == ""){
    phylum <- paste("Phylum_", tax.clean[i,2], sep = "")
    tax.clean[i, 3:7] <- phylum
  } else if (tax.clean[i,4] == ""){
    class <- paste("Class_", tax.clean[i,3], sep = "")
    tax.clean[i, 4:7] <- class
  } else if (tax.clean[i,5] == ""){
    order <- paste("Order_", tax.clean[i,4], sep = "")
    tax.clean[i, 5:7] <- order
  } else if (tax.clean[i,6] == ""){
    family <- paste("Family_", tax.clean[i,5], sep = "")
    tax.clean[i, 6:7] <- family
  } else if (tax.clean[i,7] == ""){
    tax.clean$Species[i] <- paste("Genus",tax.clean$Genus[i], sep = "_")
  }
}

tax_table(ps.clean) <- as.matrix(tax.clean)

#ps.clean.gen <- tax_glom(ps.clean,"Genus")
#ps.otu.gen <- data.frame(ps.clean.gen@otu_table)

#family
ps.clean.fam <- tax_glom(ps.clean,"Family")

ps.clean.fam.sid <- subset_samples(ps.clean.fam,spp=="ssid")
ps.clean.fam.rad <- subset_samples(ps.clean.fam,spp=="srad")

ps.clean.fam.sid.no0 <- prune_taxa(taxa_sums(ps.clean.fam.sid) > 0, ps.clean.fam.sid) 
# otu_table()   OTU Table:         [ 486 taxa and 166 samples ]
# sample_data() Sample Data:       [ 166 samples by 11 sample variables ]
# tax_table()   Taxonomy Table:    [ 486 taxa by 7 taxonomic ranks ]
ps.clean.fam.rad.no0 <- prune_taxa(taxa_sums(ps.clean.fam.rad) > 0, ps.clean.fam.rad) 
# otu_table()   OTU Table:         [ 483 taxa and 132 samples ]
# sample_data() Sample Data:       [ 132 samples by 11 sample variables ]
# tax_table()   Taxonomy Table:    [ 483 taxa by 7 taxonomic ranks ]

#saveRDS(ps.clean.fam.sid.no0,file="./files/ps.clean.fam.sid.no0")
#saveRDS(ps.clean.fam.rad.no0,file="./files/ps.clean.fam.rad.no0")
```

## Subset for sites/years{.tabset}

### S. siderea

```{r}
#subset by timepoint
ps.fam.sid.pre <- subset_samples(ps.clean.fam.sid.no0,time=="Pre")
ps.fam.sid.irm <- subset_samples(ps.clean.fam.sid.no0,time=="Irma")
ps.fam.sid.pos <- subset_samples(ps.clean.fam.sid.no0,time=="Post")

#within each timepoint, separate by sites
#lower keys 1
ps.fam.sid.pre.lk1 <- subset_samples(ps.fam.sid.pre,site=="LK1")
ps.fam.sid.irm.lk1 <- subset_samples(ps.fam.sid.irm,site=="LK1")
ps.fam.sid.pos.lk1 <- subset_samples(ps.fam.sid.pos,site=="LK1")

#upper keys 1
ps.fam.sid.pre.uk1 <- subset_samples(ps.fam.sid.pre,site=="UK1")
ps.fam.sid.irm.uk1 <- subset_samples(ps.fam.sid.irm,site=="UK1")
ps.fam.sid.pos.uk1 <- subset_samples(ps.fam.sid.pos,site=="UK1")

#upper keys 2
ps.fam.sid.pre.uk2 <- subset_samples(ps.fam.sid.pre,site=="UK2")
ps.fam.sid.irm.uk2 <- subset_samples(ps.fam.sid.irm,site=="UK2")
ps.fam.sid.pos.uk2 <- subset_samples(ps.fam.sid.pos,site=="UK2")

#inshore & offshore
#lower keys 1
ps.fam.sid.pre.lk1.in <- subset_samples(ps.fam.sid.pre.lk1,zone=="Inshore")
ps.fam.sid.pre.lk1.off <- subset_samples(ps.fam.sid.pre.lk1,zone=="Offshore")
ps.fam.sid.irm.lk1.in <- subset_samples(ps.fam.sid.irm.lk1,zone=="Inshore")
ps.fam.sid.irm.lk1.off <- subset_samples(ps.fam.sid.irm.lk1,zone=="Offshore")
ps.fam.sid.pos.lk1.in <- subset_samples(ps.fam.sid.pos.lk1,zone=="Inshore")
ps.fam.sid.pos.lk1.off <- subset_samples(ps.fam.sid.pos.lk1,zone=="Offshore")

#upper keys 1
ps.fam.sid.pre.uk1.in <- subset_samples(ps.fam.sid.pre.uk1,zone=="Inshore")
ps.fam.sid.pre.uk1.off <- subset_samples(ps.fam.sid.pre.uk1,zone=="Offshore")
ps.fam.sid.irm.uk1.in <- subset_samples(ps.fam.sid.irm.uk1,zone=="Inshore")
ps.fam.sid.irm.uk1.off <- subset_samples(ps.fam.sid.irm.uk1,zone=="Offshore")
ps.fam.sid.pos.uk1.in <- subset_samples(ps.fam.sid.pos.uk1,zone=="Inshore")
ps.fam.sid.pos.uk1.off <- subset_samples(ps.fam.sid.pos.uk1,zone=="Offshore")

#upper keys 2
ps.fam.sid.pre.uk2.in <- subset_samples(ps.fam.sid.pre.uk2,zone=="Inshore")
ps.fam.sid.pre.uk2.off <- subset_samples(ps.fam.sid.pre.uk2,zone=="Offshore")
ps.fam.sid.irm.uk2.in <- subset_samples(ps.fam.sid.irm.uk2,zone=="Inshore")
ps.fam.sid.irm.uk2.off <- subset_samples(ps.fam.sid.irm.uk2,zone=="Offshore")
ps.fam.sid.pos.uk2.in <- subset_samples(ps.fam.sid.pos.uk2,zone=="Inshore")
ps.fam.sid.pos.uk2.off <- subset_samples(ps.fam.sid.pos.uk2,zone=="Offshore")

#retrieving seq tables
#lower keys 1
seq.fam.sid.pre.lk1.in <- data.frame(ps.fam.sid.pre.lk1.in@otu_table)
seq.fam.sid.irm.lk1.in <- data.frame(ps.fam.sid.irm.lk1.in@otu_table)
seq.fam.sid.pos.lk1.in <- data.frame(ps.fam.sid.pos.lk1.in@otu_table)

seq.fam.sid.pre.lk1.off <- data.frame(ps.fam.sid.pre.lk1.off@otu_table)
seq.fam.sid.irm.lk1.off <- data.frame(ps.fam.sid.irm.lk1.off@otu_table)
seq.fam.sid.pos.lk1.off <- data.frame(ps.fam.sid.pos.lk1.off@otu_table)

#upper keys 1
seq.fam.sid.pre.uk1.in <- data.frame(ps.fam.sid.pre.uk1.in@otu_table)
seq.fam.sid.irm.uk1.in <- data.frame(ps.fam.sid.irm.uk1.in@otu_table)
seq.fam.sid.pos.uk1.in <- data.frame(ps.fam.sid.pos.uk1.in@otu_table)

seq.fam.sid.pre.uk1.off <- data.frame(ps.fam.sid.pre.uk1.off@otu_table)
seq.fam.sid.irm.uk1.off <- data.frame(ps.fam.sid.irm.uk1.off@otu_table)
seq.fam.sid.pos.uk1.off <- data.frame(ps.fam.sid.pos.uk1.off@otu_table)

#upper keys 2
seq.fam.sid.pre.uk2.in <- data.frame(ps.fam.sid.pre.uk2.in@otu_table)
seq.fam.sid.irm.uk2.in <- data.frame(ps.fam.sid.irm.uk2.in@otu_table)
seq.fam.sid.pos.uk2.in <- data.frame(ps.fam.sid.pos.uk2.in@otu_table)

seq.fam.sid.pre.uk2.off <- data.frame(ps.fam.sid.pre.uk2.off@otu_table)
seq.fam.sid.irm.uk2.off <- data.frame(ps.fam.sid.irm.uk2.off@otu_table)
seq.fam.sid.pos.uk2.off <- data.frame(ps.fam.sid.pos.uk2.off@otu_table)
```

#### Cleaning lower reads

Some data cleaning: authors recommend removing samples with less than an average of 2 reads per column. 

```{r}
#lower keys 1 inshore
seq.fam.sid.pre.lk1.in.no2 <- seq.fam.sid.pre.lk1.in[,-which(colMeans(seq.fam.sid.pre.lk1.in) <= 2)]
ncol(seq.fam.sid.pre.lk1.in.no2) #195
seq.fam.sid.irm.lk1.in.no2 <- seq.fam.sid.irm.lk1.in[,-which(colMeans(seq.fam.sid.irm.lk1.in) <= 2)]
ncol(seq.fam.sid.irm.lk1.in.no2) #251
seq.fam.sid.pos.lk1.in.no2 <- seq.fam.sid.pos.lk1.in[,-which(colMeans(seq.fam.sid.pos.lk1.in) <= 2)]
ncol(seq.fam.sid.pos.lk1.in.no2) #204

#lower keys 1 offshore
seq.fam.sid.pre.lk1.off.no2 <- seq.fam.sid.pre.lk1.off[,-which(colMeans(seq.fam.sid.pre.lk1.off) <= 2)]
ncol(seq.fam.sid.pre.lk1.off.no2) #292
seq.fam.sid.irm.lk1.off.no2 <- seq.fam.sid.irm.lk1.off[,-which(colMeans(seq.fam.sid.irm.lk1.off) <= 2)]
ncol(seq.fam.sid.irm.lk1.off.no2) #225
seq.fam.sid.pos.lk1.off.no2 <- seq.fam.sid.pos.lk1.off[,-which(colMeans(seq.fam.sid.pos.lk1.off) <= 2)]
ncol(seq.fam.sid.pos.lk1.off.no2) #222

#upper keys 1 inshore
seq.fam.sid.pre.uk1.in.no2 <- seq.fam.sid.pre.uk1.in[,-which(colMeans(seq.fam.sid.pre.uk1.in) <= 2)]
ncol(seq.fam.sid.pre.uk1.in.no2) #176
seq.fam.sid.irm.uk1.in.no2 <- seq.fam.sid.irm.uk1.in[,-which(colMeans(seq.fam.sid.irm.uk1.in) <= 2)]
ncol(seq.fam.sid.irm.uk1.in.no2) #215
seq.fam.sid.pos.uk1.in.no2 <- seq.fam.sid.pos.uk1.in[,-which(colMeans(seq.fam.sid.pos.uk1.in) <= 2)]
ncol(seq.fam.sid.pos.uk1.in.no2) #208

#upper keys 1 offshore
seq.fam.sid.pre.uk1.off.no2 <- seq.fam.sid.pre.uk1.off[,-which(colMeans(seq.fam.sid.pre.uk1.off) <= 2)]
ncol(seq.fam.sid.pre.uk1.off.no2) #235
seq.fam.sid.irm.uk1.off.no2 <- seq.fam.sid.irm.uk1.off[,-which(colMeans(seq.fam.sid.irm.uk1.off) <= 2)]
ncol(seq.fam.sid.irm.uk1.off.no2) #243
seq.fam.sid.pos.uk1.off.no2 <- seq.fam.sid.pos.uk1.off[,-which(colMeans(seq.fam.sid.pos.uk1.off) <= 2)]
ncol(seq.fam.sid.pos.uk1.off.no2) #213

#upper keys 1 inshore
seq.fam.sid.pre.uk2.in.no2 <- seq.fam.sid.pre.uk2.in[,-which(colMeans(seq.fam.sid.pre.uk2.in) <= 2)]
ncol(seq.fam.sid.pre.uk2.in.no2) #184
seq.fam.sid.irm.uk2.in.no2 <- seq.fam.sid.irm.uk2.in[,-which(colMeans(seq.fam.sid.irm.uk2.in) <= 2)]
ncol(seq.fam.sid.irm.uk2.in.no2) #208
seq.fam.sid.pos.uk2.in.no2 <- seq.fam.sid.pos.uk2.in[,-which(colMeans(seq.fam.sid.pos.uk2.in) <= 2)]
ncol(seq.fam.sid.pos.uk2.in.no2) #232

#upper keys 1 offshore
seq.fam.sid.pre.uk2.off.no2 <- seq.fam.sid.pre.uk2.off[,-which(colMeans(seq.fam.sid.pre.uk2.off) <= 2)]
ncol(seq.fam.sid.pre.uk2.off.no2) #244
seq.fam.sid.irm.uk2.off.no2 <- seq.fam.sid.irm.uk2.off[,-which(colMeans(seq.fam.sid.irm.uk2.off) <= 2)]
ncol(seq.fam.sid.irm.uk2.off.no2) #260
seq.fam.sid.pos.uk2.off.no2 <- seq.fam.sid.pos.uk2.off[,-which(colMeans(seq.fam.sid.pos.uk2.off) <= 2)]
ncol(seq.fam.sid.pos.uk2.off.no2) #179
```

### S. radians

```{r}
#just copy paste above when ready & replace with rads
```

# Networks

## Setup

Begin by installing & loading necessary packages.

(Overall pipeline & scripts followed is sourced from [here; Layeghifard *et al*., 2018, *Methods in Molecular Biology*](https://www-ncbi-nlm-nih-gov.ezproxy.bu.edu/pubmed/30298259))

```{r packages, message=FALSE}
# Install Required packages 
#install.packages("igraph") 
library("igraph")
#install.packages("qgraph") 
library("qgraph")
#install.packages("MCL")
library("MCL")
#install.packages("vegan")
library("vegan")
# Install SpiecEasi package 
#install.packages("devtools") 
library("devtools") 
#install_github("zdk123/SpiecEasi")
library("SpiecEasi")
library("ggplot2")
library("ggpubr")
library("network")
#devtools::install_github("briatte/ggnet")
library(ggnet)
```

## Building adjacency matrix & network

Building an adjacency matrix of correlations of the abundances of bacterial families

```{r build network}
# SparCC network
#lower keys 1
spar.fam.sid.pre.lk1i <- sparcc(seq.fam.sid.pre.lk1.in.no2)
spar.fam.sid.pre.lk1o <- sparcc(seq.fam.sid.pre.lk1.off.no2)

spar.fam.sid.irm.lk1i <- sparcc(seq.fam.sid.irm.lk1.in.no2)
spar.fam.sid.irm.lk1o <- sparcc(seq.fam.sid.irm.lk1.off.no2)

spar.fam.sid.pos.lk1i <- sparcc(seq.fam.sid.pos.lk1.in.no2)
spar.fam.sid.pos.lk1o <- sparcc(seq.fam.sid.pos.lk1.off.no2)

#upper keys 1
spar.fam.sid.pre.uk1i <- sparcc(seq.fam.sid.pre.uk1.in.no2)
spar.fam.sid.pre.uk1o <- sparcc(seq.fam.sid.pre.uk1.off.no2)

spar.fam.sid.irm.uk1i <- sparcc(seq.fam.sid.irm.uk1.in.no2)
spar.fam.sid.irm.uk1o <- sparcc(seq.fam.sid.irm.uk1.off.no2)

spar.fam.sid.pos.uk1i <- sparcc(seq.fam.sid.pos.uk1.in.no2)
spar.fam.sid.pos.uk1o <- sparcc(seq.fam.sid.pos.uk1.off.no2)

#upper keys 2
spar.fam.sid.pre.uk2i <- sparcc(seq.fam.sid.pre.uk2.in.no2)
spar.fam.sid.pre.uk2o <- sparcc(seq.fam.sid.pre.uk2.off.no2)

spar.fam.sid.irm.uk2i <- sparcc(seq.fam.sid.irm.uk2.in.no2)
spar.fam.sid.irm.uk2o <- sparcc(seq.fam.sid.irm.uk2.off.no2)

spar.fam.sid.pos.uk2i <- sparcc(seq.fam.sid.pos.uk2.in.no2)
spar.fam.sid.pos.uk2o <- sparcc(seq.fam.sid.pos.uk2.off.no2)

sparcc.cutoff <- 0.7

#lower keys 1
adj.fam.sid.pre.lk1i <- ifelse(abs(spar.fam.sid.pre.lk1i$Cor) >= sparcc.cutoff, 1, 0)
adj.fam.sid.pre.lk1o <- ifelse(abs(spar.fam.sid.pre.lk1o$Cor) >= sparcc.cutoff, 1, 0)

adj.fam.sid.irm.lk1i <- ifelse(abs(spar.fam.sid.irm.lk1i$Cor) >= sparcc.cutoff, 1, 0)
adj.fam.sid.irm.lk1o <- ifelse(abs(spar.fam.sid.irm.lk1o$Cor) >= sparcc.cutoff, 1, 0)

adj.fam.sid.pos.lk1i <- ifelse(abs(spar.fam.sid.pos.lk1i$Cor) >= sparcc.cutoff, 1, 0)
adj.fam.sid.pos.lk1o <- ifelse(abs(spar.fam.sid.pos.lk1o$Cor) >= sparcc.cutoff, 1, 0)

#upper keys 1
adj.fam.sid.pre.uk1i <- ifelse(abs(spar.fam.sid.pre.uk1i$Cor) >= sparcc.cutoff, 1, 0)
adj.fam.sid.pre.uk1o <- ifelse(abs(spar.fam.sid.pre.uk1o$Cor) >= sparcc.cutoff, 1, 0)

adj.fam.sid.irm.uk1i <- ifelse(abs(spar.fam.sid.irm.uk1i$Cor) >= sparcc.cutoff, 1, 0)
adj.fam.sid.irm.uk1o <- ifelse(abs(spar.fam.sid.irm.uk1o$Cor) >= sparcc.cutoff, 1, 0)

adj.fam.sid.pos.uk1i <- ifelse(abs(spar.fam.sid.pos.uk1i$Cor) >= sparcc.cutoff, 1, 0)
adj.fam.sid.pos.uk1o <- ifelse(abs(spar.fam.sid.pos.uk1o$Cor) >= sparcc.cutoff, 1, 0)

#upper keys 2
adj.fam.sid.pre.uk2i <- ifelse(abs(spar.fam.sid.pre.uk2i$Cor) >= sparcc.cutoff, 1, 0)
adj.fam.sid.pre.uk2o <- ifelse(abs(spar.fam.sid.pre.uk2o$Cor) >= sparcc.cutoff, 1, 0)

adj.fam.sid.irm.uk2i <- ifelse(abs(spar.fam.sid.irm.uk2i$Cor) >= sparcc.cutoff, 1, 0)
adj.fam.sid.irm.uk2o <- ifelse(abs(spar.fam.sid.irm.uk2o$Cor) >= sparcc.cutoff, 1, 0)

adj.fam.sid.pos.uk2i <- ifelse(abs(spar.fam.sid.pos.uk2i$Cor) >= sparcc.cutoff, 1, 0)
adj.fam.sid.pos.uk2o <- ifelse(abs(spar.fam.sid.pos.uk2o$Cor) >= sparcc.cutoff, 1, 0)

# Add names to rows and columns
#lower keys 1 inshore
rownames(adj.fam.sid.pre.lk1i) <- colnames(seq.fam.sid.pre.lk1.in.no2)
colnames(adj.fam.sid.pre.lk1i) <- colnames(seq.fam.sid.pre.lk1.in.no2) 

rownames(adj.fam.sid.irm.lk1i) <- colnames(seq.fam.sid.irm.lk1.in.no2)
colnames(adj.fam.sid.irm.lk1i) <- colnames(seq.fam.sid.irm.lk1.in.no2) 

rownames(adj.fam.sid.pos.lk1i) <- colnames(seq.fam.sid.pos.lk1.in.no2)
colnames(adj.fam.sid.pos.lk1i) <- colnames(seq.fam.sid.pos.lk1.in.no2) 

#lower keys 1 offshore
rownames(adj.fam.sid.pre.lk1o) <- colnames(seq.fam.sid.pre.lk1.off.no2)
colnames(adj.fam.sid.pre.lk1o) <- colnames(seq.fam.sid.pre.lk1.off.no2) 

rownames(adj.fam.sid.irm.lk1o) <- colnames(seq.fam.sid.irm.lk1.off.no2)
colnames(adj.fam.sid.irm.lk1o) <- colnames(seq.fam.sid.irm.lk1.off.no2) 

rownames(adj.fam.sid.pos.lk1o) <- colnames(seq.fam.sid.pos.lk1.off.no2)
colnames(adj.fam.sid.pos.lk1o) <- colnames(seq.fam.sid.pos.lk1.off.no2) 

#upper keys 1 inshore
rownames(adj.fam.sid.pre.uk1i) <- colnames(seq.fam.sid.pre.uk1.in.no2)
colnames(adj.fam.sid.pre.uk1i) <- colnames(seq.fam.sid.pre.uk1.in.no2) 

rownames(adj.fam.sid.irm.uk1i) <- colnames(seq.fam.sid.irm.uk1.in.no2)
colnames(adj.fam.sid.irm.uk1i) <- colnames(seq.fam.sid.irm.uk1.in.no2) 

rownames(adj.fam.sid.pos.uk1i) <- colnames(seq.fam.sid.pos.uk1.in.no2)
colnames(adj.fam.sid.pos.uk1i) <- colnames(seq.fam.sid.pos.uk1.in.no2) 

#upper keys 1 offshore
rownames(adj.fam.sid.pre.uk1o) <- colnames(seq.fam.sid.pre.uk1.off.no2)
colnames(adj.fam.sid.pre.uk1o) <- colnames(seq.fam.sid.pre.uk1.off.no2) 

rownames(adj.fam.sid.irm.uk1o) <- colnames(seq.fam.sid.irm.uk1.off.no2)
colnames(adj.fam.sid.irm.uk1o) <- colnames(seq.fam.sid.irm.uk1.off.no2) 

rownames(adj.fam.sid.pos.uk1o) <- colnames(seq.fam.sid.pos.uk1.off.no2)
colnames(adj.fam.sid.pos.uk1o) <- colnames(seq.fam.sid.pos.uk1.off.no2) 

#upper keys 2 inshore
rownames(adj.fam.sid.pre.uk2i) <- colnames(seq.fam.sid.pre.uk2.in.no2)
colnames(adj.fam.sid.pre.uk2i) <- colnames(seq.fam.sid.pre.uk2.in.no2) 

rownames(adj.fam.sid.irm.uk2i) <- colnames(seq.fam.sid.irm.uk2.in.no2)
colnames(adj.fam.sid.irm.uk2i) <- colnames(seq.fam.sid.irm.uk2.in.no2) 

rownames(adj.fam.sid.pos.uk2i) <- colnames(seq.fam.sid.pos.uk2.in.no2)
colnames(adj.fam.sid.pos.uk2i) <- colnames(seq.fam.sid.pos.uk2.in.no2) 

#upper keys 2 offshore
rownames(adj.fam.sid.pre.uk2o) <- colnames(seq.fam.sid.pre.uk2.off.no2)
colnames(adj.fam.sid.pre.uk2o) <- colnames(seq.fam.sid.pre.uk2.off.no2) 

rownames(adj.fam.sid.irm.uk2o) <- colnames(seq.fam.sid.irm.uk2.off.no2)
colnames(adj.fam.sid.irm.uk2o) <- colnames(seq.fam.sid.irm.uk2.off.no2) 

rownames(adj.fam.sid.pos.uk2o) <- colnames(seq.fam.sid.pos.uk2.off.no2)
colnames(adj.fam.sid.pos.uk2o) <- colnames(seq.fam.sid.pos.uk2.off.no2) 
```

Saving everything

```{r, eval=F}
#sequence tables, cleaned
#lower keys 1
saveRDS(seq.fam.sid.pre.lk1.in.no2,file="./files/seq.tables/seq.fam.sid.pre.lk1.in.no2.rds")
saveRDS(seq.fam.sid.pre.lk1.off.no2,file="./files/seq.tables/seq.fam.sid.pre.lk1.off.no2.rds")

saveRDS(seq.fam.sid.irm.lk1.in.no2,file="./files/seq.tables/seq.fam.sid.irm.lk1.in.no2.rds")
saveRDS(seq.fam.sid.irm.lk1.off.no2,file="./files/seq.tables/seq.fam.sid.irm.lk1.off.no2.rds")

saveRDS(seq.fam.sid.pos.lk1.in.no2,file="./files/seq.tables/seq.fam.sid.pos.lk1.in.no2.rds")
saveRDS(seq.fam.sid.pos.lk1.off.no2,file="./files/seq.tables/seq.fam.sid.pos.lk1.off.no2.rds")

#upper keys 1
saveRDS(seq.fam.sid.pre.uk1.in.no2,file="./files/seq.tables/seq.fam.sid.pre.uk1.in.no2.rds")
saveRDS(seq.fam.sid.pre.uk1.off.no2,file="./files/seq.tables/seq.fam.sid.pre.uk1.off.no2.rds")

saveRDS(seq.fam.sid.irm.uk1.in.no2,file="./files/seq.tables/seq.fam.sid.irm.uk1.in.no2.rds")
saveRDS(seq.fam.sid.irm.uk1.off.no2,file="./files/seq.tables/seq.fam.sid.irm.uk1.off.no2.rds")

saveRDS(seq.fam.sid.pos.uk1.in.no2,file="./files/seq.tables/seq.fam.sid.pos.uk1.in.no2.rds")
saveRDS(seq.fam.sid.pos.uk1.off.no2,file="./files/seq.tables/seq.fam.sid.pos.uk1.off.no2.rds")

#upper keys 2
saveRDS(seq.fam.sid.pre.uk2.in.no2,file="./files/seq.tables/seq.fam.sid.pre.uk2.in.no2.rds")
saveRDS(seq.fam.sid.pre.uk2.off.no2,file="./files/seq.tables/seq.fam.sid.pre.uk2.off.no2.rds")

saveRDS(seq.fam.sid.irm.uk2.in.no2,file="./files/seq.tables/seq.fam.sid.irm.uk2.in.no2.rds")
saveRDS(seq.fam.sid.irm.uk2.off.no2,file="./files/seq.tables/seq.fam.sid.irm.uk2.off.no2.rds")

saveRDS(seq.fam.sid.pos.uk2.in.no2,file="./files/seq.tables/seq.fam.sid.pos.uk2.in.no2.rds")
saveRDS(seq.fam.sid.pos.uk2.off.no2,file="./files/seq.tables/seq.fam.sid.pos.uk2.off.no2.rds")

#sparcc files
#lower keys 1
saveRDS(spar.fam.sid.pre.lk1i,file="./files/sparcc/spar.fam.sid.pre.lk1i.rds")
saveRDS(spar.fam.sid.pre.lk1o,file="./files/sparcc/spar.fam.sid.pre.lk1o.rds")

saveRDS(spar.fam.sid.irm.lk1i,file="./files/sparcc/spar.fam.sid.irm.lk1i.rds")
saveRDS(spar.fam.sid.irm.lk1o,file="./files/sparcc/spar.fam.sid.irm.lk1o.rds")

saveRDS(spar.fam.sid.pos.lk1i,file="./files/sparcc/spar.fam.sid.pos.lk1i.rds")
saveRDS(spar.fam.sid.pos.lk1o,file="./files/sparcc/spar.fam.sid.pos.lk1o.rds")

#upper keys 1
saveRDS(spar.fam.sid.pre.uk1i,file="./files/sparcc/spar.fam.sid.pre.uk1i.rds")
saveRDS(spar.fam.sid.pre.uk1o,file="./files/sparcc/spar.fam.sid.pre.uk1o.rds")

saveRDS(spar.fam.sid.irm.uk1i,file="./files/sparcc/spar.fam.sid.irm.uk1i.rds")
saveRDS(spar.fam.sid.irm.uk1o,file="./files/sparcc/spar.fam.sid.irm.uk1o.rds")

saveRDS(spar.fam.sid.pos.uk1i,file="./files/sparcc/spar.fam.sid.pos.uk1i.rds")
saveRDS(spar.fam.sid.pos.uk1o,file="./files/sparcc/spar.fam.sid.pos.uk1o.rds")

#upper keys 2
saveRDS(spar.fam.sid.pre.uk2i,file="./files/sparcc/spar.fam.sid.pre.uk2i.rds")
saveRDS(spar.fam.sid.pre.uk2o,file="./files/sparcc/spar.fam.sid.pre.uk2o.rds")

saveRDS(spar.fam.sid.irm.uk2i,file="./files/sparcc/spar.fam.sid.irm.uk2i.rds")
saveRDS(spar.fam.sid.irm.uk2o,file="./files/sparcc/spar.fam.sid.irm.uk2o.rds")

saveRDS(spar.fam.sid.pos.uk2i,file="./files/sparcc/spar.fam.sid.pos.uk2i.rds")
saveRDS(spar.fam.sid.pos.uk2o,file="./files/sparcc/spar.fam.sid.pos.uk2o.rds")

#adjacency files
#lower keys 1
saveRDS(adj.fam.sid.pre.lk1i,file="./files/adjacency/adj.fam.sid.pre.lk1i.rds")
saveRDS(adj.fam.sid.pre.lk1o,file="./files/adjacency/adj.fam.sid.pre.lk1o.rds")

saveRDS(adj.fam.sid.irm.lk1i,file="./files/adjacency/adj.fam.sid.irm.lk1i.rds")
saveRDS(adj.fam.sid.irm.lk1o,file="./files/adjacency/adj.fam.sid.irm.lk1o.rds")

saveRDS(adj.fam.sid.pos.lk1i,file="./files/adjacency/adj.fam.sid.pos.lk1i.rds")
saveRDS(adj.fam.sid.pos.lk1o,file="./files/adjacency/adj.fam.sid.pos.lk1o.rds")

#upper keys 1
saveRDS(adj.fam.sid.pre.uk1i,file="./files/adjacency/adj.fam.sid.pre.uk1i.rds")
saveRDS(adj.fam.sid.pre.uk1o,file="./files/adjacency/adj.fam.sid.pre.uk1o.rds")

saveRDS(adj.fam.sid.irm.uk1i,file="./files/adjacency/adj.fam.sid.irm.uk1i.rds")
saveRDS(adj.fam.sid.irm.uk1o,file="./files/adjacency/adj.fam.sid.irm.uk1o.rds")

saveRDS(adj.fam.sid.pos.uk1i,file="./files/adjacency/adj.fam.sid.pos.uk1i.rds")
saveRDS(adj.fam.sid.pos.uk1o,file="./files/adjacency/adj.fam.sid.pos.uk1o.rds")

#upper keys 2
saveRDS(adj.fam.sid.pre.uk2i,file="./files/adjacency/adj.fam.sid.pre.uk2i.rds")
saveRDS(adj.fam.sid.pre.uk2o,file="./files/adjacency/adj.fam.sid.pre.uk2o.rds")

saveRDS(adj.fam.sid.irm.uk2i,file="./files/adjacency/adj.fam.sid.irm.uk2i.rds")
saveRDS(adj.fam.sid.irm.uk2o,file="./files/adjacency/adj.fam.sid.irm.uk2o.rds")

saveRDS(adj.fam.sid.pos.uk2i,file="./files/adjacency/adj.fam.sid.pos.uk2i.rds")
saveRDS(adj.fam.sid.pos.uk2o,file="./files/adjacency/adj.fam.sid.pos.uk2o.rds")
```

Re-read in everything

```{r}
#texttttt
```

## Visualizing network from adjacency matrix

```{r plot net from adj matrix}
"#781C6D" #purple
"#F8850F" #orange
"#AE305C" #burgundy

"#ED7953FF"
"#8405A7FF"

# show_col(viridis_pal(option="A")(3))
# show_col(viridis_pal(option="B")(3))
# show_col(viridis_pal(option="C")(3))
# show_col(viridis_pal(option="D")(3))
# show_col(viridis_pal(option="E")(3))
# show_col(viridis_pal(option="F")(3))
# show_col(viridis_pal(option="G")(3))
# show_col(viridis_pal(option="H")(3))

#removed size.min=1 from options
net.fam.sid.pre.lk1i <- ggnet2(adj.fam.sid.pre.lk1i,size=1,alpha=0.5,color="#3BBA76")+
  ggtitle('LK1-I pre-disturbance')
net.fam.sid.pre.lk1i
net.fam.sid.pre.lk1o <- ggnet2(adj.fam.sid.pre.lk1o,size=1,alpha=0.5,color="#453882")+
  ggtitle('LK1-O pre-disturbance')
net.fam.sid.pre.lk1o

ggarrange(net.fam.sid.pre.lk1i,net.fam.sid.pre.lk1o)

net.fam.sid.irm.lk1i <- ggnet2(adj.fam.sid.irm.lk1i,size=1,alpha=0.5,color="#3BBA76")+
  ggtitle('LK1-I disturbance')
net.fam.sid.irm.lk1i
net.fam.sid.irm.lk1o <- ggnet2(adj.fam.sid.irm.lk1o,size=1,alpha=0.5,color="#453882")+
  ggtitle('LK1-O disturbance')
net.fam.sid.irm.lk1o

ggarrange(net.fam.sid.irm.lk1i,net.fam.sid.irm.lk1o)            

net.fam.sid.pos.lk1i <- ggnet2(adj.fam.sid.pos.lk1i,size=1,alpha=0.5,color="#3BBA76")+
  ggtitle('LK1-I post-disturbance')
net.fam.sid.pos.lk1i
net.fam.sid.pos.lk1o <- ggnet2(adj.fam.sid.pos.lk1o,size=1,alpha=0.5,color="#453882")+
  ggtitle('LK1-O post-disturbance')
net.fam.sid.pos.lk1o

ggarrange(net.fam.sid.pos.lk1i,net.fam.sid.pos.lk1o)   
```

## All together now

```{r}
ggarrange(net.fam.sid.pre.lk1i,net.fam.sid.pre.lk1o,net.fam.sid.irm.lk1i,net.fam.sid.irm.lk1o,net.fam.sid.pos.lk1i,net.fam.sid.pos.lk1o,ncol=2,nrow=3)
```

## Metrics

```{r}
# Build network from adjacency
#lower keys 1
net.fam.sid.pre.lk1i <- graph.adjacency(adj.fam.sid.pre.lk1i, mode = "undirected", diag = FALSE)
net.fam.sid.pre.lk1o <- graph.adjacency(adj.fam.sid.pre.lk1o, mode = "undirected", diag = FALSE)

net.fam.sid.irm.lk1i <- graph.adjacency(adj.fam.sid.irm.lk1i, mode = "undirected", diag = FALSE)
net.fam.sid.irm.lk1o <- graph.adjacency(adj.fam.sid.irm.lk1o, mode = "undirected", diag = FALSE)

net.fam.sid.pos.lk1i <- graph.adjacency(adj.fam.sid.pos.lk1i, mode = "undirected", diag = FALSE)
net.fam.sid.pos.lk1o <- graph.adjacency(adj.fam.sid.pos.lk1o, mode = "undirected", diag = FALSE)

#upper keys 1
net.fam.sid.pre.uk1i <- graph.adjacency(adj.fam.sid.pre.uk1i, mode = "undirected", diag = FALSE)
net.fam.sid.pre.uk1o <- graph.adjacency(adj.fam.sid.pre.uk1o, mode = "undirected", diag = FALSE)

net.fam.sid.irm.uk1i <- graph.adjacency(adj.fam.sid.irm.uk1i, mode = "undirected", diag = FALSE)
net.fam.sid.irm.uk1o <- graph.adjacency(adj.fam.sid.irm.uk1o, mode = "undirected", diag = FALSE)

net.fam.sid.pos.uk1i <- graph.adjacency(adj.fam.sid.pos.uk1i, mode = "undirected", diag = FALSE)
net.fam.sid.pos.uk1o <- graph.adjacency(adj.fam.sid.pos.uk1o, mode = "undirected", diag = FALSE)

#upper keys 2
net.fam.sid.pre.uk2i <- graph.adjacency(adj.fam.sid.pre.uk2i, mode = "undirected", diag = FALSE)
net.fam.sid.pre.uk2o <- graph.adjacency(adj.fam.sid.pre.uk2o, mode = "undirected", diag = FALSE)

net.fam.sid.irm.uk2i <- graph.adjacency(adj.fam.sid.irm.uk2i, mode = "undirected", diag = FALSE)
net.fam.sid.irm.uk2o <- graph.adjacency(adj.fam.sid.irm.uk2o, mode = "undirected", diag = FALSE)

net.fam.sid.pos.uk2i <- graph.adjacency(adj.fam.sid.pos.uk2i, mode = "undirected", diag = FALSE)
net.fam.sid.pos.uk2o <- graph.adjacency(adj.fam.sid.pos.uk2o, mode = "undirected", diag = FALSE)
```

### Global clustering coefficient

```{r}
#lower keys 1
#change local to global if you want one value..
clus.fam.sid.pre.lk1i <- transitivity(net.fam.sid.pre.lk1i, type = "local")
hist(clus.fam.sid.pre.lk1i)
clus.fam.sid.pre.lk1o <- transitivity(net.fam.sid.pre.lk1o, type = "local")
hist(clus.fam.sid.pre.lk1o)
clus.df <- data.frame(c(clus.fam.sid.pre.lk1i,clus.fam.sid.pre.lk1o))
colnames(clus.df) <- c("clus.num")
clus.df$samp <- c(rep("lk1i",195),rep("lk1o",292))

ggplot(clus.df,aes(x=samp,y=clus.num))+
  geom_violin()

clus.fam.sid.irm.lk1i <- transitivity(net.fam.sid.irm.lk1i, type = "global")
clus.fam.sid.irm.lk1o <- transitivity(net.fam.sid.irm.lk1o, type = "global")

clus.fam.sid.pre.lk1i <- transitivity(net.fam.sid.pre.lk1i, type = "global")
clus.fam.sid.pre.lk1o <- transitivity(net.fam.sid.pre.lk1o, type = "global")
#weird results
```

### Network metrics - centrality

```{r}
cen.sid.lk1i.15 <- eigen_centrality(net_sid.lk1i.15)$vector
cen.sid.lk1i.15.sorted <- sort(cen.sid.lk1i.15,decreasing=TRUE)
cen.sid.lk1i.15.top10 <- cen.sid.lk1i.15.sorted[1:10]

cen.sid.lk1i.15.top10.df <- data.frame(cen.sid.lk1i.15.top10)
cen.sid.lk1i.15.top10.df$sqs <- row.names(cen.sid.lk1i.15.top10.df)

bar.cen.sid.lk1i.15 <- ggplot(cen.sid.lk1i.15.top10.df,aes(x=sqs,y=cen.sid.lk1i.15.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1o.15 <- eigen_centrality(net_sid.lk1o.15)$vector
cen.sid.lk1o.15.sorted <- sort(cen.sid.lk1o.15,decreasing=TRUE)
cen.sid.lk1o.15.top10 <- cen.sid.lk1o.15.sorted[1:10]

cen.sid.lk1o.15.top10.df <- data.frame(cen.sid.lk1o.15.top10)
cen.sid.lk1o.15.top10.df$sqs <- row.names(cen.sid.lk1o.15.top10.df)

bar.cen.sid.lk1o.15 <- ggplot(cen.sid.lk1o.15.top10.df,aes(x=sqs,y=cen.sid.lk1o.15.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1o.17 <- eigen_centrality(net_sid.lk1o.17)$vector
cen.sid.lk1o.17.sorted <- sort(cen.sid.lk1o.17,decreasing=TRUE)
cen.sid.lk1o.17.top10 <- cen.sid.lk1o.17.sorted[1:10]

cen.sid.lk1o.17.top10.df <- data.frame(cen.sid.lk1o.17.top10)
cen.sid.lk1o.17.top10.df$sqs <- row.names(cen.sid.lk1o.17.top10.df)

bar.cen.sid.lk1o.17 <- ggplot(cen.sid.lk1o.17.top10.df,aes(x=sqs,y=cen.sid.lk1o.17.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1i.17 <- eigen_centrality(net_sid.lk1i.17)$vector
cen.sid.lk1i.17.sorted <- sort(cen.sid.lk1i.17,decreasing=TRUE)
cen.sid.lk1i.17.top10 <- cen.sid.lk1i.17.sorted[1:10]

cen.sid.lk1i.17.top10.df <- data.frame(cen.sid.lk1i.17.top10)
cen.sid.lk1i.17.top10.df$sqs <- row.names(cen.sid.lk1i.17.top10.df)

bar.cen.sid.lk1i.17 <- ggplot(cen.sid.lk1i.17.top10.df,aes(x=sqs,y=cen.sid.lk1i.17.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1o.18 <- eigen_centrality(net_sid.lk1o.18)$vector
cen.sid.lk1o.18.sorted <- sort(cen.sid.lk1o.18,decreasing=TRUE)
cen.sid.lk1o.18.top10 <- cen.sid.lk1o.18.sorted[1:10]

cen.sid.lk1o.18.top10.df <- data.frame(cen.sid.lk1o.18.top10)
cen.sid.lk1o.18.top10.df$sqs <- row.names(cen.sid.lk1o.18.top10.df)

bar.cen.sid.lk1o.18 <- ggplot(cen.sid.lk1o.18.top10.df,aes(x=sqs,y=cen.sid.lk1o.18.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1i.18 <- eigen_centrality(net_sid.lk1i.18)$vector
cen.sid.lk1i.18.sorted <- sort(cen.sid.lk1i.18,decreasing=TRUE)
cen.sid.lk1i.18.top10 <- cen.sid.lk1i.18.sorted[1:10]

cen.sid.lk1i.18.top10.df <- data.frame(cen.sid.lk1i.18.top10)
cen.sid.lk1i.18.top10.df$sqs <- row.names(cen.sid.lk1i.18.top10.df)

bar.cen.sid.lk1i.18 <- ggplot(cen.sid.lk1i.18.top10.df,aes(x=sqs,y=cen.sid.lk1i.18.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

ggarrange(bar.cen.sid.lk1i.15,bar.cen.sid.lk1o.15,bar.cen.sid.lk1i.17,bar.cen.sid.lk1o.17,bar.cen.sid.lk1i.18,bar.cen.sid.lk1o.18,ncol=2,nrow=3)
```

## Degree distribution

```{r}
# Degree distribution
deg.dist <- degree_distribution(net.fam.sid.pre.lk1i, mode = "all", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("sid.pre.lk1i",length(deg.dist))
deg.sid.pre.lk1i <- data.frame(deg.dist,num,treat)

deg.dist <- degree_distribution(net.fam.sid.pre.lk1o, mode = "all", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("sid.pre.lk1o",length(deg.dist))
deg.sid.pre.lk1o <- data.frame(deg.dist,num,treat)

deg.sid.pre.lk1 <- rbind(deg.sid.pre.lk1i,deg.sid.pre.lk1o)

#raw
ggplot(deg.sid.pre.lk1,aes(x=num,y=deg.dist,color=treat))+
  geom_point()

# Degree distribution
deg.dist <- degree_distribution(net.fam.sid.pre.lk1i,mode="all", cumulative=F) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("sid.pre.lk1i",length(deg.dist))
deg.sid.pre.lk1i <- data.frame(deg.dist,num,treat)

deg.dist <- degree_distribution(net.fam.sid.pre.lk1o, mode = "all", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("sid.pre.lk1o",length(deg.dist))
deg.sid.pre.lk1o <- data.frame(deg.dist,num,treat)

ggplot(deg.sid.pre.lk1,aes(x=num,y=deg.dist,color=treat))+
  geom_point()

#now log
deg.sid.pre.lk1$deg.dist.log <- log(deg.sid.pre.lk1$deg.dist)
ggplot(deg.sid.pre.lk1,aes(x=treat,y=deg.dist.log,color=treat))+
  geom_boxplot()+
  geom_jitter()

ggplot(deg.sid.pre.lk1,aes(x=num,y=deg.dist.log,color=treat))+
  geom_point()
```

```{r}
btn.sid.lk1i.15 <- igraph::betweenness(net_sid.lk1i.15)
btn.sid.lk1i.15.sorted <- sort(btn.sid.lk1i.15,decreasing=TRUE)
btn.sid.lk1i.15.top10 <- btn.sid.lk1i.15.sorted[1:10]

btn.sid.lk1o.15 <- igraph::betweenness(net_sid.lk1o.15)
btn.sid.lk1o.15.sorted <- sort(btn.sid.lk1o.15,decreasing=TRUE)
btn.sid.lk1o.15.top10 <- btn.sid.lk1o.15.sorted[1:10]

names(btn.sid.lk1i.15.top10) %in% names(btn.sid.lk1o.15.top10)

btn.sid.lk1i.17 <- igraph::betweenness(net_sid.lk1i.17)
btn.sid.lk1i.17.sorted <- sort(btn.sid.lk1i.17,decreasing=TRUE)
btn.sid.lk1i.17.top10 <- btn.sid.lk1i.17.sorted[1:10]

btn.sid.lk1o.17 <- igraph::betweenness(net_sid.lk1o.17)
btn.sid.lk1o.17.sorted <- sort(btn.sid.lk1o.17,decreasing=TRUE)
btn.sid.lk1o.17.top10 <- btn.sid.lk1o.17.sorted[1:10]

names(btn.sid.lk1i.17.top10) %in% names(btn.sid.lk1o.17.top10)

btn.sid.lk1i.18 <- igraph::betweenness(net_sid.lk1i.18)
btn.sid.lk1i.18.sorted <- sort(btn.sid.lk1i.18,decreasing=TRUE)
btn.sid.lk1i.18.top10 <- btn.sid.lk1i.18.sorted[1:10]

btn.sid.lk1o.18 <- igraph::betweenness(net_sid.lk1o.18)
btn.sid.lk1o.18.sorted <- sort(btn.sid.lk1o.18,decreasing=TRUE)
btn.sid.lk1o.18.top10 <- btn.sid.lk1o.18.sorted[1:10]

names(btn.sid.lk1i.18.top10) %in% names(btn.sid.lk1o.18.top10)

#17 v 18
names(btn.sid.lk1i.18.top10) %in% names(btn.sid.lk1i.17.top10)

#18 v 15
names(btn.sid.lk1i.18.top10) %in% names(btn.sid.lk1i.15.top10)

#17 v 15
names(btn.sid.lk1i.17.top10) %in% names(btn.sid.lk1i.15.top10)

btn.sid.lk1i.17.top10.df <- data.frame(btn.sid.lk1i.17.top10)
btn.sid.lk1i.17.top10.df$sqs <- row.names(btn.sid.lk1i.17.top10.df)

btn.sid.lk1i.15.top10.df <- data.frame(btn.sid.lk1i.15.top10)
btn.sid.lk1i.15.top10.df$sqs <- row.names(btn.sid.lk1i.15.top10.df)

ggplot(btn.sid.lk1i.15.top10.df,aes(x=sqs,y=btn.sid.lk1i.15.top10))+
  geom_bar(stat="identity")

ggplot(btn.sid.lk1i.17.top10.df,aes(x=sqs,y=btn.sid.lk1i.17.top10))+
  geom_bar(stat="identity")

ggplot(btn.sid.lk1i.17.top10.df,aes(x=sqs,y=btn.sid.lk1i.17.top10))+
  geom_bar(stat="identity")
ggplot(btn.sid.lk1i.15.top10.df,aes(x=sqs,y=btn.sid.lk1i.17.top10))+
  geom_bar(stat="identity")

ggplot(btn.sid.lk1i.17.top10.df,aes(x=row.names,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Eigenvector centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2015 & 2016 (pre-Irma)")+
  geom_hline(yintercept=0.7885872,color="#781C6D")


btwn.15.tosort$vector <- btwn.15.tosort$betweenness.net_15.
btwn.15.sorted <- btwn.15.tosort[order(-btwn.15.tosort$vector),]
btwn.15.sorted$sqs <- rownames(btwn.15.sorted)
btwn.15.top10 <- btwn.15.sorted[1:10,]
sqs_order <- btwn.15.top10$sqs
btwn.15.top10$sqs <- factor(btwn.15.top10$sqs,levels=sqs_order)



plot(deg.dist, xlab = "Nodes degree", ylab = "Probability") 
lines(deg.dist)
# qgraph method
centralityPlot(net_sid.lk1i.15)
```

```{r older}
# Hub detection
#net_15.cn <- closeness(net_15)
#net_15.bn <- betweenness(net_15) 
#net_15.pr <- page_rank(net_15)$vector 
net_sid.lk1i.15.hs <- hub_score(net_sid.lk1i.15)$vector
net_sid.lk1i.15.hs.sort <- sort(net_sid.lk1i.15.hs, decreasing = TRUE)
net_sid.lk1i.15.hs.top5 <- head(net_sid.lk1i.15.hs.sort, n = 5)
net_sid.lk1i.15.hs.top5

net_17.cn <- closeness(net_17)
net_17.bn <- betweenness(net_17) 
net_17.pr <- page_rank(net_17)$vector
net_17.hs <- hub_score(net_17)$vector
net_17.hs.sort <- sort(net_17.hs, decreasing = TRUE)
net_17.hs.top5 <- head(net_17.hs.sort, n = 5)

net_18.cn <- closeness(net_18)
net_18.bn <- betweenness(net_18) 
net_18.pr <- page_rank(net_18)$vector 
net_18.hs <- hub_score(net_18)$vector
net_18.hs.sort <- sort(net_18.hs, decreasing = TRUE)
net_18.hs.top5 <- head(net_18.hs.sort, n = 5)
```

### Eigenvector centrality

```{r network metrics 1}
eigen.15 <- eigen_centrality(net_15)
eigen.15.tosort <- data.frame(eigen.15[["vector"]])
eigen.15.tosort$vector <- eigen.15.tosort$eigen.15...vector...
eigen.15.sorted <- eigen.15.tosort[order(-eigen.15.tosort$vector),]
eigen.15.sorted$sqs <- rownames(eigen.15.sorted)
eigen.15.top10 <- eigen.15.sorted[1:10,]
sqs_order <- eigen.15.top10$sqs
eigen.15.top10$sqs <- factor(eigen.15.top10$sqs,levels=sqs_order)

eigen.17 <- eigen_centrality(net_17)
eigen.17.tosort <- data.frame(eigen.17[["vector"]])
eigen.17.tosort$vector <- eigen.17.tosort$eigen.17...vector...
eigen.17.sorted <- eigen.17.tosort[order(-eigen.17.tosort$vector),]
eigen.17.sorted$sqs <- rownames(eigen.17.sorted)
eigen.17.top10 <- eigen.17.sorted[1:10,]
sqs_order <- eigen.17.top10$sqs
eigen.17.top10$sqs <- factor(eigen.17.top10$sqs,levels=sqs_order)

eigen.18 <- eigen_centrality(net_18)
eigen.18.tosort <- data.frame(eigen.18[["vector"]])
eigen.18.tosort$vector <- eigen.18.tosort$eigen.18...vector...
eigen.18.sorted <- eigen.18.tosort[order(-eigen.18.tosort$vector),]
eigen.18.sorted$sqs <- rownames(eigen.18.sorted)
eigen.18.top10 <- eigen.18.sorted[1:10,]
sqs_order <- eigen.18.top10$sqs
eigen.18.top10$sqs <- factor(eigen.18.top10$sqs,levels=sqs_order)

ggplot(eigen.15.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Eigenvector centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2015 & 2016 (pre-Irma)")+
  geom_hline(yintercept=0.7885872,color="#781C6D")

ggplot(eigen.17.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Eigenvector centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2017 (Irma)")+
  geom_hline(yintercept=0.7885872,color="#781C6D")+
  geom_hline(yintercept=0.7140983,color="#AE305C")

ggplot(eigen.18.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Eigenvector centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2018 (post-Irma)")+
  geom_hline(yintercept=0.7140983,color="#AE305C")
```

### Betweenness centrality

```{r network networks 2}
btwn.15.tosort <- data.frame(betweenness(net_15))
btwn.15.tosort$vector <- btwn.15.tosort$betweenness.net_15.
btwn.15.sorted <- btwn.15.tosort[order(-btwn.15.tosort$vector),]
btwn.15.sorted$sqs <- rownames(btwn.15.sorted)
btwn.15.top10 <- btwn.15.sorted[1:10,]
sqs_order <- btwn.15.top10$sqs
btwn.15.top10$sqs <- factor(btwn.15.top10$sqs,levels=sqs_order)

btwn.17.tosort <- data.frame(betweenness(net_17))
btwn.17.tosort$vector <- btwn.17.tosort$betweenness.net_17.
btwn.17.sorted <- btwn.17.tosort[order(-btwn.17.tosort$vector),]
btwn.17.sorted$sqs <- rownames(btwn.17.sorted)
btwn.17.top10 <- btwn.17.sorted[1:10,]
sqs_order <- btwn.17.top10$sqs
btwn.17.top10$sqs <- factor(btwn.17.top10$sqs,levels=sqs_order)

btwn.18.tosort <- data.frame(betweenness(net_18))
btwn.18.tosort$vector <- btwn.18.tosort$betweenness.net_18.
btwn.18.sorted <- btwn.18.tosort[order(-btwn.18.tosort$vector),]
btwn.18.sorted$sqs <- rownames(btwn.18.sorted)
btwn.18.top10 <- btwn.18.sorted[1:10,]
sqs_order <- btwn.18.top10$sqs
btwn.18.top10$sqs <- factor(btwn.18.top10$sqs,levels=sqs_order)

ggplot(btwn.15.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Betweenness centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2015 & 2016 (pre-Irma)")

ggplot(btwn.17.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Betweenness centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2017 (Irma)")

ggplot(btwn.18.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Betweenness centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2018 (post-Irma)")
```

```{r}
?cohesion()

```

# Cohesion

## Read in data & scripts

```{r}
# Read in dataset
## Data should be in a matrix where each row is a sample. 
#couldn't get cohesion function to work, will run here then save results

#note: make out.df in code chunk below. It's bad organization, I know. 

b <- readRDS("./files/seq.tables/seq.fam.sid.pre.lk1.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.lk1i.rds")

# b <- readRDS("./files/seq.tables/seq.fam.sid.pre.lk1.off.no2.rds")
# saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.lk1o.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pre.uk1.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.uk1i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pre.uk1.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.uk1o.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pre.uk2.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.uk2i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pre.uk2.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.uk2o.rds")
```

## Cohesion code chunk

```{r, eval=F}
source("cohesion.R")

## Choose a persistence cutoff (min. fraction of taxon presence) for retaining taxa in the analysis
pers.cutoff <- 0.10
## Decide the number of iterations to run for each taxon. (>= 200 is recommended)
# Larger values of iter mean the script takes longer to run
iter <- 200
## Decide whether to use taxon/column shuffle (tax.shuffle = T) or row shuffle algorithm (tax.shuffle = F)
tax.shuffle <- T
## Option to input your own correlation table
# Note that your correlation table MUST have the same number of taxa as the abundance table. There should be no empty (all zero) taxon vectors in the abundance table. 
# Even if you input your own correlation table, the persistence cutoff will be applied
use.custom.cors <- F

###################################################################
###################################################################

# Read in custom correlation matrix, if desired. Must set "use.custom.cors" to TRUE
if(use.custom.cors == T) {
  custom.cor.mat <- read.csv("your_path_here.csv", header = T, row.names = 1)
  custom.cor.mat <- as.matrix(custom.cor.mat)
  #Check that correlation matrix and abundance matrix have the same dimension
  print(dim(b)[2] == dim(custom.cor.mat)[2])
}

# Suggested steps to re-format data. At the end of these steps, the data should be in a matrix "c" where there are no empty samples or blank taxon columns. 
c <- as.matrix(b)
c <- c[rowSums(c) > 0, colSums(c) > 0]

# Optionally re-order dataset to be in chronological order. Change date format for your data. 
#c <- c[order(as.Date(rownames(c), format = "%m/%d/%Y")), ]

# Save total number of individuals in each sample in the original matrix. This will be 1 if data are in relative abundance, but not if matrix c is count data
rowsums.orig <- rowSums(c)

# Based on persistence cutoff, define a cutoff for the number of zeroes allowed in a taxon's distribution
zero.cutoff <- ceiling(pers.cutoff * dim(c)[1])

# Remove taxa that are below the persistence cutoff
d <- c[ , apply(c, 2, zero) < (dim(c)[1]-zero.cutoff) ]
# Remove any samples that no longer have any individuals, due to removing taxa
d <- d[rowSums(d) > 0, ]

#If using custom correlation matrix, need to remove rows/columns corresponding to the taxa below persistence cutoff
if(use.custom.cors == T){
  custom.cor.mat.sub <- custom.cor.mat[apply(c, 2, zero) < (dim(c)[1]-zero.cutoff), apply(c, 2, zero) < (dim(c)[1]-zero.cutoff)]
}

# Create relative abundance matrix.  
rel.d <- d / rowsums.orig
# Optionally, check to see what proportion of the community is retained after cutting out taxa
hist(rowSums(rel.d))

# Create observed correlation matrix
cor.mat.true <- cor(rel.d)

# Create vector to hold median otu-otu correlations for initial otu
med.tax.cors <- vector()

# Run this loop for the null model to get expected pairwise correlations
# Bypass null model if the option to input custom correlation matrix is TRUE
if(use.custom.cors == F) {
  ifelse(tax.shuffle, {
    for(which.taxon in 1:dim(rel.d)[2]){
      
      #create vector to hold correlations from every permutation for each single otu
      ## perm.cor.vec.mat stands for permuted correlations vector matrix
      perm.cor.vec.mat <- vector()
      
      for(i in 1:iter){
        #Create empty matrix of same dimension as rel.d
        perm.rel.d <- matrix(numeric(0), dim(rel.d)[1], dim(rel.d)[2])
        rownames(perm.rel.d) <- rownames(rel.d)
        colnames(perm.rel.d) <- colnames(rel.d)
        
        #For each otu
        for(j in 1:dim(rel.d)[2]){ 
          # Replace the original taxon vector with a permuted taxon vector
          perm.rel.d[, j ] <- sample(rel.d[ ,j ]) 
        }
        
        # Do not randomize focal column 
        perm.rel.d[, which.taxon] <- rel.d[ , which.taxon]
        
        # Calculate correlation matrix of permuted matrix
        cor.mat.null <- cor(perm.rel.d)
        
        # For each iteration, save the vector of null matrix correlations between focal taxon and other taxa
        perm.cor.vec.mat <- cbind(perm.cor.vec.mat, cor.mat.null[, which.taxon])
        
      }
      # Save the median correlations between the focal taxon and all other taxa  
      med.tax.cors <- cbind(med.tax.cors, apply(perm.cor.vec.mat, 1, median))
      
      # For large datasets, this can be helpful to know how long this loop will run
      if(which.taxon %% 20 == 0){print(which.taxon)}
    }
  } , {
    for(which.taxon in 1:dim(rel.d)[2]){
      
      #create vector to hold correlations from every permutation for each single otu
      ## perm.cor.vec.mat stands for permuted correlations vector matrix
      perm.cor.vec.mat <- vector()
      
      for(i in 1:iter){
        #Create duplicate matrix to shuffle abundances
        perm.rel.d <- rel.d 
        
        #For each taxon
        for(j in 1:dim(rel.d)[1]){ 
          which.replace <- which(rel.d[j, ] > 0 ) 
          # if the focal taxon is greater than zero, take it out of the replacement vector, so the focal abundance stays the same
          which.replace.nonfocal <- which.replace[!(which.replace %in% which.taxon)]
          
          #Replace the original taxon vector with a vector where the values greater than 0 have been randomly permuted 
          perm.rel.d[j, which.replace.nonfocal] <- sample(rel.d[ j, which.replace.nonfocal]) 
        }
        
        # Calculate correlation matrix of permuted matrix
        cor.mat.null <- cor(perm.rel.d)
        
        # For each iteration, save the vector of null matrix correlations between focal taxon and other taxa
        perm.cor.vec.mat <- cbind(perm.cor.vec.mat, cor.mat.null[, which.taxon])
        
      }
      # Save the median correlations between the focal taxon and all other taxa  
      med.tax.cors <- cbind(med.tax.cors, apply(perm.cor.vec.mat, 1, median))
      
      # For large datasets, this can be helpful to know how long this loop will run
      if(which.taxon %% 20 == 0){print(which.taxon)}
    }
  }
  )
}

# Save observed minus expected correlations. Use custom correlations if use.custom.cors = TRUE
ifelse(use.custom.cors == T, {
  obs.exp.cors.mat <- custom.cor.mat.sub}, {
    obs.exp.cors.mat <- cor.mat.true - med.tax.cors
  }
)

diag(obs.exp.cors.mat) <- 0

#### 
#### Produce desired vectors of connectedness and cohesion 

# Calculate connectedness by averaging positive and negative observed - expected correlations
connectedness.pos <- apply(obs.exp.cors.mat, 2, pos.mean)
connectedness.neg <- apply(obs.exp.cors.mat, 2, neg.mean)

# Calculate cohesion by multiplying the relative abundance dataset by associated connectedness
cohesion.pos <- rel.d %*% connectedness.pos
cohesion.neg <- rel.d %*% connectedness.neg

####
#### Combine vectors into one list and print 
output <- list(connectedness.neg, connectedness.pos, cohesion.neg, cohesion.pos)
names(output) <- c("Negative Connectedness", "Positive Connectedness", "Negative Cohesion", "Positive Cohesion")
print(output)

#saving output a different way
coh.neg <- output[["Negative Cohesion"]]
coh.pos <- output[["Positive Cohesion"]]
row.names(coh.neg)==row.names(coh.pos)

out.df <- data.frame(coh.neg,coh.pos)
```

## Cohesion results

```{r}
library(ggplot2)
library(cowplot)
library(ggpubr)

setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_16s/05.networks/files/cohesion")
```

Ran once then re-read in later

```{r cohesion results, eval=F}
df.coh.sid.lk1i <- readRDS("df.cohesion.sid.lk1i.rds")
df.coh.sid.lk1o <- readRDS("df.cohesion.sid.lk1o.rds")
df.coh.sid.uk1i <- readRDS("df.cohesion.sid.uk1i.rds")
df.coh.sid.uk1o <- readRDS("df.cohesion.sid.uk1o.rds")
df.coh.sid.uk2i <- readRDS("df.cohesion.sid.uk2i.rds")
df.coh.sid.uk2o <- readRDS("df.cohesion.sid.uk2o.rds")

df.coh.sid.lk1i$year <- 

df.list <- list(df1,df2,...)
res <- lapply(df.list, function(x) rowMeans(subset(x, select = c(start, stop)), na.rm = TRUE))
# to keep the original data.frame also
res <- lapply(df.list, function(x) cbind(x,"rowmean"=rowMeans(subset(x, select = c(start, stop)), na.rm = TRUE)))
  
negco15$year <- c(rep("2015",57))
negco17$year <- c(rep("2017",56))
negco18$year <- c(rep("2018",28))

posco15$year <- c(rep("2015",57))
posco17$year <- c(rep("2017",56))
posco18$year <- c(rep("2018",28))

neg1517 <- rbind(negco15, negco17)
neg.all <- rbind(neg1517, negco18)

pos1517 <- rbind(posco15, posco17)
pos.all <- rbind(pos1517, posco18)

pos.all <- unname(pos.all)
colnames(pos.all) <- c("cohesion","year")

neg.all <- unname(neg.all)
colnames(neg.all) <- c("cohesion","year")

gg.pos <- ggplot(pos.all,aes(x=year,y=cohesion,color=year))+
  geom_boxplot()+
  scale_color_manual(name="Time point",values=c("#781C6D","#F8850F","#AE305C"),labels=c("Pre-Irma","Irma","Post-Irma"))+
  theme_cowplot()+
  xlab('Year')+
  ylab('Cohesion')
gg.pos

gg.neg <- ggplot(neg.all,aes(x=year,y=cohesion,color=year))+
  geom_boxplot()+
  scale_color_manual(name="Time point",values=c("#781C6D","#F8850F","#AE305C"),labels=c("Pre-Irma","Irma","Post-Irma"))+
  theme_cowplot()+
  xlab('Year')+
  ylab('Cohesion')
gg.neg

quartz()
ggarrange(gg.pos,gg.neg,ncol=2,common.legend=TRUE,legend="left")

#stats
neg.all$year <- as.factor(neg.all$year)

shapiro.test(neg.all$cohesion)
neg.all$coh.log <- log(abs(neg.all$cohesion))
shapiro.test(neg.all$coh.log)
kruskal.test(cohesion~year,data=neg.all)

#install.packages("dunn.test")
#library(dunn.test)
dunn.test(neg.all$cohesion,neg.all$year,method="bh")
str(neg.all)

#stats pos
pos.all$year <- as.factor(pos.all$year)

shapiro.test(pos.all$cohesion)
pos.all$coh.log <- log(abs(pos.all$cohesion))
shapiro.test(pos.all$coh.log)
kruskal.test(cohesion~year,data=pos.all)

#install.packages("dunn.test")
#library(dunn.test)
dunn.test(pos.all$cohesion,pos.all$year,method="bh")
str(pos.all)
```


