---
title: "fl16s_networks"
author: "Nicola Kriefall"
date: "06/03/2022"
output: html_document
---

# Setup

## Load libraries

```{r libraries}
library("devtools")
library("stringr")
#install_github("zdk123/SpiecEasi")
#library(SpiecEasi)
#library(igraph)
#library(vegan)
#library(Matrix)
#library(reshape2)
#library(plyr)
library(dplyr)
library(gridExtra)
library(grid)
#library(microbiome)

setwd("~/nicfall@bu.edu - Google Drive/My Drive/Flirma/flirma_networks_master/fl_16s/05.networks")
```

### Extra function

```{r extra 'not in' function}
#extra function
# load in the following function
'%!in%' <- function(x,y) {
!('%in%'(x,y))
}
# END
```

## Read in & process data

```{r}
ps.cleaner <- readRDS("../01.generate_asv_table/fl16s.ps.cleaner.rd3.rds")

tax <- as.data.frame(ps.cleaner@tax_table@.Data)

tax.clean <- data.frame(row.names = row.names(tax),
                        Kingdom = str_replace(tax[,1], "D_0__",""),
                        Phylum = str_replace(tax[,2], "D_1__",""),
                        Class = str_replace(tax[,3], "D_2__",""),
                        Order = str_replace(tax[,4], "D_3__",""),
                        Family = str_replace(tax[,5], "D_4__",""),
                        Genus = str_replace(tax[,6], "D_5__",""),
                        Species = str_replace(tax[,7], "D_6__",""),
                        stringsAsFactors = FALSE)
tax.clean[is.na(tax.clean)] <- ""

for (i in 1:7){ tax.clean[,i] <- as.character(tax.clean[,i])}
####### Fill holes in the tax table
tax.clean[is.na(tax.clean)] <- ""
for (i in 1:nrow(tax.clean)){
  if (tax.clean[i,2] == ""){
    kingdom <- paste("Kingdom_", tax.clean[i,1], sep = "")
    tax.clean[i, 2:7] <- kingdom
  } else if (tax.clean[i,3] == ""){
    phylum <- paste("Phylum_", tax.clean[i,2], sep = "")
    tax.clean[i, 3:7] <- phylum
  } else if (tax.clean[i,4] == ""){
    class <- paste("Class_", tax.clean[i,3], sep = "")
    tax.clean[i, 4:7] <- class
  } else if (tax.clean[i,5] == ""){
    order <- paste("Order_", tax.clean[i,4], sep = "")
    tax.clean[i, 5:7] <- order
  } else if (tax.clean[i,6] == ""){
    family <- paste("Family_", tax.clean[i,5], sep = "")
    tax.clean[i, 6:7] <- family
  } else if (tax.clean[i,7] == ""){
    tax.clean$Species[i] <- paste("Genus",tax.clean$Genus[i], sep = "_")
  }
}

tax_table(ps.cleaner) <- as.matrix(tax.clean)

#ps.clean.gen <- tax_glom(ps.clean,"Genus")
#ps.otu.gen <- data.frame(ps.clean.gen@otu_table)

#family
ps.clean.fam <- tax_glom(ps.cleaner,"Family")

ps.clean.fam.sid <- subset_samples(ps.clean.fam,spp=="ssid")
ps.clean.fam.rad <- subset_samples(ps.clean.fam,spp=="srad")

ps.clean.fam.sid.no0 <- prune_taxa(taxa_sums(ps.clean.fam.sid) > 0, ps.clean.fam.sid) 
# otu_table()   OTU Table:         [ 489 taxa and 201 samples ]
# sample_data() Sample Data:       [ 201 samples by 9 sample variables ]
# tax_table()   Taxonomy Table:    [ 489 taxa by 7 taxonomic ranks ]
ps.clean.fam.rad.no0 <- prune_taxa(taxa_sums(ps.clean.fam.rad) > 0, ps.clean.fam.rad) 
# otu_table()   OTU Table:         [ 486 taxa and 155 samples ]
# sample_data() Sample Data:       [ 155 samples by 9 sample variables ]
# tax_table()   Taxonomy Table:    [ 486 taxa by 7 taxonomic ranks ]
```

## Subset for sites/years{.tabset}

### S. siderea

```{r}
seq.sid <- data.frame(ps.clean.fam.sid.no0@otu_table)
df.sid <- data.frame(ps.clean.fam.sid.no0@sam_data)
row.names(df.sid)==row.names(seq.sid)

#LK1 in & off
df.sid.lk1i <- subset(df.sid,site_zone=="LK1-I")
df.sid.lk1o <- subset(df.sid,site_zone=="LK1-O")

names.lk1i <- c(row.names(df.sid.lk1i))
names.lk1o <- c(row.names(df.sid.lk1o))

seq.sid.lk1i <- seq.sid[c(names.lk1i),]
seq.sid.lk1o <- seq.sid[c(names.lk1o),]

#subset for years
df.sid.lk1i.18 <- subset(df.sid.lk1i,year=="2018")
df.sid.lk1i.17 <- subset(df.sid.lk1i,year=="2017")
df.sid.lk1i.15 <- subset(df.sid.lk1i,year=="2016")

df.sid.lk1o.18 <- subset(df.sid.lk1o,year=="2018")
df.sid.lk1o.17 <- subset(df.sid.lk1o,year=="2017")
df.sid.lk1o.15 <- subset(df.sid.lk1o,year=="2015")

names.lk1i.18 <- c(row.names(df.sid.lk1i.18))
names.lk1i.17 <- c(row.names(df.sid.lk1i.17))
names.lk1i.15 <- c(row.names(df.sid.lk1i.15))

names.lk1o.18 <- c(row.names(df.sid.lk1o.18))
names.lk1o.17 <- c(row.names(df.sid.lk1o.17))
names.lk1o.15 <- c(row.names(df.sid.lk1o.15))

seq.sid.lk1i.18 <- seq.sid[c(names.lk1i.18),]
seq.sid.lk1i.17 <- seq.sid[c(names.lk1i.17),]
seq.sid.lk1i.15 <- seq.sid[c(names.lk1i.15),]

seq.sid.lk1o.18 <- seq.sid[c(names.lk1o.18),]
seq.sid.lk1o.17 <- seq.sid[c(names.lk1o.17),]
seq.sid.lk1o.15 <- seq.sid[c(names.lk1o.15),]
```

#### Cleaning lower reads

Some data cleaning: authors recommend removing samples with less than an average of 2 reads per column. 

```{r}
seq.sid.lk1i.18.no2 <- seq.sid.lk1i.18[,-which(colMeans(seq.sid.lk1i.18) <= 2)]
seq.sid.lk1i.17.no2 <- seq.sid.lk1i.17[,-which(colMeans(seq.sid.lk1i.17) <= 2)]
seq.sid.lk1i.15.no2 <- seq.sid.lk1i.15[,-which(colMeans(seq.sid.lk1i.15) <= 2)]

seq.sid.lk1o.18.no2 <- seq.sid.lk1o.18[,-which(colMeans(seq.sid.lk1o.18) <= 2)]
seq.sid.lk1o.17.no2 <- seq.sid.lk1o.17[,-which(colMeans(seq.sid.lk1o.17) <= 2)]
seq.sid.lk1o.15.no2 <- seq.sid.lk1o.15[,-which(colMeans(seq.sid.lk1o.15) <= 2)]

# otu.lk1i.18.no0 <- otu.lk1i.18[,c(colSums(otu.lk1i.18)>0)]
# otu.lk1i.17.no0 <- otu.lk1i.18[,c(colSums(otu.lk1i.17)>0)]
# otu.lk1i.15.no0 <- otu.lk1i.18[,c(colSums(otu.lk1i.15)>0)]
# 
# otu.lk1o.18.no0 <- otu.lk1o.18[,c(colSums(otu.lk1o.18)>0)]
# otu.lk1o.17.no0 <- otu.lk1o.18[,c(colSums(otu.lk1o.17)>0)]
# otu.lk1o.15.no0 <- otu.lk1o.18[,c(colSums(otu.lk1o.15)>0)]

#otu.lk1o.15.no0.m <- as.matrix(otu.lk1o.15.no0)
```

### S. radians

```{r}
```

# Networks

## Setup

Begin by installing & loading necessary packages.

(Overall pipeline & scripts followed is sourced from [here; Layeghifard *et al*., 2018, *Methods in Molecular Biology*](https://www-ncbi-nlm-nih-gov.ezproxy.bu.edu/pubmed/30298259))

```{r packages, message=FALSE}
# Install Required packages 
#install.packages("igraph") 
library("igraph")
#install.packages("qgraph") 
library("qgraph")
#install.packages("MCL")
library("MCL")
#install.packages("vegan")
library("vegan")
# Install SpiecEasi package 
#install.packages("devtools") 
library("devtools") 
#install_github("zdk123/SpiecEasi")
library("SpiecEasi")
library("ggplot2")
library("ggpubr")
#devtools::install_github("briatte/ggnet")
library(ggnet)
```

## Building adjacency matrix & network

Building an adjacency matrix of correlations of the abundances of bacterial families, one per sampling year. 

```{r build network}
# SparCC network
sparcc.matrix_sid.lk1i.18 <- sparcc(seq.sid.lk1i.18.no2)
sparcc.matrix_sid.lk1o.18 <- sparcc(seq.sid.lk1o.18.no2)

sparcc.matrix_sid.lk1i.17 <- sparcc(seq.sid.lk1i.17.no2)
sparcc.matrix_sid.lk1o.17 <- sparcc(seq.sid.lk1o.17.no2)

sparcc.matrix_sid.lk1i.15 <- sparcc(seq.sid.lk1i.15.no2)
sparcc.matrix_sid.lk1o.15 <- sparcc(seq.sid.lk1o.15.no2)

sparcc.cutoff <- 0.7

sparcc.adj_sid.lk1i.15 <- ifelse(abs(sparcc.matrix_sid.lk1i.15$Cor) >= sparcc.cutoff, 1, 0)
sparcc.adj_sid.lk1o.15 <- ifelse(abs(sparcc.matrix_sid.lk1o.15$Cor) >= sparcc.cutoff, 1, 0)

sparcc.adj_sid.lk1i.17 <- ifelse(abs(sparcc.matrix_sid.lk1i.17$Cor) >= sparcc.cutoff, 1, 0)
sparcc.adj_sid.lk1o.17 <- ifelse(abs(sparcc.matrix_sid.lk1o.17$Cor) >= sparcc.cutoff, 1, 0)

sparcc.adj_sid.lk1i.18 <- ifelse(abs(sparcc.matrix_sid.lk1i.18$Cor) >= sparcc.cutoff, 1, 0)
sparcc.adj_sid.lk1o.18 <- ifelse(abs(sparcc.matrix_sid.lk1o.18$Cor) >= sparcc.cutoff, 1, 0)

# Add names to rows and columns
rownames(sparcc.adj_sid.lk1i.15) <- colnames(seq.sid.lk1i.15.no2)
colnames(sparcc.adj_sid.lk1i.15) <- colnames(seq.sid.lk1i.15.no2) 

rownames(sparcc.adj_sid.lk1o.15) <- colnames(seq.sid.lk1o.15.no2)
colnames(sparcc.adj_sid.lk1o.15) <- colnames(seq.sid.lk1o.15.no2) 

rownames(sparcc.adj_sid.lk1i.17) <- colnames(seq.sid.lk1i.17.no2)
colnames(sparcc.adj_sid.lk1i.17) <- colnames(seq.sid.lk1i.17.no2) 

rownames(sparcc.adj_sid.lk1o.17) <- colnames(seq.sid.lk1o.17.no2)
colnames(sparcc.adj_sid.lk1o.17) <- colnames(seq.sid.lk1o.17.no2) 

rownames(sparcc.adj_sid.lk1i.18) <- colnames(seq.sid.lk1i.18.no2)
colnames(sparcc.adj_sid.lk1i.18) <- colnames(seq.sid.lk1i.18.no2) 

rownames(sparcc.adj_sid.lk1o.18) <- colnames(seq.sid.lk1o.18.no2)
colnames(sparcc.adj_sid.lk1o.18) <- colnames(seq.sid.lk1o.18.no2) 
```

## Visualizing network from adjacency matrix

```{r plot net from adj matrix}
"#781C6D" #purple
"#F8850F" #orange
"#AE305C" #burgundy

"#ED7953FF"
"#8405A7FF"

# show_col(viridis_pal(option="A")(3))
# show_col(viridis_pal(option="B")(3))
# show_col(viridis_pal(option="C")(3))
# show_col(viridis_pal(option="D")(3))
# show_col(viridis_pal(option="E")(3))
# show_col(viridis_pal(option="F")(3))
# show_col(viridis_pal(option="G")(3))
# show_col(viridis_pal(option="H")(3))

net.sid.lk1i.15 <- ggnet2(sparcc.adj_sid.lk1i.15,size="degree",size.cut=TRUE,alpha=0.5,color="#ED7953FF",size.min=1)+
  ggtitle('LK inshore baseline')
net.sid.lk1o.15 <- ggnet2(sparcc.adj_sid.lk1o.15,size="degree",size.cut=TRUE,alpha=0.5,color="#8405A7FF",size.min=1)+
  ggtitle('LK offshore baseline')

ggarrange(net.sid.lk1i.15,net.sid.lk1o.15)

net.sid.lk1i.17 <- ggnet2(sparcc.adj_sid.lk1i.17,size="degree",size.cut=TRUE,alpha=0.5,color="#ED7953FF",size.min=1)+
  ggtitle('LK inshore disturbance')
net.sid.lk1o.17 <- ggnet2(sparcc.adj_sid.lk1o.17,size="degree",size.cut=TRUE,alpha=0.5,color="#8405A7FF",size.min=1)+
  ggtitle('LK offshore disturbance')

ggarrange(net.sid.lk1i.17,net.sid.lk1o.17)

net.sid.lk1i.18 <- ggnet2(sparcc.adj_sid.lk1i.18,size="degree",size.cut=TRUE,alpha=0.5,color="#ED7953FF",size.min=1)+
  ggtitle('LK inshore post')
net.sid.lk1o.18 <- ggnet2(sparcc.adj_sid.lk1o.18,size="degree",size.cut=TRUE,alpha=0.5,color="#8405A7FF",size.min=1)+
  ggtitle('LK offshore post')

ggarrange(net.sid.lk1i.18,net.sid.lk1o.18)
```

## All together now

```{r}
ggarrange(net.sid.lk1i.15,net.sid.lk1o.15,net.sid.lk1i.17,net.sid.lk1o.17,net.sid.lk1i.18,net.sid.lk1o.18,ncol=2,nrow=3)
```

## Metrics

```{r}
# Build network from adjacency
net_sid.lk1i.15 <- graph.adjacency(sparcc.adj_sid.lk1i.15, mode = "undirected", diag = FALSE)
net_sid.lk1o.15 <- graph.adjacency(sparcc.adj_sid.lk1o.15, mode = "undirected", diag = FALSE)

net_sid.lk1i.17 <- graph.adjacency(sparcc.adj_sid.lk1i.17, mode = "undirected", diag = FALSE)
net_sid.lk1o.17 <- graph.adjacency(sparcc.adj_sid.lk1o.17, mode = "undirected", diag = FALSE)

net_sid.lk1i.18 <- graph.adjacency(sparcc.adj_sid.lk1i.18, mode = "undirected", diag = FALSE)
net_sid.lk1o.18 <- graph.adjacency(sparcc.adj_sid.lk1o.18, mode = "undirected", diag = FALSE)
```

### Network metrics - centrality

```{r}
cen.sid.lk1i.15 <- eigen_centrality(net_sid.lk1i.15)$vector
cen.sid.lk1i.15.sorted <- sort(cen.sid.lk1i.15,decreasing=TRUE)
cen.sid.lk1i.15.top10 <- cen.sid.lk1i.15.sorted[1:10]

cen.sid.lk1i.15.top10.df <- data.frame(cen.sid.lk1i.15.top10)
cen.sid.lk1i.15.top10.df$sqs <- row.names(cen.sid.lk1i.15.top10.df)

bar.cen.sid.lk1i.15 <- ggplot(cen.sid.lk1i.15.top10.df,aes(x=sqs,y=cen.sid.lk1i.15.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1o.15 <- eigen_centrality(net_sid.lk1o.15)$vector
cen.sid.lk1o.15.sorted <- sort(cen.sid.lk1o.15,decreasing=TRUE)
cen.sid.lk1o.15.top10 <- cen.sid.lk1o.15.sorted[1:10]

cen.sid.lk1o.15.top10.df <- data.frame(cen.sid.lk1o.15.top10)
cen.sid.lk1o.15.top10.df$sqs <- row.names(cen.sid.lk1o.15.top10.df)

bar.cen.sid.lk1o.15 <- ggplot(cen.sid.lk1o.15.top10.df,aes(x=sqs,y=cen.sid.lk1o.15.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1o.17 <- eigen_centrality(net_sid.lk1o.17)$vector
cen.sid.lk1o.17.sorted <- sort(cen.sid.lk1o.17,decreasing=TRUE)
cen.sid.lk1o.17.top10 <- cen.sid.lk1o.17.sorted[1:10]

cen.sid.lk1o.17.top10.df <- data.frame(cen.sid.lk1o.17.top10)
cen.sid.lk1o.17.top10.df$sqs <- row.names(cen.sid.lk1o.17.top10.df)

bar.cen.sid.lk1o.17 <- ggplot(cen.sid.lk1o.17.top10.df,aes(x=sqs,y=cen.sid.lk1o.17.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1i.17 <- eigen_centrality(net_sid.lk1i.17)$vector
cen.sid.lk1i.17.sorted <- sort(cen.sid.lk1i.17,decreasing=TRUE)
cen.sid.lk1i.17.top10 <- cen.sid.lk1i.17.sorted[1:10]

cen.sid.lk1i.17.top10.df <- data.frame(cen.sid.lk1i.17.top10)
cen.sid.lk1i.17.top10.df$sqs <- row.names(cen.sid.lk1i.17.top10.df)

bar.cen.sid.lk1i.17 <- ggplot(cen.sid.lk1i.17.top10.df,aes(x=sqs,y=cen.sid.lk1i.17.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1o.18 <- eigen_centrality(net_sid.lk1o.18)$vector
cen.sid.lk1o.18.sorted <- sort(cen.sid.lk1o.18,decreasing=TRUE)
cen.sid.lk1o.18.top10 <- cen.sid.lk1o.18.sorted[1:10]

cen.sid.lk1o.18.top10.df <- data.frame(cen.sid.lk1o.18.top10)
cen.sid.lk1o.18.top10.df$sqs <- row.names(cen.sid.lk1o.18.top10.df)

bar.cen.sid.lk1o.18 <- ggplot(cen.sid.lk1o.18.top10.df,aes(x=sqs,y=cen.sid.lk1o.18.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

cen.sid.lk1i.18 <- eigen_centrality(net_sid.lk1i.18)$vector
cen.sid.lk1i.18.sorted <- sort(cen.sid.lk1i.18,decreasing=TRUE)
cen.sid.lk1i.18.top10 <- cen.sid.lk1i.18.sorted[1:10]

cen.sid.lk1i.18.top10.df <- data.frame(cen.sid.lk1i.18.top10)
cen.sid.lk1i.18.top10.df$sqs <- row.names(cen.sid.lk1i.18.top10.df)

bar.cen.sid.lk1i.18 <- ggplot(cen.sid.lk1i.18.top10.df,aes(x=sqs,y=cen.sid.lk1i.18.top10))+
  geom_bar(stat="identity")+
  theme_cowplot()

ggarrange(bar.cen.sid.lk1i.15,bar.cen.sid.lk1o.15,bar.cen.sid.lk1i.17,bar.cen.sid.lk1o.17,bar.cen.sid.lk1i.18,bar.cen.sid.lk1o.18,ncol=2,nrow=3)
```

## Degree distribution

```{r}
# Degree distribution
deg.dist <- degree_distribution(net_sid.lk1i.15, mode = "all", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("sid.lk1i.15",length(deg.dist))
deg.dist.sid.lk1i.15.df <- data.frame(deg.dist,num,treat)

deg.dist <- degree_distribution(net_sid.lk1o.15, mode = "all", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("sid.lk1o.15",length(deg.dist))
deg.dist.sid.lk1o.15.df <- data.frame(deg.dist,num,treat)

deg.sid.lk1.15 <- rbind(deg.dist.sid.lk1i.15.df,deg.dist.sid.lk1o.15.df)

ggplot(deg.sid.lk1.15,aes(x=num,y=deg.dist,color=treat))+
  geom_point()
```

```{r}
btn.sid.lk1i.15 <- igraph::betweenness(net_sid.lk1i.15)
btn.sid.lk1i.15.sorted <- sort(btn.sid.lk1i.15,decreasing=TRUE)
btn.sid.lk1i.15.top10 <- btn.sid.lk1i.15.sorted[1:10]

btn.sid.lk1o.15 <- igraph::betweenness(net_sid.lk1o.15)
btn.sid.lk1o.15.sorted <- sort(btn.sid.lk1o.15,decreasing=TRUE)
btn.sid.lk1o.15.top10 <- btn.sid.lk1o.15.sorted[1:10]

names(btn.sid.lk1i.15.top10) %in% names(btn.sid.lk1o.15.top10)

btn.sid.lk1i.17 <- igraph::betweenness(net_sid.lk1i.17)
btn.sid.lk1i.17.sorted <- sort(btn.sid.lk1i.17,decreasing=TRUE)
btn.sid.lk1i.17.top10 <- btn.sid.lk1i.17.sorted[1:10]

btn.sid.lk1o.17 <- igraph::betweenness(net_sid.lk1o.17)
btn.sid.lk1o.17.sorted <- sort(btn.sid.lk1o.17,decreasing=TRUE)
btn.sid.lk1o.17.top10 <- btn.sid.lk1o.17.sorted[1:10]

names(btn.sid.lk1i.17.top10) %in% names(btn.sid.lk1o.17.top10)

btn.sid.lk1i.18 <- igraph::betweenness(net_sid.lk1i.18)
btn.sid.lk1i.18.sorted <- sort(btn.sid.lk1i.18,decreasing=TRUE)
btn.sid.lk1i.18.top10 <- btn.sid.lk1i.18.sorted[1:10]

btn.sid.lk1o.18 <- igraph::betweenness(net_sid.lk1o.18)
btn.sid.lk1o.18.sorted <- sort(btn.sid.lk1o.18,decreasing=TRUE)
btn.sid.lk1o.18.top10 <- btn.sid.lk1o.18.sorted[1:10]

names(btn.sid.lk1i.18.top10) %in% names(btn.sid.lk1o.18.top10)

#17 v 18
names(btn.sid.lk1i.18.top10) %in% names(btn.sid.lk1i.17.top10)

#18 v 15
names(btn.sid.lk1i.18.top10) %in% names(btn.sid.lk1i.15.top10)

#17 v 15
names(btn.sid.lk1i.17.top10) %in% names(btn.sid.lk1i.15.top10)

btn.sid.lk1i.17.top10.df <- data.frame(btn.sid.lk1i.17.top10)
btn.sid.lk1i.17.top10.df$sqs <- row.names(btn.sid.lk1i.17.top10.df)

btn.sid.lk1i.15.top10.df <- data.frame(btn.sid.lk1i.15.top10)
btn.sid.lk1i.15.top10.df$sqs <- row.names(btn.sid.lk1i.15.top10.df)

ggplot(btn.sid.lk1i.15.top10.df,aes(x=sqs,y=btn.sid.lk1i.15.top10))+
  geom_bar(stat="identity")

ggplot(btn.sid.lk1i.17.top10.df,aes(x=sqs,y=btn.sid.lk1i.17.top10))+
  geom_bar(stat="identity")

ggplot(btn.sid.lk1i.17.top10.df,aes(x=sqs,y=btn.sid.lk1i.17.top10))+
  geom_bar(stat="identity")
ggplot(btn.sid.lk1i.15.top10.df,aes(x=sqs,y=btn.sid.lk1i.17.top10))+
  geom_bar(stat="identity")

ggplot(btn.sid.lk1i.17.top10.df,aes(x=row.names,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Eigenvector centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2015 & 2016 (pre-Irma)")+
  geom_hline(yintercept=0.7885872,color="#781C6D")


btwn.15.tosort$vector <- btwn.15.tosort$betweenness.net_15.
btwn.15.sorted <- btwn.15.tosort[order(-btwn.15.tosort$vector),]
btwn.15.sorted$sqs <- rownames(btwn.15.sorted)
btwn.15.top10 <- btwn.15.sorted[1:10,]
sqs_order <- btwn.15.top10$sqs
btwn.15.top10$sqs <- factor(btwn.15.top10$sqs,levels=sqs_order)



plot(deg.dist, xlab = "Nodes degree", ylab = "Probability") 
lines(deg.dist)
# qgraph method
centralityPlot(net_sid.lk1i.15)
```

```{r older}
# Hub detection
#net_15.cn <- closeness(net_15)
#net_15.bn <- betweenness(net_15) 
#net_15.pr <- page_rank(net_15)$vector 
net_sid.lk1i.15.hs <- hub_score(net_sid.lk1i.15)$vector
net_sid.lk1i.15.hs.sort <- sort(net_sid.lk1i.15.hs, decreasing = TRUE)
net_sid.lk1i.15.hs.top5 <- head(net_sid.lk1i.15.hs.sort, n = 5)
net_sid.lk1i.15.hs.top5

net_17.cn <- closeness(net_17)
net_17.bn <- betweenness(net_17) 
net_17.pr <- page_rank(net_17)$vector
net_17.hs <- hub_score(net_17)$vector
net_17.hs.sort <- sort(net_17.hs, decreasing = TRUE)
net_17.hs.top5 <- head(net_17.hs.sort, n = 5)

net_18.cn <- closeness(net_18)
net_18.bn <- betweenness(net_18) 
net_18.pr <- page_rank(net_18)$vector 
net_18.hs <- hub_score(net_18)$vector
net_18.hs.sort <- sort(net_18.hs, decreasing = TRUE)
net_18.hs.top5 <- head(net_18.hs.sort, n = 5)
```

### Eigenvector centrality

```{r network metrics 1}
eigen.15 <- eigen_centrality(net_15)
eigen.15.tosort <- data.frame(eigen.15[["vector"]])
eigen.15.tosort$vector <- eigen.15.tosort$eigen.15...vector...
eigen.15.sorted <- eigen.15.tosort[order(-eigen.15.tosort$vector),]
eigen.15.sorted$sqs <- rownames(eigen.15.sorted)
eigen.15.top10 <- eigen.15.sorted[1:10,]
sqs_order <- eigen.15.top10$sqs
eigen.15.top10$sqs <- factor(eigen.15.top10$sqs,levels=sqs_order)

eigen.17 <- eigen_centrality(net_17)
eigen.17.tosort <- data.frame(eigen.17[["vector"]])
eigen.17.tosort$vector <- eigen.17.tosort$eigen.17...vector...
eigen.17.sorted <- eigen.17.tosort[order(-eigen.17.tosort$vector),]
eigen.17.sorted$sqs <- rownames(eigen.17.sorted)
eigen.17.top10 <- eigen.17.sorted[1:10,]
sqs_order <- eigen.17.top10$sqs
eigen.17.top10$sqs <- factor(eigen.17.top10$sqs,levels=sqs_order)

eigen.18 <- eigen_centrality(net_18)
eigen.18.tosort <- data.frame(eigen.18[["vector"]])
eigen.18.tosort$vector <- eigen.18.tosort$eigen.18...vector...
eigen.18.sorted <- eigen.18.tosort[order(-eigen.18.tosort$vector),]
eigen.18.sorted$sqs <- rownames(eigen.18.sorted)
eigen.18.top10 <- eigen.18.sorted[1:10,]
sqs_order <- eigen.18.top10$sqs
eigen.18.top10$sqs <- factor(eigen.18.top10$sqs,levels=sqs_order)

ggplot(eigen.15.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Eigenvector centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2015 & 2016 (pre-Irma)")+
  geom_hline(yintercept=0.7885872,color="#781C6D")

ggplot(eigen.17.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Eigenvector centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2017 (Irma)")+
  geom_hline(yintercept=0.7885872,color="#781C6D")+
  geom_hline(yintercept=0.7140983,color="#AE305C")

ggplot(eigen.18.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Eigenvector centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2018 (post-Irma)")+
  geom_hline(yintercept=0.7140983,color="#AE305C")
```

### Betweenness centrality

```{r network networks 2}
btwn.15.tosort <- data.frame(betweenness(net_15))
btwn.15.tosort$vector <- btwn.15.tosort$betweenness.net_15.
btwn.15.sorted <- btwn.15.tosort[order(-btwn.15.tosort$vector),]
btwn.15.sorted$sqs <- rownames(btwn.15.sorted)
btwn.15.top10 <- btwn.15.sorted[1:10,]
sqs_order <- btwn.15.top10$sqs
btwn.15.top10$sqs <- factor(btwn.15.top10$sqs,levels=sqs_order)

btwn.17.tosort <- data.frame(betweenness(net_17))
btwn.17.tosort$vector <- btwn.17.tosort$betweenness.net_17.
btwn.17.sorted <- btwn.17.tosort[order(-btwn.17.tosort$vector),]
btwn.17.sorted$sqs <- rownames(btwn.17.sorted)
btwn.17.top10 <- btwn.17.sorted[1:10,]
sqs_order <- btwn.17.top10$sqs
btwn.17.top10$sqs <- factor(btwn.17.top10$sqs,levels=sqs_order)

btwn.18.tosort <- data.frame(betweenness(net_18))
btwn.18.tosort$vector <- btwn.18.tosort$betweenness.net_18.
btwn.18.sorted <- btwn.18.tosort[order(-btwn.18.tosort$vector),]
btwn.18.sorted$sqs <- rownames(btwn.18.sorted)
btwn.18.top10 <- btwn.18.sorted[1:10,]
sqs_order <- btwn.18.top10$sqs
btwn.18.top10$sqs <- factor(btwn.18.top10$sqs,levels=sqs_order)

ggplot(btwn.15.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Betweenness centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2015 & 2016 (pre-Irma)")

ggplot(btwn.17.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Betweenness centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2017 (Irma)")

ggplot(btwn.18.top10,aes(x=sqs,y=vector))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ylab("Betweenness centrality")+
  xlab("Bacterial sequence")+
  ggtitle("2018 (post-Irma)")
```

# Script archive

```{r}
spieceasi.net <- spiec.easi(otu.lk1o.15.no0, method = 'mb',lambda.min.ratio
= 1e-2, nlambda = 20, icov.select.params = list(rep.num = 50))
```

```{r}
otu.sids <- data.frame(ps.sid@otu_table)
otu.rads <- data.frame(ps.rad@otu_table)

# Cuts OTUs with <0.01% of reads total:
# seq.sid.keep <- which(colSums(otu.sids)*100/(sum(colSums(otu.sids))) > 0.01)
# seq.sid <- otu.sids[,c(seq.sid.keep)]
# tail(colSums(seq.sid)) #around minimum ~730 reads/otu left, 687 taxa
# 
# seq.rad.keep <- which(colSums(otu.rads)*100/(sum(colSums(otu.rads))) > 0.01)
# seq.rad <- otu.rads[,c(seq.rad.keep)] #around >660 reads/otu left, 1379 taxa
# tail(colSums(seq.rad))
```
