---
title: "fl16s_cohesion"
author: "Nicola Kriefall"
date: "8/25/2022"
output: html_document
---

# Cohesion

## Read in data & scripts

```{r}
setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_16s/05.networks/")
source("cohesion.R")
```

### Pre time point - sids

```{r}
# Read in dataset
## Data should be in a matrix where each row is a sample. 
#couldn't get cohesion function to work, will run here then save results

#note: make out.df in code chunk below. It's bad organization, I know. 

#b <- readRDS("./files/seq.tables/seq.fam.sid.pre.lk1.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pre.lk1i.rds")

# b <- readRDS("./files/seq.tables/seq.fam.sid.pre.lk1.off.no2.rds")
# saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pre.lk1o.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pre.uk1.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pre.uk1i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pre.uk1.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pre.uk1o.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pre.uk2.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pre.uk2i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pre.uk2.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pre.uk2o.rds")
```

### Irma time point - sids

```{r}
#b <- readRDS("./files/seq.tables/seq.fam.sid.irm.lk1.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.irm.lk1i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.irm.lk1.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.irm.lk1o.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.irm.uk1.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.irm.uk1i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.irm.uk1.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.irm.uk1o.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.irm.uk2.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.irm.uk2i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.irm.uk2.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.irm.uk2o.rds")
```

### Post time point - sids

```{r}
#b <- readRDS("./files/seq.tables/seq.fam.sid.pos.lk1.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pos.lk1i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pos.lk1.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pos.lk1o.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pos.uk1.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pos.uk1i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pos.uk1.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pos.uk1o.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pos.uk2.in.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pos.uk2i.rds")

#b <- readRDS("./files/seq.tables/seq.fam.sid.pos.uk2.off.no2.rds")
#saveRDS(out.df, file="./files/cohesion/df.cohesion.sid.pos.uk2o.rds")
```

### Cohesion code chunk

```{r, eval=F}
## Choose a persistence cutoff (min. fraction of taxon presence) for retaining taxa in the analysis
pers.cutoff <- 0.10
## Decide the number of iterations to run for each taxon. (>= 200 is recommended)
# Larger values of iter mean the script takes longer to run
iter <- 200
## Decide whether to use taxon/column shuffle (tax.shuffle = T) or row shuffle algorithm (tax.shuffle = F)
tax.shuffle <- T
## Option to input your own correlation table
# Note that your correlation table MUST have the same number of taxa as the abundance table. There should be no empty (all zero) taxon vectors in the abundance table. 
# Even if you input your own correlation table, the persistence cutoff will be applied
use.custom.cors <- F

###################################################################
###################################################################

# Read in custom correlation matrix, if desired. Must set "use.custom.cors" to TRUE
if(use.custom.cors == T) {
  custom.cor.mat <- read.csv("your_path_here.csv", header = T, row.names = 1)
  custom.cor.mat <- as.matrix(custom.cor.mat)
  #Check that correlation matrix and abundance matrix have the same dimension
  print(dim(b)[2] == dim(custom.cor.mat)[2])
}

# Suggested steps to re-format data. At the end of these steps, the data should be in a matrix "c" where there are no empty samples or blank taxon columns. 
c <- as.matrix(b)
c <- c[rowSums(c) > 0, colSums(c) > 0]

# Optionally re-order dataset to be in chronological order. Change date format for your data. 
#c <- c[order(as.Date(rownames(c), format = "%m/%d/%Y")), ]

# Save total number of individuals in each sample in the original matrix. This will be 1 if data are in relative abundance, but not if matrix c is count data
rowsums.orig <- rowSums(c)

# Based on persistence cutoff, define a cutoff for the number of zeroes allowed in a taxon's distribution
zero.cutoff <- ceiling(pers.cutoff * dim(c)[1])

# Remove taxa that are below the persistence cutoff
d <- c[ , apply(c, 2, zero) < (dim(c)[1]-zero.cutoff) ]
# Remove any samples that no longer have any individuals, due to removing taxa
d <- d[rowSums(d) > 0, ]

#If using custom correlation matrix, need to remove rows/columns corresponding to the taxa below persistence cutoff
if(use.custom.cors == T){
  custom.cor.mat.sub <- custom.cor.mat[apply(c, 2, zero) < (dim(c)[1]-zero.cutoff), apply(c, 2, zero) < (dim(c)[1]-zero.cutoff)]
}

# Create relative abundance matrix.  
rel.d <- d / rowsums.orig
# Optionally, check to see what proportion of the community is retained after cutting out taxa
hist(rowSums(rel.d))

# Create observed correlation matrix
cor.mat.true <- cor(rel.d)

# Create vector to hold median otu-otu correlations for initial otu
med.tax.cors <- vector()

# Run this loop for the null model to get expected pairwise correlations
# Bypass null model if the option to input custom correlation matrix is TRUE
if(use.custom.cors == F) {
  ifelse(tax.shuffle, {
    for(which.taxon in 1:dim(rel.d)[2]){
      
      #create vector to hold correlations from every permutation for each single otu
      ## perm.cor.vec.mat stands for permuted correlations vector matrix
      perm.cor.vec.mat <- vector()
      
      for(i in 1:iter){
        #Create empty matrix of same dimension as rel.d
        perm.rel.d <- matrix(numeric(0), dim(rel.d)[1], dim(rel.d)[2])
        rownames(perm.rel.d) <- rownames(rel.d)
        colnames(perm.rel.d) <- colnames(rel.d)
        
        #For each otu
        for(j in 1:dim(rel.d)[2]){ 
          # Replace the original taxon vector with a permuted taxon vector
          perm.rel.d[, j ] <- sample(rel.d[ ,j ]) 
        }
        
        # Do not randomize focal column 
        perm.rel.d[, which.taxon] <- rel.d[ , which.taxon]
        
        # Calculate correlation matrix of permuted matrix
        cor.mat.null <- cor(perm.rel.d)
        
        # For each iteration, save the vector of null matrix correlations between focal taxon and other taxa
        perm.cor.vec.mat <- cbind(perm.cor.vec.mat, cor.mat.null[, which.taxon])
        
      }
      # Save the median correlations between the focal taxon and all other taxa  
      med.tax.cors <- cbind(med.tax.cors, apply(perm.cor.vec.mat, 1, median))
      
      # For large datasets, this can be helpful to know how long this loop will run
      if(which.taxon %% 20 == 0){print(which.taxon)}
    }
  } , {
    for(which.taxon in 1:dim(rel.d)[2]){
      
      #create vector to hold correlations from every permutation for each single otu
      ## perm.cor.vec.mat stands for permuted correlations vector matrix
      perm.cor.vec.mat <- vector()
      
      for(i in 1:iter){
        #Create duplicate matrix to shuffle abundances
        perm.rel.d <- rel.d 
        
        #For each taxon
        for(j in 1:dim(rel.d)[1]){ 
          which.replace <- which(rel.d[j, ] > 0 ) 
          # if the focal taxon is greater than zero, take it out of the replacement vector, so the focal abundance stays the same
          which.replace.nonfocal <- which.replace[!(which.replace %in% which.taxon)]
          
          #Replace the original taxon vector with a vector where the values greater than 0 have been randomly permuted 
          perm.rel.d[j, which.replace.nonfocal] <- sample(rel.d[ j, which.replace.nonfocal]) 
        }
        
        # Calculate correlation matrix of permuted matrix
        cor.mat.null <- cor(perm.rel.d)
        
        # For each iteration, save the vector of null matrix correlations between focal taxon and other taxa
        perm.cor.vec.mat <- cbind(perm.cor.vec.mat, cor.mat.null[, which.taxon])
        
      }
      # Save the median correlations between the focal taxon and all other taxa  
      med.tax.cors <- cbind(med.tax.cors, apply(perm.cor.vec.mat, 1, median))
      
      # For large datasets, this can be helpful to know how long this loop will run
      if(which.taxon %% 20 == 0){print(which.taxon)}
    }
  }
  )
}

# Save observed minus expected correlations. Use custom correlations if use.custom.cors = TRUE
ifelse(use.custom.cors == T, {
  obs.exp.cors.mat <- custom.cor.mat.sub}, {
    obs.exp.cors.mat <- cor.mat.true - med.tax.cors
  }
)

diag(obs.exp.cors.mat) <- 0

#### 
#### Produce desired vectors of connectedness and cohesion 

# Calculate connectedness by averaging positive and negative observed - expected correlations
connectedness.pos <- apply(obs.exp.cors.mat, 2, pos.mean)
connectedness.neg <- apply(obs.exp.cors.mat, 2, neg.mean)

# Calculate cohesion by multiplying the relative abundance dataset by associated connectedness
cohesion.pos <- rel.d %*% connectedness.pos
cohesion.neg <- rel.d %*% connectedness.neg

####
#### Combine vectors into one list and print 
output <- list(connectedness.neg, connectedness.pos, cohesion.neg, cohesion.pos)
names(output) <- c("Negative Connectedness", "Positive Connectedness", "Negative Cohesion", "Positive Cohesion")
print(output)

#saving output a different way
coh.neg <- output[["Negative Cohesion"]]
coh.pos <- output[["Positive Cohesion"]]
row.names(coh.neg)==row.names(coh.pos)

out.df <- data.frame(coh.neg,coh.pos)
```

## Cohesion results

```{r}
library(ggplot2)
library(cowplot)
library(ggpubr)

setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_16s/05.networks/files/cohesion")
```

### Creating data frame from outputs above {.tabset}

Ran once then re-read in later

#### Pre time point up first - sids

```{r cohesion results pre, eval=F}
#LOWER KEYS 1
df.coh.sid.pre.lk1i <- readRDS("df.cohesion.sid.pre.lk1i.rds")
df.coh.sid.pre.lk1o <- readRDS("df.cohesion.sid.pre.lk1o.rds")

df.coh.sid.pre.lk1i$zone <- rep("Inshore",nrow(df.coh.sid.pre.lk1i))
df.coh.sid.pre.lk1o$zone <- rep("Offshore",nrow(df.coh.sid.pre.lk1o))

df.coh.sid.pre.lk1 <- rbind(df.coh.sid.pre.lk1i,df.coh.sid.pre.lk1o)

df.coh.sid.pre.lk1$time <- rep("Pre",nrow(df.coh.sid.pre.lk1))
df.coh.sid.pre.lk1$site <- rep("LK1",nrow(df.coh.sid.pre.lk1))

ggplot(df.coh.sid.pre.lk1,aes(x=zone,y=coh.pos))+
  geom_boxplot()

#UPPER KEYS 1
df.coh.sid.pre.uk1i <- readRDS("df.cohesion.sid.pre.uk1i.rds")
df.coh.sid.pre.uk1o <- readRDS("df.cohesion.sid.pre.uk1o.rds")

df.coh.sid.pre.uk1i$zone <- rep("Inshore",nrow(df.coh.sid.pre.uk1i))
df.coh.sid.pre.uk1o$zone <- rep("Offshore",nrow(df.coh.sid.pre.uk1o))

df.coh.sid.pre.uk1 <- rbind(df.coh.sid.pre.uk1i,df.coh.sid.pre.uk1o)

df.coh.sid.pre.uk1$time <- rep("Pre",nrow(df.coh.sid.pre.uk1))
df.coh.sid.pre.uk1$site <- rep("UK1",nrow(df.coh.sid.pre.uk1))

#UPPER KEYS 2
df.coh.sid.pre.uk2i <- readRDS("df.cohesion.sid.pre.uk2i.rds")
df.coh.sid.pre.uk2o <- readRDS("df.cohesion.sid.pre.uk2o.rds")

df.coh.sid.pre.uk2i$zone <- rep("Inshore",nrow(df.coh.sid.pre.uk2i))
df.coh.sid.pre.uk2o$zone <- rep("Offshore",nrow(df.coh.sid.pre.uk2o))

df.coh.sid.pre.uk2 <- rbind(df.coh.sid.pre.uk2i,df.coh.sid.pre.uk2o)

df.coh.sid.pre.uk2$time <- rep("Pre",nrow(df.coh.sid.pre.uk2))
df.coh.sid.pre.uk2$site <- rep("UK2",nrow(df.coh.sid.pre.uk2))
```

#### Irma time point - sids

```{r cohesion results irma, eval=F}
#LOWER KEYS 1
df.coh.sid.irm.lk1i <- readRDS("df.cohesion.sid.irm.lk1i.rds")
df.coh.sid.irm.lk1o <- readRDS("df.cohesion.sid.irm.lk1o.rds")

df.coh.sid.irm.lk1i$zone <- rep("Inshore",nrow(df.coh.sid.irm.lk1i))
df.coh.sid.irm.lk1o$zone <- rep("Offshore",nrow(df.coh.sid.irm.lk1o))

df.coh.sid.irm.lk1 <- rbind(df.coh.sid.irm.lk1i,df.coh.sid.irm.lk1o)

df.coh.sid.irm.lk1$time <- rep("Irma",nrow(df.coh.sid.irm.lk1))
df.coh.sid.irm.lk1$site <- rep("LK1",nrow(df.coh.sid.irm.lk1))

#UPPER KEYS 1
df.coh.sid.irm.uk1i <- readRDS("df.cohesion.sid.irm.uk1i.rds")
df.coh.sid.irm.uk1o <- readRDS("df.cohesion.sid.irm.uk1o.rds")

df.coh.sid.irm.uk1i$zone <- rep("Inshore",nrow(df.coh.sid.irm.uk1i))
df.coh.sid.irm.uk1o$zone <- rep("Offshore",nrow(df.coh.sid.irm.uk1o))

df.coh.sid.irm.uk1 <- rbind(df.coh.sid.irm.uk1i,df.coh.sid.irm.uk1o)

df.coh.sid.irm.uk1$time <- rep("Irma",nrow(df.coh.sid.irm.uk1))
df.coh.sid.irm.uk1$site <- rep("UK1",nrow(df.coh.sid.irm.uk1))

#UPPER KEYS 2
df.coh.sid.irm.uk2i <- readRDS("df.cohesion.sid.irm.uk2i.rds")
df.coh.sid.irm.uk2o <- readRDS("df.cohesion.sid.irm.uk2o.rds")

df.coh.sid.irm.uk2i$zone <- rep("Inshore",nrow(df.coh.sid.irm.uk2i))
df.coh.sid.irm.uk2o$zone <- rep("Offshore",nrow(df.coh.sid.irm.uk2o))

df.coh.sid.irm.uk2 <- rbind(df.coh.sid.irm.uk2i,df.coh.sid.irm.uk2o)

df.coh.sid.irm.uk2$time <- rep("Irma",nrow(df.coh.sid.irm.uk2))
df.coh.sid.irm.uk2$site <- rep("UK2",nrow(df.coh.sid.irm.uk2))
```

#### Post - sids

```{r cohesion results post, eval=F}
#LOWER KEYS 1
df.coh.sid.pos.lk1i <- readRDS("df.cohesion.sid.pos.lk1i.rds")
df.coh.sid.pos.lk1o <- readRDS("df.cohesion.sid.pos.lk1o.rds")

df.coh.sid.pos.lk1i$zone <- rep("Inshore",nrow(df.coh.sid.pos.lk1i))
df.coh.sid.pos.lk1o$zone <- rep("Offshore",nrow(df.coh.sid.pos.lk1o))

df.coh.sid.pos.lk1 <- rbind(df.coh.sid.pos.lk1i,df.coh.sid.pos.lk1o)

df.coh.sid.pos.lk1$time <- rep("Post",nrow(df.coh.sid.pos.lk1))
df.coh.sid.pos.lk1$site <- rep("LK1",nrow(df.coh.sid.pos.lk1))

#UPPER KEYS 1
df.coh.sid.pos.uk1i <- readRDS("df.cohesion.sid.pos.uk1i.rds")
df.coh.sid.pos.uk1o <- readRDS("df.cohesion.sid.pos.uk1o.rds")

df.coh.sid.pos.uk1i$zone <- rep("Inshore",nrow(df.coh.sid.pos.uk1i))
df.coh.sid.pos.uk1o$zone <- rep("Offshore",nrow(df.coh.sid.pos.uk1o))

df.coh.sid.pos.uk1 <- rbind(df.coh.sid.pos.uk1i,df.coh.sid.pos.uk1o)

df.coh.sid.pos.uk1$time <- rep("Post",nrow(df.coh.sid.pos.uk1))
df.coh.sid.pos.uk1$site <- rep("UK1",nrow(df.coh.sid.pos.uk1))

#UPPER KEYS 2
df.coh.sid.pos.uk2i <- readRDS("df.cohesion.sid.pos.uk2i.rds")
df.coh.sid.pos.uk2o <- readRDS("df.cohesion.sid.pos.uk2o.rds")

df.coh.sid.pos.uk2i$zone <- rep("Inshore",nrow(df.coh.sid.pos.uk2i))
df.coh.sid.pos.uk2o$zone <- rep("Offshore",nrow(df.coh.sid.pos.uk2o))

df.coh.sid.pos.uk2 <- rbind(df.coh.sid.pos.uk2i,df.coh.sid.pos.uk2o)

df.coh.sid.pos.uk2$time <- rep("Post",nrow(df.coh.sid.pos.uk2))
df.coh.sid.pos.uk2$site <- rep("UK2",nrow(df.coh.sid.pos.uk2))
```

### All together - sids

```{r, eval=F}
df.coh.sid <- rbind(df.coh.sid.pre.lk1,df.coh.sid.pre.uk1,df.coh.sid.pre.uk2,df.coh.sid.irm.lk1,df.coh.sid.irm.uk1,df.coh.sid.irm.uk2,df.coh.sid.pos.lk1,df.coh.sid.pos.uk1,df.coh.sid.pos.uk2)
```

```{r}
library(ggplot2)
library(cowplot)

setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_16s/05.networks")
#saveRDS(df.coh.sid,file="df.cohesion.sids.rds")
df.coh.sid <- readRDS("./files/df.cohesion.sids.rds")

df.coh.sid$zone <- as.factor(df.coh.sid$zone)
df.coh.sid$time <- factor(df.coh.sid$time,levels=c("Pre","Irma","Post"))
```

### Plotting time - sids

```{r}
gg.coh.pos.sids.yr <- ggplot(df.coh.sid,aes(x=time,y=coh.pos,fill=time,color=time,shape=zone))+
  facet_grid(site~zone)+  
  geom_jitter(alpha=0.5)+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Cohesion (positive)")+
  xlab("Time point")+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("(a) S. siderea")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
gg.coh.pos.sids.yr

ggsave(gg.coh.pos.sids.yr,file="plot.cohesion.sids.pdf",width=3.5,height=3.5)

##point & error bars - not using!
#df.coh.sid.se <- summarySE(df.coh.sid,groupvars=c("time","zone","site"),measurevar="coh.pos")

# gg.coh.pos.sids.yr <- ggplot(df.coh.sid.se,aes(x=time,y=coh.pos,fill=time,color=time,shape=zone))+
#   facet_grid(site~zone)+  
#   geom_jitter(data=df.coh.sid,aes(x=time,y=coh.pos),alpha=0.5)+
#   #add color="black" here for outlines
#   #geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
#   geom_point()+
#   geom_errorbar(aes(ymin=coh.pos-sd,ymax=coh.pos+sd),width=0.1)+
#   ylab("Cohesion (positive)")+
#   xlab("Time point")+
#   theme_bw()+
#   scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
#   scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
#   scale_shape_manual(values=c(21,23),name="Reef zone")+
#   theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
#   ggtitle("S. siderea")+
#   #scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
#   guides(fill="none",color="none")+
#   scale_x_discrete(labels=c("Pre","Disturb.","Post"))
# gg.coh.pos.sids.yr

gg.coh.neg.sids.yr <- ggplot(df.coh.sid,aes(x=time,y=coh.neg,fill=time,color=time,shape=zone))+
  facet_grid(site~.)+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Cohesion (negative)")+
  xlab("Time point")+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("S. siderea")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))
gg.coh.neg.sids.yr
```

### Cohesion stats - sids

```{r}

```

### Plotting time - radians

```{r}

```

### Cohesion stats - rads

```{r}

```

### Cohesion statistics - update

```{r, eval=F}
#stats
neg.all$year <- as.factor(neg.all$year)

shapiro.test(neg.all$cohesion)
neg.all$coh.log <- log(abs(neg.all$cohesion))
shapiro.test(neg.all$coh.log)
kruskal.test(cohesion~year,data=neg.all)

#install.packages("dunn.test")
#library(dunn.test)
dunn.test(neg.all$cohesion,neg.all$year,method="bh")
str(neg.all)

#stats pos
pos.all$year <- as.factor(pos.all$year)

shapiro.test(pos.all$cohesion)
pos.all$coh.log <- log(abs(pos.all$cohesion))
shapiro.test(pos.all$coh.log)
kruskal.test(cohesion~year,data=pos.all)

#install.packages("dunn.test")
#library(dunn.test)
dunn.test(pos.all$cohesion,pos.all$year,method="bh")
str(pos.all)
```
