---
title: "fl16s_cohesion"
author: "Nicola Kriefall"
date: "11/29/2022"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
---

# Cohesion

## Read in data & scripts

```{r}
setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_16s/04.networks")
source("./cohesion/cohesion.R")
```

### Seq tables

```{r}
# Read in dataset
## Data should be in a matrix where each row is a sample. 
#couldn't get cohesion function to work, will run here then save results

#note: make out.df in code chunk below. It's bad organization, I know. 
#ps <- readRDS("./nets_revised/ps.sid.pre.fam.2")
#ps <- readRDS("./nets_revised/ps.sid.irm.fam.2")
#ps <- readRDS("./nets_revised/ps.sid.pos.fam.2")

#ps <- readRDS("./nets_revised/ps.rad.pre.fam.2")
#ps <- readRDS("./nets_revised/ps.rad.irm.fam.2")
#ps <- readRDS("./nets_revised/ps.rad.pos.fam.2")

ps.sid.trim <- readRDS("./nets_revised/ps.sid.trim.rds")
ps.rad.trim <- readRDS("./nets_revised/ps.rad.trim.rds")

ps.sid.pre <- subset_samples(ps.sid.trim,time=="Pre")
ps.sid.irm <- subset_samples(ps.sid.trim,time=="Irma")
ps.sid.pos <- subset_samples(ps.sid.trim,time=="Post")

ps.sid.pre.no0 <- prune_taxa(taxa_sums(ps.sid.pre) > 55, ps.sid.pre)
ps.sid.pre.no0 #133 taxa

ps.sid.irm.no0 <- prune_taxa(taxa_sums(ps.sid.irm) > 55, ps.sid.irm)
ps.sid.irm.no0 #134 taxa

ps.sid.pos.no0 <- prune_taxa(taxa_sums(ps.sid.pos) > 55, ps.sid.pos)
ps.sid.pos.no0 #127 taxa

ps.rad.pre <- subset_samples(ps.rad.trim,time=="Pre")
ps.rad.irm <- subset_samples(ps.rad.trim,time=="Irma")
ps.rad.pos <- subset_samples(ps.rad.trim,time=="Post")

ps.rad.pre.no0 <- prune_taxa(taxa_sums(ps.rad.pre) > 55, ps.rad.pre)
ps.rad.pre.no0 #133 taxa

ps.rad.irm.no0 <- prune_taxa(taxa_sums(ps.rad.irm) > 55, ps.rad.irm)
ps.rad.irm.no0 #134 taxa

ps.rad.pos.no0 <- prune_taxa(taxa_sums(ps.rad.pos) > 55, ps.rad.pos)
ps.rad.pos.no0 #127 taxa

##first up
b <- data.frame(ps.sid.pre.no0@otu_table)
```

## Cohesion code chunk

```{r, eval=F}
## Choose a persistence cutoff (min. fraction of taxon presence) for retaining taxa in the analysis
pers.cutoff <- 0.01
## Decide the number of iterations to run for each taxon. (>= 200 is recommended)
# Larger values of iter mean the script takes longer to run
iter <- 200
## Decide whether to use taxon/column shuffle (tax.shuffle = T) or row shuffle algorithm (tax.shuffle = F)
tax.shuffle <- T
## Option to input your own correlation table
# Note that your correlation table MUST have the same number of taxa as the abundance table. There should be no empty (all zero) taxon vectors in the abundance table. 
# Even if you input your own correlation table, the persistence cutoff will be applied
use.custom.cors <- F

###################################################################
###################################################################

# Read in custom correlation matrix, if desired. Must set "use.custom.cors" to TRUE
if(use.custom.cors == T) {
  custom.cor.mat <- read.csv("your_path_here.csv", header = T, row.names = 1)
  custom.cor.mat <- as.matrix(custom.cor.mat)
  #Check that correlation matrix and abundance matrix have the same dimension
  print(dim(b)[2] == dim(custom.cor.mat)[2])
}

# Suggested steps to re-format data. At the end of these steps, the data should be in a matrix "c" where there are no empty samples or blank taxon columns. 
c <- as.matrix(b)
c <- c[rowSums(c) > 0, colSums(c) > 0]

# Optionally re-order dataset to be in chronological order. Change date format for your data. 
#c <- c[order(as.Date(rownames(c), format = "%m/%d/%Y")), ]

# Save total number of individuals in each sample in the original matrix. This will be 1 if data are in relative abundance, but not if matrix c is count data
rowsums.orig <- rowSums(c)

# Based on persistence cutoff, define a cutoff for the number of zeroes allowed in a taxon's distribution
zero.cutoff <- ceiling(pers.cutoff * dim(c)[1])

# Remove taxa that are below the persistence cutoff
d <- c[ , apply(c, 2, zero) < (dim(c)[1]-zero.cutoff) ]
# Remove any samples that no longer have any individuals, due to removing taxa
d <- d[rowSums(d) > 0, ]

#If using custom correlation matrix, need to remove rows/columns corresponding to the taxa below persistence cutoff
if(use.custom.cors == T){
  custom.cor.mat.sub <- custom.cor.mat[apply(c, 2, zero) < (dim(c)[1]-zero.cutoff), apply(c, 2, zero) < (dim(c)[1]-zero.cutoff)]
}

# Create relative abundance matrix.  
rel.d <- d / rowsums.orig
# Optionally, check to see what proportion of the community is retained after cutting out taxa
hist(rowSums(rel.d))

# Create observed correlation matrix
cor.mat.true <- cor(rel.d)

# Create vector to hold median otu-otu correlations for initial otu
med.tax.cors <- vector()

# Run this loop for the null model to get expected pairwise correlations
# Bypass null model if the option to input custom correlation matrix is TRUE
if(use.custom.cors == F) {
  ifelse(tax.shuffle, {
    for(which.taxon in 1:dim(rel.d)[2]){
      
      #create vector to hold correlations from every permutation for each single otu
      ## perm.cor.vec.mat stands for permuted correlations vector matrix
      perm.cor.vec.mat <- vector()
      
      for(i in 1:iter){
        #Create empty matrix of same dimension as rel.d
        perm.rel.d <- matrix(numeric(0), dim(rel.d)[1], dim(rel.d)[2])
        rownames(perm.rel.d) <- rownames(rel.d)
        colnames(perm.rel.d) <- colnames(rel.d)
        
        #For each otu
        for(j in 1:dim(rel.d)[2]){ 
          # Replace the original taxon vector with a permuted taxon vector
          perm.rel.d[, j ] <- sample(rel.d[ ,j ]) 
        }
        
        # Do not randomize focal column 
        perm.rel.d[, which.taxon] <- rel.d[ , which.taxon]
        
        # Calculate correlation matrix of permuted matrix
        cor.mat.null <- cor(perm.rel.d)
        
        # For each iteration, save the vector of null matrix correlations between focal taxon and other taxa
        perm.cor.vec.mat <- cbind(perm.cor.vec.mat, cor.mat.null[, which.taxon])
        
      }
      # Save the median correlations between the focal taxon and all other taxa  
      med.tax.cors <- cbind(med.tax.cors, apply(perm.cor.vec.mat, 1, median))
      
      # For large datasets, this can be helpful to know how long this loop will run
      if(which.taxon %% 20 == 0){print(which.taxon)}
    }
  } , {
    for(which.taxon in 1:dim(rel.d)[2]){
      
      #create vector to hold correlations from every permutation for each single otu
      ## perm.cor.vec.mat stands for permuted correlations vector matrix
      perm.cor.vec.mat <- vector()
      
      for(i in 1:iter){
        #Create duplicate matrix to shuffle abundances
        perm.rel.d <- rel.d 
        
        #For each taxon
        for(j in 1:dim(rel.d)[1]){ 
          which.replace <- which(rel.d[j, ] > 0 ) 
          # if the focal taxon is greater than zero, take it out of the replacement vector, so the focal abundance stays the same
          which.replace.nonfocal <- which.replace[!(which.replace %in% which.taxon)]
          
          #Replace the original taxon vector with a vector where the values greater than 0 have been randomly permuted 
          perm.rel.d[j, which.replace.nonfocal] <- sample(rel.d[ j, which.replace.nonfocal]) 
        }
        
        # Calculate correlation matrix of permuted matrix
        cor.mat.null <- cor(perm.rel.d)
        
        # For each iteration, save the vector of null matrix correlations between focal taxon and other taxa
        perm.cor.vec.mat <- cbind(perm.cor.vec.mat, cor.mat.null[, which.taxon])
        
      }
      # Save the median correlations between the focal taxon and all other taxa  
      med.tax.cors <- cbind(med.tax.cors, apply(perm.cor.vec.mat, 1, median))
      
      # For large datasets, this can be helpful to know how long this loop will run
      if(which.taxon %% 20 == 0){print(which.taxon)}
    }
  }
  )
}

# Save observed minus expected correlations. Use custom correlations if use.custom.cors = TRUE
ifelse(use.custom.cors == T, {
  obs.exp.cors.mat <- custom.cor.mat.sub}, {
    obs.exp.cors.mat <- cor.mat.true - med.tax.cors
  }
)

diag(obs.exp.cors.mat) <- 0

#### 
#### Produce desired vectors of connectedness and cohesion 

# Calculate connectedness by averaging positive and negative observed - expected correlations
connectedness.pos <- apply(obs.exp.cors.mat, 2, pos.mean)
connectedness.neg <- apply(obs.exp.cors.mat, 2, neg.mean)

# Calculate cohesion by multiplying the relative abundance dataset by associated connectedness
cohesion.pos <- rel.d %*% connectedness.pos
cohesion.neg <- rel.d %*% connectedness.neg

####
#### Combine vectors into one list and print 
output <- list(connectedness.neg, connectedness.pos, cohesion.neg, cohesion.pos)
names(output) <- c("Negative Connectedness", "Positive Connectedness", "Negative Cohesion", "Positive Cohesion")
print(output)

#saving output a different way
coh.neg <- output[["Negative Cohesion"]]
coh.pos <- output[["Positive Cohesion"]]
row.names(coh.neg)==row.names(coh.pos)

out.df <- data.frame(coh.neg,coh.pos)
```

```{r}
#saveRDS(out.df, file="./cohesion_revised/coh.sid.pre.fam.2.rds")
#saveRDS(out.df, file="./cohesion_revised/coh.sid.irm.fam.2.rds")
#saveRDS(out.df, file="./cohesion_revised/coh.sid.pos.fam.2.rds")

#saveRDS(out.df, file="./cohesion_revised/coh.rad.pre.fam.2.rds")
#saveRDS(out.df, file="./cohesion_revised/coh.rad.irm.fam.2.rds")
#saveRDS(out.df, file="./cohesion_revised/coh.rad.pos.fam.2.rds")
```

# Cohesion results

## Initial setup

```{r}
library(ggplot2)
library(cowplot)
library(ggpubr)

setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_16s/04.networks")
```

## Creating data frame from outputs above - ASV {.tabset}

```{r}
coh.sid.pre <- readRDS("./cohesion_revised/coh.sid.pre.fam.2.rds")
coh.sid.irm <- readRDS("./cohesion_revised/coh.sid.irm.fam.2.rds")
coh.sid.pos <- readRDS("./cohesion_revised/coh.sid.pos.fam.2.rds")

coh.sid.pre$time <- rep("Pre",nrow(coh.sid.pre))
coh.sid.irm$time <- rep("Irma",nrow(coh.sid.irm))
coh.sid.pos$time <- rep("Post",nrow(coh.sid.pos))

df.coh.sid <- rbind(coh.sid.pre,coh.sid.irm,coh.sid.pos)

ggplot(df.coh.sid,aes(x=time,y=coh.pos))+
  geom_boxplot()

ggplot(df.coh.sid,aes(x=time,y=coh.neg))+
  geom_boxplot()

df.coh.sid$ratio <- df.coh.sid$coh.pos/df.coh.sid$coh.neg

ggplot(df.coh.sid,aes(x=time,y=ratio))+
  geom_boxplot()

kruskal.test(coh.neg~time,data=df.coh.sid)
kruskal.test(coh.pos~time,data=df.coh.sid)
kruskal.test(ratio~time,data=df.coh.sid)
```

### Pre time point up first - sids

```{r cohesion results pre sids, eval=F}
#LOWER KEYS 1
df.coh.sid.pre.lk1i <- readRDS("./files/cohesion/df.cohesion.asv.sid.pre.lk1i.rds")
df.coh.sid.pre.lk1o <- readRDS("./files/cohesion/df.cohesion.asv.sid.pre.lk1o.rds")

df.coh.sid.pre.lk1i$zone <- rep("Inshore",nrow(df.coh.sid.pre.lk1i))
df.coh.sid.pre.lk1o$zone <- rep("Offshore",nrow(df.coh.sid.pre.lk1o))

df.coh.sid.pre.lk1 <- rbind(df.coh.sid.pre.lk1i,df.coh.sid.pre.lk1o)

df.coh.sid.pre.lk1$time <- rep("Pre",nrow(df.coh.sid.pre.lk1))
df.coh.sid.pre.lk1$site <- rep("LK1",nrow(df.coh.sid.pre.lk1))

ggplot(df.coh.sid.pre.lk1,aes(x=zone,y=coh.pos))+
  geom_boxplot()

#UPPER KEYS 1
df.coh.sid.pre.uk1i <- readRDS("./files/cohesion/df.cohesion.asv.sid.pre.uk1i.rds")
df.coh.sid.pre.uk1o <- readRDS("./files/cohesion/df.cohesion.asv.sid.pre.uk1o.rds")

df.coh.sid.pre.uk1i$zone <- rep("Inshore",nrow(df.coh.sid.pre.uk1i))
df.coh.sid.pre.uk1o$zone <- rep("Offshore",nrow(df.coh.sid.pre.uk1o))

df.coh.sid.pre.uk1 <- rbind(df.coh.sid.pre.uk1i,df.coh.sid.pre.uk1o)

df.coh.sid.pre.uk1$time <- rep("Pre",nrow(df.coh.sid.pre.uk1))
df.coh.sid.pre.uk1$site <- rep("UK1",nrow(df.coh.sid.pre.uk1))

ggplot(df.coh.sid.pre.uk1,aes(x=zone,y=coh.pos))+
  geom_boxplot()

#UPPER KEYS 2
df.coh.sid.pre.uk2i <- readRDS("./files/cohesion/df.cohesion.asv.sid.pre.uk2i.rds")
df.coh.sid.pre.uk2o <- readRDS("./files/cohesion/df.cohesion.asv.sid.pre.uk2o.rds")

df.coh.sid.pre.uk2i$zone <- rep("Inshore",nrow(df.coh.sid.pre.uk2i))
df.coh.sid.pre.uk2o$zone <- rep("Offshore",nrow(df.coh.sid.pre.uk2o))

df.coh.sid.pre.uk2 <- rbind(df.coh.sid.pre.uk2i,df.coh.sid.pre.uk2o)

df.coh.sid.pre.uk2$time <- rep("Pre",nrow(df.coh.sid.pre.uk2))
df.coh.sid.pre.uk2$site <- rep("UK2",nrow(df.coh.sid.pre.uk2))

ggplot(df.coh.sid.pre.uk2,aes(x=zone,y=coh.pos))+
  geom_boxplot()
```

### Irma time point - sids

```{r cohesion results irma sids, eval=F}
#LOWER KEYS 1
df.coh.sid.irm.lk1i <- readRDS("./files/cohesion/df.cohesion.asv.sid.irm.lk1i.rds")
df.coh.sid.irm.lk1o <- readRDS("./files/cohesion/df.cohesion.asv.sid.irm.lk1o.rds")

df.coh.sid.irm.lk1i$zone <- rep("Inshore",nrow(df.coh.sid.irm.lk1i))
df.coh.sid.irm.lk1o$zone <- rep("Offshore",nrow(df.coh.sid.irm.lk1o))

df.coh.sid.irm.lk1 <- rbind(df.coh.sid.irm.lk1i,df.coh.sid.irm.lk1o)

df.coh.sid.irm.lk1$time <- rep("Irma",nrow(df.coh.sid.irm.lk1))
df.coh.sid.irm.lk1$site <- rep("LK1",nrow(df.coh.sid.irm.lk1))

#UPPER KEYS 1
df.coh.sid.irm.uk1i <- readRDS("./files/cohesion/df.cohesion.asv.sid.irm.uk1i.rds")
df.coh.sid.irm.uk1o <- readRDS("./files/cohesion/df.cohesion.asv.sid.irm.uk1o.rds")

df.coh.sid.irm.uk1i$zone <- rep("Inshore",nrow(df.coh.sid.irm.uk1i))
df.coh.sid.irm.uk1o$zone <- rep("Offshore",nrow(df.coh.sid.irm.uk1o))

df.coh.sid.irm.uk1 <- rbind(df.coh.sid.irm.uk1i,df.coh.sid.irm.uk1o)

df.coh.sid.irm.uk1$time <- rep("Irma",nrow(df.coh.sid.irm.uk1))
df.coh.sid.irm.uk1$site <- rep("UK1",nrow(df.coh.sid.irm.uk1))

#UPPER KEYS 2
df.coh.sid.irm.uk2i <- readRDS("./files/cohesion/df.cohesion.asv.sid.irm.uk2i.rds")
df.coh.sid.irm.uk2o <- readRDS("./files/cohesion/df.cohesion.asv.sid.irm.uk2o.rds")

df.coh.sid.irm.uk2i$zone <- rep("Inshore",nrow(df.coh.sid.irm.uk2i))
df.coh.sid.irm.uk2o$zone <- rep("Offshore",nrow(df.coh.sid.irm.uk2o))

df.coh.sid.irm.uk2 <- rbind(df.coh.sid.irm.uk2i,df.coh.sid.irm.uk2o)

df.coh.sid.irm.uk2$time <- rep("Irma",nrow(df.coh.sid.irm.uk2))
df.coh.sid.irm.uk2$site <- rep("UK2",nrow(df.coh.sid.irm.uk2))
```

### Post - sids

```{r cohesion results post sids, eval=F}
#LOWER KEYS 1
df.coh.sid.pos.lk1i <- readRDS("./files/cohesion/df.cohesion.asv.sid.pos.lk1i.rds")
df.coh.sid.pos.lk1o <- readRDS("./files/cohesion/df.cohesion.asv.sid.pos.lk1o.rds")

df.coh.sid.pos.lk1i$zone <- rep("Inshore",nrow(df.coh.sid.pos.lk1i))
df.coh.sid.pos.lk1o$zone <- rep("Offshore",nrow(df.coh.sid.pos.lk1o))

df.coh.sid.pos.lk1 <- rbind(df.coh.sid.pos.lk1i,df.coh.sid.pos.lk1o)

df.coh.sid.pos.lk1$time <- rep("Post",nrow(df.coh.sid.pos.lk1))
df.coh.sid.pos.lk1$site <- rep("LK1",nrow(df.coh.sid.pos.lk1))

#UPPER KEYS 1
df.coh.sid.pos.uk1i <- readRDS("./files/cohesion/df.cohesion.asv.sid.pos.uk1i.rds")
df.coh.sid.pos.uk1o <- readRDS("./files/cohesion/df.cohesion.asv.sid.pos.uk1o.rds")

df.coh.sid.pos.uk1i$zone <- rep("Inshore",nrow(df.coh.sid.pos.uk1i))
df.coh.sid.pos.uk1o$zone <- rep("Offshore",nrow(df.coh.sid.pos.uk1o))

df.coh.sid.pos.uk1 <- rbind(df.coh.sid.pos.uk1i,df.coh.sid.pos.uk1o)

df.coh.sid.pos.uk1$time <- rep("Post",nrow(df.coh.sid.pos.uk1))
df.coh.sid.pos.uk1$site <- rep("UK1",nrow(df.coh.sid.pos.uk1))

#UPPER KEYS 2
df.coh.sid.pos.uk2i <- readRDS("./files/cohesion/df.cohesion.asv.sid.pos.uk2i.rds")
df.coh.sid.pos.uk2o <- readRDS("./files/cohesion/df.cohesion.asv.sid.pos.uk2o.rds")

df.coh.sid.pos.uk2i$zone <- rep("Inshore",nrow(df.coh.sid.pos.uk2i))
df.coh.sid.pos.uk2o$zone <- rep("Offshore",nrow(df.coh.sid.pos.uk2o))

df.coh.sid.pos.uk2 <- rbind(df.coh.sid.pos.uk2i,df.coh.sid.pos.uk2o)

df.coh.sid.pos.uk2$time <- rep("Post",nrow(df.coh.sid.pos.uk2))
df.coh.sid.pos.uk2$site <- rep("UK2",nrow(df.coh.sid.pos.uk2))
```

### All together - sids

```{r, eval=F}
df.coh.sid <- rbind(df.coh.sid.pre.lk1,df.coh.sid.pre.uk1,df.coh.sid.pre.uk2,df.coh.sid.irm.lk1,df.coh.sid.irm.uk1,df.coh.sid.irm.uk2,df.coh.sid.pos.lk1,df.coh.sid.pos.uk1,df.coh.sid.pos.uk2)

#saveRDS(df.coh.sid,file="df.cohesion.asv.sids.rds")
```

### Pre time point up first - rads

```{r cohesion results pre rads, eval=F}
#LOWER KEYS 1
df.coh.rad.pre.lk1i <- readRDS("./files/cohesion/df.cohesion.asv.rad.pre.lk1i.rds")
df.coh.rad.pre.lk1o <- readRDS("./files/cohesion/df.cohesion.asv.rad.pre.lk1o.rds")

df.coh.rad.pre.lk1i$zone <- rep("Inshore",nrow(df.coh.rad.pre.lk1i))
df.coh.rad.pre.lk1o$zone <- rep("Offshore",nrow(df.coh.rad.pre.lk1o))

df.coh.rad.pre.lk1 <- rbind(df.coh.rad.pre.lk1i,df.coh.rad.pre.lk1o)

df.coh.rad.pre.lk1$time <- rep("Pre",nrow(df.coh.rad.pre.lk1))
df.coh.rad.pre.lk1$site <- rep("LK1",nrow(df.coh.rad.pre.lk1))

ggplot(df.coh.rad.pre.lk1,aes(x=zone,y=coh.pos))+
  geom_boxplot()

#UPPER KEYS 1
df.coh.rad.pre.uk1i <- readRDS("./files/cohesion/df.cohesion.asv.rad.pre.uk1i.rds")
df.coh.rad.pre.uk1o <- readRDS("./files/cohesion/df.cohesion.asv.rad.pre.uk1o.rds")

df.coh.rad.pre.uk1i$zone <- rep("Inshore",nrow(df.coh.rad.pre.uk1i))
df.coh.rad.pre.uk1o$zone <- rep("Offshore",nrow(df.coh.rad.pre.uk1o))

df.coh.rad.pre.uk1 <- rbind(df.coh.rad.pre.uk1i,df.coh.rad.pre.uk1o)

df.coh.rad.pre.uk1$time <- rep("Pre",nrow(df.coh.rad.pre.uk1))
df.coh.rad.pre.uk1$site <- rep("UK1",nrow(df.coh.rad.pre.uk1))

ggplot(df.coh.rad.pre.uk1,aes(x=zone,y=coh.pos))+
  geom_boxplot()

#UPPER KEYS 2
df.coh.rad.pre.uk2i <- readRDS("./files/cohesion/df.cohesion.asv.rad.pre.uk2i.rds")
df.coh.rad.pre.uk2o <- readRDS("./files/cohesion/df.cohesion.asv.rad.pre.uk2o.rds")

df.coh.rad.pre.uk2i$zone <- rep("Inshore",nrow(df.coh.rad.pre.uk2i))
df.coh.rad.pre.uk2o$zone <- rep("Offshore",nrow(df.coh.rad.pre.uk2o))

df.coh.rad.pre.uk2 <- rbind(df.coh.rad.pre.uk2i,df.coh.rad.pre.uk2o)

df.coh.rad.pre.uk2$time <- rep("Pre",nrow(df.coh.rad.pre.uk2))
df.coh.rad.pre.uk2$site <- rep("UK2",nrow(df.coh.rad.pre.uk2))

ggplot(df.coh.rad.pre.uk2,aes(x=zone,y=coh.pos))+
  geom_boxplot()
```

### Irma time point - rads

```{r cohesion results irma rads, eval=F}
#LOWER KEYS 1
df.coh.rad.irm.lk1i <- readRDS("./files/cohesion/df.cohesion.asv.rad.irm.lk1i.rds")
df.coh.rad.irm.lk1o <- readRDS("./files/cohesion/df.cohesion.asv.rad.irm.lk1o.rds")

df.coh.rad.irm.lk1i$zone <- rep("Inshore",nrow(df.coh.rad.irm.lk1i))
df.coh.rad.irm.lk1o$zone <- rep("Offshore",nrow(df.coh.rad.irm.lk1o))

df.coh.rad.irm.lk1 <- rbind(df.coh.rad.irm.lk1i,df.coh.rad.irm.lk1o)

df.coh.rad.irm.lk1$time <- rep("Irma",nrow(df.coh.rad.irm.lk1))
df.coh.rad.irm.lk1$site <- rep("LK1",nrow(df.coh.rad.irm.lk1))

#UPPER KEYS 1
df.coh.rad.irm.uk1i <- readRDS("./files/cohesion/df.cohesion.asv.rad.irm.uk1i.rds")

df.coh.rad.irm.uk1i$zone <- rep("Inshore",nrow(df.coh.rad.irm.uk1i))

df.coh.rad.irm.uk1 <- rbind(df.coh.rad.irm.uk1i)

df.coh.rad.irm.uk1$time <- rep("Irma",nrow(df.coh.rad.irm.uk1))
df.coh.rad.irm.uk1$site <- rep("UK1",nrow(df.coh.rad.irm.uk1))

#UPPER KEYS 2
df.coh.rad.irm.uk2i <- readRDS("./files/cohesion/df.cohesion.asv.rad.irm.uk2i.rds")
df.coh.rad.irm.uk2o <- readRDS("./files/cohesion/df.cohesion.asv.rad.irm.uk2o.rds")

df.coh.rad.irm.uk2i$zone <- rep("Inshore",nrow(df.coh.rad.irm.uk2i))
df.coh.rad.irm.uk2o$zone <- rep("Offshore",nrow(df.coh.rad.irm.uk2o))

df.coh.rad.irm.uk2 <- rbind(df.coh.rad.irm.uk2i,df.coh.rad.irm.uk2o)

df.coh.rad.irm.uk2$time <- rep("Irma",nrow(df.coh.rad.irm.uk2))
df.coh.rad.irm.uk2$site <- rep("UK2",nrow(df.coh.rad.irm.uk2))
```

### Post - rads

```{r cohesion results post rads, eval=F}
#LOWER KEYS 1
df.coh.rad.pos.lk1i <- readRDS("./files/cohesion/df.cohesion.asv.rad.pos.lk1i.rds")
df.coh.rad.pos.lk1o <- readRDS("./files/cohesion/df.cohesion.asv.rad.pos.lk1o.rds")

df.coh.rad.pos.lk1i$zone <- rep("Inshore",nrow(df.coh.rad.pos.lk1i))
df.coh.rad.pos.lk1o$zone <- rep("Offshore",nrow(df.coh.rad.pos.lk1o))

df.coh.rad.pos.lk1 <- rbind(df.coh.rad.pos.lk1i,df.coh.rad.pos.lk1o)

df.coh.rad.pos.lk1$time <- rep("Post",nrow(df.coh.rad.pos.lk1))
df.coh.rad.pos.lk1$site <- rep("LK1",nrow(df.coh.rad.pos.lk1))

#UPPER KEYS 1 - not available

#UPPER KEYS 2
df.coh.rad.pos.uk2i <- readRDS("./files/cohesion/df.cohesion.asv.rad.pos.uk2i.rds")
df.coh.rad.pos.uk2o <- readRDS("./files/cohesion/df.cohesion.asv.rad.pos.uk2o.rds")

df.coh.rad.pos.uk2i$zone <- rep("Inshore",nrow(df.coh.rad.pos.uk2i))
df.coh.rad.pos.uk2o$zone <- rep("Offshore",nrow(df.coh.rad.pos.uk2o))

df.coh.rad.pos.uk2 <- rbind(df.coh.rad.pos.uk2i,df.coh.rad.pos.uk2o)

df.coh.rad.pos.uk2$time <- rep("Post",nrow(df.coh.rad.pos.uk2))
df.coh.rad.pos.uk2$site <- rep("UK2",nrow(df.coh.rad.pos.uk2))
```

### All together - rads

```{r, eval=F}
df.coh.rad <- rbind(df.coh.rad.pre.lk1,df.coh.rad.pre.uk1,df.coh.rad.pre.uk2,df.coh.rad.irm.lk1,df.coh.rad.irm.uk1,df.coh.rad.irm.uk2,df.coh.rad.pos.lk1,df.coh.rad.pos.uk2)

#saveRDS(df.coh.rad,file="df.cohesion.asv.rads.rds")
```

## Setup for plotting

```{r}
library(ggplot2)
library(cowplot)

setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_16s/04.networks")
#ASV sids
df.coh.sid <- readRDS("df.cohesion.asv.sids.rds")
df.coh.sid$zone <- as.factor(df.coh.sid$zone)
df.coh.sid$time <- factor(df.coh.sid$time,levels=c("Pre","Irma","Post"))
df.coh.sid$site <- factor(df.coh.sid$site,levels=c("UK2","UK1","LK1"))

df.coh.rad <- readRDS("df.cohesion.asv.rads.rds")
df.coh.rad$zone <- as.factor(df.coh.rad$zone)
df.coh.rad$time <- factor(df.coh.rad$time,levels=c("Pre","Irma","Post"))
df.coh.rad$site <- factor(df.coh.rad$site,levels=c("UK2","UK1","LK1"))
```

## Plotting time{.tabset}

### Sids plot

```{r}
gg.coh.pos.sids.yr <- ggplot(df.coh.sid,aes(x=time,y=coh.pos,fill=time,color=time,shape=zone))+
  facet_grid(site~zone)+  
  geom_jitter(alpha=0.5)+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Cohesion (positive)")+
  xlab("Time point")+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("(a) S. siderea")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none",shape="none",alpha="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  ylim(0,0.5)
gg.coh.pos.sids.yr

#ggsave(gg.coh.pos.sids.yr,file="plot.cohesion.sids.pdf",width=3.5,height=3.5)

gg.coh.neg.sids.yr <- ggplot(df.coh.sid,aes(x=time,y=coh.neg,fill=time,color=time,shape=zone))+
  facet_grid(site~zone)+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Cohesion (negative)")+
  xlab("Time point")+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("(a) S. siderea")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none",shape="none",alpha="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  ylim(-0.7,0.1)
gg.coh.neg.sids.yr
```

### Rads plot

```{r}
gg.coh.pos.rads.yr <- ggplot(df.coh.rad,aes(x=time,y=coh.pos,fill=time,color=time,shape=zone))+
  facet_grid(site~zone)+  
  geom_jitter(alpha=0.5)+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Cohesion (positive)")+
  xlab("Time point")+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("(b) S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none",shape="none",alpha="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  ylim(0,0.5)
gg.coh.pos.rads.yr

#ggsave(gg.coh.pos.rads.yr,file="plot.cohesion.rads.pdf",width=3.5,height=3.5)

gg.coh.neg.rads.yr <- ggplot(df.coh.rad,aes(x=time,y=coh.neg,fill=time,color=time,shape=zone))+
  facet_grid(site~zone)+  
  geom_jitter(aes(alpha=zone),position = position_jitterdodge())+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Cohesion (negative)")+
  xlab("Time point")+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  ggtitle("(b) S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none",shape="none",alpha="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  ylim(-0.7,0.1)
gg.coh.neg.rads.yr
```

## "Final" plot

```{r}
ggarrange(gg.coh.pos.sids.yr,gg.coh.pos.rads.yr)

#ggsave("both.coh.pos.pdf",height=4)

ggarrange(gg.coh.neg.sids.yr,gg.coh.neg.rads.yr)

#ggsave("both.coh.neg.pdf",height=4)
```

## Checking for reef zone differences

```{r}
ggplot(df.coh.sid,aes(x=zone,y=coh.pos,shape=zone,color=zone))+
  facet_grid(site~time)+  
  geom_jitter(alpha=0.5)+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  ylab("Cohesion (positive)")+
  xlab("Time point")+
  theme_bw()+
  scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  #ggtitle("(b) S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none",shape="none",alpha="none")+
  scale_x_discrete(labels=c("Pre","Disturb.","Post"))+
  ylim(0,0.5)

ggplot(df.coh.sid,aes(x=zone,y=coh.pos,shape=zone,color=zone))+
  facet_grid(site~time)+  
  geom_jitter(alpha=0.5)+
  #add color="black" here for outlines
  geom_boxplot(outlier.shape=NA,color="black",aes(alpha=zone))+
  #ylab("Cohesion (positive)")+
  #xlab("Time point")+
  theme_bw()+
  #scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  #scale_fill_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  theme(plot.title=element_text(face = "italic"),axis.text.x=element_text(angle=45,vjust=1.1,hjust=1))+
  #ggtitle("(b) S. radians")+
  scale_alpha_manual(values=c(0.45,0.75),name="Reef zone")+
  guides(fill="none",color="none",shape="none",alpha="none")+
  ylim(0,0.5)
```

## Cohesion statistics

### Sids, zone

```{r}
df.coh.sid.pre <- subset(df.coh.sid,time=="Pre")
df.coh.sid.pre.lk1 <- subset(df.coh.sid.pre,site=="LK1")
df.coh.sid.pre.uk1 <- subset(df.coh.sid.pre,site=="UK1")
df.coh.sid.pre.uk2 <- subset(df.coh.sid.pre,site=="UK2")

wilcox.test(coh.pos~zone,data=df.coh.sid.pre.lk1) #marg.
wilcox.test(coh.pos~zone,data=df.coh.sid.pre.uk1) #ns
wilcox.test(coh.pos~zone,data=df.coh.sid.pre.uk2) #ns

df.coh.sid.irm <- subset(df.coh.sid,time=="Irma")
df.coh.sid.irm.lk1 <- subset(df.coh.sid.irm,site=="LK1")
df.coh.sid.irm.uk1 <- subset(df.coh.sid.irm,site=="UK1")
df.coh.sid.irm.uk2 <- subset(df.coh.sid.irm,site=="UK2")

wilcox.test(coh.pos~zone,data=df.coh.sid.irm.lk1) #marg.
wilcox.test(coh.pos~zone,data=df.coh.sid.irm.uk1) #marg.
wilcox.test(coh.pos~zone,data=df.coh.sid.irm.uk2) #ns

df.coh.sid.pos <- subset(df.coh.sid,time=="Post")
df.coh.sid.pos.lk1 <- subset(df.coh.sid.pos,site=="LK1")
df.coh.sid.pos.uk1 <- subset(df.coh.sid.pos,site=="UK1")
df.coh.sid.pos.uk2 <- subset(df.coh.sid.pos,site=="UK2")

wilcox.test(coh.pos~zone,data=df.coh.sid.pos.lk1) #sig
wilcox.test(coh.pos~zone,data=df.coh.sid.pos.uk1) #ns
wilcox.test(coh.pos~zone,data=df.coh.sid.pos.uk2) #sig
```

### Sids, time

Subset

```{r}
#install.packages("dunn.test")
library(dunn.test)

df.coh.sid.lk1 <- subset(df.coh.sid,site=="LK1")
df.coh.sid.lk1i <- subset(df.coh.sid.lk1,zone=="Inshore")
df.coh.sid.lk1o <- subset(df.coh.sid.lk1,zone=="Offshore")

df.coh.sid.uk1 <- subset(df.coh.sid,site=="UK1")
df.coh.sid.uk1i <- subset(df.coh.sid.uk1,zone=="Inshore")
df.coh.sid.uk1o <- subset(df.coh.sid.uk1,zone=="Offshore")

df.coh.sid.uk2 <- subset(df.coh.sid,site=="UK2")
df.coh.sid.uk2i <- subset(df.coh.sid.uk2,zone=="Inshore")
df.coh.sid.uk2o <- subset(df.coh.sid.uk2,zone=="Offshore")
```

Go

```{r}
#LK1 - inshore
kruskal.test(coh.pos~time,data=df.coh.sid.lk1i) #p < 0.01
dunn.test(df.coh.sid.lk1i$coh.pos,df.coh.sid.lk1i$time,method="bh")
#PRE & POST ARE NOT DIFFERENT - RESILIENCE!!
# Kruskal-Wallis rank sum test
# 
# data: x and group
# Kruskal-Wallis chi-squared = 8.9707, df = 2, p-value = 0.01
# 
# 
#                            Comparison of x by group                            
#                              (Benjamini-Hochberg)                              
# Col Mean-|
# Row Mean |       Irma       Post
#     Post |   2.359643
#          |    0.0137*
#          |
#      Pre |   2.750700   0.151603
#          |    0.0089*     0.4397

#LK1 - offshore
kruskal.test(coh.pos~time,data=df.coh.sid.lk1o) #ns
dunn.test(df.coh.sid.lk1o$coh.pos,df.coh.sid.lk1o$time,method="bh") #ns

#UK1 - inshore
kruskal.test(coh.pos~time,data=df.coh.sid.uk1i) #p = 0 ***
dunn.test(df.coh.sid.uk1i$coh.pos,df.coh.sid.uk1i$time,method="bh")
#   Kruskal-Wallis rank sum test
# 
# data: x and group
# Kruskal-Wallis chi-squared = 18.718, df = 2, p-value = 0
# 
# 
#                            Comparison of x by group                            
#                              (Benjamini-Hochberg)                              
# Col Mean-|
# Row Mean |       Irma       Post
#     Post |  -3.487240
#          |    0.0004*
#          |
#      Pre |  -3.658445   0.529050
#          |    0.0004*     0.2984
# 
# alpha = 0.05
# Reject Ho if p <= alpha/2

#uk1 - offshore
kruskal.test(coh.pos~time,data=df.coh.sid.uk1o) #p < 0.01 **
dunn.test(df.coh.sid.uk1o$coh.pos,df.coh.sid.uk1o$time,method="bh") #sig!
#   Kruskal-Wallis rank sum test
# 
# data: x and group
# Kruskal-Wallis chi-squared = 13.5297, df = 2, p-value = 0
# 
# 
#                            Comparison of x by group                            
#                              (Benjamini-Hochberg)                              
# Col Mean-|
# Row Mean |       Irma       Post
#     Post |  -3.484365
#          |    0.0007*
#          |
#      Pre |  -2.515414   0.990289
#          |    0.0089*     0.1610

#UK2 - inshore
kruskal.test(coh.pos~time,data=df.coh.sid.uk2i) #p = 0 ***
dunn.test(df.coh.sid.uk2i$coh.pos,df.coh.sid.uk2i$time,method="bh")
#   Kruskal-Wallis rank sum test
# 
# data: x and group
# Kruskal-Wallis chi-squared = 14.2396, df = 2, p-value = 0
# 
# 
#                            Comparison of x by group                            
#                              (Benjamini-Hochberg)                              
# Col Mean-|
# Row Mean |       Irma       Post
#     Post |  -3.673529
#          |    0.0004*
#          |
#      Pre |  -2.359870   1.511807
#          |    0.0137*     0.0653
# 
# alpha = 0.05
# Reject Ho if p <= alpha/2

#UK2 - offshore
kruskal.test(coh.pos~time,data=df.coh.sid.uk2o) #p < 0.001 ***
dunn.test(df.coh.sid.uk2o$coh.pos,df.coh.sid.uk2o$time,method="bh")
#  Kruskal-Wallis rank sum test
# 
# data: x and group
# Kruskal-Wallis chi-squared = 16.6155, df = 2, p-value = 0
# 
# 
#                            Comparison of x by group                            
#                              (Benjamini-Hochberg)                              
# Col Mean-|
# Row Mean |       Irma       Post
#     Post |  -3.280346
#          |    0.0008*
#          |
#      Pre |  -3.663319  -0.274695
#          |    0.0004*     0.3918
# 
# alpha = 0.05
# Reject Ho if p <= alpha/2
```

### Rads, time

Setup

```{r}
#install.packages("dunn.test")
library(dunn.test)

df.coh.rad.lk1 <- subset(df.coh.rad,site=="LK1")
df.coh.rad.lk1i <- subset(df.coh.rad.lk1,zone=="Inshore")
df.coh.rad.lk1o <- subset(df.coh.rad.lk1,zone=="Offshore")

df.coh.rad.uk1 <- subset(df.coh.rad,site=="UK1")
df.coh.rad.uk1i <- subset(df.coh.rad.uk1,zone=="Inshore")
df.coh.rad.uk1o <- subset(df.coh.rad.uk1,zone=="Offshore")

df.coh.rad.uk2 <- subset(df.coh.rad,site=="UK2")
df.coh.rad.uk2i <- subset(df.coh.rad.uk2,zone=="Inshore")
df.coh.rad.uk2o <- subset(df.coh.rad.uk2,zone=="Offshore")
```

Go

```{r}
##LK1 - inshore
kruskal.test(coh.pos~time,data=df.coh.rad.lk1i) #marg sig
dunn.test(df.coh.rad.lk1i$coh.pos,df.coh.rad.lk1i$time,method="bh")
# Col Mean-|
# Row Mean |       Irma       Post
#     Post |   1.978767
#          |     0.0718
#          |
#      Pre |  -0.006093  -1.937408
#          |     0.4976     0.0395
#
# alpha = 0.05
# Reject Ho if p <= alpha/2

#LK1 - offshore
kruskal.test(coh.pos~time,data=df.coh.rad.lk1o) #marg sig
dunn.test(df.coh.rad.lk1o$coh.pos,df.coh.rad.lk1o$time,method="bh") #marg sig
 
##UK1 - inshore
kruskal.test(coh.pos~time,data=df.coh.rad.uk1i) #ns
#dunn.test(df.coh.rad.uk1i$coh.pos,df.coh.rad.uk1i$time,method="bh") #ns

#UK2 - inshore
kruskal.test(coh.pos~time,data=df.coh.rad.uk2i) #ns
dunn.test(df.coh.rad.uk2i$coh.pos,df.coh.rad.uk2i$time,method="bh") #ns
# Col Mean-|
# Row Mean |       Irma       Post
#     Post |  -0.205834
#          |     0.4185
#          |
#      Pre |  -2.004130  -1.856398
#          |     0.0676     0.0475
#
# alpha = 0.05
# Reject Ho if p <= alpha/2

#UK2 - offshore
kruskal.test(coh.pos~time,data=df.coh.rad.uk2o) #ns
dunn.test(df.coh.rad.uk2o$coh.pos,df.coh.rad.uk2o$time,method="bh") #ns
```