---
title: "Florida ITS2 analysis"
author: "Nicola G. Kriefall"
date: "12/1/21"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
---

# SymPortal pre-submission

Submitting ITS2 samples to [Symportal](symportal.org)

Prior to submission: retaining only paired reads that match ITS2 primer (we pooled with 16S during sequencing)

```{bash setup, eval=FALSE}
# *note: most of this was written by Dr. Carly D. Kenkel

# in Terminal home directory:
# following instructions of installing BBtools from https://jgi.doe.gov/data-and-tools/bbtools/bb-tools-user-guide/installation-guide/
# 1. download BBMap package, sftp to installation directory
# 2. untar: 
tar -xvzf BBMap_(version).tar.gz
# 3. test package:
cd bbmap
~/bin/bbmap/stats.sh in=~/bin/bbmap/resources/phix174_ill.ref.fa.gz

# my adaptors, which I saved as "adaptors.fasta"
# >forward
# AATGATACGGCGACCAC
# >forwardrc
# GTGGTCGCCGTATCATT
# >reverse
# CAAGCAGAAGACGGCATAC
# >reverserc
# GTATGCCGTCTTCTGCTTG

# primers for ITS2:
# >forward
# GTGAATTGCAGAACTCCGTG
# >reverse
# CCTCCGCTTACTTATATGCTT

# making a sample list based on the first phrase before the underscore in the .fastq name
ls *R1_001.fastq | cut -d '_' -f 2 > samples.list

# cuts off the extra words in the .fastq files
for file in $(cat samples.list); do  mv ${file}_*R1*.fastq ${file}_R1.fastq; mv ${file}_*R2*.fastq ${file}_R2.fastq; done 

# gets rid of reads that still have the adaptor sequence
# [I stopped doing this 'cause it never happened]
#for file in $(cat samples.list); do ~/bin/bbmap/bbduk.sh in1=${file}_R1.fastq in2=${file}_R2.fastq ref=adaptors.fasta out1=${file}_R1_NoIll.fastq out2=${file}_R2_NoIll.fastq; done &>bbduk_NoIll.log

##getting rid of first 4 bases (degenerate primers created them)
for file in $(cat samples.list); do ~/bin/bbmap/bbduk.sh in1=${file}_R1.fastq in2=${file}_R2.fastq ftl=4 out1=${file}_R1_No4N.fastq out2=${file}_R2_No4N.fastq; done &>bbduk_No4N.log

# only keeping reads that start with the primer
for file in $(cat samples.list); do ~/bin/bbmap/bbduk.sh in1=${file}_R1.fastq in2=${file}_R2.fastq k=15 restrictleft=21 literal=GTGAATTGCAGAACTCCGTG,CCTCCGCTTACTTATATGCTT outm1=${file}_R1_ITS.fastq outu1=${file}_R1_check.fastq outm2=${file}_R2_ITS.fastq outu2=${file}_R2_check.fastq; done &>bbduk_ITS.log
# higher k = more reads removed, but can't surpass k=20 or 21

# renamed them to the shorter version again after checking
for file in $(cat samples.list); do  mv ${file}_*R1*.fastq ${file}_R1.fastq; mv ${file}_*R2*.fastq ${file}_R2.fastq; done 
```

Then transferred all "R1.fastq" & "R2.fastq" files to the folder to be submitted to SymPortal

# SymPortal ITS2 analysis

Information on Symportal output documents [here](https://github.com/didillysquat/SymPortal_framework/wiki/SymPortal-output-documents)

Formatting notes:

- Cleaned up file called 188_20211214_03_DBV_20211215T030311.profiles.absolute.abund_and_meta.txt to format for phyloseq

## Setup

```{r packages, echo=FALSE}
library(phyloseq)
library('ggplot2')
library('Rmisc')
library(cowplot)
library("ggpubr")
library("vegan")
library(scales)
library(colorspace)
```

```{r working directory, include=FALSE}
#setwd("~/Google Drive (nicfall@bu.edu)/Flirma/flirma_networks/fl_its2")
setwd("/Volumes/GoogleDrive-104519233854090018057/My Drive/Flirma/flirma_networks/fl_its2")
```

## Checking for no read samples

```{r counts per sample}
counts <- read.csv('flits_symportal_profile_counts.csv',header=TRUE,row.names=1,check.names=FALSE)
#325 samples, 75 type profiles
#+1 sample that's fake 'UK1-O_000' so I can plot UK1-O below

sort(rowSums(counts))
counts.no0 <- counts[rowSums(counts)>0,]
#2 that are 0, removing them now: LK1-I_1199_srad_2018, UK2-O_1105_srad_2018
```

## Phyloseq object - type profiles

Ran once then saved to re-read in later

```{r phyloseq object, eval=F}
# import dataframe holding sample information
samdf <- read.csv("fl_sample_info - ITS2_all.csv")
head(samdf)
samdf$full_sample <- paste0(samdf$sample,"_",samdf$spp,"_",samdf$year)
rownames(samdf) <- samdf$full_sample

# import taxa info
taxa <- read.csv("flits_symportal_taxa.csv",header=TRUE,row.names=1)
#rownames(taxa) <- as.factor(taxa$ITS2_type_profile)
mtaxa <- as.matrix(taxa)

# import counts (absolute abundance from its2 type profiles)
mcounts <- as.matrix(counts.no0)

# Construct phyloseq object 
ps <- phyloseq(otu_table(mcounts, taxa_are_rows=FALSE),
               sample_data(samdf),
               tax_table(mtaxa))

ps
# phyloseq-class experiment-level object
# otu_table()   OTU Table:         [ 75 taxa and 324 samples ]
# sample_data() Sample Data:       [ 324 samples by 12 sample variables ]
# tax_table()   Taxonomy Table:    [ 75 taxa by 5 taxonomic ranks ]

#saveRDS(ps,file="ps.its2.rds")
```

## Re-read in data

```{r re-read data}
ps <- readRDS("ps.its2.RDS")
```

## Subset data for bar plots

```{r}
ps <- subset_samples(ps,site!="UK3")

ps.sid <- subset_samples(ps,spp=="ssid")

ps.sid.pre <- subset_samples(ps.sid,time=="Pre")
ps.sid.irm <- subset_samples(ps.sid,time=="Irma")
ps.sid.pos <- subset_samples(ps.sid,time=="Post")

ps.sid.pre.lk1 <- subset_samples(ps.sid.pre,site=="LK1")
ps.sid.pre.uk1 <- subset_samples(ps.sid.pre,site=="UK1")
ps.sid.pre.uk2 <- subset_samples(ps.sid.pre,site=="UK2")

ps.sid.irm.lk1 <- subset_samples(ps.sid.irm,site=="LK1")
ps.sid.irm.uk1 <- subset_samples(ps.sid.irm,site=="UK1")
ps.sid.irm.uk2 <- subset_samples(ps.sid.irm,site=="UK2")

ps.sid.pos.lk1 <- subset_samples(ps.sid.pos,site=="LK1")
ps.sid.pos.uk1 <- subset_samples(ps.sid.pos,site=="UK1")
ps.sid.pos.uk2 <- subset_samples(ps.sid.pos,site=="UK2")

ps.gen <- tax_glom(ps,"Clade")
ntaxa(ps); ntaxa(ps.gen)

#siderea
ps.sid.gen <- subset_samples(ps.gen,spp=="ssid")

ps.sid.gen.pre <- subset_samples(ps.sid.gen,time=="Pre")
ps.sid.gen.irm <- subset_samples(ps.sid.gen,time=="Irma")
ps.sid.gen.pos <- subset_samples(ps.sid.gen,time=="Post")

#radians
ps.rad.gen <- subset_samples(ps.gen,spp=="srad")

ps.rad.gen.pre <- subset_samples(ps.rad.gen,time=="Pre")
ps.rad.gen.irm <- subset_samples(ps.rad.gen,time=="Irma")
ps.rad.gen.pos <- subset_samples(ps.rad.gen,time=="Post")
```

## Bar plots by genus {.tabset}

### S. siderea

```{r genus ssid}
ps.sid.gen.pre.rel <- transform_sample_counts(ps.sid.gen.pre, function(x) x / sum(x))
ps.sid.gen.pre.rel.sz <- merge_samples(ps.sid.gen.pre.rel, "site_zone")
ps.sid.gen.pre.rel.sz.rel <- transform_sample_counts(ps.sid.gen.pre.rel.sz, function(x) x / sum(x))

bar.sid.gen.pre.sz <- plot_bar(ps.sid.gen.pre.rel.sz.rel, fill="Clade")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.gen.pre.sz

ps.sid.gen.irm.rel <- transform_sample_counts(ps.sid.gen.irm, function(x) x / sum(x))
ps.sid.gen.irm.rel.sz <- merge_samples(ps.sid.gen.irm.rel, "site_zone")
ps.sid.gen.irm.rel.sz.rel <- transform_sample_counts(ps.sid.gen.irm.rel.sz, function(x) x / sum(x))

bar.sid.gen.irm.sz <- plot_bar(ps.sid.gen.irm.rel.sz.rel, fill="Clade")+
    ggtitle("irm")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.gen.irm.sz

ps.sid.gen.pos.rel <- transform_sample_counts(ps.sid.gen.pos, function(x) x / sum(x))
ps.sid.gen.pos.rel.sz <- merge_samples(ps.sid.gen.pos.rel, "site_zone")
ps.sid.gen.pos.rel.sz.rel <- transform_sample_counts(ps.sid.gen.pos.rel.sz, function(x) x / sum(x))

bar.sid.gen.pos.sz <- plot_bar(ps.sid.gen.pos.rel.sz.rel, fill="Clade")+
    ggtitle("pos")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.gen.pos.sz

gg.bar.clade <- ggarrange(bar.sid.gen.pre.sz,bar.sid.gen.irm.sz,bar.sid.gen.pos.sz,ncol=3,common.legend=T,legend="right")
gg.bar.clade
#ggsave("bar.clade_horizontal.pdf",width=9,height=4)
```

### S. radians

```{r genus srad}
ps.rad.gen.pre.rel <- transform_sample_counts(ps.rad.gen.pre, function(x) x / sum(x))
ps.rad.gen.pre.rel.sz <- merge_samples(ps.rad.gen.pre.rel, "site_zone")
ps.rad.gen.pre.rel.sz <- transform_sample_counts(ps.rad.gen.pre.rel.sz, function(x) x / sum(x))

gg.bar.pre <- plot_bar(ps.rad.gen.pre.rel.sz, fill="Clade")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
gg.bar.pre

ps.rad.gen.irm.rel <- transform_sample_counts(ps.rad.gen.irm, function(x) x / sum(x))
ps.rad.gen.irm.rel.sz <- merge_samples(ps.rad.gen.irm.rel, "site_zone")
ps.rad.gen.irm.rel.sz <- transform_sample_counts(ps.rad.gen.irm.rel.sz, function(x) x / sum(x))

gg.bar.irm <- plot_bar(ps.rad.gen.irm.rel.sz, fill="Clade")+
    ggtitle("Irma")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")

ps.rad.gen.pos.rel <- transform_sample_counts(ps.rad.gen.pos, function(x) x / sum(x))
ps.rad.gen.pos.rel.sz <- merge_samples(ps.rad.gen.pos.rel, "site_zone")
ps.rad.gen.pos.rel.sz <- transform_sample_counts(ps.rad.gen.pos.rel.sz, function(x) x / sum(x))

gg.bar.pos <- plot_bar(ps.rad.gen.pos.rel.sz, fill="Clade")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")

gg.bar.clade <- ggarrange(gg.bar.pre,gg.bar.irm,gg.bar.pos,ncol=3,common.legend=T,legend="right")
gg.bar.clade
#ggsave("bar.clade.radians.pdf",width=9,height=4)
```

## Bar plots by majority sequence

### Assessing type profile distances

Note - used file "20211215T030311_unifrac_profiles_PCoA_coords_B_sqrt.csv", made the name shorter. I also removed the 'proportion explained' line at the end. Also added the first type that shows up as its own column, 'first_type'

Proportion explained: PC1 0.584828597, PC2 0.146734687
For bray curtis: PC1 0.231, PC2 0.139

```{r determine groupings}
library(ggrepel)

setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_its2")

uni.cord <- read.csv("unifrac_profiles_PCoA_coords_B_sqrt.csv")

ggplot(uni.cord,aes(x=PC1,y=PC2,color=type_collapsed,label=sample))+
  geom_point()+
  xlab("PC1 (58.5%)")+
  ylab("PC2 (14.7%)")+
  geom_text_repel(max.overlaps=20)+
  stat_ellipse()+
  theme_bw()
#separated B5-1* & B5-2* by the 0 on PC2, except for 1 that was just below 0

#ggsave(file="pca_grouped.pdf",w=12,h=10)

#checking bray curtis
bray.cord <- read.csv("braycurtis_profiles_PCoA_coords_B_sqrt.csv")

ggplot(bray.cord,aes(x=PC1,y=PC2,color=type_bray,label=sample))+
  geom_point()+
  geom_text_repel(max.overlaps=20)+
  stat_ellipse()
```

Important setup

```{r set up its2 profiles}
ps.maj <- tax_glom(ps,"Majority_ITS2_collapsed")
#ps.maj <- tax_glom(ps,"Majority_ITS2_sequence_bray")

ntaxa(ps); ntaxa(ps.maj) #18 for unifrac sids, 14 for rads
#16 for bray sids

ps.maj <- subset_samples(ps.maj,site!="UK3")

#siderea
ps.maj.sid <- subset_samples(ps.maj,spp=="ssid")

ps.maj.sid.pre <- subset_samples(ps.maj.sid,time=="Pre")
ps.maj.sid.pre.lk1 <- subset_samples(ps.maj.sid.pre,site=="LK1")
ps.maj.sid.pre.uk1 <- subset_samples(ps.maj.sid.pre,site=="UK1")
ps.maj.sid.pre.uk2 <- subset_samples(ps.maj.sid.pre,site=="UK2")

ps.maj.sid.irm <- subset_samples(ps.maj.sid,time=="Irma")
ps.maj.sid.irm.lk1 <- subset_samples(ps.maj.sid.irm,site=="LK1")
ps.maj.sid.irm.uk1 <- subset_samples(ps.maj.sid.irm,site=="UK1")
ps.maj.sid.irm.uk2 <- subset_samples(ps.maj.sid.irm,site=="UK2")

ps.maj.sid.pos <- subset_samples(ps.maj.sid,time=="Post")
ps.maj.sid.pos.lk1 <- subset_samples(ps.maj.sid.pos,site=="LK1")
ps.maj.sid.pos.uk1 <- subset_samples(ps.maj.sid.pos,site=="UK1")
ps.maj.sid.pos.uk2 <- subset_samples(ps.maj.sid.pos,site=="UK2")

#radians
ps.maj.rad <- subset_samples(ps.maj,spp=="srad")

ps.maj.rad.pre <- subset_samples(ps.maj.rad,time=="Pre")
ps.maj.rad.pre.lk1 <- subset_samples(ps.maj.rad.pre,site=="LK1")
ps.maj.rad.pre.uk1 <- subset_samples(ps.maj.rad.pre,site=="UK1")
ps.maj.rad.pre.uk2 <- subset_samples(ps.maj.rad.pre,site=="UK2")

ps.maj.rad.irm <- subset_samples(ps.maj.rad,time=="Irma")
ps.maj.rad.irm.lk1 <- subset_samples(ps.maj.rad.irm,site=="LK1")
ps.maj.rad.irm.uk1 <- subset_samples(ps.maj.rad.irm,site=="UK1")
ps.maj.rad.irm.uk2 <- subset_samples(ps.maj.rad.irm,site=="UK2")

ps.maj.rad.pos <- subset_samples(ps.maj.rad,time=="Post")
ps.maj.rad.pos.lk1 <- subset_samples(ps.maj.rad.pos,site=="LK1")
#ps.maj.rad.pos.uk1 <- subset_samples(ps.maj.rad.pos,site=="UK1")
#not available
ps.maj.rad.pos.uk2 <- subset_samples(ps.maj.rad.pos,site=="UK2")
```

Removing black bars from phyloseq plot

```{r}
plot_bar2 <-  function (physeq, x = "Sample", y = "Abundance", fill = NULL, title = NULL, facet_grid = NULL, border_color = NA) 
{
  mdf = psmelt(physeq)
  p = ggplot(mdf, aes_string(x = x, y = y, fill = fill))
  p = p + geom_bar(stat = "identity", position = "stack",  color = border_color)
  p = p + theme(axis.text.x = element_text(angle = -90, hjust = 0))
  if (!is.null(facet_grid)) {
    p <- p + facet_grid(facet_grid)
  }
  if (!is.null(title)) {
    p <- p + ggtitle(title)
  }
  return(p)
}

maj.seq.colors <- c("#474747","#7A7A7A","#A8A8A8","#00294D","#195481","#5882AF","#9AB0CE","#D6DDE9","#D3E0D2","#95B792","#548C4E","#1F5D12","#002F00","#B8773A")
```

### The plots{.tabset}

#### S. siderea

LOWER KEYS 1

```{r}
ps.maj.sid.pre.lk1.rel <- transform_sample_counts(ps.maj.sid.pre.lk1, function(x) x / sum(x))
ps.maj.sid.pre.lk1.rel.zone <- merge_samples(ps.maj.sid.pre.lk1.rel, "zone")
ps.maj.sid.pre.lk1.zone <- transform_sample_counts(ps.maj.sid.pre.lk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.pre.lk1.zone <- plot_bar2(ps.maj.sid.pre.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pre.lk1.zone

ps.maj.sid.irm.lk1.rel <- transform_sample_counts(ps.maj.sid.irm.lk1, function(x) x / sum(x))
ps.maj.sid.irm.lk1.rel.zone <- merge_samples(ps.maj.sid.irm.lk1.rel, "zone")
ps.maj.sid.irm.lk1.zone <- transform_sample_counts(ps.maj.sid.irm.lk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.irm.lk1.zone <- plot_bar2(ps.maj.sid.irm.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.irm.lk1.zone

ps.maj.sid.pos.lk1.rel <- transform_sample_counts(ps.maj.sid.pos.lk1, function(x) x / sum(x))
ps.maj.sid.pos.lk1.rel.zone <- merge_samples(ps.maj.sid.pos.lk1.rel, "zone")
ps.maj.sid.pos.lk1.zone <- transform_sample_counts(ps.maj.sid.pos.lk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.pos.lk1.zone <- plot_bar2(ps.maj.sid.pos.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pos.lk1.zone

#ggarrange(gg.maj.sid.pre.lk1.zone,gg.maj.sid.irm.lk1.zone,gg.maj.sid.pos.lk1.zone,nrow=1)
```

UPPER KEYS 1

```{r}
ps.maj.sid.pre.uk1.rel <- transform_sample_counts(ps.maj.sid.pre.uk1, function(x) x / sum(x))
ps.maj.sid.pre.uk1.rel.zone <- merge_samples(ps.maj.sid.pre.uk1.rel, "zone")
ps.maj.sid.pre.uk1.zone <- transform_sample_counts(ps.maj.sid.pre.uk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.pre.uk1.zone <- plot_bar2(ps.maj.sid.pre.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pre.uk1.zone

ps.maj.sid.irm.uk1.rel <- transform_sample_counts(ps.maj.sid.irm.uk1, function(x) x / sum(x))
ps.maj.sid.irm.uk1.rel.zone <- merge_samples(ps.maj.sid.irm.uk1.rel, "zone")
ps.maj.sid.irm.uk1.zone <- transform_sample_counts(ps.maj.sid.irm.uk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.irm.uk1.zone <- plot_bar2(ps.maj.sid.irm.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.irm.uk1.zone

ps.maj.sid.pos.uk1.rel <- transform_sample_counts(ps.maj.sid.pos.uk1, function(x) x / sum(x))
ps.maj.sid.pos.uk1.rel.zone <- merge_samples(ps.maj.sid.pos.uk1.rel, "zone")
ps.maj.sid.pos.uk1.zone <- transform_sample_counts(ps.maj.sid.pos.uk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.pos.uk1.zone <- plot_bar2(ps.maj.sid.pos.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pos.uk1.zone

#ggarrange(gg.maj.sid.pre.uk1.zone,gg.maj.sid.irm.uk1.zone,gg.maj.sid.pos.uk1.zone,nrow=1)
```

UPPER KEYS 2

```{r}
ps.maj.sid.pre.uk2.rel <- transform_sample_counts(ps.maj.sid.pre.uk2, function(x) x / sum(x))
ps.maj.sid.pre.uk2.rel.zone <- merge_samples(ps.maj.sid.pre.uk2.rel, "zone")
ps.maj.sid.pre.uk2.zone <- transform_sample_counts(ps.maj.sid.pre.uk2.rel.zone, function(x) x / sum(x))

gg.maj.sid.pre.uk2.zone <- plot_bar2(ps.maj.sid.pre.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pre.uk2.zone

ps.maj.sid.irm.uk2.rel <- transform_sample_counts(ps.maj.sid.irm.uk2, function(x) x / sum(x))
ps.maj.sid.irm.uk2.rel.zone <- merge_samples(ps.maj.sid.irm.uk2.rel, "zone")
ps.maj.sid.irm.uk2.zone <- transform_sample_counts(ps.maj.sid.irm.uk2.rel.zone, function(x) x / sum(x))

gg.maj.sid.irm.uk2.zone <- plot_bar2(ps.maj.sid.irm.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.irm.uk2.zone

ps.maj.sid.pos.uk2.rel <- transform_sample_counts(ps.maj.sid.pos.uk2, function(x) x / sum(x))
ps.maj.sid.pos.uk2.rel.zone <- merge_samples(ps.maj.sid.pos.uk2.rel, "zone")
ps.maj.sid.pos.uk2.zone <- transform_sample_counts(ps.maj.sid.pos.uk2.rel.zone, function(x) x / sum(x))

gg.maj.sid.pos.uk2.zone <- plot_bar2(ps.maj.sid.pos.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pos.uk2.zone

#ggarrange(gg.maj.sid.pre.uk2.zone,gg.maj.sid.irm.uk2.zone,gg.maj.sid.pos.uk2.zone,nrow=1)
```

All the sites

```{r}
ggarrange(gg.maj.sid.pre.lk1.zone,gg.maj.sid.irm.lk1.zone,gg.maj.sid.pos.lk1.zone,gg.maj.sid.pre.uk1.zone,gg.maj.sid.irm.uk1.zone,gg.maj.sid.pos.uk1.zone,gg.maj.sid.pre.uk2.zone,gg.maj.sid.irm.uk2.zone,gg.maj.sid.pos.uk2.zone,nrow=3,ncol=3,common.legend=T,legend="right")

#ggsave("gg.its2.sids.pdf",h=8,w=7)
```

#### S. radians

LOWER KEYS 1

```{r rad lk1}
ps.maj.rad.pre.lk1.rel <- transform_sample_counts(ps.maj.rad.pre.lk1, function(x) x / sum(x))
ps.maj.rad.pre.lk1.rel.zone <- merge_samples(ps.maj.rad.pre.lk1.rel, "zone")
ps.maj.rad.pre.lk1.zone <- transform_sample_counts(ps.maj.rad.pre.lk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.pre.lk1.zone <- plot_bar2(ps.maj.rad.pre.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pre.lk1.zone

ps.maj.rad.irm.lk1.rel <- transform_sample_counts(ps.maj.rad.irm.lk1, function(x) x / sum(x))
ps.maj.rad.irm.lk1.rel.zone <- merge_samples(ps.maj.rad.irm.lk1.rel, "zone")
ps.maj.rad.irm.lk1.zone <- transform_sample_counts(ps.maj.rad.irm.lk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.irm.lk1.zone <- plot_bar2(ps.maj.rad.irm.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.irm.lk1.zone

ps.maj.rad.pos.lk1.rel <- transform_sample_counts(ps.maj.rad.pos.lk1, function(x) x / sum(x))
ps.maj.rad.pos.lk1.rel.zone <- merge_samples(ps.maj.rad.pos.lk1.rel, "zone")
ps.maj.rad.pos.lk1.zone <- transform_sample_counts(ps.maj.rad.pos.lk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.pos.lk1.zone <- plot_bar2(ps.maj.rad.pos.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pos.lk1.zone

#ggarrange(gg.maj.rad.pre.lk1.zone,gg.maj.rad.irm.lk1.zone,gg.maj.rad.pos.lk1.zone,nrow=1)
```

UPPER KEYS 1

```{r rad uk1}
ps.maj.rad.pre.uk1.rel <- transform_sample_counts(ps.maj.rad.pre.uk1, function(x) x / sum(x))
ps.maj.rad.pre.uk1.rel.zone <- merge_samples(ps.maj.rad.pre.uk1.rel, "zone")
ps.maj.rad.pre.uk1.zone <- transform_sample_counts(ps.maj.rad.pre.uk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.pre.uk1.zone <- plot_bar2(ps.maj.rad.pre.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pre.uk1.zone

ps.maj.rad.irm.uk1.rel <- transform_sample_counts(ps.maj.rad.irm.uk1, function(x) x / sum(x))
ps.maj.rad.irm.uk1.rel.zone <- merge_samples(ps.maj.rad.irm.uk1.rel, "zone")
ps.maj.rad.irm.uk1.zone <- transform_sample_counts(ps.maj.rad.irm.uk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.irm.uk1.zone <- plot_bar2(ps.maj.rad.irm.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.irm.uk1.zone

#uk1 not available for Post

#ggarrange(gg.maj.rad.pre.uk1.zone,gg.maj.rad.irm.uk1.zone,gg.maj.rad.pos.uk1.zone,nrow=1)
```

UPPER KEYS 2

```{r}
ps.maj.rad.pre.uk2.rel <- transform_sample_counts(ps.maj.rad.pre.uk2, function(x) x / sum(x))
ps.maj.rad.pre.uk2.rel.zone <- merge_samples(ps.maj.rad.pre.uk2.rel, "zone")
ps.maj.rad.pre.uk2.zone <- transform_sample_counts(ps.maj.rad.pre.uk2.rel.zone, function(x) x / sum(x))

gg.maj.rad.pre.uk2.zone <- plot_bar2(ps.maj.rad.pre.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pre.uk2.zone

ps.maj.rad.irm.uk2.rel <- transform_sample_counts(ps.maj.rad.irm.uk2, function(x) x / sum(x))
ps.maj.rad.irm.uk2.rel.zone <- merge_samples(ps.maj.rad.irm.uk2.rel, "zone")
ps.maj.rad.irm.uk2.zone <- transform_sample_counts(ps.maj.rad.irm.uk2.rel.zone, function(x) x / sum(x))

gg.maj.rad.irm.uk2.zone <- plot_bar2(ps.maj.rad.irm.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.irm.uk2.zone

ps.maj.rad.pos.uk2.rel <- transform_sample_counts(ps.maj.rad.pos.uk2, function(x) x / sum(x))
ps.maj.rad.pos.uk2.rel.zone <- merge_samples(ps.maj.rad.pos.uk2.rel, "zone")
ps.maj.rad.pos.uk2.zone <- transform_sample_counts(ps.maj.rad.pos.uk2.rel.zone, function(x) x / sum(x))

gg.maj.rad.pos.uk2.zone <- plot_bar2(ps.maj.rad.pos.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pos.uk2.zone

#ggarrange(gg.maj.rad.pre.uk2.zone,gg.maj.rad.irm.uk2.zone,gg.maj.rad.pos.uk2.zone,nrow=1)
```

All the sites

```{r}
ggarrange(gg.maj.rad.pre.lk1.zone,gg.maj.rad.irm.lk1.zone,gg.maj.rad.pos.lk1.zone,gg.maj.rad.pre.uk1.zone,gg.maj.rad.irm.uk1.zone,gg.maj.rad.pre.uk2.zone,gg.maj.rad.irm.uk2.zone,gg.maj.rad.pos.uk2.zone,nrow=3,ncol=3,common.legend=T,legend="right")

#ggsave("gg.its2.rads.pdf",h=8,w=7)
```

### Different version of the same type profile plot

```{r sids by maj seq unifrac}
ps.maj.sid.pre.rel <- transform_sample_counts(ps.maj.sid.pre, function(x) x / sum(x))
ps.maj.sid.pre.rel.sz <- merge_samples(ps.maj.sid.pre.rel, "site_zone")
ps.maj.sid.pre.rel.sz <- transform_sample_counts(ps.maj.sid.pre.rel.sz, function(x) x / sum(x))

gg.bar.pre <- plot_bar2(ps.maj.sid.pre.rel.sz, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")
gg.bar.pre

ps.maj.sid.irm.rel <- transform_sample_counts(ps.maj.sid.irm, function(x) x / sum(x))
ps.maj.sid.irm.rel.sz <- merge_samples(ps.maj.sid.irm.rel, "site_zone")
ps.maj.sid.irm.rel.sz <- transform_sample_counts(ps.maj.sid.irm.rel.sz, function(x) x / sum(x))

gg.bar.irm <- plot_bar(ps.maj.sid.irm.rel.sz, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturbance")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
    scale_fill_manual(values=maj.seq.colors)
gg.bar.irm

ps.maj.sid.pos.rel <- transform_sample_counts(ps.maj.sid.pos, function(x) x / sum(x))
ps.maj.sid.pos.rel.sz <- merge_samples(ps.maj.sid.pos.rel, "site_zone")
ps.maj.sid.pos.rel.sz <- transform_sample_counts(ps.maj.sid.pos.rel.sz, function(x) x / sum(x))

gg.bar.pos <- plot_bar(ps.maj.sid.pos.rel.sz, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
    scale_fill_manual(values=maj.seq.colors)
gg.bar.pos

gg.bar.its2 <- ggarrange(gg.bar.pre,gg.bar.irm,gg.bar.pos,ncol=3,common.legend=T,legend="right")
gg.bar.its2
#ggsave("bar.its2.sids.pdf",width=9,height=4)
```

Type profile - Bray-Curtis distance

```{r types by bray}
maj.seq.colors <- c("#1B1B1B","#969696","#F9F9F9","#00294D","#195481","#5882AF","#9AB0CE","#D6DDE9","#D3E0D2","#95B792","#548C4E","#1F5D12","#002F00","#B8773A")
                         
ps.maj.sid.pre.rel <- transform_sample_counts(ps.maj.sid.pre, function(x) x / sum(x))
ps.maj.sid.pre.rel.sz <- merge_samples(ps.maj.sid.pre.rel, "site_zone")
ps.maj.sid.pre.rel.sz <- transform_sample_counts(ps.maj.sid.pre.rel.sz, function(x) x / sum(x))

gg.bar.pre <- plot_bar(ps.maj.sid.pre.rel.sz, fill="Majority_ITS2_sequence_bray")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_fill_manual(values=maj.seq.colors)
gg.bar.pre

ps.maj.sid.irm.rel <- transform_sample_counts(ps.maj.sid.irm, function(x) x / sum(x))
ps.maj.sid.irm.rel.sz <- merge_samples(ps.maj.sid.irm.rel, "site_zone")
ps.maj.sid.irm.rel.sz <- transform_sample_counts(ps.maj.sid.irm.rel.sz, function(x) x / sum(x))

gg.bar.irm <- plot_bar(ps.maj.sid.irm.rel.sz, fill="Majority_ITS2_sequence_bray")+
    ggtitle("Disturbance")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
    scale_fill_manual(values=maj.seq.colors)
gg.bar.irm

ps.maj.sid.pos.rel <- transform_sample_counts(ps.maj.sid.pos, function(x) x / sum(x))
ps.maj.sid.pos.rel.sz <- merge_samples(ps.maj.sid.pos.rel, "site_zone")
ps.maj.sid.pos.rel.sz <- transform_sample_counts(ps.maj.sid.pos.rel.sz, function(x) x / sum(x))

gg.bar.pos <- plot_bar(ps.maj.sid.pos.rel.sz, fill="Majority_ITS2_sequence_bray")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
    scale_fill_manual(values=maj.seq.colors)
gg.bar.pos

gg.bar.its2 <- ggarrange(gg.bar.pre,gg.bar.irm,gg.bar.pos,ncol=3,common.legend=T,legend="right")
gg.bar.its2
#ggsave("bar.its2.sids.pdf",width=9,height=4)
```

## Bar plot by type profile

### Setup - packages

```{r}
#remotes::install_github("KarstensLab/microshades")
library("microshades")
#remotes::install_github("mikemc/speedyseq")
library("speedyseq")
library(ggpubr)
library(cowplot)

#setwd("/Volumes/GoogleDrive-104519233854090018057/My Drive/Flirma/flirma_networks/fl_its2")
setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_its2")
```

### Setup - data

```{r}
ps <- readRDS("ps.its2.rds")

ps <- subset_samples(ps,site!="UK3")

ps.sid <- subset_samples(ps,spp=="ssid")
ps.rad <- subset_samples(ps,spp=="srad")

ps.sid.no0 <- prune_taxa(taxa_sums(ps.sid)!=0,ps.sid)
ps.rad.no0 <- prune_taxa(taxa_sums(ps.rad)!=0,ps.rad)
```

### Microshades!{.tabset}

#### Microshades plot - sids

```{r}
# Use microshades function prep_mdf to agglomerate, normalize, and melt the phyloseq object
mdf.ps.sid <- prep_mdf(ps.sid.no0,subgroup_level="Majority_ITS2_collapsed")

type_groups <- c(unique(mdf.ps.sid$Clade))

# Create a color object for the specified data
col.mdf.ps.sid <- create_color_dfs(mdf.ps.sid, top_orientation = FALSE,group_level="Clade",subgroup_level="Majority_ITS2_collapsed",selected_groups=c("A","B","C","D"),cvd=TRUE)

# Extract
col.mdf.ps.sid.m <- col.mdf.ps.sid$mdf
col.mdf.ps.sid.c <- col.mdf.ps.sid$cdf

col.mdf.ps.sid.m$zone <- sub("I","Inshore",col.mdf.ps.sid.m$zone)
col.mdf.ps.sid.m$zone <- sub("O","Offshore",col.mdf.ps.sid.m$zone)

col.mdf.ps.sid.m$time <- factor(col.mdf.ps.sid.m$time,levels=c("Pre","Irma","Post"))

col.mdf.ps.sid.c.new <- color_reassign(col.mdf.ps.sid.c,
                          group_assignment = c("A","B","C","D"),
                          color_assignment = c("micro_gray","micro_cvd_blue","micro_cvd_green","micro_brown"),group_level="Clade")

col.mdf.ps.sid.m.lk1 <- subset(col.mdf.ps.sid.m,site=="LK1")

ms.plot.lk1 <- plot_microshades(col.mdf.ps.sid.m.lk1, col.mdf.ps.sid.c.new)+
  facet_wrap(zone~time,scales="free_x")+
  theme_cowplot()+
  theme(axis.text.x=element_blank())+
  ggtitle("Lower Keys 1")
  #theme(axis.text.x=element_text(angle=45,hjust=1))
ms.plot.lk1

col.mdf.ps.sid.m.uk1 <- subset(col.mdf.ps.sid.m,site=="UK1")

ms.plot.uk1 <- plot_microshades(col.mdf.ps.sid.m.uk1, col.mdf.ps.sid.c.new)+
  facet_wrap(zone~time,scales="free_x")+
  theme_cowplot()+
  theme(axis.text.x=element_blank())+
  ggtitle("Upper Keys 1")
  #theme(axis.text.x=element_text(angle=45,hjust=1))
ms.plot.uk1


```

```{r}
ps.sid.pre.lk1i.rel <- transform_sample_counts(ps.sid.pre.lk1i, function(x) x / sum(x))

bar.sid.pre.lk1i <- plot_bar(ps.sid.pre.lk1i.rel, fill="ITS2_type_profile")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1),legend.position="bottom")+
    xlab("")
bar.sid.pre.lk1i

ps.sid.irm.rel <- transform_sample_counts(ps.sid.irm, function(x) x / sum(x))
ps.sid.irm.rel.sz <- merge_samples(ps.sid.irm.rel, "site_zone")
ps.sid.irm.rel.sz.rel <- transform_sample_counts(ps.sid.irm.rel.sz, function(x) x / sum(x))

bar.sid.irm.sz <- plot_bar(ps.sid.irm.rel.sz.rel, fill="Clade")+
    ggtitle("irm")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.irm.sz

ps.sid.pos.rel <- transform_sample_counts(ps.sid.pos, function(x) x / sum(x))
ps.sid.pos.rel.sz <- merge_samples(ps.sid.pos.rel, "site_zone")
ps.sid.pos.rel.sz.rel <- transform_sample_counts(ps.sid.pos.rel.sz, function(x) x / sum(x))

bar.sid.pos.sz <- plot_bar(ps.sid.pos.rel.sz.rel, fill="Clade")+
    ggtitle("pos")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.pos.sz

gg.bar.clade <- ggarrange(bar.sid.pre.sz,bar.sid.irm.sz,bar.sid.pos.sz,ncol=3,common.legend=T,legend="right")
gg.bar.clade
```


```{r heat map?}
ps.sid.pre.sz <- merge_samples(ps.sid.pre,"site_zone")
ps.sid.pre.sz <- merge_samples(ps.sid.pre,"site_zone")
ps.sid.pre.sz <- merge_samples(ps.sid.pre,"site_zone")

ps.sid.pre.sz.no0 <- prune_taxa(taxa_sums(ps.sid.pre.sz)!=0,ps.sid.pre.sz)
ps.sid.pre.sz.no0.rel <- transform_sample_counts(ps.sid.pre.sz.no0, function(x) x / sum(x))

sppAbun <- as.data.frame(ps.sid.pre.sz.no0.rel@otu_table)
heatmap(as.matrix(sppAbun))


plot_heatmap(ps.sid.pre.lk1.z.no0.rel)

sppAbun <- as.data.frame(ps.sid.pre.lk1.z@otu_table)

sppAbun[sppAbun > 0] <- 1 #converts from abundance to P/A
sppAbun

sppAbun2 <- sppAbun[,colSums(sppAbun)>0]

heatmap(as.matrix(sppAbun2))

heatmap.2(as.matrix(sppAbun2),Rowv=FALSE,Colv=FALSE)


ps.sid.lk1 <- subset_samples(ps.sid.no0,site=="LK1")
ps.sid.lk1.rel <- transform_sample_counts(ps.sid.lk1, function(x) x / sum(x))

plot_heatmap(ps.sid.lk1.rel)

plot_heatmap(ps.sid.lk1.rel,sample.order="zone",low="blue",high="red",na.value="black",method=NULL,distance=NULL)

## Presence/absence



mnwb.names <- subset(samdf,site_zone=="MNW-B")
mnwf.names <- subset(samdf,site_zone=="MNW-F")

mnwb.rows <- c(row.names(mnwb.names))

mnwb.pres <- sppAbun[row.names(sppAbun) %in% mnwb.rows,]
colSums(mnwb.pres)
plot(colSums(mnwb.pres))

#install.packages("gplots")
library(gplots)
heatmap.2(as.matrix(sppAbun),Rowv=FALSE,Colv=FALSE)
dev.off()

heatmap(as.matrix(sppAbun), scale='none')

ps.bin <- phyloseq(otu_table(sppAbun, taxa_are_rows=FALSE),
               sample_data(samdf),
               tax_table(mtaxa))

ps.bin


plot_heatmap(ps.bin,sample.order="site_zone")
dev.off()


#install.packages("gplots")
library(gplots)
heatmap.2(as.matrix(sppAbun),Rowv=FALSE,Colv=FALSE)
dev.off()

heatmap(as.matrix(sppAbun), scale='none')

ps.bin <- phyloseq(otu_table(sppAbun, taxa_are_rows=FALSE),
               sample_data(samdf),
               tax_table(mtaxa))

ps.bin


plot_heatmap(ps.bin,sample.order="site_zone")
dev.off()

```

```{r bubble plot?}
library(reshape2)

ps.sid.lk1.rel.pre <- subset_samples(ps.sid.lk1.rel,time=="Pre")
ps.sid.lk1.rel.pre.no0 <- prune_taxa(taxa_sums(ps.sid.lk1.rel.pre)!=0,ps.sid.lk1.rel.pre)

pc <- data.frame(ps.sid.lk1.rel.pre.no0@otu_table)
pc$Sample <- row.names(pc)
pcm = melt(pc, id = "Sample")

#pcm$Sample <- factor(pcm$Sample,levels=unique(pcm$Sample))
pcm$value <- as.numeric(pcm$value)

ggplot(pcm, aes(x = Sample, y = variable)) + 
  geom_point(aes(size = value, fill = variable), alpha = 0.75, shape = 21) + 
  scale_size_continuous(limits = c(0.01, 1)) + 
  labs( x= "", y = "", size = "Relative Abundance (%)", fill = "")  + 
  theme(legend.key=element_blank(), 
  axis.text.x = element_text(colour = "black", size = 12, face = "bold", angle = 90, vjust = 0.3, hjust = 1), 
  axis.text.y = element_text(colour = "black", face = "bold", size = 11), 
  #legend.text = element_text(size = 10, face ="bold", colour ="black"), 
  #legend.title = element_text(size = 12, face = "bold"), 
  #panel.background = element_blank(), panel.border = element_rect(colour = "black", fill = NA, size = 1.2), 
  legend.position = "right")  
  #scale_fill_manual(values = colours, guide = FALSE) + 
  #scale_y_discrete(limits = rev(levels(pcm$variable))) 

library(Rmisc)

melt.ps.sid.lk1.rel <- psmelt(ps.sid.lk1.rel)
melt.ps.sid.lk1.rel$Abundance[is.na(melt.ps.sid.lk1.rel$Abundance)] <- 0
melt.ps.sid.lk1.rel.sum <- summarySE(melt.ps.sid.lk1.rel,measurevar="Abundance",groupvars = c("ITS2_type_profile","zone"))

melt.ps.sid.lk1.rel.sum[melt.ps.sid.lk1.rel.sum==0] <- NA
melt.ps.sid.lk1.rel.sum2 <-melt.ps.sid.lk1.rel.sum[complete.cases(melt.ps.sid.lk1.rel.sum),]

bub.genus.mse <- ggplot(melt.ps.sid.lk1.rel.sum2, aes(x = zone, y = ITS2_type_profile)) + 
  geom_point(aes(size = Abundance, fill = ITS2_type_profile), alpha = 0.75, shape = 21)+
  #scale_size_continuous(limits=c(0.00001,1),breaks = c(.0001,.10,.50,.75)) + 
  #scale_size_continuous(limits = c(0.01, 1), breaks = c(.1,.5,.75,1)) + 
  #facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()+
  #scale_fill_manual(values=cols.mse, guide=FALSE)+
  #ggtitle("Moorea SE")+
  #ylab("ASV")+
  #xlab("")+
  #scale_x_discrete(labels=c("Back","Fore"))+
  guides(fill="none")
bub.genus.mse


library(dplyr)
tb <- psmelt(ps.sid.lk1.rel) %>%
  filter(!is.na(ITS2_type_profile)) %>%
  group_by(zone,sample,ITS2_type_profile) %>%
  # Add abundances within each phylum and sample
  summarize_at("Abundance", sum) %>%
  # Get phylum proportions within each sample
  #summarize_at("Proportion", ~ . / sum(.)) %>%
  # Get the mean proportion each phylum across samples within the `Sex` (Male/Female) variable
  #summarize_at("Proportion", mean)
#### bubble plot - genus ####
library(dplyr)

#MOOREA NW
melt.mnw <- psmelt(indic.mnw.rel)
melt.mnw$Abundance[is.na(melt.mnw$Abundance)] <- 0
melt.mnw.sum <- summarySE(melt.mnw,measurevar="Abundance",groupvars = c("Genus","zone"))

melt.mnw.sum$bool_col <- melt.mnw.sum$Genus %in% genus.mnwi$genus
melt.mnw.sum$indic_res <- ifelse(melt.mnw.sum$bool_col == T, "Back reef", "Fore reef")

bub.genus.mnw <- ggplot(melt.mnw.sum, aes(x = zone, y = Genus)) + 
  geom_point(aes(size = Abundance, fill = Genus), alpha = 0.75, shape = 21)+
  facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()+
  #scale_fill_manual(values=cols.mnw, guide=FALSE)+
  ggtitle("Moorea NW")+
  ylab("ASV")+
  xlab("")+
  scale_x_discrete(labels=c("Back","Fore"))
bub.genus.mnw

```

## PCAs{.tabset}

### Type profiles

```{r type profiles by site}
ps.ord <- ordinate(ps,"PCoA",distance="bray")
plot_ordination(ps, ps.ord, color ="site", shape="zone")+
  geom_point(alpha=0.5)+
  scale_color_manual(values=c("darkslategray3","darkslategray4","#000004"))+
  scale_shape_manual(values=c(16,15))+
  stat_ellipse(aes(linetype=zone))+
  theme_cowplot()

#ggsave(filename="pcoa.types.site.pdf")
```

```{r pcoa type profiles}
#just cladocopium
# ps.c <- subset_taxa(ps,Clade=="C")
# ps.c.no0 <- subset_samples(ps.c,sample_sums(ps.c)!=0)
# 
# ps.ord.c <- ordinate(ps.c.no0,"PCoA",distance="bray")
# plot_ordination(ps.c.no0, ps.ord.c, color ="site")+
#   geom_point(alpha=0.5)
# #doesn't really change between C or C+A

ps.mnw <- subset_samples(ps,site=="MNW")
gg.pc.mnw.types <- plot_ordination(ps.mnw, ordinate(ps.mnw,"PCoA",distance="bray"), color ="zone",shape="zone")+
  geom_point()+
  stat_ellipse()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  theme_cowplot()+
  xlab("Axis 1 (61.4%)")+
  ylab("Axis 2 (12.2%)")+
  #theme(legend.position="none")+
  ggtitle("Mo'orea NW")
gg.pc.mnw.types

ps.mse <- subset_samples(ps,site=="MSE")
gg.pc.mse.types <- plot_ordination(ps.mse, ordinate(ps.mse,"PCoA",distance="bray"), color ="zone",shape="zone")+
  geom_point()+
  stat_ellipse()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  theme_cowplot()+
  ggtitle("Mo'orea SE")+
  xlab("Axis 1 (52.4%)")+
  ylab("Axis 2 (23.5%)")
gg.pc.mse.types

ps.tnw <- subset_samples(ps,site=="TNW")
gg.pc.tnw.types <- plot_ordination(ps.tnw, ordinate(ps.tnw,"PCoA",distance="bray"), color ="zone",shape="zone")+
  geom_point()+
  stat_ellipse()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  theme_cowplot()+
  ggtitle("Tahiti NW")+
  xlab("Axis 1 (41.1%)")+
  ylab("Axis 2 (21.5%)")
gg.pc.tnw.types
```

### All types

Reading in coordinate files given by SymPortal:
(done on full suite of sequences, not the type profiles)

```{r pcoa only C genus}
pcoa.c <- read.csv("symportal_bray_pcoa_cladec.csv")
#pcoa.c <- read.csv("symportal_bray_pcoa_cladec_sqrt.csv")
pcoa.c$Sample <- pcoa.c$sample
pcoa.samdata.c <- merge(pcoa.c,samdf,by="Sample")
```

### Plot - site & zone

```{r C pcoa plot sz}
#quick raw plot
ggplot(pcoa.samdata.c,aes(x=PC1,y=PC2,color=site))+
  geom_point()

ggplot(pcoa.samdata.c,aes(x=PC1,y=PC2,color=site_zone,shape=site,linetype=zone))+
  geom_point()+
  stat_ellipse()+
  #scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  #scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))
```

### Plot - zone summed

```{r C pcoa plot z}
ggplot(pcoa.samdata.c,aes(x=PC1,y=PC2,color=zone,shape=zone))+
  geom_point()+
  stat_ellipse()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))
```

## PCAs by site{.tabset}

### MNW

```{r pcoa mnw}
pcoa.mnw <- subset(pcoa.samdata.c,site=="MNW")

gg.pc.mnw <- ggplot(pcoa.mnw,aes(x=PC1,y=PC2,color=zone,shape=zone))+
  geom_point()+
  stat_ellipse()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  theme_cowplot()+
  theme(legend.position="none")+
  ggtitle("Mo'orea NW")+
  xlab(" ")
gg.pc.mnw
```

### MSE

```{r pcoa mse}
pcoa.mse <- subset(pcoa.samdata.c,site=="MSE")

gg.pc.mse <- ggplot(pcoa.mse,aes(x=PC1,y=PC2,color=zone,shape=zone))+
  geom_point()+
  stat_ellipse()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  theme_cowplot()+
  ggtitle("Mo'orea SE")+
  theme(legend.position="none")+
  ylab(" ")
gg.pc.mse
```

### TNW

```{r pcoa tnw}
pcoa.tnw <- subset(pcoa.samdata.c,site=="TNW")

gg.pc.tnw <- ggplot(pcoa.tnw,aes(x=PC1,y=PC2,color=zone,shape=zone))+
  geom_point()+
  stat_ellipse()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  theme_cowplot()+
  ggtitle("Tahiti NW")+
  ylab(" ")+
  xlab(" ")
gg.pc.tnw
```

## Synthesizing results

```{r multi pca}
library(ggpubr)
```

```{r}
gg.pca <- ggarrange(gg.pc.mnw.types,gg.pc.mse.types,gg.pc.tnw.types,labels=c("(a)","(b)","(c)"),nrow=1,common.legend=T,legend="right")
gg.pca
gg.bar <- ggarrange(bar.mnw,bar.mse,bar.tnw,labels=c("(d)","(e)","(f)"),nrow=1,common.legend=TRUE,legend="right")
gg.bar

ggarrange(gg.pca,gg.bar,nrow=2)
#ggsave(file="pca.bar.pdf",height=5.5,width=9.5)
```

## Normalized results

Thank you to Ryan Eckhart for parts of this: [Github here](https://github.com/RyanEckert/Belize_Mcav_Symbiodiniaceae_ITS2)

```{r normalized type profiles}
#BiocManager::install("edgeR", update = FALSE)
library(edgeR)

seqs.types <- as.data.frame(ps@otu_table)
seqs.types.t <- t(seqs.types)

its2SeqList = DGEList(counts = seqs.types.t)
head(its2SeqList$samples)

its2SeqNorm =  calcNormFactors(its2SeqList, method = "TMM")
head(its2SeqNorm$samples)
its2TMM = t(cpm(its2SeqNorm, normalized.lib.sizes = TRUE))

#phyloseq
row.names(samdf) <- samdf$Sample
ps.norm <- phyloseq(otu_table(its2TMM, taxa_are_rows=FALSE),
               sample_data(samdf),
               tax_table(mtaxa))

ps.norm
```


```{r}
ps.norm.ord <- ordinate(ps.norm,"PCoA",distance="bray")
plot_ordination(ps.norm, ps.norm.ord, color ="site")+
  geom_point(alpha=0.5)

ps.norm.mnw <- subset_samples(ps.norm,site=="MNW")

plot_ordination(ps.norm.mnw, ordinate(ps.norm.mnw,"PCoA","bray"), color ="zone")+
  geom_point(alpha=0.5)+
  stat_ellipse()

ps.norm.mse <- subset_samples(ps.norm,site=="MSE")

plot_ordination(ps.norm.mse, ordinate(ps.norm.mse,"PCoA","bray"), color ="zone")+
  geom_point(alpha=0.5)+
  stat_ellipse()

ps.norm.tnw <- subset_samples(ps.norm,site=="TNW")

plot_ordination(ps.norm.tnw, ordinate(ps.norm.tnw,"PCoA","bray"), color ="zone")+
  geom_point(alpha=0.5)+
  stat_ellipse()
```

```{norm for all seqs}
#BiocManager::install("edgeR", update = FALSE)
library(edgeR)

seqs.all <- as.data.frame(ps.all@otu_table)
seqs.all.t <- t(seqs.all)

its2SeqList.all = DGEList(counts = seqs.all.t)
head(its2SeqList.all$samples)

its2SeqNorm.all =  calcNormFactors(its2SeqList.all, method = "TMM")
head(its2SeqNorm.all$samples)
its2TMM.all = t(cpm(its2SeqNorm.all, normalized.lib.sizes = TRUE))

#phyloseq
ps.norm.all <- phyloseq(otu_table(its2TMM.all, taxa_are_rows=FALSE),
               sample_data(samdf))

ps.norm.all

ps.norm.all.ord <- ordinate(ps.norm.all,"PCoA",distance="bray")
plot_ordination(ps.norm.all, ps.norm.all.ord, color ="site")+
  geom_point(alpha=0.5)+
  stat_ellipse()
```

# Collapsing type profiles via phylogeny tree

Started with file: "188_20211214_03_DBV_20211215T030311.seqs.fasta" in the post-med seqs folder. Also started with the taxa info 'Majority_ITS2_sequence", removed the slashes between types, & removed duplicates. That left 24 unique ITS2 types, put these in 'names.txt'. Want to extract the relevant sequences from the fasta file now

```{bash, eval=F}
for word in $(cat names.txt); do echo $word; grep -w -A 1 $word postmedseqs.fasta >> output.fasta; done
```

*Important notes:* produced a fasta file with '--' in between some desired entries, removed that manually, but I'm sure there's a better way than that. It also gave me an unwanted one (A4.3), took that out manually. Easy to do with 24 types, but would be harder with more than that.. processed file was named _output_types_cleaned.fasta_

Then went to ngphylogeny.fr to plot.

More notes: 
- A is fine, the majority sequences are pretty disparate. 
- The Bs are a total mess, will plot below
- Cs are fine
- Ds are fine

## Clade B plotted

```{r}


p <- ggtree(higher_tree)
dd <- data.frame(taxa = c("Acroporidae","Pocilloporidae","Astrocoeniidae","Merulinidae","Dendrophylliidae","Caryophylliidae","Agariciidae","Gorgoniidae","Coralliidae"),
                 strategy = c("mixed","brood",rep("broadcast",2),"brood","broadcast",rep("brood",3)),
                 prop = c(9,8,1,4,3,1,1,1,2))
p <- p %<+% dd + geom_tiplab(aes(x=x+6,color=strategy)) +
  geom_tippoint(aes(x=x+3.2,size=prop,color=strategy),alpha=0.25)+
  scale_color_manual(values=colorz,name="Spawning mode",labels=c("Broadcasting","Brooding","Mixed"))+
  theme(legend.position="right")+
  guides(size=guide_legend("Number of studies"))
p + ggplot2::xlim(0,90)+geom_treescale()
```

# Stats

## New phyloseq object

Fuller data counts from Symportal before type profiles identified

First we purge sequences and transpose the data to work with *edgeR*
```{r, purging outlying sequences and normalizing reads, eval=FALSE}
goods = purgeOutliers(its2Seq, count.columns = 4:length(its2Seq), otu.cut = 0.0001, sampleZcut = -5)
```

```{r, seq norm, results = 'hide', eval=FALSE}
its2SeqTransposed = t(goods[, 4:length(goods[1, ])])
its2SeqList = DGEList(counts = its2SeqTransposed)
head(its2SeqList$samples)
```

Normalize

```{r}
```

## Stats - type profiles

```{r adonis stats packages}
library(vegan)
#remotes::install_github("Jtrachsel/funfuns")
library(funfuns)
library(dplyr)
library(edgeR)
```

Raw

```{r by site}
seq.ps <- data.frame(ps@otu_table)
samdf.ps <- data.frame(ps@sam_data)

dist.ps <- vegdist(seq.ps)
bet.ps <- betadisper(dist.ps,samdf.ps$site)
#anova(bet.ps) #ns
permutest(bet.ps,pairwise=TRUE,permutations=999)
plot(bet.ps)

adonis(seq.ps ~ site/zone, data=samdf.ps, permutations=999) #p<001***

pairwise.adonis(seq.ps, factors=samdf.ps$site, permutations=999) #tahiti different from other two
#        pairs    F.Model         R2 p.value p.adjusted
# 1 MSE vs MNW  0.8174161 0.01344049   0.445      0.445
# 2 MSE vs TNW 13.6939515 0.18333414   0.001      0.001
# 3 MNW vs TNW 12.1951261 0.17129159   0.001      0.001
```

Normalized

```{r stats by site norm}
seq.ps.norm <- data.frame(ps.norm@otu_table)
samdf.ps.norm <- data.frame(ps.norm@sam_data)

dist.ps.norm <- vegdist(seq.ps.norm)
bet.ps.norm <- betadisper(dist.ps.norm,samdf.ps.norm$site)
anova(bet.ps.norm) #ns
plot(bet.ps.norm)

adonis(seq.ps.norm ~ site/zone, data=samdf.ps.norm, permutations=999) #p<001***

pairwise.adonis(seq.ps.norm, factors=samdf.ps.norm$site, permutations=999) #tahiti different from other two
#        pairs    F.Model         R2 p.value p.adjusted
# 1 MSE vs MNW  0.8174161 0.01344049   0.445      0.445
# 2 MSE vs TNW 13.6939515 0.18333414   0.001      0.001
# 3 MNW vs TNW 12.1951261 0.17129159   0.001      0.001
```

Relative abundance

```{r stats by site rel}
seq.ps.rel <- data.frame(ps.rel@otu_table)
samdf.ps.rel <- data.frame(ps.rel@sam_data)

dist.ps.rel <- vegdist(seq.ps.rel)
bet.ps.rel <- betadisper(dist.ps.rel,samdf.ps.rel$site)
anova(bet.ps.rel) #ns
plot(bet.ps.rel)

adonis(seq.ps.rel ~ site/zone, data=samdf.ps.rel, permutations=999) #p<001***

pairwise.adonis(seq.ps.rel, factors=samdf.ps.rel$site, permutations=999) #tahiti different from other two
#        pairs    F.Model         R2 p.value p.adjusted
# 1 MSE vs MNW  0.8174161 0.01344049   0.445      0.445
# 2 MSE vs TNW 13.6939515 0.18333414   0.001      0.001
# 3 MNW vs TNW 12.1951261 0.17129159   0.001      0.001
```

```{r subset by site}
ps.mnw <- subset_samples(ps,site=="MNW")
ps.mnw.rel <- subset_samples(ps.rel,site=="MNW")
ps.mnw.norm <- subset_samples(ps.norm,site=="MNW")

ps.mse <- subset_samples(ps,site=="MSE")
ps.mse.rel <- subset_samples(ps.rel,site=="MSE")
ps.mse.norm <- subset_samples(ps.norm,site=="MSE")

ps.tnw <- subset_samples(ps,site=="TNW")
ps.tnw.rel <- subset_samples(ps.rel,site=="TNW")
ps.tnw.norm <- subset_samples(ps.norm,site=="TNW")
```

Mo'orea NW

```{r mnw stats}
seq.ps.mnw <- data.frame(otu_table(ps.mnw))
samdf.ps.mnw <- data.frame(sample_data(ps.mnw))
row.names(seq.ps.mnw)==row.names(samdf.ps.mnw)

dist.ps.mnw <- vegdist(seq.ps.mnw)
bet.ps.mnw <- betadisper(dist.ps.mnw,samdf.ps.mnw$zone)
anova(bet.ps.mnw) #ns
plot(bet.ps.mnw)

adonis(seq.ps.mnw ~ zone, data=samdf.ps.mnw, permutations=999) #p<01**
```

Normalized

```{r normalized mnw stats}
seq.ps.mnw.norm <- data.frame(otu_table(ps.mnw.norm))
samdf.ps.mnw.norm <- data.frame(sample_data(ps.mnw.norm))
row.names(seq.ps.mnw.norm)==row.names(samdf.ps.mnw.norm)

dist.ps.mnw.norm <- vegdist(seq.ps.mnw.norm)
bet.ps.mnw.norm <- betadisper(dist.ps.mnw.norm,samdf.ps.mnw.norm$zone)
anova(bet.ps.mnw.norm) #ns
plot(bet.ps.mnw.norm)

adonis(seq.ps.mnw.norm ~ zone, data=samdf.ps.mnw.norm, permutations=999) #p<01**
```

Rel abundance

```{r mnw rel}
seq.ps.mnw.rel <- data.frame(otu_table(ps.mnw.rel))

dist.ps.mnw <- vegdist(seq.ps.mnw.rel)
bet.ps.mnw <- betadisper(dist.ps.mnw,samdf.ps.mnw$zone)
anova(bet.ps.mnw) #ns
permutest(bet.ps.mnw, permutations = 999,pairwise=F)
plot(bet.ps.mnw) #ns

adonis(seq.ps.mnw.rel ~ zone, data=samdf.ps.mnw, permutations=999) #sig p < 0.01
```

Mo'orea SE

```{r mse stats}
seq.ps.mse <- data.frame(otu_table(ps.mse))
samdf.ps.mse <- data.frame(sample_data(ps.mse))
row.names(seq.ps.mse)==row.names(samdf.ps.mse)

dist.ps.mse <- vegdist(seq.ps.mse)
bet.ps.mse <- betadisper(dist.ps.mse,samdf.ps.mse$zone)
anova(bet.ps.mse) #ns
plot(bet.ps.mse)

adonis(seq.ps.mse ~ zone, data=samdf.ps.mse, permutations=999) #p<01**
```

Normalized

```{r normalized mse stats}
seq.ps.mse.norm <- data.frame(otu_table(ps.mse.norm))
samdf.ps.mse.norm <- data.frame(sample_data(ps.mse.norm))
row.names(seq.ps.mse.norm)==row.names(samdf.ps.mse.norm)

dist.ps.mse.norm <- vegdist(seq.ps.mse.norm)
bet.ps.mse.norm <- betadisper(dist.ps.mse.norm,samdf.ps.mse.norm$zone)
anova(bet.ps.mse.norm) #ns
plot(bet.ps.mse.norm)

adonis(seq.ps.mse.norm ~ zone, data=samdf.ps.mse.norm, permutations=999) #p<01**
```

Rel abundance

```{r mse rel}
seq.ps.mse.rel <- data.frame(otu_table(ps.mse.rel))

dist.ps.mse <- vegdist(seq.ps.mse.rel)
bet.ps.mse <- betadisper(dist.ps.mse,samdf.ps.mse$zone)
anova(bet.ps.mse) #ns
permutest(bet.ps.mse, permutations = 999,pairwise=F)
plot(bet.ps.mse) #ns

adonis(seq.ps.mse.rel ~ zone, data=samdf.ps.mse, permutations=999) #sig p < 0.01
```

Tahiti NW

```{r tnw stats}
seq.ps.tnw <- data.frame(otu_table(ps.tnw))
samdf.ps.tnw <- data.frame(sample_data(ps.tnw))
row.names(seq.ps.tnw)==row.names(samdf.ps.tnw)

dist.ps.tnw <- vegdist(seq.ps.tnw)
bet.ps.tnw <- betadisper(dist.ps.tnw,samdf.ps.tnw$zone)
anova(bet.ps.tnw) #ns
plot(bet.ps.tnw)

adonis(seq.ps.tnw ~ zone, data=samdf.ps.tnw, permutations=999) #p<01**
```

Normalized

```{r normalized tnw stats}
seq.ps.tnw.norm <- data.frame(otu_table(ps.tnw.norm))
samdf.ps.tnw.norm <- data.frame(sample_data(ps.tnw.norm))
row.names(seq.ps.tnw.norm)==row.names(samdf.ps.tnw.norm)

dist.ps.tnw.norm <- vegdist(seq.ps.tnw.norm)
bet.ps.tnw.norm <- betadisper(dist.ps.tnw.norm,samdf.ps.tnw.norm$zone)
anova(bet.ps.tnw.norm) #ns
plot(bet.ps.tnw.norm)

adonis(seq.ps.tnw.norm ~ zone, data=samdf.ps.tnw.norm, permutations=999) #p<01**
```

Rel abundance

```{r tnw rel}
seq.ps.tnw.rel <- data.frame(otu_table(ps.tnw.rel))

dist.ps.tnw <- vegdist(seq.ps.tnw.rel)
bet.ps.tnw <- betadisper(dist.ps.tnw,samdf.ps.tnw$zone)
anova(bet.ps.tnw) #ns
permutest(bet.ps.tnw, permutations = 999,pairwise=F)
plot(bet.ps.tnw) #ns

adonis(seq.ps.tnw.rel ~ zone, data=samdf.ps.tnw, permutations=999) #sig p < 0.01
```

All syms

```{r all syms stats, eval=FALSE}
seq.all <- data.frame(otu_table(ps.all))
samdf.ps.all <- data.frame(sample_data(ps.all))
row.names(seq.all)==row.names(samdf.ps.all)

dist.all <- vegdist(seq.all)
bet.mnw.c <- betadisper(dist.all,samdf.ps.all$zone)
anova(bet.mnw.c) #ns
plot(bet.mnw.c) #very much overlap, not sig
adonis(otu.mnw.c ~ site*zone, data=samdf.mnw.c, permutations=999)
```

```{r, eval=FALSE}
seq.a <- select(seq.all,contains('A')) 
#get rid of column 29 - it's a C
seq.a.clean <- seq.a[,1:28]

seq.c <- select(seq.all,contains('C')) 
#get rid of column 1, it's an A
seq.c.clean <- seq.c[,2:129]

seq.ac <- seq.all %>%
  select(contains('A')) %>%
  select(contains('C'))
#just those two

seq.ac <- select(seq.all,!contains(c('C','A'))) 
#there's a B1 in there haha

seq.c.clean2 <- seq.c.clean[!rowSums(seq.c.clean)==0,]

ps.all.c <- phyloseq(otu_table(as.matrix(seq.c.clean2), taxa_are_rows=FALSE),
               sample_data(samdf))

ps.all.c

seq.a.clean2 <- seq.a.clean[!rowSums(seq.a.clean)==0,]

ps.all.a <- phyloseq(otu_table(as.matrix(seq.a.clean2), taxa_are_rows=FALSE),
               sample_data(samdf))

ps.all.a

#stats time - CLADOCOPIUM
dist.c <- vegdist(seq.c.clean2)
samdf.ps.c <- data.frame(sample_data(ps.all.c))
row.names(samdf.ps.c)==row.names(seq.c.clean2)

bet.c <- betadisper(dist.c,samdf.ps.c$site)
anova(bet.c) #ns
plot(bet.c) #very much overlap, not sig

adonis(seq.c.clean2 ~ site/zone, data=samdf.ps.c, permutations=999)

pairwise.adonis(seq.c.clean2, factors = samdf.ps.c$site, permutations = 999)
#Tahiti different from other two

ps.mnw.c <- subset_samples(ps.all.c,site=="MNW")
otu.mnw.c <- data.frame(otu_table(ps.mnw.c))
samdf.mnw.c <- data.frame(sample_data(ps.mnw.c))
row.names(otu.mnw.c)==row.names(samdf.mnw.c)

dist.mnw.c <- vegdist(otu.mnw.c)
bet.mnw.c <- betadisper(dist.mnw.c,samdf.mnw.c$zone)
anova(bet.mnw.c) #ns
plot(bet.mnw.c) #very much overlap, not sig
adonis(otu.mnw.c ~ zone, data=samdf.mnw.c, permutations=999)


```

## Find "most frequent" sym

Just ran once to get the info

```{r top sym, eval=FALSE}
find.top.asv <- function(x,num){
  require(phyloseq)
  require(magrittr)
  
  otu <- otu_table(x)
  tax <- tax_table(x)
  j1 <- apply(otu,1,sort,index.return=T, decreasing=T) # modifying which.max to return a list of sorted index
  j2 <- lapply(j1,'[[',"ix") # select for index
  
  l <- data.frame(unique(tax@.Data[unlist(j2),]))
  m <- data.frame(otu@.Data[,unique(unlist(j2))])
  n <- apply(m,1,sort,index.return=T, decreasing=T) %>%
    lapply('[[',"ix") %>%  # Extract index
    lapply(head,n=num) # This to returns the top x tax

  p <- list()
  for(i in 1:length(n)){
    p[[i]]<- colnames(m)[n[[i]]]
  }
  m$taxa <- p
  return(m)
}

top.asvs <- find.top.asv(ps.sid,5)
top.asvs$taxa <- as.character(top.asvs$taxa)

#write.csv(top.asvs,file="top_sym.csv",row.names=TRUE)
```

```{r}
table <- read.csv("silly_its_table.csv",header=T)

heatmap(as.matrix(table[,2:11]), labRow=table[,1],rowv=NA)
```

```{r scraps, include=FALSE, eval=FALSE}
#### Genus by site & zone

#Nothing interesting

# ps.sz <- merge_samples(ps, "site_zone")
# ps.sz.clade <- tax_glom(ps.sz, "Clade")
# ps.sz.clade.rel <- transform_sample_counts(ps.sz.clade, function(x) x / sum(x))
# plot_bar(ps.sz.clade.rel, fill="Clade")+
#     geom_bar(aes(color=Clade, fill=Clade), stat="identity", position="stack")

#messy scraps

## Trying out pie charts

#install.packages("remotes")
#remotes::install_github("cpauvert/psadd")

ggplot(melt.ps.rel.mnw, aes(x = "", y = Abundance, fill = ITS2_type_profile)) +
  geom_bar(stat = "identity") +
  coord_polar("y", start = 0)+
  #geom_text(aes(y = lab.ypos,), color = "white")+
  #scale_fill_manual(values = mycols) +
  theme_void()


ps.sz.rel <- transform_sample_counts(ps.sz, function(x) x / sum(x))

plot_heatmap(ps.rel,sample.label="site_zone",sample.order="site_zone")
plot_heatmap(ps.sz.rel,sample.order="site_zone",low="blue",high="red",na.value="black")+
  facet_wrap(~site)

rownames(dat) = dat$weather

ps.sz.rel@sam_data$zone <- c("BR","FR","BR","FR","BR","FR")
plot_heatmap(ps.sz.rel,sample.order="site_zone",low="blue",high="red",na.value="black",method=NULL,distance=NULL)


seq.sz.rel <- data.frame(ps.sid.irm.rel@otu_table)
heatmap.2(as.matrix(t(seq.sz.rel)),Rowv=FALSE,Colv=FALSE)

melt.sz.rel <- psmelt(ps.sz.rel)

ggplot(melt.sz.rel, aes(x = Sample, y = OTU)) + 
  geom_point(aes(size = Abundance, fill = OTU), alpha = 0.75, shape = 21)+
  #facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()
  #scale_fill_manual(values=cols.mnw, guide=FALSE)+
  #ggtitle("Moorea NW")+
  #ylab("ASV")+
  #xlab("")+
  #scale_x_discrete(labels=c("Back","Fore"))

melt.ps <- psmelt(ps)
ggplot(melt.ps, aes(x = sample_full, y = OTU)) + 
  geom_point(aes(size = Abundance, fill = OTU), alpha = 0.75, shape = 21)+
  #facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()
  #scale_fill_manual(values=cols.mnw, guide=FALSE)+
  #ggtitle("Moorea NW")+
  #ylab("ASV")+
  #xlab("")+
  #scale_x_discrete(labels=c("Back","Fore"))

melt.ps.rel <- psmelt(ps.rel)
melt.ps.rel.mnw <- subset(melt.ps.rel,site=="MNW")
melt.ps.rel.mnw.no0 <- subset(melt.ps.rel.mnw,Abundance>0)
ggplot(melt.ps.rel.mnw.no0, aes(x = sample_full, y = OTU)) + 
  geom_point(aes(size = Abundance, fill = OTU), alpha = 0.75, shape = 21)+
  #facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()

plot_heatmap(ps.sz.rel,sample.order="site_zone",low="blue",high="red",na.value="black",method=NULL,distance=NULL)

## Presence/absence

sppAbun <- as.data.frame(ps@otu_table)

sppAbun[sppAbun > 0] <- 1 #converts from abundance to P/A
sppAbun

mnwb.names <- subset(samdf,site_zone=="MNW-B")
mnwf.names <- subset(samdf,site_zone=="MNW-F")

mnwb.rows <- c(row.names(mnwb.names))

mnwb.pres <- sppAbun[row.names(sppAbun) %in% mnwb.rows,]
colSums(mnwb.pres)
plot(colSums(mnwb.pres))

#install.packages("gplots")
library(gplots)
heatmap.2(as.matrix(sppAbun),Rowv=FALSE,Colv=FALSE)
dev.off()

heatmap(as.matrix(sppAbun), scale='none')

ps.bin <- phyloseq(otu_table(sppAbun, taxa_are_rows=FALSE),
               sample_data(samdf),
               tax_table(mtaxa))

ps.bin


plot_heatmap(ps.bin,sample.order="site_zone")
dev.off()

```

