---
title: "Florida ITS2 analysis"
author: "Nicola G. Kriefall"
date: "12/1/21"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
---

# SymPortal pre-submission

Submitting ITS2 samples to [Symportal](symportal.org)

Prior to submission: retaining only paired reads that match ITS2 primer (we pooled with 16S during sequencing)

```{bash setup, eval=FALSE}
# *note: most of this was written by Dr. Carly D. Kenkel

# in Terminal home directory:
# following instructions of installing BBtools from https://jgi.doe.gov/data-and-tools/bbtools/bb-tools-user-guide/installation-guide/
# 1. download BBMap package, sftp to installation directory
# 2. untar: 
tar -xvzf BBMap_(version).tar.gz
# 3. test package:
cd bbmap
~/bin/bbmap/stats.sh in=~/bin/bbmap/resources/phix174_ill.ref.fa.gz

# my adaptors, which I saved as "adaptors.fasta"
# >forward
# AATGATACGGCGACCAC
# >forwardrc
# GTGGTCGCCGTATCATT
# >reverse
# CAAGCAGAAGACGGCATAC
# >reverserc
# GTATGCCGTCTTCTGCTTG

# primers for ITS2:
# >forward
# GTGAATTGCAGAACTCCGTG
# >reverse
# CCTCCGCTTACTTATATGCTT

# making a sample list based on the first phrase before the underscore in the .fastq name
ls *R1_001.fastq | cut -d '_' -f 2 > samples.list

# cuts off the extra words in the .fastq files
for file in $(cat samples.list); do  mv ${file}_*R1*.fastq ${file}_R1.fastq; mv ${file}_*R2*.fastq ${file}_R2.fastq; done 

# gets rid of reads that still have the adaptor sequence
# [I stopped doing this 'cause it never happened]
#for file in $(cat samples.list); do ~/bin/bbmap/bbduk.sh in1=${file}_R1.fastq in2=${file}_R2.fastq ref=adaptors.fasta out1=${file}_R1_NoIll.fastq out2=${file}_R2_NoIll.fastq; done &>bbduk_NoIll.log

##getting rid of first 4 bases (degenerate primers created them)
for file in $(cat samples.list); do ~/bin/bbmap/bbduk.sh in1=${file}_R1.fastq in2=${file}_R2.fastq ftl=4 out1=${file}_R1_No4N.fastq out2=${file}_R2_No4N.fastq; done &>bbduk_No4N.log

# only keeping reads that start with the primer
for file in $(cat samples.list); do ~/bin/bbmap/bbduk.sh in1=${file}_R1.fastq in2=${file}_R2.fastq k=15 restrictleft=21 literal=GTGAATTGCAGAACTCCGTG,CCTCCGCTTACTTATATGCTT outm1=${file}_R1_ITS.fastq outu1=${file}_R1_check.fastq outm2=${file}_R2_ITS.fastq outu2=${file}_R2_check.fastq; done &>bbduk_ITS.log
# higher k = more reads removed, but can't surpass k=20 or 21

# renamed them to the shorter version again after checking
for file in $(cat samples.list); do  mv ${file}_*R1*.fastq ${file}_R1.fastq; mv ${file}_*R2*.fastq ${file}_R2.fastq; done 
```

Then transferred all "R1.fastq" & "R2.fastq" files to the folder to be submitted to SymPortal

# SymPortal ITS2 analysis

Information on Symportal output documents [here](https://github.com/didillysquat/SymPortal_framework/wiki/SymPortal-output-documents)

Formatting notes:

- Cleaned up file called 188_20211214_03_DBV_20211215T030311.profiles.absolute.abund_and_meta.txt to format for phyloseq

## Setup

```{r packages, echo=FALSE}
library(phyloseq)
library('ggplot2')
library('Rmisc')
library(cowplot)
library("ggpubr")
library("vegan")
library(scales)
library(colorspace)
```

```{r working directory, include=FALSE}
setwd("~/Google Drive (nicfall@bu.edu)/Flirma/flirma_networks/fl_its2")
#setwd("/Volumes/GoogleDrive-104519233854090018057/My Drive/Flirma/flirma_networks/fl_its2")
```

## Checking for no read samples

```{r counts per sample}
counts <- read.csv('flits_symportal_profile_counts.csv',header=TRUE,row.names=1,check.names=FALSE)
#325 samples, 75 type profiles
#+1 sample that's fake 'UK1-O_000' so I can plot UK1-O below

sort(rowSums(counts))
counts.no0 <- counts[rowSums(counts)>0,]
#2 that are 0, removing them now: LK1-I_1199_srad_2018, UK2-O_1105_srad_2018
```

## Phyloseq object - type profiles

Ran once then saved to re-read in later

```{r phyloseq object, eval=F}
# import dataframe holding sample information
samdf <- read.csv("fl_sample_info - ITS2_all.csv")
head(samdf)
samdf$full_sample <- paste0(samdf$sample,"_",samdf$spp,"_",samdf$year)
rownames(samdf) <- samdf$full_sample

# import taxa info
taxa <- read.csv("flits_symportal_taxa.csv",header=TRUE,row.names=1)
#rownames(taxa) <- as.factor(taxa$ITS2_type_profile)
mtaxa <- as.matrix(taxa)

# import counts (absolute abundance from its2 type profiles)
mcounts <- as.matrix(counts.no0)

# Construct phyloseq object 
ps <- phyloseq(otu_table(mcounts, taxa_are_rows=FALSE),
               sample_data(samdf),
               tax_table(mtaxa))

ps
# phyloseq-class experiment-level object
# otu_table()   OTU Table:         [ 75 taxa and 324 samples ]
# sample_data() Sample Data:       [ 324 samples by 12 sample variables ]
# tax_table()   Taxonomy Table:    [ 75 taxa by 5 taxonomic ranks ]

#saveRDS(ps,file="ps.its2.rds")
```

## Re-read in data

```{r re-read data}
ps <- readRDS("ps.its2.RDS")
```

## Subset data for bar plots

```{r}
ps <- subset_samples(ps,site!="UK3")

ps.sid <- subset_samples(ps,spp=="ssid")

ps.sid.pre <- subset_samples(ps.sid,time=="Pre")
ps.sid.irm <- subset_samples(ps.sid,time=="Irma")
ps.sid.pos <- subset_samples(ps.sid,time=="Post")

ps.sid.pre.lk1 <- subset_samples(ps.sid.pre,site=="LK1")
ps.sid.pre.uk1 <- subset_samples(ps.sid.pre,site=="UK1")
ps.sid.pre.uk2 <- subset_samples(ps.sid.pre,site=="UK2")

ps.sid.irm.lk1 <- subset_samples(ps.sid.irm,site=="LK1")
ps.sid.irm.uk1 <- subset_samples(ps.sid.irm,site=="UK1")
ps.sid.irm.uk2 <- subset_samples(ps.sid.irm,site=="UK2")

ps.sid.pos.lk1 <- subset_samples(ps.sid.pos,site=="LK1")
ps.sid.pos.uk1 <- subset_samples(ps.sid.pos,site=="UK1")
ps.sid.pos.uk2 <- subset_samples(ps.sid.pos,site=="UK2")

ps.gen <- tax_glom(ps,"Clade")
ntaxa(ps); ntaxa(ps.gen)

#siderea
ps.sid.gen <- subset_samples(ps.gen,spp=="ssid")

ps.sid.gen.pre <- subset_samples(ps.sid.gen,time=="Pre")
ps.sid.gen.irm <- subset_samples(ps.sid.gen,time=="Irma")
ps.sid.gen.pos <- subset_samples(ps.sid.gen,time=="Post")

#radians
ps.rad.gen <- subset_samples(ps.gen,spp=="srad")

ps.rad.gen.pre <- subset_samples(ps.rad.gen,time=="Pre")
ps.rad.gen.irm <- subset_samples(ps.rad.gen,time=="Irma")
ps.rad.gen.pos <- subset_samples(ps.rad.gen,time=="Post")
```

## Bar plots by genus {.tabset}

### S. siderea

```{r genus ssid}
ps.sid.gen.pre.rel <- transform_sample_counts(ps.sid.gen.pre, function(x) x / sum(x))
ps.sid.gen.pre.rel.sz <- merge_samples(ps.sid.gen.pre.rel, "site_zone")
ps.sid.gen.pre.rel.sz.rel <- transform_sample_counts(ps.sid.gen.pre.rel.sz, function(x) x / sum(x))

bar.sid.gen.pre.sz <- plot_bar(ps.sid.gen.pre.rel.sz.rel, fill="Clade")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.gen.pre.sz

ps.sid.gen.irm.rel <- transform_sample_counts(ps.sid.gen.irm, function(x) x / sum(x))
ps.sid.gen.irm.rel.sz <- merge_samples(ps.sid.gen.irm.rel, "site_zone")
ps.sid.gen.irm.rel.sz.rel <- transform_sample_counts(ps.sid.gen.irm.rel.sz, function(x) x / sum(x))

bar.sid.gen.irm.sz <- plot_bar(ps.sid.gen.irm.rel.sz.rel, fill="Clade")+
    ggtitle("irm")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.gen.irm.sz

ps.sid.gen.pos.rel <- transform_sample_counts(ps.sid.gen.pos, function(x) x / sum(x))
ps.sid.gen.pos.rel.sz <- merge_samples(ps.sid.gen.pos.rel, "site_zone")
ps.sid.gen.pos.rel.sz.rel <- transform_sample_counts(ps.sid.gen.pos.rel.sz, function(x) x / sum(x))

bar.sid.gen.pos.sz <- plot_bar(ps.sid.gen.pos.rel.sz.rel, fill="Clade")+
    ggtitle("pos")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.gen.pos.sz

gg.bar.clade <- ggarrange(bar.sid.gen.pre.sz,bar.sid.gen.irm.sz,bar.sid.gen.pos.sz,ncol=3,common.legend=T,legend="right")
gg.bar.clade
#ggsave("bar.clade_horizontal.pdf",width=9,height=4)
```

### S. radians

```{r genus srad}
ps.rad.gen.pre.rel <- transform_sample_counts(ps.rad.gen.pre, function(x) x / sum(x))
ps.rad.gen.pre.rel.sz <- merge_samples(ps.rad.gen.pre.rel, "site_zone")
ps.rad.gen.pre.rel.sz <- transform_sample_counts(ps.rad.gen.pre.rel.sz, function(x) x / sum(x))

gg.bar.pre <- plot_bar(ps.rad.gen.pre.rel.sz, fill="Clade")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
gg.bar.pre

ps.rad.gen.irm.rel <- transform_sample_counts(ps.rad.gen.irm, function(x) x / sum(x))
ps.rad.gen.irm.rel.sz <- merge_samples(ps.rad.gen.irm.rel, "site_zone")
ps.rad.gen.irm.rel.sz <- transform_sample_counts(ps.rad.gen.irm.rel.sz, function(x) x / sum(x))

gg.bar.irm <- plot_bar(ps.rad.gen.irm.rel.sz, fill="Clade")+
    ggtitle("Irma")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")

ps.rad.gen.pos.rel <- transform_sample_counts(ps.rad.gen.pos, function(x) x / sum(x))
ps.rad.gen.pos.rel.sz <- merge_samples(ps.rad.gen.pos.rel, "site_zone")
ps.rad.gen.pos.rel.sz <- transform_sample_counts(ps.rad.gen.pos.rel.sz, function(x) x / sum(x))

gg.bar.pos <- plot_bar(ps.rad.gen.pos.rel.sz, fill="Clade")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")

gg.bar.clade <- ggarrange(gg.bar.pre,gg.bar.irm,gg.bar.pos,ncol=3,common.legend=T,legend="right")
gg.bar.clade
#ggsave("bar.clade.radians.pdf",width=9,height=4)
```

## Bar plots by majority sequence

### Assessing type profile distances

Note - used file "20211215T030311_unifrac_profiles_PCoA_coords_B_sqrt.csv", made the name shorter. I also removed the 'proportion explained' line at the end. Also added the first type that shows up as its own column, 'first_type'

Proportion explained: PC1 0.584828597, PC2 0.146734687
For bray curtis: PC1 0.231, PC2 0.139

```{r determine groupings}
library(ggrepel)

setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_its2")

uni.cord <- read.csv("unifrac_profiles_PCoA_coords_B_sqrt.csv")

ggplot(uni.cord,aes(x=PC1,y=PC2,color=type_collapsed,label=sample))+
  geom_point()+
  xlab("PC1 (58.5%)")+
  ylab("PC2 (14.7%)")+
  geom_text_repel(max.overlaps=20)+
  stat_ellipse()+
  theme_bw()
#separated B5-1* & B5-2* by the 0 on PC2, except for 1 that was just below 0

#ggsave(file="pca_grouped.pdf",w=12,h=10)

#checking bray curtis
bray.cord <- read.csv("braycurtis_profiles_PCoA_coords_B_sqrt.csv")

ggplot(bray.cord,aes(x=PC1,y=PC2,color=type_bray,label=sample))+
  geom_point()+
  geom_text_repel(max.overlaps=20)+
  stat_ellipse()
```

Important setup

```{r set up its2 profiles}
ps.maj <- tax_glom(ps,"Majority_ITS2_collapsed")
#ps.maj <- tax_glom(ps,"Majority_ITS2_sequence_bray")

ntaxa(ps); ntaxa(ps.maj) #18 for unifrac sids, 14 for rads
#16 for bray sids

ps.maj <- subset_samples(ps.maj,site!="UK3")

#siderea
ps.maj.sid <- subset_samples(ps.maj,spp=="ssid")

ps.maj.sid.pre <- subset_samples(ps.maj.sid,time=="Pre")
ps.maj.sid.pre.lk1 <- subset_samples(ps.maj.sid.pre,site=="LK1")
ps.maj.sid.pre.uk1 <- subset_samples(ps.maj.sid.pre,site=="UK1")
ps.maj.sid.pre.uk2 <- subset_samples(ps.maj.sid.pre,site=="UK2")

ps.maj.sid.irm <- subset_samples(ps.maj.sid,time=="Irma")
ps.maj.sid.irm.lk1 <- subset_samples(ps.maj.sid.irm,site=="LK1")
ps.maj.sid.irm.uk1 <- subset_samples(ps.maj.sid.irm,site=="UK1")
ps.maj.sid.irm.uk2 <- subset_samples(ps.maj.sid.irm,site=="UK2")

ps.maj.sid.pos <- subset_samples(ps.maj.sid,time=="Post")
ps.maj.sid.pos.lk1 <- subset_samples(ps.maj.sid.pos,site=="LK1")
ps.maj.sid.pos.uk1 <- subset_samples(ps.maj.sid.pos,site=="UK1")
ps.maj.sid.pos.uk2 <- subset_samples(ps.maj.sid.pos,site=="UK2")

#radians
ps.maj.rad <- subset_samples(ps.maj,spp=="srad")

ps.maj.rad.pre <- subset_samples(ps.maj.rad,time=="Pre")
ps.maj.rad.pre.lk1 <- subset_samples(ps.maj.rad.pre,site=="LK1")
ps.maj.rad.pre.uk1 <- subset_samples(ps.maj.rad.pre,site=="UK1")
ps.maj.rad.pre.uk2 <- subset_samples(ps.maj.rad.pre,site=="UK2")

ps.maj.rad.irm <- subset_samples(ps.maj.rad,time=="Irma")
ps.maj.rad.irm.lk1 <- subset_samples(ps.maj.rad.irm,site=="LK1")
ps.maj.rad.irm.uk1 <- subset_samples(ps.maj.rad.irm,site=="UK1")
ps.maj.rad.irm.uk2 <- subset_samples(ps.maj.rad.irm,site=="UK2")

ps.maj.rad.pos <- subset_samples(ps.maj.rad,time=="Post")
ps.maj.rad.pos.lk1 <- subset_samples(ps.maj.rad.pos,site=="LK1")
#ps.maj.rad.pos.uk1 <- subset_samples(ps.maj.rad.pos,site=="UK1")
#not available
ps.maj.rad.pos.uk2 <- subset_samples(ps.maj.rad.pos,site=="UK2")
```

Removing black bars from phyloseq plot

```{r}
plot_bar2 <-  function (physeq, x = "Sample", y = "Abundance", fill = NULL, title = NULL, facet_grid = NULL, border_color = NA) 
{
  mdf = psmelt(physeq)
  p = ggplot(mdf, aes_string(x = x, y = y, fill = fill))
  p = p + geom_bar(stat = "identity", position = "stack",  color = border_color)
  p = p + theme(axis.text.x = element_text(angle = -90, hjust = 0))
  if (!is.null(facet_grid)) {
    p <- p + facet_grid(facet_grid)
  }
  if (!is.null(title)) {
    p <- p + ggtitle(title)
  }
  return(p)
}

maj.seq.colors <- c("#474747","#7A7A7A","#A8A8A8","#00294D","#195481","#5882AF","#9AB0CE","#D6DDE9","#D3E0D2","#95B792","#548C4E","#1F5D12","#002F00","#B8773A")
```

### The plots{.tabset}

#### S. siderea

LOWER KEYS 1

```{r}
ps.maj.sid.pre.lk1.rel <- transform_sample_counts(ps.maj.sid.pre.lk1, function(x) x / sum(x))
ps.maj.sid.pre.lk1.rel.zone <- merge_samples(ps.maj.sid.pre.lk1.rel, "zone")
ps.maj.sid.pre.lk1.zone <- transform_sample_counts(ps.maj.sid.pre.lk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.pre.lk1.zone <- plot_bar2(ps.maj.sid.pre.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pre.lk1.zone

ps.maj.sid.irm.lk1.rel <- transform_sample_counts(ps.maj.sid.irm.lk1, function(x) x / sum(x))
ps.maj.sid.irm.lk1.rel.zone <- merge_samples(ps.maj.sid.irm.lk1.rel, "zone")
ps.maj.sid.irm.lk1.zone <- transform_sample_counts(ps.maj.sid.irm.lk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.irm.lk1.zone <- plot_bar2(ps.maj.sid.irm.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.irm.lk1.zone

ps.maj.sid.pos.lk1.rel <- transform_sample_counts(ps.maj.sid.pos.lk1, function(x) x / sum(x))
ps.maj.sid.pos.lk1.rel.zone <- merge_samples(ps.maj.sid.pos.lk1.rel, "zone")
ps.maj.sid.pos.lk1.zone <- transform_sample_counts(ps.maj.sid.pos.lk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.pos.lk1.zone <- plot_bar2(ps.maj.sid.pos.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pos.lk1.zone

#ggarrange(gg.maj.sid.pre.lk1.zone,gg.maj.sid.irm.lk1.zone,gg.maj.sid.pos.lk1.zone,nrow=1)
```

UPPER KEYS 1

```{r}
ps.maj.sid.pre.uk1.rel <- transform_sample_counts(ps.maj.sid.pre.uk1, function(x) x / sum(x))
ps.maj.sid.pre.uk1.rel.zone <- merge_samples(ps.maj.sid.pre.uk1.rel, "zone")
ps.maj.sid.pre.uk1.zone <- transform_sample_counts(ps.maj.sid.pre.uk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.pre.uk1.zone <- plot_bar2(ps.maj.sid.pre.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pre.uk1.zone

ps.maj.sid.irm.uk1.rel <- transform_sample_counts(ps.maj.sid.irm.uk1, function(x) x / sum(x))
ps.maj.sid.irm.uk1.rel.zone <- merge_samples(ps.maj.sid.irm.uk1.rel, "zone")
ps.maj.sid.irm.uk1.zone <- transform_sample_counts(ps.maj.sid.irm.uk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.irm.uk1.zone <- plot_bar2(ps.maj.sid.irm.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.irm.uk1.zone

ps.maj.sid.pos.uk1.rel <- transform_sample_counts(ps.maj.sid.pos.uk1, function(x) x / sum(x))
ps.maj.sid.pos.uk1.rel.zone <- merge_samples(ps.maj.sid.pos.uk1.rel, "zone")
ps.maj.sid.pos.uk1.zone <- transform_sample_counts(ps.maj.sid.pos.uk1.rel.zone, function(x) x / sum(x))

gg.maj.sid.pos.uk1.zone <- plot_bar2(ps.maj.sid.pos.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pos.uk1.zone

#ggarrange(gg.maj.sid.pre.uk1.zone,gg.maj.sid.irm.uk1.zone,gg.maj.sid.pos.uk1.zone,nrow=1)
```

UPPER KEYS 2

```{r}
ps.maj.sid.pre.uk2.rel <- transform_sample_counts(ps.maj.sid.pre.uk2, function(x) x / sum(x))
ps.maj.sid.pre.uk2.rel.zone <- merge_samples(ps.maj.sid.pre.uk2.rel, "zone")
ps.maj.sid.pre.uk2.zone <- transform_sample_counts(ps.maj.sid.pre.uk2.rel.zone, function(x) x / sum(x))

gg.maj.sid.pre.uk2.zone <- plot_bar2(ps.maj.sid.pre.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pre.uk2.zone

ps.maj.sid.irm.uk2.rel <- transform_sample_counts(ps.maj.sid.irm.uk2, function(x) x / sum(x))
ps.maj.sid.irm.uk2.rel.zone <- merge_samples(ps.maj.sid.irm.uk2.rel, "zone")
ps.maj.sid.irm.uk2.zone <- transform_sample_counts(ps.maj.sid.irm.uk2.rel.zone, function(x) x / sum(x))

gg.maj.sid.irm.uk2.zone <- plot_bar2(ps.maj.sid.irm.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.irm.uk2.zone

ps.maj.sid.pos.uk2.rel <- transform_sample_counts(ps.maj.sid.pos.uk2, function(x) x / sum(x))
ps.maj.sid.pos.uk2.rel.zone <- merge_samples(ps.maj.sid.pos.uk2.rel, "zone")
ps.maj.sid.pos.uk2.zone <- transform_sample_counts(ps.maj.sid.pos.uk2.rel.zone, function(x) x / sum(x))

gg.maj.sid.pos.uk2.zone <- plot_bar2(ps.maj.sid.pos.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.sid.pos.uk2.zone

#ggarrange(gg.maj.sid.pre.uk2.zone,gg.maj.sid.irm.uk2.zone,gg.maj.sid.pos.uk2.zone,nrow=1)
```

All the sites

```{r}
ggarrange(gg.maj.sid.pre.lk1.zone,gg.maj.sid.irm.lk1.zone,gg.maj.sid.pos.lk1.zone,gg.maj.sid.pre.uk1.zone,gg.maj.sid.irm.uk1.zone,gg.maj.sid.pos.uk1.zone,gg.maj.sid.pre.uk2.zone,gg.maj.sid.irm.uk2.zone,gg.maj.sid.pos.uk2.zone,nrow=3,ncol=3,common.legend=T,legend="right")

#ggsave("gg.its2.sids.pdf",h=8,w=7)
```

#### S. radians

LOWER KEYS 1

```{r rad lk1}
ps.maj.rad.pre.lk1.rel <- transform_sample_counts(ps.maj.rad.pre.lk1, function(x) x / sum(x))
ps.maj.rad.pre.lk1.rel.zone <- merge_samples(ps.maj.rad.pre.lk1.rel, "zone")
ps.maj.rad.pre.lk1.zone <- transform_sample_counts(ps.maj.rad.pre.lk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.pre.lk1.zone <- plot_bar2(ps.maj.rad.pre.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pre.lk1.zone

ps.maj.rad.irm.lk1.rel <- transform_sample_counts(ps.maj.rad.irm.lk1, function(x) x / sum(x))
ps.maj.rad.irm.lk1.rel.zone <- merge_samples(ps.maj.rad.irm.lk1.rel, "zone")
ps.maj.rad.irm.lk1.zone <- transform_sample_counts(ps.maj.rad.irm.lk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.irm.lk1.zone <- plot_bar2(ps.maj.rad.irm.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.irm.lk1.zone

ps.maj.rad.pos.lk1.rel <- transform_sample_counts(ps.maj.rad.pos.lk1, function(x) x / sum(x))
ps.maj.rad.pos.lk1.rel.zone <- merge_samples(ps.maj.rad.pos.lk1.rel, "zone")
ps.maj.rad.pos.lk1.zone <- transform_sample_counts(ps.maj.rad.pos.lk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.pos.lk1.zone <- plot_bar2(ps.maj.rad.pos.lk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pos.lk1.zone

#ggarrange(gg.maj.rad.pre.lk1.zone,gg.maj.rad.irm.lk1.zone,gg.maj.rad.pos.lk1.zone,nrow=1)
```

UPPER KEYS 1

```{r rad uk1}
ps.maj.rad.pre.uk1.rel <- transform_sample_counts(ps.maj.rad.pre.uk1, function(x) x / sum(x))
ps.maj.rad.pre.uk1.rel.zone <- merge_samples(ps.maj.rad.pre.uk1.rel, "zone")
ps.maj.rad.pre.uk1.zone <- transform_sample_counts(ps.maj.rad.pre.uk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.pre.uk1.zone <- plot_bar2(ps.maj.rad.pre.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pre.uk1.zone

ps.maj.rad.irm.uk1.rel <- transform_sample_counts(ps.maj.rad.irm.uk1, function(x) x / sum(x))
ps.maj.rad.irm.uk1.rel.zone <- merge_samples(ps.maj.rad.irm.uk1.rel, "zone")
ps.maj.rad.irm.uk1.zone <- transform_sample_counts(ps.maj.rad.irm.uk1.rel.zone, function(x) x / sum(x))

gg.maj.rad.irm.uk1.zone <- plot_bar2(ps.maj.rad.irm.uk1.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.irm.uk1.zone

#uk1 not available for Post

#ggarrange(gg.maj.rad.pre.uk1.zone,gg.maj.rad.irm.uk1.zone,gg.maj.rad.pos.uk1.zone,nrow=1)
```

UPPER KEYS 2

```{r}
ps.maj.rad.pre.uk2.rel <- transform_sample_counts(ps.maj.rad.pre.uk2, function(x) x / sum(x))
ps.maj.rad.pre.uk2.rel.zone <- merge_samples(ps.maj.rad.pre.uk2.rel, "zone")
ps.maj.rad.pre.uk2.zone <- transform_sample_counts(ps.maj.rad.pre.uk2.rel.zone, function(x) x / sum(x))

gg.maj.rad.pre.uk2.zone <- plot_bar2(ps.maj.rad.pre.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pre.uk2.zone

ps.maj.rad.irm.uk2.rel <- transform_sample_counts(ps.maj.rad.irm.uk2, function(x) x / sum(x))
ps.maj.rad.irm.uk2.rel.zone <- merge_samples(ps.maj.rad.irm.uk2.rel, "zone")
ps.maj.rad.irm.uk2.zone <- transform_sample_counts(ps.maj.rad.irm.uk2.rel.zone, function(x) x / sum(x))

gg.maj.rad.irm.uk2.zone <- plot_bar2(ps.maj.rad.irm.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturb.")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.irm.uk2.zone

ps.maj.rad.pos.uk2.rel <- transform_sample_counts(ps.maj.rad.pos.uk2, function(x) x / sum(x))
ps.maj.rad.pos.uk2.rel.zone <- merge_samples(ps.maj.rad.pos.uk2.rel, "zone")
ps.maj.rad.pos.uk2.zone <- transform_sample_counts(ps.maj.rad.pos.uk2.rel.zone, function(x) x / sum(x))

gg.maj.rad.pos.uk2.zone <- plot_bar2(ps.maj.rad.pos.uk2.zone, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_x_discrete(labels=c("Inshore","Offshore"))+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  theme(axis.text.x=element_text(angle=45))
  
gg.maj.rad.pos.uk2.zone

#ggarrange(gg.maj.rad.pre.uk2.zone,gg.maj.rad.irm.uk2.zone,gg.maj.rad.pos.uk2.zone,nrow=1)
```

All the sites

```{r}
ggarrange(gg.maj.rad.pre.lk1.zone,gg.maj.rad.irm.lk1.zone,gg.maj.rad.pos.lk1.zone,gg.maj.rad.pre.uk1.zone,gg.maj.rad.irm.uk1.zone,gg.maj.rad.pre.uk2.zone,gg.maj.rad.irm.uk2.zone,gg.maj.rad.pos.uk2.zone,nrow=3,ncol=3,common.legend=T,legend="right")

#ggsave("gg.its2.rads.pdf",h=8,w=7)
```

### Different version of the same type profile plot

```{r sids by maj seq unifrac}
ps.maj.sid.pre.rel <- transform_sample_counts(ps.maj.sid.pre, function(x) x / sum(x))
ps.maj.sid.pre.rel.sz <- merge_samples(ps.maj.sid.pre.rel, "site_zone")
ps.maj.sid.pre.rel.sz <- transform_sample_counts(ps.maj.sid.pre.rel.sz, function(x) x / sum(x))

gg.bar.pre <- plot_bar2(ps.maj.sid.pre.rel.sz, fill="Majority_ITS2_collapsed")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_fill_manual(values=maj.seq.colors)+
  geom_bar(stat = "identity")
gg.bar.pre

ps.maj.sid.irm.rel <- transform_sample_counts(ps.maj.sid.irm, function(x) x / sum(x))
ps.maj.sid.irm.rel.sz <- merge_samples(ps.maj.sid.irm.rel, "site_zone")
ps.maj.sid.irm.rel.sz <- transform_sample_counts(ps.maj.sid.irm.rel.sz, function(x) x / sum(x))

gg.bar.irm <- plot_bar(ps.maj.sid.irm.rel.sz, fill="Majority_ITS2_collapsed")+
    ggtitle("Disturbance")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
    scale_fill_manual(values=maj.seq.colors)
gg.bar.irm

ps.maj.sid.pos.rel <- transform_sample_counts(ps.maj.sid.pos, function(x) x / sum(x))
ps.maj.sid.pos.rel.sz <- merge_samples(ps.maj.sid.pos.rel, "site_zone")
ps.maj.sid.pos.rel.sz <- transform_sample_counts(ps.maj.sid.pos.rel.sz, function(x) x / sum(x))

gg.bar.pos <- plot_bar(ps.maj.sid.pos.rel.sz, fill="Majority_ITS2_collapsed")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
    scale_fill_manual(values=maj.seq.colors)
gg.bar.pos

gg.bar.its2 <- ggarrange(gg.bar.pre,gg.bar.irm,gg.bar.pos,ncol=3,common.legend=T,legend="right")
gg.bar.its2
#ggsave("bar.its2.sids.pdf",width=9,height=4)
```

Type profile - Bray-Curtis distance

```{r types by bray}
maj.seq.colors <- c("#1B1B1B","#969696","#F9F9F9","#00294D","#195481","#5882AF","#9AB0CE","#D6DDE9","#D3E0D2","#95B792","#548C4E","#1F5D12","#002F00","#B8773A")
                         
ps.maj.sid.pre.rel <- transform_sample_counts(ps.maj.sid.pre, function(x) x / sum(x))
ps.maj.sid.pre.rel.sz <- merge_samples(ps.maj.sid.pre.rel, "site_zone")
ps.maj.sid.pre.rel.sz <- transform_sample_counts(ps.maj.sid.pre.rel.sz, function(x) x / sum(x))

gg.bar.pre <- plot_bar(ps.maj.sid.pre.rel.sz, fill="Majority_ITS2_sequence_bray")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
  scale_fill_manual(values=maj.seq.colors)
gg.bar.pre

ps.maj.sid.irm.rel <- transform_sample_counts(ps.maj.sid.irm, function(x) x / sum(x))
ps.maj.sid.irm.rel.sz <- merge_samples(ps.maj.sid.irm.rel, "site_zone")
ps.maj.sid.irm.rel.sz <- transform_sample_counts(ps.maj.sid.irm.rel.sz, function(x) x / sum(x))

gg.bar.irm <- plot_bar(ps.maj.sid.irm.rel.sz, fill="Majority_ITS2_sequence_bray")+
    ggtitle("Disturbance")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
    scale_fill_manual(values=maj.seq.colors)
gg.bar.irm

ps.maj.sid.pos.rel <- transform_sample_counts(ps.maj.sid.pos, function(x) x / sum(x))
ps.maj.sid.pos.rel.sz <- merge_samples(ps.maj.sid.pos.rel, "site_zone")
ps.maj.sid.pos.rel.sz <- transform_sample_counts(ps.maj.sid.pos.rel.sz, function(x) x / sum(x))

gg.bar.pos <- plot_bar(ps.maj.sid.pos.rel.sz, fill="Majority_ITS2_sequence_bray")+
    ggtitle("Post")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")+
    scale_fill_manual(values=maj.seq.colors)
gg.bar.pos

gg.bar.its2 <- ggarrange(gg.bar.pre,gg.bar.irm,gg.bar.pos,ncol=3,common.legend=T,legend="right")
gg.bar.its2
#ggsave("bar.its2.sids.pdf",width=9,height=4)
```

## Bar plot by type profile

### Setup - packages

```{r}
#remotes::install_github("KarstensLab/microshades")
library("microshades")
#remotes::install_github("mikemc/speedyseq")
library("speedyseq")
library(ggpubr)
library(cowplot)

#setwd("/Volumes/GoogleDrive-104519233854090018057/My Drive/Flirma/flirma_networks/fl_its2")
setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_its2")
```

### Setup - data

```{r}
ps <- readRDS("ps.its2.rds")

ps <- subset_samples(ps,site!="UK3")

ps.sid <- subset_samples(ps,spp=="ssid")
ps.rad <- subset_samples(ps,spp=="srad")

ps.sid.no0 <- prune_taxa(taxa_sums(ps.sid)!=0,ps.sid)
ps.rad.no0 <- prune_taxa(taxa_sums(ps.rad)!=0,ps.rad)
```

### Microshades!{.tabset}

#### Microshades plot - sids

```{r}
# Use microshades function prep_mdf to agglomerate, normalize, and melt the phyloseq object
mdf.ps.sid <- prep_mdf(ps.sid.no0,subgroup_level="Majority_ITS2_collapsed")

type_groups <- c(unique(mdf.ps.sid$Clade))

# Create a color object for the specified data
col.mdf.ps.sid <- create_color_dfs(mdf.ps.sid, top_orientation = FALSE,group_level="Clade",subgroup_level="Majority_ITS2_collapsed",selected_groups=c("A","B","C","D"),cvd=TRUE)

# Extract
col.mdf.ps.sid.m <- col.mdf.ps.sid$mdf
col.mdf.ps.sid.c <- col.mdf.ps.sid$cdf

col.mdf.ps.sid.m$zone <- sub("I","Inshore",col.mdf.ps.sid.m$zone)
col.mdf.ps.sid.m$zone <- sub("O","Offshore",col.mdf.ps.sid.m$zone)

col.mdf.ps.sid.m$time <- factor(col.mdf.ps.sid.m$time,levels=c("Pre","Irma","Post"))

col.mdf.ps.sid.c.new <- color_reassign(col.mdf.ps.sid.c,
                          group_assignment = c("A","B","C","D"),
                          color_assignment = c("micro_gray","micro_cvd_blue","micro_cvd_green","micro_brown"),group_level="Clade")

col.mdf.ps.sid.m.lk1 <- subset(col.mdf.ps.sid.m,site=="LK1")

ms.plot.lk1 <- plot_microshades(col.mdf.ps.sid.m.lk1, col.mdf.ps.sid.c.new)+
  facet_wrap(zone~time,scales="free_x")+
  theme_cowplot()+
  theme(axis.text.x=element_blank())+
  ggtitle("Lower Keys 1")+
  guides(color=guide_legend("Majority ITS2 sequence"),fill=guide_legend("Majority ITS2 sequence")) 
  #theme(axis.text.x=element_text(angle=45,hjust=1))
ms.plot.lk1

col.mdf.ps.sid.m.uk1 <- subset(col.mdf.ps.sid.m,site=="UK1")

ms.plot.uk1 <- plot_microshades(col.mdf.ps.sid.m.uk1, col.mdf.ps.sid.c.new)+
  facet_wrap(zone~time,scales="free_x")+
  theme_cowplot()+
  theme(axis.text.x=element_blank())+
  ggtitle("Upper Keys 1")+
  guides(color=guide_legend("Majority ITS2 sequence"),fill=guide_legend("Majority ITS2 sequence")) 
ms.plot.uk1

col.mdf.ps.sid.m.uk2 <- subset(col.mdf.ps.sid.m,site=="UK2")

ms.plot.uk2 <- plot_microshades(col.mdf.ps.sid.m.uk2, col.mdf.ps.sid.c.new)+
  facet_wrap(zone~time,scales="free_x")+
  theme_cowplot()+
  theme(axis.text.x=element_blank())+
  ggtitle("Upper Keys 2")+
  guides(color=guide_legend("Majority ITS2 sequence"),fill=guide_legend("Majority ITS2 sequence")) 
ms.plot.uk2

ms.plot.sid <- ggarrange(ms.plot.lk1,ms.plot.uk1,ms.plot.uk2,nrow=3,ncol=1,labels="AUTO")
annotate_figure(ms.plot.sid,top=text_grob("S. siderea",face="italic",size=16))

#ggsave("ms.plot.sid.pdf",height=10,width=8)
```

#### Microshades plot - rads

```{r}
# Use microshades function prep_mdf to agglomerate, normalize, and melt the phyloseq object
mdf.ps.rad <- prep_mdf(ps.rad.no0,subgroup_level="Majority_ITS2_collapsed")

type_groups <- c(unique(mdf.ps.rad$Clade))

# Create a color object for the specified data
col.mdf.ps.rad <- create_color_dfs(mdf.ps.rad, top_orientation = FALSE,group_level="Clade",subgroup_level="Majority_ITS2_collapsed",selected_groups=c("A","B","C","D"),cvd=TRUE)

# Extract
col.mdf.ps.rad.m <- col.mdf.ps.rad$mdf
col.mdf.ps.rad.c <- col.mdf.ps.rad$cdf

col.mdf.ps.rad.m$zone <- sub("I","Inshore",col.mdf.ps.rad.m$zone)
col.mdf.ps.rad.m$zone <- sub("O","Offshore",col.mdf.ps.rad.m$zone)

col.mdf.ps.rad.m$time <- factor(col.mdf.ps.rad.m$time,levels=c("Pre","Irma","Post"))

col.mdf.ps.rad.c.new <- color_reassign(col.mdf.ps.rad.c,
                          group_assignment = c("A","B","C","D"),
                          color_assignment = c("micro_gray","micro_cvd_blue","micro_cvd_green","micro_brown"),group_level="Clade")

col.mdf.ps.rad.m.lk1 <- subset(col.mdf.ps.rad.m,site=="LK1")

ms.plot.lk1 <- plot_microshades(col.mdf.ps.rad.m.lk1, col.mdf.ps.rad.c.new)+
  facet_wrap(zone~time,scales="free_x")+
  theme_cowplot()+
  theme(axis.text.x=element_blank())+
  ggtitle("Lower Keys 1")+
  guides(color=guide_legend("Majority ITS2 sequence"),fill=guide_legend("Majority ITS2 sequence")) 
ms.plot.lk1

col.mdf.ps.rad.m.uk1 <- subset(col.mdf.ps.rad.m,site=="UK1")

ms.plot.uk1 <- plot_microshades(col.mdf.ps.rad.m.uk1, col.mdf.ps.rad.c.new)+
  facet_wrap(zone~time,scales="free_x")+
  theme_cowplot()+
  theme(axis.text.x=element_blank())+
  ggtitle("Upper Keys 1")+
  guides(color=guide_legend("Majority ITS2 sequence"),fill=guide_legend("Majority ITS2 sequence")) 
ms.plot.uk1

col.mdf.ps.rad.m.uk2 <- subset(col.mdf.ps.rad.m,site=="UK2")

ms.plot.uk2 <- plot_microshades(col.mdf.ps.rad.m.uk2, col.mdf.ps.rad.c.new)+
  facet_wrap(zone~time,scales="free_x")+
  theme_cowplot()+
  theme(axis.text.x=element_blank())+
  ggtitle("Upper Keys 1")+
  guides(color=guide_legend("Majority ITS2 sequence"),fill=guide_legend("Majority ITS2 sequence")) 
ms.plot.uk2

ms.plot.rad <- ggarrange(ms.plot.lk1,ms.plot.uk1,ms.plot.uk2,nrow=3,ncol=1)
annotate_figure(ms.plot.rad,top=text_grob("S. radians",face="italic",size=16))

#ggsave("ms.plot.rad.pdf",height=10,width=8)
```

```{r}
ps.sid.pre.lk1i.rel <- transform_sample_counts(ps.sid.pre.lk1i, function(x) x / sum(x))

bar.sid.pre.lk1i <- plot_bar(ps.sid.pre.lk1i.rel, fill="ITS2_type_profile")+
    ggtitle("Pre")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1),legend.position="bottom")+
    xlab("")
bar.sid.pre.lk1i

ps.sid.irm.rel <- transform_sample_counts(ps.sid.irm, function(x) x / sum(x))
ps.sid.irm.rel.sz <- merge_samples(ps.sid.irm.rel, "site_zone")
ps.sid.irm.rel.sz.rel <- transform_sample_counts(ps.sid.irm.rel.sz, function(x) x / sum(x))

bar.sid.irm.sz <- plot_bar(ps.sid.irm.rel.sz.rel, fill="Clade")+
    ggtitle("irm")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.irm.sz

ps.sid.pos.rel <- transform_sample_counts(ps.sid.pos, function(x) x / sum(x))
ps.sid.pos.rel.sz <- merge_samples(ps.sid.pos.rel, "site_zone")
ps.sid.pos.rel.sz.rel <- transform_sample_counts(ps.sid.pos.rel.sz, function(x) x / sum(x))

bar.sid.pos.sz <- plot_bar(ps.sid.pos.rel.sz.rel, fill="Clade")+
    ggtitle("pos")+
    theme_cowplot()+
    theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("")
bar.sid.pos.sz

gg.bar.clade <- ggarrange(bar.sid.pre.sz,bar.sid.irm.sz,bar.sid.pos.sz,ncol=3,common.legend=T,legend="right")
gg.bar.clade
```


```{r heat map?}
ps.sid.pre.sz <- merge_samples(ps.sid.pre,"site_zone")
ps.sid.pre.sz <- merge_samples(ps.sid.pre,"site_zone")
ps.sid.pre.sz <- merge_samples(ps.sid.pre,"site_zone")

ps.sid.pre.sz.no0 <- prune_taxa(taxa_sums(ps.sid.pre.sz)!=0,ps.sid.pre.sz)
ps.sid.pre.sz.no0.rel <- transform_sample_counts(ps.sid.pre.sz.no0, function(x) x / sum(x))

sppAbun <- as.data.frame(ps.sid.pre.sz.no0.rel@otu_table)
heatmap(as.matrix(sppAbun))


plot_heatmap(ps.sid.pre.lk1.z.no0.rel)

sppAbun <- as.data.frame(ps.sid.pre.lk1.z@otu_table)

sppAbun[sppAbun > 0] <- 1 #converts from abundance to P/A
sppAbun

sppAbun2 <- sppAbun[,colSums(sppAbun)>0]

heatmap(as.matrix(sppAbun2))

heatmap.2(as.matrix(sppAbun2),Rowv=FALSE,Colv=FALSE)


ps.sid.lk1 <- subset_samples(ps.sid.no0,site=="LK1")
ps.sid.lk1.rel <- transform_sample_counts(ps.sid.lk1, function(x) x / sum(x))

plot_heatmap(ps.sid.lk1.rel)

plot_heatmap(ps.sid.lk1.rel,sample.order="zone",low="blue",high="red",na.value="black",method=NULL,distance=NULL)

## Presence/absence



mnwb.names <- subset(samdf,site_zone=="MNW-B")
mnwf.names <- subset(samdf,site_zone=="MNW-F")

mnwb.rows <- c(row.names(mnwb.names))

mnwb.pres <- sppAbun[row.names(sppAbun) %in% mnwb.rows,]
colSums(mnwb.pres)
plot(colSums(mnwb.pres))

#install.packages("gplots")
library(gplots)
heatmap.2(as.matrix(sppAbun),Rowv=FALSE,Colv=FALSE)
dev.off()

heatmap(as.matrix(sppAbun), scale='none')

ps.bin <- phyloseq(otu_table(sppAbun, taxa_are_rows=FALSE),
               sample_data(samdf),
               tax_table(mtaxa))

ps.bin


plot_heatmap(ps.bin,sample.order="site_zone")
dev.off()


#install.packages("gplots")
library(gplots)
heatmap.2(as.matrix(sppAbun),Rowv=FALSE,Colv=FALSE)
dev.off()

heatmap(as.matrix(sppAbun), scale='none')

ps.bin <- phyloseq(otu_table(sppAbun, taxa_are_rows=FALSE),
               sample_data(samdf),
               tax_table(mtaxa))

ps.bin


plot_heatmap(ps.bin,sample.order="site_zone")
dev.off()

```

```{r bubble plot?}
library(reshape2)

ps.sid.lk1.rel.pre <- subset_samples(ps.sid.lk1.rel,time=="Pre")
ps.sid.lk1.rel.pre.no0 <- prune_taxa(taxa_sums(ps.sid.lk1.rel.pre)!=0,ps.sid.lk1.rel.pre)

pc <- data.frame(ps.sid.lk1.rel.pre.no0@otu_table)
pc$Sample <- row.names(pc)
pcm = melt(pc, id = "Sample")

#pcm$Sample <- factor(pcm$Sample,levels=unique(pcm$Sample))
pcm$value <- as.numeric(pcm$value)

ggplot(pcm, aes(x = Sample, y = variable)) + 
  geom_point(aes(size = value, fill = variable), alpha = 0.75, shape = 21) + 
  scale_size_continuous(limits = c(0.01, 1)) + 
  labs( x= "", y = "", size = "Relative Abundance (%)", fill = "")  + 
  theme(legend.key=element_blank(), 
  axis.text.x = element_text(colour = "black", size = 12, face = "bold", angle = 90, vjust = 0.3, hjust = 1), 
  axis.text.y = element_text(colour = "black", face = "bold", size = 11), 
  #legend.text = element_text(size = 10, face ="bold", colour ="black"), 
  #legend.title = element_text(size = 12, face = "bold"), 
  #panel.background = element_blank(), panel.border = element_rect(colour = "black", fill = NA, size = 1.2), 
  legend.position = "right")  
  #scale_fill_manual(values = colours, guide = FALSE) + 
  #scale_y_discrete(limits = rev(levels(pcm$variable))) 

library(Rmisc)

melt.ps.sid.lk1.rel <- psmelt(ps.sid.lk1.rel)
melt.ps.sid.lk1.rel$Abundance[is.na(melt.ps.sid.lk1.rel$Abundance)] <- 0
melt.ps.sid.lk1.rel.sum <- summarySE(melt.ps.sid.lk1.rel,measurevar="Abundance",groupvars = c("ITS2_type_profile","zone"))

melt.ps.sid.lk1.rel.sum[melt.ps.sid.lk1.rel.sum==0] <- NA
melt.ps.sid.lk1.rel.sum2 <-melt.ps.sid.lk1.rel.sum[complete.cases(melt.ps.sid.lk1.rel.sum),]

bub.genus.mse <- ggplot(melt.ps.sid.lk1.rel.sum2, aes(x = zone, y = ITS2_type_profile)) + 
  geom_point(aes(size = Abundance, fill = ITS2_type_profile), alpha = 0.75, shape = 21)+
  #scale_size_continuous(limits=c(0.00001,1),breaks = c(.0001,.10,.50,.75)) + 
  #scale_size_continuous(limits = c(0.01, 1), breaks = c(.1,.5,.75,1)) + 
  #facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()+
  #scale_fill_manual(values=cols.mse, guide=FALSE)+
  #ggtitle("Moorea SE")+
  #ylab("ASV")+
  #xlab("")+
  #scale_x_discrete(labels=c("Back","Fore"))+
  guides(fill="none")
bub.genus.mse


library(dplyr)
tb <- psmelt(ps.sid.lk1.rel) %>%
  filter(!is.na(ITS2_type_profile)) %>%
  group_by(zone,sample,ITS2_type_profile) %>%
  # Add abundances within each phylum and sample
  summarize_at("Abundance", sum) %>%
  # Get phylum proportions within each sample
  #summarize_at("Proportion", ~ . / sum(.)) %>%
  # Get the mean proportion each phylum across samples within the `Sex` (Male/Female) variable
  #summarize_at("Proportion", mean)
#### bubble plot - genus ####
library(dplyr)

#MOOREA NW
melt.mnw <- psmelt(indic.mnw.rel)
melt.mnw$Abundance[is.na(melt.mnw$Abundance)] <- 0
melt.mnw.sum <- summarySE(melt.mnw,measurevar="Abundance",groupvars = c("Genus","zone"))

melt.mnw.sum$bool_col <- melt.mnw.sum$Genus %in% genus.mnwi$genus
melt.mnw.sum$indic_res <- ifelse(melt.mnw.sum$bool_col == T, "Back reef", "Fore reef")

bub.genus.mnw <- ggplot(melt.mnw.sum, aes(x = zone, y = Genus)) + 
  geom_point(aes(size = Abundance, fill = Genus), alpha = 0.75, shape = 21)+
  facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()+
  #scale_fill_manual(values=cols.mnw, guide=FALSE)+
  ggtitle("Moorea NW")+
  ylab("ASV")+
  xlab("")+
  scale_x_discrete(labels=c("Back","Fore"))
bub.genus.mnw

```

# PCoAs{.tabset}

```{r}
library(cowplot)
library(phyloseq)
library(vegan)
library(ggplot2)
```

```{r no uk3 for pcoas}
setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_its2")
#ps <- readRDS("ps.its2.rds")
#ps.rel <- transform_sample_counts(ps, function(x) x / sum(x))
#saveRDS(ps.rel,"ps.its2.rel.rds")
ps1 <- readRDS("ps.its2.rel.rds")
ps <- subset_samples(ps1,site!="UK3")

ps.sid <- subset_samples(ps,spp=="ssid")

ps.sid.pre <- subset_samples(ps.sid,time=="Pre")
ps.sid.irm <- subset_samples(ps.sid,time=="Irma")
ps.sid.pos <- subset_samples(ps.sid,time=="Post")

ps.sid.pre.lk1 <- subset_samples(ps.sid.pre,site=="LK1")
ps.sid.pre.uk1 <- subset_samples(ps.sid.pre,site=="UK1")
ps.sid.pre.uk2 <- subset_samples(ps.sid.pre,site=="UK2")

ps.sid.irm.lk1 <- subset_samples(ps.sid.irm,site=="LK1")
ps.sid.irm.uk1 <- subset_samples(ps.sid.irm,site=="UK1")
ps.sid.irm.uk2 <- subset_samples(ps.sid.irm,site=="UK2")

ps.sid.pos.lk1 <- subset_samples(ps.sid.pos,site=="LK1")
ps.sid.pos.uk1 <- subset_samples(ps.sid.pos,site=="UK1")
ps.sid.pos.uk2 <- subset_samples(ps.sid.pos,site=="UK2")

##for time stats
ps.sid.lk1 <- subset_samples(ps.sid,site=="LK1")
ps.sid.uk1 <- subset_samples(ps.sid,site=="UK1")
ps.sid.uk2 <- subset_samples(ps.sid,site=="UK2")

ps.sid.lk1i <- subset_samples(ps.sid.lk1,zone=="I")
ps.sid.lk1o <- subset_samples(ps.sid.lk1,zone=="O")

ps.sid.uk1i <- subset_samples(ps.sid.uk1,zone=="I")
ps.sid.uk1o <- subset_samples(ps.sid.uk1,zone=="O")

ps.sid.uk2i <- subset_samples(ps.sid.uk2,zone=="I")
ps.sid.uk2o <- subset_samples(ps.sid.uk2,zone=="O")
```

### Reef zones

```{r type profiles by site}
ord.sid.pre.lk1 <- ordinate(ps.sid.pre.lk1,"PCoA",distance="bray")
plot_ordination(ps.sid.pre.lk1, ord.sid.pre.lk1, color ="zone")+
  #geom_point(alpha=0.5)+
  #scale_color_manual(values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(values=c(16,15))+
  stat_ellipse()+
  theme_cowplot()
  #facet_grid(site~zone)

#ggsave(filename="pcoa.types.site.pdf")
```

# Stats - type profiles

## Setup

```{r adonis stats packages}
library(vegan)
#remotes::install_github("Jtrachsel/funfuns")
library(funfuns)
library(dplyr)
library(edgeR)

setwd("/Volumes/GoogleDrive/My Drive/Flirma/flirma_networks/fl_its2")
ps <- readRDS("ps.its2.rds")

ps <- subset_samples(ps,site!="UK3")
```

## Subset

```{r subset by site}
ps.sid <- subset_samples(ps,spp="ssid")
ps.sid <- transform_sample_counts(ps.sid, function(x) x / sum(x))

##for in v off stats
ps.sid.pre <- subset_samples(ps.sid,time=="Pre")
ps.sid.irm <- subset_samples(ps.sid,time=="Irma")
ps.sid.pos <- subset_samples(ps.sid,time=="Post")

ps.sid.pre.lk1 <- subset_samples(ps.sid.pre,site=="LK1")
ps.sid.pre.uk1 <- subset_samples(ps.sid.pre,site=="UK1")
ps.sid.pre.uk2 <- subset_samples(ps.sid.pre,site=="UK2")

ps.sid.irm.lk1 <- subset_samples(ps.sid.irm,site=="LK1")
ps.sid.irm.uk1 <- subset_samples(ps.sid.irm,site=="UK1")
ps.sid.irm.uk2 <- subset_samples(ps.sid.irm,site=="UK2")

ps.sid.pos.lk1 <- subset_samples(ps.sid.pos,site=="LK1")
ps.sid.pos.uk1 <- subset_samples(ps.sid.pos,site=="UK1")
ps.sid.pos.uk2 <- subset_samples(ps.sid.pos,site=="UK2")

##for time stats
ps.sid.lk1 <- subset_samples(ps.sid,site=="LK1")
ps.sid.uk1 <- subset_samples(ps.sid,site=="UK1")
ps.sid.uk2 <- subset_samples(ps.sid,site=="UK2")

ps.sid.lk1i <- subset_samples(ps.sid.lk1,zone=="I")
ps.sid.lk1o <- subset_samples(ps.sid.lk1,zone=="O")

ps.sid.uk1i <- subset_samples(ps.sid.uk1,zone=="I")
ps.sid.uk1o <- subset_samples(ps.sid.uk1,zone=="O")

ps.sid.uk2i <- subset_samples(ps.sid.uk2,zone=="I")
ps.sid.uk2o <- subset_samples(ps.sid.uk2,zone=="O")
```

## Adonises{.tabset}

### Lower Keys 1

```{r stats lk1 rel}
##reef zone pre
seq.sid.pre.lk1 <- data.frame(ps.sid.pre.lk1@otu_table)
samdf.sid.pre.lk1 <- data.frame(ps.sid.pre.lk1@sam_data)

dist.sid.pre.lk1 <- vegdist(seq.sid.pre.lk1)
##zone
bet.sid.pre.lk1 <- betadisper(dist.sid.pre.lk1,samdf.sid.pre.lk1$zone)
#anova(bet.ps)
permutest(bet.sid.pre.lk1,pairwise=FALSE,permutations=999) #ns
plot(bet.sid.pre.lk1) #ns

adonis2(seq.sid.pre.lk1 ~ zone, data=samdf.sid.pre.lk1, permutations=999) #ns

##reef zone irm
seq.sid.irm.lk1 <- data.frame(ps.sid.irm.lk1@otu_table)
samdf.sid.irm.lk1 <- data.frame(ps.sid.irm.lk1@sam_data)

dist.sid.irm.lk1 <- vegdist(seq.sid.irm.lk1)
##zone
bet.sid.irm.lk1 <- betadisper(dist.sid.irm.lk1,samdf.sid.irm.lk1$zone)
#anova(bet.ps)
permutest(bet.sid.irm.lk1,pairwise=FALSE,permutations=999) #ns
plot(bet.sid.irm.lk1) #ns

adonis2(seq.sid.irm.lk1 ~ zone, data=samdf.sid.irm.lk1, permutations=999)
#adonis2(formula = seq.sid.irm.lk1 ~ zone, data = samdf.sid.irm.lk1, permutations = 999)
#          Df SumOfSqs      R2     F Pr(>F)  
# zone      1   0.8368 0.06787 1.966  0.038 *
# Residual 27  11.4929 0.93213               
# Total    28  12.3298 1.00000               
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

##reef zone post
seq.sid.pos.lk1 <- data.frame(ps.sid.pos.lk1@otu_table)
samdf.sid.pos.lk1 <- data.frame(ps.sid.pos.lk1@sam_data)

dist.sid.pos.lk1 <- vegdist(seq.sid.pos.lk1)
##zone
bet.sid.pos.lk1 <- betadisper(dist.sid.pos.lk1,samdf.sid.pos.lk1$zone)
#anova(bet.ps)
permutest(bet.sid.pos.lk1,pairwise=FALSE,permutations=999) #ns
plot(bet.sid.pos.lk1) #ns

adonis2(seq.sid.pos.lk1 ~ zone, data=samdf.sid.pos.lk1, permutations=999) #ns

##time - inshore
seq.sid.lk1i <- data.frame(ps.sid.lk1i@otu_table)
samdf.sid.lk1i <- data.frame(ps.sid.lk1i@sam_data)

dist.sid.lk1i <- vegdist(seq.sid.lk1i)

bet.sid.lk1i <- betadisper(dist.sid.lk1i,samdf.sid.lk1i$time)
#anova(bet.ps)
permutest(bet.sid.lk1i,pairwise=TRUE,permutations=999)
#post different than other two, looks more constrained
# Permutation test for homogeneity of multivariate dispersions
# Permutation: free
# Number of permutations: 999
# 
# Response: Distances
#           Df  Sum Sq   Mean Sq      F N.Perm Pr(>F)  
# Groups     2 0.05045 0.0252251 4.4942    999  0.016 *
# Residuals 46 0.25819 0.0056128                       
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Pairwise comparisons:
# (Observed p-value below diagonal, permuted p-value above diagonal)
#           Irma      Post   Pre
# Irma           0.0240000 0.349
# Post 0.0239826           0.006
# Pre  0.3359886 0.0082901  
plot(bet.sid.lk1i) 

adonis2(seq.sid.lk1i ~ time, data=samdf.sid.lk1i, permutations=999) #p<0.001***

pairwise.adonis(seq.sid.lk1i, factors=samdf.sid.lk1i$time, permutations=999)
##pre diff than post
#          pairs  F.Model         R2 p.value p.adjusted
# 1  Pre vs Irma 1.273944 0.04208053   0.272      0.272
# 2  Pre vs Post 3.211953 0.08869871   0.001      0.001
# 3 Irma vs Post 1.507718 0.04785234   0.124      0.124

##time - offshore
seq.sid.lk1o <- data.frame(ps.sid.lk1o@otu_table)
samdf.sid.lk1o <- data.frame(ps.sid.lk1o@sam_data)

dist.sid.lk1o <- vegdist(seq.sid.lk1o)

bet.sid.lk1o <- betadisper(dist.sid.lk1o,samdf.sid.lk1o$time)
#anova(bet.ps)
permutest(bet.sid.lk1o,pairwise=TRUE,permutations=999)
# Response: Distances
#           Df  Sum Sq Mean Sq      F N.Perm Pr(>F)  
# Groups     2 0.75134 0.37567 4.6472    999  0.013 *
# Residuals 23 1.85927 0.08084                       
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Pairwise comparisons:
# (Observed p-value below diagonal, permuted p-value above diagonal)
#          Irma     Post   Pre
# Irma          0.023000 0.258
# Post 0.016582          0.016
# Pre  0.244461 0.012564      
plot(bet.sid.lk1o) 

adonis2(seq.sid.lk1o ~ time, data=samdf.sid.lk1o, permutations=999) #p<0.001***

pairwise.adonis(seq.sid.lk1o, factors=samdf.sid.lk1o$time, permutations=999)
#all different 
#          pairs  F.Model        R2 p.value p.adjusted
# 1  Post vs Pre 4.748312 0.2288529   0.004      0.004
# 2 Post vs Irma 3.634191 0.1950281   0.001      0.001
# 3  Pre vs Irma 2.850122 0.1596696   0.048      0.048
```

### Upper Keys 1

```{r stats uk1 rel}
##reef zone pre
seq.sid.pre.uk1 <- data.frame(ps.sid.pre.uk1@otu_table)
samdf.sid.pre.uk1 <- data.frame(ps.sid.pre.uk1@sam_data)

dist.sid.pre.uk1 <- vegdist(seq.sid.pre.uk1)
##zone
bet.sid.pre.uk1 <- betadisper(dist.sid.pre.uk1,samdf.sid.pre.uk1$zone)
#anova(bet.ps)
permutest(bet.sid.pre.uk1,pairwise=FALSE,permutations=999)
plot(bet.sid.pre.uk1)
#          Df SumOfSqs      R2      F Pr(>F)  
# zone      1    0.914 0.06604 2.0507  0.023 *
# Residual 29   12.925 0.93396                
# Total    30   13.839 1.00000                

adonis2(seq.sid.pre.uk1 ~ zone, data=samdf.sid.pre.uk1, permutations=999) 
# adonis2(formula = seq.sid.pre.uk1 ~ zone, data = samdf.sid.pre.uk1, permutations = 999)
#          Df SumOfSqs      R2      F Pr(>F)  
# zone      1    0.914 0.06604 2.0507  0.021 *
# Residual 29   12.925 0.93396                
# Total    30   13.839 1.00000                
# ---

##reef zone irm
seq.sid.irm.uk1 <- data.frame(ps.sid.irm.uk1@otu_table)
samdf.sid.irm.uk1 <- data.frame(ps.sid.irm.uk1@sam_data)

dist.sid.irm.uk1 <- vegdist(seq.sid.irm.uk1)
##zone
bet.sid.irm.uk1 <- betadisper(dist.sid.irm.uk1,samdf.sid.irm.uk1$zone)
#anova(bet.ps)
permutest(bet.sid.irm.uk1,pairwise=FALSE,permutations=999) #ns
plot(bet.sid.irm.uk1) #ns

adonis2(seq.sid.irm.uk1 ~ zone, data=samdf.sid.irm.uk1, permutations=999)
# adonis2(formula = seq.sid.irm.uk1 ~ zone, data = samdf.sid.irm.uk1, permutations = 999)
#          Df SumOfSqs      R2      F Pr(>F)   
# zone      1   1.3958 0.09887 3.2915  0.002 **
# Residual 30  12.7216 0.90113                 
# Total    31  14.1174 1.00000          

##reef zone post
seq.sid.pos.uk1 <- data.frame(ps.sid.pos.uk1@otu_table)
samdf.sid.pos.uk1 <- data.frame(ps.sid.pos.uk1@sam_data)

dist.sid.pos.uk1 <- vegdist(seq.sid.pos.uk1)
##zone
bet.sid.pos.uk1 <- betadisper(dist.sid.pos.uk1,samdf.sid.pos.uk1$zone)
#anova(bet.ps)
permutest(bet.sid.pos.uk1,pairwise=FALSE,permutations=999) #ns
plot(bet.sid.pos.uk1) #ns

adonis2(seq.sid.pos.uk1 ~ zone, data=samdf.sid.pos.uk1, permutations=999) #ns

##time
seq.sid.uk1i <- data.frame(ps.sid.uk1i@otu_table)
samdf.sid.uk1i <- data.frame(ps.sid.uk1i@sam_data)

dist.sid.uk1i <- vegdist(seq.sid.uk1i)

bet.sid.uk1i <- betadisper(dist.sid.uk1i,samdf.sid.uk1i$time)
#anova(bet.ps)
permutest(bet.sid.uk1i,pairwise=TRUE,permutations=999) #ns
plot(bet.sid.uk1i) 

adonis2(seq.sid.uk1i ~ time, data=samdf.sid.uk1i, permutations=999) #p<0.01**

pairwise.adonis(seq.sid.uk1i, factors=samdf.sid.uk1i$time, permutations=999)
#          pairs  F.Model         R2 p.value p.adjusted
# 1  Post vs Pre 1.903144 0.07347155   0.016      0.016
# 2 Post vs Irma 2.306884 0.08149552   0.009      0.009
# 3  Pre vs Irma 1.898341 0.05600101   0.054      0.054

#almost all different, but pre v irma not bt
```





```{r}
ps.sid.rel <- transform_sample_counts(ps.sid, function(x) x / sum(x))
## Presence/absence

sppAbun <- as.data.frame(ps.sid.rel@otu_table)

sppAbun[sppAbun > 0] <- 1 #converts from abundance to P/A
sppAbun

rowSums(sppAbun)

morethan1 <- sppAbun[rowSums(sppAbun)>1,]

find.top.taxa <- function(x,taxa){
  require(phyloseq)
  top.taxa <- tax_glom(x, taxa)
  otu <- otu_table(t(top.taxa)) # remove the transformation if using a merge_sample object
  tax <- tax_table(top.taxa)
  j<-apply(otu,1,which.max)
  k <- j[!duplicated(j)]
  l <- data.frame(tax[k,])
  m <- data.frame(otu[,k])
  s <- as.name(taxa)
  colnames(m) = l[,taxa]
  n <- colnames(m)[apply(m,1,which.max)]
  m[,taxa] <- n
  return(m)
}
find.top.taxa(top.pdy,"Phylum")

#chi-square, top vs side
chisq.test(SymPortalDataK_1$variable, SymPortalDataK_1$label, correct=FALSE)
#Pearson's Chi-squared test

#data:  SymPortalDataK_1$variable and SymPortalDataK_1$label
#X-squared = 5.5824, df = 6, p-value = 0.4716


```





## Find "most frequent" sym

Just ran once to get the info

```{r top sym, eval=FALSE}
find.top.asv <- function(x,num){
  require(phyloseq)
  require(magrittr)
  
  otu <- otu_table(x)
  tax <- tax_table(x)
  j1 <- apply(otu,1,sort,index.return=T, decreasing=T) # modifying which.max to return a list of sorted index
  j2 <- lapply(j1,'[[',"ix") # select for index
  
  l <- data.frame(unique(tax@.Data[unlist(j2),]))
  m <- data.frame(otu@.Data[,unique(unlist(j2))])
  n <- apply(m,1,sort,index.return=T, decreasing=T) %>%
    lapply('[[',"ix") %>%  # Extract index
    lapply(head,n=num) # This to returns the top x tax

  p <- list()
  for(i in 1:length(n)){
    p[[i]]<- colnames(m)[n[[i]]]
  }
  m$taxa <- p
  return(m)
}

top.asvs <- find.top.asv(ps.sid,5)
top.asvs$taxa <- as.character(top.asvs$taxa)

#write.csv(top.asvs,file="top_sym.csv",row.names=TRUE)
```

```{r}
table <- read.csv("silly_its_table.csv",header=T)

heatmap(as.matrix(table[,2:11]), labRow=table[,1],rowv=NA)
```

```{r scraps, include=FALSE, eval=FALSE}
#### Genus by site & zone

#Nothing interesting

# ps.sz <- merge_samples(ps, "site_zone")
# ps.sz.clade <- tax_glom(ps.sz, "Clade")
# ps.sz.clade.rel <- transform_sample_counts(ps.sz.clade, function(x) x / sum(x))
# plot_bar(ps.sz.clade.rel, fill="Clade")+
#     geom_bar(aes(color=Clade, fill=Clade), stat="identity", position="stack")

#messy scraps

## Trying out pie charts

#install.packages("remotes")
#remotes::install_github("cpauvert/psadd")

ggplot(melt.ps.rel.mnw, aes(x = "", y = Abundance, fill = ITS2_type_profile)) +
  geom_bar(stat = "identity") +
  coord_polar("y", start = 0)+
  #geom_text(aes(y = lab.ypos,), color = "white")+
  #scale_fill_manual(values = mycols) +
  theme_void()


ps.sz.rel <- transform_sample_counts(ps.sz, function(x) x / sum(x))

plot_heatmap(ps.rel,sample.label="site_zone",sample.order="site_zone")
plot_heatmap(ps.sz.rel,sample.order="site_zone",low="blue",high="red",na.value="black")+
  facet_wrap(~site)

rownames(dat) = dat$weather

ps.sz.rel@sam_data$zone <- c("BR","FR","BR","FR","BR","FR")
plot_heatmap(ps.sz.rel,sample.order="site_zone",low="blue",high="red",na.value="black",method=NULL,distance=NULL)


seq.sz.rel <- data.frame(ps.sid.irm.rel@otu_table)
heatmap.2(as.matrix(t(seq.sz.rel)),Rowv=FALSE,Colv=FALSE)

melt.sz.rel <- psmelt(ps.sz.rel)

ggplot(melt.sz.rel, aes(x = Sample, y = OTU)) + 
  geom_point(aes(size = Abundance, fill = OTU), alpha = 0.75, shape = 21)+
  #facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()
  #scale_fill_manual(values=cols.mnw, guide=FALSE)+
  #ggtitle("Moorea NW")+
  #ylab("ASV")+
  #xlab("")+
  #scale_x_discrete(labels=c("Back","Fore"))

melt.ps <- psmelt(ps)
ggplot(melt.ps, aes(x = sample_full, y = OTU)) + 
  geom_point(aes(size = Abundance, fill = OTU), alpha = 0.75, shape = 21)+
  #facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()
  #scale_fill_manual(values=cols.mnw, guide=FALSE)+
  #ggtitle("Moorea NW")+
  #ylab("ASV")+
  #xlab("")+
  #scale_x_discrete(labels=c("Back","Fore"))

melt.ps.rel <- psmelt(ps.rel)
melt.ps.rel.mnw <- subset(melt.ps.rel,site=="MNW")
melt.ps.rel.mnw.no0 <- subset(melt.ps.rel.mnw,Abundance>0)
ggplot(melt.ps.rel.mnw.no0, aes(x = sample_full, y = OTU)) + 
  geom_point(aes(size = Abundance, fill = OTU), alpha = 0.75, shape = 21)+
  #facet_grid(indic_res~.,scales="free",space="free")+
  theme_cowplot()

plot_heatmap(ps.sz.rel,sample.order="site_zone",low="blue",high="red",na.value="black",method=NULL,distance=NULL)

## Presence/absence

sppAbun <- as.data.frame(ps@otu_table)

sppAbun[sppAbun > 0] <- 1 #converts from abundance to P/A
sppAbun

mnwb.names <- subset(samdf,site_zone=="MNW-B")
mnwf.names <- subset(samdf,site_zone=="MNW-F")

mnwb.rows <- c(row.names(mnwb.names))

mnwb.pres <- sppAbun[row.names(sppAbun) %in% mnwb.rows,]
colSums(mnwb.pres)
plot(colSums(mnwb.pres))

#install.packages("gplots")
library(gplots)
heatmap.2(as.matrix(sppAbun),Rowv=FALSE,Colv=FALSE)
dev.off()

heatmap(as.matrix(sppAbun), scale='none')

ps.bin <- phyloseq(otu_table(sppAbun, taxa_are_rows=FALSE),
               sample_data(samdf),
               tax_table(mtaxa))

ps.bin


plot_heatmap(ps.bin,sample.order="site_zone")
dev.off()

```


# Flirma scripts scraps

## Collapsing type profiles via phylogeny tree

Started with file: "188_20211214_03_DBV_20211215T030311.seqs.fasta" in the post-med seqs folder. Also started with the taxa info 'Majority_ITS2_sequence", removed the slashes between types, & removed duplicates. That left 24 unique ITS2 types, put these in 'names.txt'. Want to extract the relevant sequences from the fasta file now

```{bash, eval=F}
for word in $(cat names.txt); do echo $word; grep -w -A 1 $word postmedseqs.fasta >> output.fasta; done
```

*Important notes:* produced a fasta file with '--' in between some desired entries, removed that manually, but I'm sure there's a better way than that. It also gave me an unwanted one (A4.3), took that out manually. Easy to do with 24 types, but would be harder with more than that.. processed file was named _output_types_cleaned.fasta_

Then went to ngphylogeny.fr to plot.

More notes: 
- A is fine, the majority sequences are pretty disparate. 
- The Bs are a total mess, will plot below
- Cs are fine
- Ds are fine

