---
title: "fl16s_networks_revised"
author: "Nicola Kriefall"
date: "11/20/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Setup

## Libraries, data

```{r}
#install.packages("devtools")
library(devtools)
install_github("zdk123/SpiecEasi")
#had some issues here, this solution worked:
#https://www.cynkra.com/blog/2021-03-16-gfortran-macos/
library(SpiecEasi)
library("stringr")
library("igraph")
#library("MCMC.OTU")
library("phyloseq")
library("ggplot2")
#install.packages("remotes")
#remotes::install_github("vmikk/metagMisc")
library("metagMisc")

##work
#setwd("~/Library/CloudStorage/GoogleDrive-nicfall@bu.edu/My Drive/Flirma/flirma_networks/fl_16s/04.networks")

##home
setwd("~/nicfall@bu.edu - Google Drive/My Drive/Flirma/flirma_networks/fl_16s/04.networks")

##re-read ps object to work with [first run-through]:
#ps.clean <- readRDS("../01.generate_asv_table/fl16s.23.ps.cleaner.less.rds")

##made below:
ps.clean <- readRDS("ps.clean.asvsnamed.rds")
```

## Name the ASVs

```{r, eval=F}
tax <- as.data.frame(ps.clean@tax_table@.Data)

tax.clean <- data.frame(row.names = row.names(tax),
                        Kingdom = str_replace(tax[,1], "D_0__",""),
                        Phylum = str_replace(tax[,2], "D_1__",""),
                        Class = str_replace(tax[,3], "D_2__",""),
                        Order = str_replace(tax[,4], "D_3__",""),
                        Family = str_replace(tax[,5], "D_4__",""),
                        Genus = str_replace(tax[,6], "D_5__",""),
                        Species = str_replace(tax[,7], "D_6__",""),
                        stringsAsFactors = FALSE)
tax.clean[is.na(tax.clean)] <- ""

for (i in 1:7){ tax.clean[,i] <- as.character(tax.clean[,i])}
####### Fill holes in the tax table
tax.clean[is.na(tax.clean)] <- ""
for (i in 1:nrow(tax.clean)){
  if (tax.clean[i,2] == ""){
    kingdom <- paste("Kingdom_", tax.clean[i,1], sep = "")
    tax.clean[i, 2:7] <- kingdom
  } else if (tax.clean[i,3] == ""){
    phylum <- paste("Phylum_", tax.clean[i,2], sep = "")
    tax.clean[i, 3:7] <- phylum
  } else if (tax.clean[i,4] == ""){
    class <- paste("Class_", tax.clean[i,3], sep = "")
    tax.clean[i, 4:7] <- class
  } else if (tax.clean[i,5] == ""){
    order <- paste("Order_", tax.clean[i,4], sep = "")
    tax.clean[i, 5:7] <- order
  } else if (tax.clean[i,6] == ""){
    family <- paste("Family_", tax.clean[i,5], sep = "")
    tax.clean[i, 6:7] <- family
  } else if (tax.clean[i,7] == ""){
    tax.clean$Species[i] <- paste("Genus",tax.clean$Genus[i], sep = "_")
  }
}

tax_table(ps.clean) <- as.matrix(tax.clean)

#saveRDS(ps.clean,file="ps.clean.asvsnamed.rds")
```

## More data processing

```{r}
ps.gen <- tax_glom(ps.clean,taxrank="Genus")
ps.fam <- tax_glom(ps.clean,taxrank="Family")
##saving
#saveRDS(ps.gen,file="ps.clean.gen.rds")
#saveRDS(ps.fam,file="ps.clean.fam.rds")

ps.sid <- subset_samples(ps.gen,spp=="ssid")

ps.rad1 <- subset_samples(ps.gen,spp=="srad")

#radians is missing too many samples at UK1 to include that site
ps.rad <- subset_samples(ps.rad1,site=="UK2"|site=="LK1")
```

## Filtering OTUs

### Checking out read depth things

```{r}
sum(sample_sums(ps.clean))
#11798865 
#117 = 0.001% of total reads

df <- data.frame(ps.gen@otu_table) # Put sample_data into aggplot-friendly data.frame
df.t <- data.frame(t(df))
df.t$libsize <- rowSums(df.t)

df <- df.t[order(df.t$libsize),]

df$Index <- seq(nrow(df))
##all of them:
ggplot(data=df, aes(x=Index, y=libsize))+
  geom_point()
#3 crazy outliers:
tail(df$libsize)
#so the 'max' should be around 626557, excluding the higher outliers

ggplot(data=df, aes(x=Index, y=log(libsize)))+
  geom_point()
  #xlim(0,50000)+
  #ylim(0,200)

```

Should be present in ~10-30% of samples [different papers do different thresholds]

### Siderea

```{r}
ps.sid.trim <- phyloseq_filter_prevalence(ps.sid,abund.trh=62,prev.trh=0.2,threshold_condition="AND")
ps.sid.trim #192 taxa

#saveRDS(ps.sid.trim,file="ps.sid.gen.trim.rds")
#ps.sid.trim <- readRDS("./nets_revised/ps.sid.trim.rds")

ps.sid.pre <- subset_samples(ps.sid.trim,time=="Pre")
ps.sid.irm <- subset_samples(ps.sid.trim,time=="Irma")
ps.sid.pos <- subset_samples(ps.sid.trim,time=="Post")

ps.sid.pre2 <- phyloseq_filter_prevalence(ps.sid.pre,prev.trh=0.2)
ps.sid.pre2 #168 taxa
##58 samples = must be in 11.6 samples

ps.sid.irm2 <- phyloseq_filter_prevalence(ps.sid.irm,prev.trh=0.2)
ps.sid.irm2 #172 taxa
##65 samples = must be in 13 samples

ps.sid.pos2 <- phyloseq_filter_prevalence(ps.sid.pos,prev.trh=0.2)
ps.sid.pos2 #161 taxa
##44 samples = must be in 8.8 samples
```

### Radians

```{r}
ps.rad.trim <- phyloseq_filter_prevalence(ps.rad,abund.trh=62,prev.trh=0.2,threshold_condition="AND")
ps.rad.trim #349 taxa

#saveRDS(ps.rad.trim,file="ps.rad.gen.trim.rds")
#ps.rad.trim <- readRDS("./nets_revised/ps.rad.trim.rds")

ps.rad.pre <- subset_samples(ps.rad.trim,time=="Pre")
ps.rad.irm <- subset_samples(ps.rad.trim,time=="Irma")
ps.rad.pos <- subset_samples(ps.rad.trim,time=="Post")

ps.rad.pre2 <- phyloseq_filter_prevalence(ps.rad.pre,prev.trh=0.2)
ps.rad.pre2 #341 taxa
##37 samples = must be in 7.4 samples

ps.rad.irm2 <- phyloseq_filter_prevalence(ps.rad.irm,prev.trh=0.2)
ps.rad.irm2 #311 taxa
##37 samples = must be in 7.4 samples

ps.rad.pos2 <- phyloseq_filter_prevalence(ps.rad.pos,prev.trh=0.2)
ps.rad.pos2 #185 taxa
##30 samples = must be in 6 samples
```

```{r}
##gen.2 level
# saveRDS(ps.sid.pre2,file="./nets_revised/ps.sid.pre.gen.2")
# saveRDS(ps.sid.irm2,file="./nets_revised/ps.sid.irm.gen.2")
# saveRDS(ps.sid.pos2,file="./nets_revised/ps.sid.pos.gen.2")
# 
# saveRDS(ps.rad.pre2,file="./nets_revised/ps.rad.pre.gen.2")
# saveRDS(ps.rad.irm2,file="./nets_revised/ps.rad.irm.gen.2")
# saveRDS(ps.rad.pos2,file="./nets_revised/ps.rad.pos.gen.2")
```

# Checking spatial relationship

## Setup

Using this page [here](https://jkzorz.github.io/2019/07/08/mantel-test.html)

```{r}
#library("ade4")
library(vegan)
#install.packages("geosphere")
library(geosphere)
```

## Lat/lon info

```{r}
##constructing site info data frame
lat <- c(24.535409, 24.495846,  24.90383722, 24.89525025, 25.2179648, 25.2012167)
lon <- c(-81.6223756, -81.6485388, -80.60967778, -80.57261263, -80.2760984, -80.2268668)
site_zone <- c("LK1-I","LK1-O","UK1-I","UK1-O","UK2-I","UK2-O")
df.site <- data.frame(lat,lon,site_zone)
```

## Siderea

### Pre

```{r}
##transferring lat lon info to sample data frame
samdf.sid.pre <- data.frame(ps.sid.pre2@sam_data)
otu.sid.pre <- data.frame(ps.sid.pre2@otu_table)

samdf.sid.pre.lat <- merge(samdf.sid.pre,df.site)
row.names(samdf.sid.pre.lat) <- samdf.sid.pre.lat$sample_num
row.names(otu.sid.pre)==row.names(samdf.sid.pre.lat)

##calculating distances between sites
geo.sid.pre <- data.frame(samdf.sid.pre.lat$lat, samdf.sid.pre.lat$lon)
d.geo.sid.pre = distm(geo.sid.pre, fun = distHaversine)
dist.geo.sid.pre = as.dist(d.geo.sid.pre)

##distances between samples
dist.sid.pre = vegdist(otu.sid.pre, method = "bray")

##mantel comparison
otu.geo.sid.pre <- mantel(dist.sid.pre, dist.geo.sid.pre, method = "spearman", permutations = 999, na.rm = TRUE)
otu.geo.sid.pre

# Mantel statistic r: 0.1273 
#       Significance: 0.004 
```

### Irma

```{r}
samdf.sid.irm <- data.frame(ps.sid.irm2@sam_data)
otu.sid.irm <- data.frame(ps.sid.irm2@otu_table)

samdf.sid.irm.lat <- merge(samdf.sid.irm,df.site)
row.names(samdf.sid.irm.lat) <- samdf.sid.irm.lat$sample_num
row.names(otu.sid.irm)==row.names(samdf.sid.irm.lat)

##calculating distances between sites
geo.sid.irm <- data.frame(samdf.sid.irm.lat$lat, samdf.sid.irm.lat$lon)
d.geo.sid.irm = distm(geo.sid.irm, fun = distHaversine)
dist.geo.sid.irm = as.dist(d.geo.sid.irm)

##distances between samples
dist.sid.irm = vegdist(otu.sid.irm, method = "bray")

##mantel comparison
otu.geo.sid.irm <- mantel(dist.sid.irm, dist.geo.sid.irm, method = "spearman", permutations = 999, na.rm = TRUE)
otu.geo.sid.irm
# Mantel statistic r: 0.05987 
#       Significance: 0.083 
```

### Post

```{r}
samdf.sid.pos <- data.frame(ps.sid.pos2@sam_data)
otu.sid.pos <- data.frame(ps.sid.pos2@otu_table)

samdf.sid.pos.lat <- merge(samdf.sid.pos,df.site)
row.names(samdf.sid.pos.lat) <- samdf.sid.pos.lat$sample_num
row.names(otu.sid.pos)==row.names(samdf.sid.pos.lat)

##calculating distances between sites
geo.sid.pos <- data.frame(samdf.sid.pos.lat$lat, samdf.sid.pos.lat$lon)
d.geo.sid.pos = distm(geo.sid.pos, fun = distHaversine)
dist.geo.sid.pos = as.dist(d.geo.sid.pos)

##distances between samples
dist.sid.pos = vegdist(otu.sid.pos, method = "bray")

##mantel comparison
otu.geo.sid.pos <- mantel(dist.sid.pos, dist.geo.sid.pos, method = "spearman", permutations = 999, na.rm = TRUE)
otu.geo.sid.pos
# Mantel statistic r: -0.02654 
#       Significance: 0.786 
```

## Radians

### Pre rads

```{r}
##transferring lat lon info to sample data frame

samdf.rad.pre <- data.frame(ps.rad.pre2@sam_data)
otu.rad.pre <- data.frame(ps.rad.pre2@otu_table)

samdf.rad.pre.lat <- merge(samdf.rad.pre,df.site)
row.names(samdf.rad.pre.lat) <- samdf.rad.pre.lat$sample_num
row.names(otu.rad.pre)==row.names(samdf.rad.pre.lat)

##calculating distances between sites
geo.rad.pre <- data.frame(samdf.rad.pre.lat$lat, samdf.rad.pre.lat$lon)
d.geo.rad.pre = distm(geo.rad.pre, fun = distHaversine)
dist.geo.rad.pre = as.dist(d.geo.rad.pre)

##distances between samples
dist.rad.pre = vegdist(otu.rad.pre, method = "bray")

##mantel comparison
otu.geo.rad.pre <- mantel(dist.rad.pre, dist.geo.rad.pre, method = "spearman", permutations = 999, na.rm = TRUE)
otu.geo.rad.pre
# Mantel statistic r: 0.03674 
#       Significance: 0.155 
```

### Irma

```{r}
samdf.rad.irm <- data.frame(ps.rad.irm2@sam_data)
otu.rad.irm <- data.frame(ps.rad.irm2@otu_table)

samdf.rad.irm.lat <- merge(samdf.rad.irm,df.site)
row.names(samdf.rad.irm.lat) <- samdf.rad.irm.lat$sample_num
row.names(otu.rad.irm)==row.names(samdf.rad.irm.lat)

##calculating distances between sites
geo.rad.irm <- data.frame(samdf.rad.irm.lat$lat, samdf.rad.irm.lat$lon)
d.geo.rad.irm = distm(geo.rad.irm, fun = distHaversine)
dist.geo.rad.irm = as.dist(d.geo.rad.irm)

##distances between samples
dist.rad.irm = vegdist(otu.rad.irm, method = "bray")

##mantel comparison
otu.geo.rad.irm <- mantel(dist.rad.irm, dist.geo.rad.irm, method = "spearman", permutations = 999, na.rm = TRUE)
otu.geo.rad.irm
# Mantel statistic r: 0.07332 
#       Significance: 0.06 
```

### Post

```{r}
samdf.rad.pos <- data.frame(ps.rad.pos2@sam_data)
otu.rad.pos <- data.frame(ps.rad.pos2@otu_table)

samdf.rad.pos.lat <- merge(samdf.rad.pos,df.site)
row.names(samdf.rad.pos.lat) <- samdf.rad.pos.lat$sample_num
row.names(otu.rad.pos)==row.names(samdf.rad.pos.lat)

##calculating distances between sites
geo.rad.pos <- data.frame(samdf.rad.pos.lat$lat, samdf.rad.pos.lat$lon)
d.geo.rad.pos = distm(geo.rad.pos, fun = distHaversine)
dist.geo.rad.pos = as.dist(d.geo.rad.pos)

##distances between samples
dist.rad.pos = vegdist(otu.rad.pos, method = "bray")

##mantel comparison
otu.geo.rad.pos <- mantel(dist.rad.pos, dist.geo.rad.pos, method = "spearman", permutations = 999, na.rm = TRUE)
otu.geo.rad.pos
# Mantel statistic r: 0.01746 
#       Significance: 0.324 
```

# Constructing networks

Stabilities 2023: 

## Siderea

```{r}
set.seed(10010)

##PRE
se.sid.pre <- spiec.easi(as.matrix(otu.sid.pre), method='mb', lambda.min.ratio=1e-1,nlambda=40, pulsar.params=list(rep.num=50))
getStability(se.sid.pre)
#0.04621272

## Create igraph objects
ig.sid.pre <- adj2igraph(getRefit(se.sid.pre))

## set size of vertex proportional to clr-mean
vsize.sid.pre    <- rowMeans(clr(otu.sid.pre, 1))+6
coord.sid.pre <- igraph::layout.fruchterman.reingold(ig.sid.pre)

par(mfrow=c(1,3))
plot(ig.sid.pre, layout=coord.sid.pre, vertex.size=vsize.sid.pre, vertex.label=NA, main="MB")

##IRM
se.sid.irm <- spiec.easi(as.matrix(otu.sid.irm), method='mb', lambda.min.ratio=1e-1,nlambda=40, pulsar.params=list(rep.num=50))
getStability(se.sid.irm) 
#0.04978833

## Create igraph objects
ig.sid.irm <- adj2igraph(getRefit(se.sid.irm))

## set size of vertex proportional to clr-mean
vsize.sid.irm    <- rowMeans(clr(otu.sid.irm, 1))+6
coord.sid.irm <- igraph::layout.fruchterman.reingold(ig.sid.irm)

#par(mfrow=c(1,3))
plot(ig.sid.irm, layout=coord.sid.irm, vertex.size=vsize.sid.irm, vertex.label=NA, main="MB")

##POS
se.sid.pos <- spiec.easi(as.matrix(otu.sid.pos), method='mb', lambda.min.ratio=1e-1,nlambda=40, pulsar.params=list(rep.num=50))
#nlambda being bumped up in order to get closer to target 0.05 stability level
getStability(se.sid.pos) 
#0.04584497

## Create igraph objects
ig.sid.pos <- adj2igraph(getRefit(se.sid.pos))

## set size of vertex proportional to clr-mean
vsize.sid.pos <- rowMeans(clr(otu.sid.pos, 1))+6
coord.sid.pos <- igraph::layout.fruchterman.reingold(ig.sid.pos)

#par(mfrow=c(1,3))
plot(ig.sid.pos, layout=coord.sid.pos, vertex.size=vsize.sid.pos, vertex.label=NA, main="MB")

#saveRDS(se.sid.pre,file="./nets_revised/se.sid.pre.gen.2.rds")
#saveRDS(se.sid.irm,file="./nets_revised/se.sid.irm.gen.2.rds")
#saveRDS(se.sid.pos,file="./nets_revised/se.sid.pos.gen.2.rds")
```

## Radians

```{r}
set.seed(10010)

##PRE
se.rad.pre <- spiec.easi(as.matrix(otu.rad.pre), method='mb', lambda.min.ratio=1e-1,nlambda=40, pulsar.params=list(rep.num=50))
getStability(se.rad.pre)
#0.04958292

## Create igraph objects
ig.rad.pre <- adj2igraph(getRefit(se.rad.pre))

## set size of vertex proportional to clr-mean
vsize.rad.pre    <- rowMeans(clr(otu.rad.pre, 1))+6
coord.rad.pre <- igraph::layout.fruchterman.reingold(ig.rad.pre)

par(mfrow=c(1,3))
plot(ig.rad.pre, layout=coord.rad.pre, vertex.size=vsize.rad.pre, vertex.label=NA, main="MB")

se.rad.irm <- spiec.easi(as.matrix(otu.rad.irm), method='mb', lambda.min.ratio=1e-1,nlambda=40, pulsar.params=list(rep.num=50))
getStability(se.rad.irm) 
#0.04989162

## Create igraph objects
ig.rad.irm <- adj2igraph(getRefit(se.rad.irm))

## set size of vertex proportional to clr-mean
vsize.rad.irm    <- rowMeans(clr(otu.rad.irm, 1))+6
coord.rad.irm <- igraph::layout.fruchterman.reingold(ig.rad.irm)

#par(mfrow=c(1,3))
plot(ig.rad.irm, layout=coord.rad.irm, vertex.size=vsize.rad.irm, vertex.label=NA, main="MB")

se.rad.pos <- spiec.easi(as.matrix(otu.rad.pos), method='mb', lambda.min.ratio=1e-1,nlambda=40, pulsar.params=list(rep.num=50))
getStability(se.rad.pos) 
#0.04518881

## Create igraph objects
ig.rad.pos <- adj2igraph(getRefit(se.rad.pos))

## set size of vertex proportional to clr-mean
vsize.rad.pos <- rowMeans(clr(otu.rad.pos, 1))+6
coord.rad.pos <- igraph::layout.fruchterman.reingold(ig.rad.pos)

#par(mfrow=c(1,3))
plot(ig.rad.pos, layout=coord.rad.pos, vertex.size=vsize.rad.pos, vertex.label=NA, main="MB")

# saveRDS(se.rad.pre,file="./nets_revised/se.rad.pre.gen.2.rds")
# saveRDS(se.rad.irm,file="./nets_revised/se.rad.irm.gen.2.rds")
# saveRDS(se.rad.pos,file="./nets_revised/se.rad.pos.gen.2.rds")
```

# Basic igraph info

## Setup

### Libraries

```{r}
#install.packages("ggraph")
library("ggraph")
library("tidygraph")
#plot_network(ig.rad.pre, ps.rad.pre, type='taxa', color="Rank3")
#install.packages("ggnet")

#install.packages("GGally")
library("GGally") #contains ggnet
#install.packages("intergraph")
library("intergraph")
#install.packages("sna")
library("sna")
library(ggpubr)
library("Rmisc")

setwd("~/nicfall@bu.edu - Google Drive/My Drive/Flirma/flirma_networks/fl_16s/04.networks")

##very pretty resource: http://web.stanford.edu/class/bios221/NetworkSlides.html
```

### Re-read in nets & ps objects

```{r}
##sids
se.sid.pre <- readRDS("./nets_revised/se.sid.pre.gen.2.rds")
getStability(se.sid.pre) #0.04621272

se.sid.irm <- readRDS("./nets_revised/se.sid.irm.gen.2.rds")
getStability(se.sid.irm) #0.04978833 

se.sid.pos <- readRDS("./nets_revised/se.sid.pos.gen.2.rds")
getStability(se.sid.pos) #0.04584497

ps.sid.pre <- readRDS("./nets_revised/ps.sid.pre.gen.2")
ps.sid.irm <- readRDS("./nets_revised/ps.sid.irm.gen.2")
ps.sid.pos <- readRDS("./nets_revised/ps.sid.pos.gen.2")

ig.sid.pre <- adj2igraph(getRefit(se.sid.pre))
ig.sid.irm <- adj2igraph(getRefit(se.sid.irm))
ig.sid.pos <- adj2igraph(getRefit(se.sid.pos))

##rads
se.rad.pre <- readRDS("./nets_revised/se.rad.pre.gen.2.rds")
getStability(se.rad.pre) #0.04958292

se.rad.irm <- readRDS("./nets_revised/se.rad.irm.gen.2.rds")
getStability(se.rad.irm) #0.04989162

se.rad.pos <- readRDS("./nets_revised/se.rad.pos.gen.2.rds")
getStability(se.rad.pos) #0.04518881

ps.rad.pre <- readRDS("./nets_revised/ps.rad.pre.gen.2")
ps.rad.irm <- readRDS("./nets_revised/ps.rad.irm.gen.2")
ps.rad.pos <- readRDS("./nets_revised/ps.rad.pos.gen.2")

##made these extra info igraph objects below:
ig.sid.pre <- readRDS("./nets_revised/ig.sid.pre.gen.2.rds")
ig.sid.irm <- readRDS("./nets_revised/ig.sid.irm.gen.2.rds")
ig.sid.pos <- readRDS("./nets_revised/ig.sid.pos.gen.2.rds")

ig.rad.pre <- readRDS("./nets_revised/ig.rad.pre.gen.2.rds")
ig.rad.irm <- readRDS("./nets_revised/ig.rad.irm.gen.2.rds")
ig.rad.pos <- readRDS("./nets_revised/ig.rad.pos.gen.2.rds")
```

## Basic igraph info{.tabset}

Taken from [this site](https://kateto.net/netscix2016.html)

"The description of an igraph object starts with up to four letters:

D or U, for a directed or undirected graph
N for a named graph (where nodes have a name attribute)
W for a weighted graph (where edges have a weight attribute)
B for a bipartite (two-mode) graph (where nodes have a type attribute)
The two numbers that follow (7 5) refer to the number of nodes and edges in the graph. The description also lists node & edge attributes, for example:

(g/c) - graph-level character attribute
(v/c) - vertex-level character attribute
(e/n) - edge-level numeric attribute

### Siderea pre

```{r}
#ig.sid.pre
# IGRAPH 8f13dcd UNW- 145 174 -- 
# + attr: name (v/n), weight (e/n)
# + edges from 8f13dcd (vertex names):
#U=undirected
#N=named
#W=weighted

##getting some more info from the spieceasi objects before making the igraph object
##following things here: https://github.com/zdk123/SpiecEasi/issues/109
##here's a more complete chapter: https://mibwurrepo.github.io/Microbial-bioinformatics-introductory-course-Material-2018/inference-of-microbial-ecological-networks.html
sebeta.sid.pre <- symBeta(getOptBeta(se.sid.pre),mode='maxabs')
rownames(sebeta.sid.pre) <- colnames(sebeta.sid.pre) <- taxa_names(ps.sid.pre)
elist.sid.pre <- summary(sebeta.sid.pre)
emat.sid.pre <- data.frame(as.matrix(sebeta.sid.pre))

positive=length(emat.sid.pre[emat.sid.pre>0])/2 #205
negative=length(emat.sid.pre[emat.sid.pre<0])/2 #80
total=length(emat.sid.pre[emat.sid.pre!=0])/2 #285
# We divide by two since an edge is represented by two entries in the matrix.

ig.sid.pre <- adj2igraph(getRefit(se.sid.pre),diag=TRUE,
                  edge.attr=elist.sid.pre,
                  vertex.attr=list(name=taxa_names(ps.sid.pre)))

otu.ids=colnames(se.sid.pre$est$data)
edges=E(ig.sid.pre)
edge.colors=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.sid.pre,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.sid.pre[xindex,yindex]
        if(beta>0){
                edge.colors=append(edge.colors,"forestgreen")
        }else if(beta<0){
                edge.colors=append(edge.colors,"red")
        }
}
E(ig.sid.pre)$color=edge.colors

#weights
#https://github.com/zdk123/SpiecEasi/issues/81
edges.wts=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.sid.pre,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.sid.pre[xindex,yindex]
        edges.wts=append(edges.wts,abs(beta))
        }
E(ig.sid.pre)$width=edges.wts

##will plot nicer below
ggnet2(ig.sid.pre,size="degree",max_size=4,size.cut=3,edge.color="color",edge.size="width")

##In terms of interpretation, apparently it's not great to assign 'strength' of 'correlations':
#https://github.com/zdk123/SpiecEasi/issues/54
##This is given by the absolute value of the coefficients (the beta matrix). However, due to the penalization/shrinkage, it is not really possible to compare association strengths across experiments but this is generally true of any LASSO type regression.
```

### Siderea irm

```{r}
#ig.sid.irm
# IGRAPH 8f13dcd UNW- 145 174 -- 
# + attr: name (v/n), weight (e/n)
# + edges from 8f13dcd (vertex names):
#U=undirected
#N=named
#W=weighted

##getting some more info from the spieceasi objects before making the igraph object
##following things here: https://github.com/zdk123/SpiecEasi/issues/109
##here's a more complete chapter: https://mibwurrepo.github.io/Microbial-bioinformatics-introductory-course-Material-2018/inference-of-microbial-ecological-networks.html
sebeta.sid.irm <- symBeta(getOptBeta(se.sid.irm),mode='maxabs')
rownames(sebeta.sid.irm) <- colnames(sebeta.sid.irm) <- taxa_names(ps.sid.irm)
elist.sid.irm <- summary(sebeta.sid.irm)
emat.sid.irm <- data.frame(as.matrix(sebeta.sid.irm))

positive=length(emat.sid.irm[emat.sid.irm>0])/2 #207
negative=length(emat.sid.irm[emat.sid.irm<0])/2 #102
total=length(emat.sid.irm[emat.sid.irm!=0])/2 #309
# We divide by two since an edge is reirmsented by two entries in the matrix.

ig.sid.irm <- adj2igraph(getRefit(se.sid.irm),diag=TRUE,
                  edge.attr=elist.sid.irm,
                  vertex.attr=list(name=taxa_names(ps.sid.irm)))

otu.ids=colnames(se.sid.irm$est$data)
edges=E(ig.sid.irm)
edge.colors=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.sid.irm,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.sid.irm[xindex,yindex]
        if(beta>0){
                edge.colors=append(edge.colors,"forestgreen")
        }else if(beta<0){
                edge.colors=append(edge.colors,"red")
        }
}
E(ig.sid.irm)$color=edge.colors

#weights
#https://github.com/zdk123/SpiecEasi/issues/81
edges.wts=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.sid.irm,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.sid.irm[xindex,yindex]
        edges.wts=append(edges.wts,abs(beta))
        }
E(ig.sid.irm)$width=edges.wts

ggnet2(ig.sid.irm,size="degree",max_size=4,size.cut=3,edge.color="color",edge.size="width")
```

### Siderea pos

```{r}
#ig.sid.pos
# IGRAPH 8f13dcd UNW- 145 174 -- 
# + attr: name (v/n), weight (e/n)
# + edges from 8f13dcd (vertex names):
#U=undirected
#N=named
#W=weighted

##getting some more info from the spieceasi objects before making the igraph object
##following things here: https://github.com/zdk123/SpiecEasi/issues/109
##here's a more complete chapter: https://mibwurrepo.github.io/Microbial-bioinformatics-introductory-course-Material-2018/inference-of-microbial-ecological-networks.html
sebeta.sid.pos <- symBeta(getOptBeta(se.sid.pos),mode='maxabs')
rownames(sebeta.sid.pos) <- colnames(sebeta.sid.pos) <- taxa_names(ps.sid.pos)
elist.sid.pos <- summary(sebeta.sid.pos)
emat.sid.pos <- data.frame(as.matrix(sebeta.sid.pos))

positive=length(emat.sid.pos[emat.sid.pos>0])/2 #163
negative=length(emat.sid.pos[emat.sid.pos<0])/2 #73
total=length(emat.sid.pos[emat.sid.pos!=0])/2 #236
# We divide by two since an edge is repossented by two entries in the matrix.

ig.sid.pos <- adj2igraph(getRefit(se.sid.pos),diag=TRUE,
                  edge.attr=elist.sid.pos,
                  vertex.attr=list(name=taxa_names(ps.sid.pos)))

otu.ids=colnames(se.sid.pos$est$data)
edges=E(ig.sid.pos)
edge.colors=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.sid.pos,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.sid.pos[xindex,yindex]
        if(beta>0){
                edge.colors=append(edge.colors,"forestgreen")
        }else if(beta<0){
                edge.colors=append(edge.colors,"red")
        }
}
E(ig.sid.pos)$color=edge.colors

#weights
#https://github.com/zdk123/SpiecEasi/issues/81
edges.wts=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.sid.pos,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.sid.pos[xindex,yindex]
        edges.wts=append(edges.wts,abs(beta))
        }
E(ig.sid.pos)$width=edges.wts

ggnet2(ig.sid.pos,size="degree",max_size=4,size.cut=3,edge.color="color",edge.size="width")
```

### Radians pre

```{r}
#ig.rad.pre
# IGRAPH 8f13dcd UNW- 145 174 -- 
# + attr: name (v/n), weight (e/n)
# + edges from 8f13dcd (vertex names):
#U=undirected
#N=named
#W=weighted

##getting some more info from the spieceasi objects before making the igraph object
##following things here: https://github.com/zdk123/SpiecEasi/issues/109
##here's a more complete chapter: https://mibwurrepo.github.io/Microbial-bioinformatics-introductory-course-Material-2018/inference-of-microbial-ecological-networks.html
sebeta.rad.pre <- symBeta(getOptBeta(se.rad.pre),mode='maxabs')
rownames(sebeta.rad.pre) <- colnames(sebeta.rad.pre) <- taxa_names(ps.rad.pre)
elist.rad.pre <- summary(sebeta.rad.pre)
emat.rad.pre <- data.frame(as.matrix(sebeta.rad.pre))

positive=length(emat.rad.pre[emat.rad.pre>0])/2 #731
negative=length(emat.rad.pre[emat.rad.pre<0])/2 #398
total=length(emat.rad.pre[emat.rad.pre!=0])/2 #1129
# We divide by two since an edge is represented by two entries in the matrix.

ig.rad.pre <- adj2igraph(getRefit(se.rad.pre),diag=TRUE,
                  edge.attr=elist.rad.pre,
                  vertex.attr=list(name=taxa_names(ps.rad.pre)))

otu.ids=colnames(se.rad.pre$est$data)
edges=E(ig.rad.pre)
edge.colors=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.rad.pre,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.rad.pre[xindex,yindex]
        if(beta>0){
                edge.colors=append(edge.colors,"forestgreen")
        }else if(beta<0){
                edge.colors=append(edge.colors,"red")
        }
}
E(ig.rad.pre)$color=edge.colors

#weights
#https://github.com/zdk123/SpiecEasi/issues/81
edges.wts=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.rad.pre,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.rad.pre[xindex,yindex]
        edges.wts=append(edges.wts,abs(beta))
        }
E(ig.rad.pre)$width=edges.wts

##will plot nicer below
ggnet2(ig.rad.pre,size="degree",max_size=5,size.cut=3,edge.color="color")
```

### Radians irm

```{r}
#ig.rad.irm
# IGRAPH 8f13dcd UNW- 145 174 -- 
# + attr: name (v/n), weight (e/n)
# + edges from 8f13dcd (vertex names):
#U=undirected
#N=named
#W=weighted

##getting some more info from the spieceasi objects before making the igraph object
##following things here: https://github.com/zdk123/SpiecEasi/issues/109
##here's a more complete chapter: https://mibwurrepo.github.io/Microbial-bioinformatics-introductory-course-Material-2018/inference-of-microbial-ecological-networks.html
sebeta.rad.irm <- symBeta(getOptBeta(se.rad.irm),mode='maxabs')
rownames(sebeta.rad.irm) <- colnames(sebeta.rad.irm) <- taxa_names(ps.rad.irm)
elist.rad.irm <- summary(sebeta.rad.irm)
emat.rad.irm <- data.frame(as.matrix(sebeta.rad.irm))

positive=length(emat.rad.irm[emat.rad.irm>0])/2 #648
negative=length(emat.rad.irm[emat.rad.irm<0])/2 #299
total=length(emat.rad.irm[emat.rad.irm!=0])/2 #947
# We divide by two since an edge is reirmsented by two entries in the matrix.

ig.rad.irm <- adj2igraph(getRefit(se.rad.irm),diag=TRUE,
                  edge.attr=elist.rad.irm,
                  vertex.attr=list(name=taxa_names(ps.rad.irm)))

otu.ids=colnames(se.rad.irm$est$data)
edges=E(ig.rad.irm)
edge.colors=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.rad.irm,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.rad.irm[xindex,yindex]
        if(beta>0){
                edge.colors=append(edge.colors,"forestgreen")
        }else if(beta<0){
                edge.colors=append(edge.colors,"red")
        }
}
E(ig.rad.irm)$color=edge.colors

#weights
#https://github.com/zdk123/SpiecEasi/issues/81
edges.wts=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.rad.irm,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.rad.irm[xindex,yindex]
        edges.wts=append(edges.wts,abs(beta))
        }
E(ig.rad.irm)$width=edges.wts

#ggnet2(ig.rad.irm,size="degree",max_size=4,size.cut=3,edge.color="color",edge.size="width")
ggnet2(ig.rad.irm,size="degree",max_size=5,size.cut=3,edge.color="color",edge.size="width")
```

### Radians pos

```{r}
#ig.rad.pos
# IGRAPH 8f13dcd UNW- 145 174 -- 
# + attr: name (v/n), weight (e/n)
# + edges from 8f13dcd (vertex names):
#U=undirected
#N=named
#W=weighted

##getting some more info from the spieceasi objects before making the igraph object
##following things here: https://github.com/zdk123/SpiecEasi/issues/109
##here's a more complete chapter: https://mibwurrepo.github.io/Microbial-bioinformatics-introductory-course-Material-2018/inference-of-microbial-ecological-networks.html
sebeta.rad.pos <- symBeta(getOptBeta(se.rad.pos),mode='maxabs')
rownames(sebeta.rad.pos) <- colnames(sebeta.rad.pos) <- taxa_names(ps.rad.pos)
elist.rad.pos <- summary(sebeta.rad.pos)
emat.rad.pos <- data.frame(as.matrix(sebeta.rad.pos))

positive=length(emat.rad.pos[emat.rad.pos>0])/2 #206
negative=length(emat.rad.pos[emat.rad.pos<0])/2 #83
total=length(emat.rad.pos[emat.rad.pos!=0])/2 #289
# We divide by two since an edge is repossented by two entries in the matrix.

ig.rad.pos <- adj2igraph(getRefit(se.rad.pos),diag=TRUE,
                  edge.attr=elist.rad.pos,
                  vertex.attr=list(name=taxa_names(ps.rad.pos)))

otu.ids=colnames(se.rad.pos$est$data)
edges=E(ig.rad.pos)
edge.colors=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.rad.pos,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.rad.pos[xindex,yindex]
        if(beta>0){
                edge.colors=append(edge.colors,"forestgreen")
        }else if(beta<0){
                edge.colors=append(edge.colors,"red")
        }
}
E(ig.rad.pos)$color=edge.colors

#weights
#https://github.com/zdk123/SpiecEasi/issues/81
edges.wts=c()
for(e.index in 1:length(edges)){
        adj.nodes=ends(ig.rad.pos,edges[e.index])
        xindex=which(otu.ids==adj.nodes[1])
        yindex=which(otu.ids==adj.nodes[2])
        beta=emat.rad.pos[xindex,yindex]
        edges.wts=append(edges.wts,abs(beta))
        }
E(ig.rad.pos)$width=edges.wts

ggnet2(ig.rad.pos,size="degree",max_size=4,size.cut=3,edge.color="color",edge.size="width")
```

## Some igraph metrics

### Transitivity

"The transitivity or clustering coefficient of a network is a measure of the tendency of the nodes to cluster together. High transitivity means that the network contains communities or groups of nodes that are densely connected internally." [from here](https://www.ebi.ac.uk/training/online/courses/network-analysis-of-protein-interaction-data-an-introduction/protein-protein-interaction-networks/properties-of-ppins-transitivity/#:~:text=The%20transitivity%20or%20clustering%20coefficient,that%20are%20densely%20connected%20internally.)

#### Sids

```{r}
transitivity(ig.sid.pre,type = "globalundirected") #0.1076336
transitivity(ig.sid.irm,type = "globalundirected") #0.102439
transitivity(ig.sid.pos,type = "globalundirected") #0.1156069

transitivity(ig.rad.pre,type = "globalundirected") #0.09109785
transitivity(ig.rad.irm,type = "globalundirected") #0.07662902
transitivity(ig.rad.pos,type = "globalundirected") #0.07676561
 
transitivity(ig.sid.pre,type = "average") #0.1035044
transitivity(ig.sid.irm,type = "average") #0.08923723
transitivity(ig.sid.pos,type = "average") #0.1510539

transitivity(ig.rad.pre,type = "average") #0.08904219
transitivity(ig.rad.irm,type = "average") #0.07206697
transitivity(ig.rad.pos,type = "average") #0.09027498

tran.sid.pre <- data.frame(transitivity(ig.sid.pre,type = "local"))
tran.sid.irm <- data.frame(transitivity(ig.sid.irm,type = "local"))
tran.sid.pos <- data.frame(transitivity(ig.sid.pos,type = "local"))

tran.rad.pre <- data.frame(transitivity(ig.rad.pre,type = "local"))
tran.rad.irm <- data.frame(transitivity(ig.rad.irm,type = "local"))
tran.rad.pos <- data.frame(transitivity(ig.rad.pos,type = "local"))

tran.sid.pre$time <- rep("Pre",nrow(tran.sid.pre))
colnames(tran.sid.pre) <- c("tran","time")

tran.sid.irm$time <- rep("Irma",nrow(tran.sid.irm))
colnames(tran.sid.irm) <- c("tran","time")

tran.sid.pos$time <- rep("Post",nrow(tran.sid.pos))
colnames(tran.sid.pos) <- c("tran","time")

tran.sid <- rbind(tran.sid.pre,tran.sid.irm,tran.sid.pos)
tran.sid.complete <- tran.sid[complete.cases(tran.sid),]

tran.sid.se <- summarySE(tran.sid.complete,measurevar="tran",groupvars=c("time"))

ggplot(tran.sid.se,aes(x=time,y=log(tran)))+
  geom_jitter(data=tran.sid.complete,alpha=0.5)+
  geom_violin(data=tran.sid.complete,alpha=0.5)+
  geom_point(size=2)+
  geom_errorbar(aes(ymin=log(tran-se),ymax=log(tran+se)))

ggplot(tran.sid.complete,aes(x=time,y=log(tran)))+
  geom_jitter(alpha=0.5)+
  geom_boxplot(alpha=0.5)
####clean up? show?####

pairwise.wilcox.test(tran.sid.complete$tran,tran.sid.complete$time,p.adjust.method = "BH")
```

#### Rads

```{r}
tran.rad.pre$time <- rep("Pre",nrow(tran.rad.pre))
colnames(tran.rad.pre) <- c("tran","time")

tran.rad.irm$time <- rep("Irma",nrow(tran.rad.irm))
colnames(tran.rad.irm) <- c("tran","time")

tran.rad.pos$time <- rep("Post",nrow(tran.rad.pos))
colnames(tran.rad.pos) <- c("tran","time")

tran.rad <- rbind(tran.rad.pre,tran.rad.irm,tran.rad.pos)

tran.rad.complete <- tran.rad[complete.cases(tran.rad),]

tran.rad.se <- summarySE(tran.rad.complete,measurevar="tran",groupvars=c("time"))

ggplot(tran.rad.se,aes(x=time,y=log(tran)))+
  geom_jitter(data=tran.rad.complete,alpha=0.5)+
  geom_violin(data=tran.rad.complete,alpha=0.5)+
  geom_point(size=2)+
  geom_errorbar(aes(ymin=log(tran-se),ymax=log(tran+se)))

ggplot(tran.rad.complete,aes(x=time,y=log(tran)))+
  geom_jitter(alpha=0.5)+
  geom_boxplot(alpha=0.5)
####clean up? show?####

pairwise.wilcox.test(tran.rad.complete$tran,tran.rad.complete$time,p.adjust.method = "BH")
```

### Betweenness

```{r}
btn.sid.pre <- data.frame(igraph::betweenness(ig.sid.pre))
btn.sid.irm <- data.frame(igraph::betweenness(ig.sid.irm))
btn.sid.pos <- data.frame(igraph::betweenness(ig.sid.pos))

btn.sid.pre$time <- rep("Pre",nrow(btn.sid.pre))
colnames(btn.sid.pre) <- c("btwn","time")

btn.sid.irm$time <- rep("Irma",nrow(btn.sid.irm))
colnames(btn.sid.irm) <- c("btwn","time")

btn.sid.pos$time <- rep("Post",nrow(btn.sid.pos))
colnames(btn.sid.pos) <- c("btwn","time")

btn.sid <- rbind(btn.sid.pre,btn.sid.irm,btn.sid.pos)

ggplot(btn.sid,aes(x=time,y=log(btwn)))+
  geom_boxplot()

btn.rad.pre <- data.frame(igraph::betweenness(ig.rad.pre))
btn.rad.irm <- data.frame(igraph::betweenness(ig.rad.irm))
btn.rad.pos <- data.frame(igraph::betweenness(ig.rad.pos))

btn.rad.pre$time <- rep("Pre",nrow(btn.rad.pre))
colnames(btn.rad.pre) <- c("btwn","time")

btn.rad.irm$time <- rep("Irma",nrow(btn.rad.irm))
colnames(btn.rad.irm) <- c("btwn","time")

btn.rad.pos$time <- rep("Post",nrow(btn.rad.pos))
colnames(btn.rad.pos) <- c("btwn","time")

btn.rad <- rbind(btn.rad.pre,btn.rad.irm,btn.rad.pos)

ggplot(btn.rad,aes(x=time,y=log(btwn)))+
  geom_boxplot()
```

### Degree

#### Sids

```{r}
deg.sid.pre <- data.frame(igraph::degree(ig.sid.pre,normalized=TRUE))
deg.sid.irm <- data.frame(igraph::degree(ig.sid.irm,normalized=TRUE))
deg.sid.pos <- data.frame(igraph::degree(ig.sid.pos,normalized=TRUE))

deg.sid.pre$time <- rep("Pre",nrow(deg.sid.pre))
colnames(deg.sid.pre) <- c("deg","time")

deg.sid.irm$time <- rep("Irma",nrow(deg.sid.irm))
colnames(deg.sid.irm) <- c("deg","time")

deg.sid.pos$time <- rep("Post",nrow(deg.sid.pos))
colnames(deg.sid.pos) <- c("deg","time")

deg.sid <- rbind(deg.sid.pre,deg.sid.irm,deg.sid.pos)

ggplot(deg.sid,aes(x=time,y=deg))+
  geom_boxplot()

pairwise.wilcox.test(deg.sid$deg,deg.sid$time,p.adjust.method = "BH")

deg.rad.pre <- data.frame(igraph::degree(ig.rad.pre,normalized=TRUE))
deg.rad.irm <- data.frame(igraph::degree(ig.rad.irm,normalized=TRUE))
deg.rad.pos <- data.frame(igraph::degree(ig.rad.pos,normalized=TRUE))

deg.rad.pre$time <- rep("Pre",nrow(deg.rad.pre))
colnames(deg.rad.pre) <- c("deg","time")

deg.rad.irm$time <- rep("Irma",nrow(deg.rad.irm))
colnames(deg.rad.irm) <- c("deg","time")

deg.rad.pos$time <- rep("Post",nrow(deg.rad.pos))
colnames(deg.rad.pos) <- c("deg","time")

deg.rad <- rbind(deg.rad.pre,deg.rad.irm,deg.rad.pos)

ggplot(deg.rad,aes(x=time,y=deg))+
  geom_boxplot()

pairwise.wilcox.test(deg.rad$deg,deg.rad$time,p.adjust.method = "BH")
```

### Saving all

```{r}
# saveRDS(ig.sid.pre,file="./nets_revised/ig.sid.pre.gen.2.rds")
# saveRDS(ig.sid.irm,file="./nets_revised/ig.sid.irm.gen.2.rds")
# saveRDS(ig.sid.pos,file="./nets_revised/ig.sid.pos.gen.2.rds")
# 
# saveRDS(ig.rad.pre,file="./nets_revised/ig.rad.pre.gen.2.rds")
# saveRDS(ig.rad.irm,file="./nets_revised/ig.rad.irm.gen.2.rds")
# saveRDS(ig.rad.pos,file="./nets_revised/ig.rad.pos.gen.2.rds")
```

## Exploring igraph plots

```{r}
plot.igraph(ig.sid.pre)

plot.igraph(ig.sid.irm, 
            vertex.size=igraph::degree(ig.sid.irm),
            main="degree")
```

## Degree distribution 

```{r}
#https://www.researchgate.net/publication/249316106_Quantification_and_Comparison_of_Degree_Distributions_in_Complex_Networks
#to compare?^

#was .pre2 before..
deg.dist <- degree_distribution(ig.rad.pre,cumulative=T,mode="total") # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("rad.pre",length(deg.dist))
deg.rad.pre <- data.frame(deg.dist,num,treat)

deg.rad.pre$num2 <- deg.rad.pre$num/341

ggplot(deg.rad.pre,aes(x=num,y=num2))+
  geom_point()

deg.dist <- degree_distribution(ig.rad.irm, mode = "total", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("rad.irm",length(deg.dist))
deg.rad.irm <- data.frame(deg.dist,num,treat)

deg.rad.irm$num2 <- deg.rad.irm$num/311

deg.dist <- degree_distribution(ig.rad.pos, mode = "total", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("rad.pos",length(deg.dist))
deg.rad.pos <- data.frame(deg.dist,num,treat)

deg.rad.pos$num2 <- deg.rad.pos$num/185

deg.rad <- rbind(deg.rad.pre,deg.rad.irm,deg.rad.pos)

#raw
ggplot(deg.rad,aes(x=num,y=deg.dist,color=treat))+
  geom_point()+
  geom_line()

#normalized?
ggplot(deg.rad,aes(x=num2,y=deg.dist,color=treat))+
  geom_point()+
  geom_line()

deg.dist <- degree_distribution(ig.sid.pre, mode = "total", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("sid.pre",length(deg.dist))
deg.sid.pre <- data.frame(deg.dist,num,treat)

deg.sid.pre$num2 <- deg.sid.pre$num/168

deg.dist <- degree_distribution(ig.sid.irm, mode = "total", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("sid.irm",length(deg.dist))
deg.sid.irm <- data.frame(deg.dist,num,treat)

deg.sid.irm$num2 <- deg.sid.irm$num/172

deg.dist <- degree_distribution(ig.sid.pos, mode = "total", cumulative = T) # Plot degree distribution
num <- (1:length(deg.dist))
treat <- rep("sid.pos",length(deg.dist))
deg.sid.pos <- data.frame(deg.dist,num,treat)

deg.sid.pos$num2 <- deg.sid.pos$num/161

deg.sid <- rbind(deg.sid.pre,deg.sid.irm,deg.sid.pos)

#raw
ggplot(deg.sid,aes(x=num,y=deg.dist,color=treat))+
  geom_point()+
  geom_line()

ggplot(deg.sid,aes(x=num2,y=deg.dist,color=treat))+
  geom_point()+
  geom_line()
```

# Eigen centrality

## Libs

```{r}
library("tidyr")
library("Rmisc")
library("plyr")
library("dplyr")
library("cowplot")
library(colorBlindness)
```

### Siderea{.tabset}

#### Prep for all time points

Minimum eigen 0.4.. for ease of plotting.. 

```{r}
cen.sid.pre <- eigen_centrality(ig.sid.pre)$vector
cen.sid.irm <- eigen_centrality(ig.sid.irm)$vector
cen.sid.pos <- eigen_centrality(ig.sid.pos)$vector

cen.sid.pre.25 <- data.frame(cen.sid.pre[cen.sid.pre>0.4])
cen.sid.irm.25 <- data.frame(cen.sid.irm[cen.sid.irm>0.4])
cen.sid.pos.25 <- data.frame(cen.sid.pos[cen.sid.pos>0.4])

colnames(cen.sid.pre.25) <- c("cent")
colnames(cen.sid.irm.25) <- c("cent")
colnames(cen.sid.pos.25) <- c("cent")

tax.sid.pre <- as.data.frame(ps.sid.pre@tax_table)
tax.sid.irm <- as.data.frame(ps.sid.irm@tax_table)
tax.sid.pos <- as.data.frame(ps.sid.pos@tax_table)

cen.sid.pre.tax <- merge(cen.sid.pre.25,tax.sid.pre,by=0)
cen.sid.irm.tax <- merge(cen.sid.irm.25,tax.sid.irm,by=0)
cen.sid.pos.tax <- merge(cen.sid.pos.25,tax.sid.pos,by=0)

cen.sid.pre.tax$time <- "pre"
cen.sid.irm.tax$time <- "irm"
cen.sid.pos.tax$time <- "pos"

cen.sid.all <- rbind(cen.sid.pre.tax,cen.sid.irm.tax,cen.sid.pos.tax)

table(cen.sid.all$Family)

cen.sid.famz <- cen.sid.all[duplicated(cen.sid.all$Family),]
unique(cen.sid.famz$Family)

##plotting
cen.sid.famz.ord <- cen.sid.famz[order(cen.sid.famz$Class),]

##note: made some changes to this original one below in the multi-panel plot
pal.fam <- c("#201158","#00784C","#003E5F","#E89E6B","#FFADC1","#005E5E","#578B21","#FFCEF4","#A89800","white")
                      
names(pal.fam) <- c("Cyclobacteriaceae","Xanthobacteraceae","Flavobacteriaceae","Burkholderiaceae","Puniceicoccaceae","Order_Cytophagales","AEGEAN-169 marine group","Cyanobiaceae","Clade I","unique")
```

#### Pre plot

```{r}
#making a new variable
cen.sid.pre.tax <- cen.sid.pre.tax %>%
  mutate(special=case_when(
    Family=="Cyclobacteriaceae"~"Cyclobacteriaceae",
    Family=="Xanthobacteraceae"~"Xanthobacteraceae",
    Family=="Flavobacteriaceae"~"Flavobacteriaceae",
    Family=="Burkholderiaceae"~"Burkholderiaceae",
    Family=="Puniceicoccaceae"~"Puniceicoccaceae",
    Family=="Order_Cytophagales"~"Order_Cytophagales",
    Family=="AEGEAN-169 marine group"~"AEGEAN-169 marine group",
    Family=="Cyanobiaceae"~"Cyanobiaceae",
    Family=="Clade I"~"Clade I",
    .default="unique"))

gg.bar.sid.pre <- ggplot(cen.sid.pre.tax,aes(y=reorder(Genus,cent),x=cent,fill=special))+
  geom_bar(stat="identity",color="black")+
  theme_cowplot()+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  ylab(" ")+
  xlab(" ")+
  scale_x_continuous(expand=c(0,0))+
  scale_fill_manual(values=pal.fam)+
  ggtitle("Pre")
#gg.bar.simple.sid.pre
```

#### Irma plot

```{r}
#making a new variable
cen.sid.irm.tax <- cen.sid.irm.tax %>%
  mutate(special=case_when(
    Family=="Cyclobacteriaceae"~"Cyclobacteriaceae",
    Family=="Xanthobacteraceae"~"Xanthobacteraceae",
    Family=="Flavobacteriaceae"~"Flavobacteriaceae",
    Family=="Burkholderiaceae"~"Burkholderiaceae",
    Family=="Puniceicoccaceae"~"Puniceicoccaceae",
    Family=="Order_Cytophagales"~"Order_Cytophagales",
    Family=="AEGEAN-169 marine group"~"AEGEAN-169 marine group",
    Family=="Cyanobiaceae"~"Cyanobiaceae",
    Family=="Clade I"~"Clade I",
    .default="unique"))

gg.bar.sid.irm <- ggplot(cen.sid.irm.tax,aes(y=reorder(Genus,cent),x=cent,fill=special))+
  geom_bar(stat="identity",color="black")+
  theme_cowplot()+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  ylab("Genus")+
  xlab(" ")+
  scale_fill_manual(values=pal.fam)+
  scale_x_continuous(expand=c(0,0))+
  ggtitle("Disturbance")
gg.bar.sid.irm
```

#### Post plot

```{r}
#making a new variable
cen.sid.pos.tax <- cen.sid.pos.tax %>%
  mutate(special=case_when(
    Family=="Cyclobacteriaceae"~"Cyclobacteriaceae",
    Family=="Xanthobacteraceae"~"Xanthobacteraceae",
    Family=="Flavobacteriaceae"~"Flavobacteriaceae",
    Family=="Burkholderiaceae"~"Burkholderiaceae",
    Family=="Puniceicoccaceae"~"Puniceicoccaceae",
    Family=="Order_Cytophagales"~"Order_Cytophagales",
    Family=="AEGEAN-169 marine group"~"AEGEAN-169 marine group",
    Family=="Cyanobiaceae"~"Cyanobiaceae",
    Family=="Clade I"~"Clade I",
    .default="unique"))

gg.bar.sid.pos <- ggplot(cen.sid.pos.tax,aes(y=reorder(Genus,cent),x=cent,fill=special))+
  geom_bar(stat="identity",color="black")+
  scale_x_continuous(expand=c(0,0))+
  theme_cowplot()+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  ylab(" ")+
  xlab("Eigen. cent.")+
  scale_fill_manual(values=pal.fam)+
  #guides(fill=guide_legend(override.aes=list(fill=pal.fam)))+
  ggtitle("Post-disturb.")

gg.bar.sid.pos
```

### Multi-panel sid plot

```{r}
gg.bar.sid.all <- ggarrange(gg.bar.sid.pre,gg.bar.sid.irm,gg.bar.sid.pos,nrow=3,legend="none",align="hv")
gg.bar.sid.all

# define your custom color palette and labels
pal.fam2 <- c("#201158", "#00784C", "#003E5F", "#E89E6B", "#FFADC1", "#005E5E", "#578B21", "#FFCEF4", "#A89800", "white")
labels <- c("Cyclobacteriaceae", "Xanthobacteraceae", "Flavobacteriaceae", "Burkholderiaceae", "Puniceicoccaceae", "Order_Cytophagales", "AEGEAN-169 marine group", "Cyanobiaceae", "Clade I", "unique")

# create a fake plot with the custom color palette and labels
dummy_plot <- ggplot() +
  guides(fill = guide_legend(title = "Family", nrow = 10, keywidth = unit(1, "cm"), direction = "vertical"),color="black") +
  geom_bar(stat = "identity", aes(x = 1, y = 1, fill = labels),color="black") +
  scale_fill_manual(values = pal.fam2, labels = labels, name = NULL)

# arrange the plots using cowplot
plot_grid(gg.bar.sid.all, get_legend(dummy_plot), ncol=2,rel_widths=c(2,1))
```

Assigning family colors to the igraph object

```{r family color nodes?}
ig.sid.pre.copy <- ig.sid.pre

tax.sid.pre <- data.frame(ps.sid.pre@tax_table)
row.names(tax.sid.pre) == c(igraph::get.vertex.attribute(ig.sid.pre.copy)$name)

tax.sid.pre <- tax.sid.pre %>%
  mutate(special=case_when(
    Family=="Cyclobacteriaceae"~"Cyclobacteriaceae",
    Family=="Xanthobacteraceae"~"Xanthobacteraceae",
    Family=="Flavobacteriaceae"~"Flavobacteriaceae",
    Family=="Burkholderiaceae"~"Burkholderiaceae",
    Family=="Puniceicoccaceae"~"Puniceicoccaceae",
    Family=="Order_Cytophagales"~"Order_Cytophagales",
    Family=="AEGEAN-169 marine group"~"AEGEAN-169 marine group",
    Family=="Cyanobiaceae"~"Cyanobiaceae",
    Family=="Clade I"~"Clade I",
    .default="unique"))

tax.sid.pre <- tax.sid.pre %>%
  mutate(alf=case_when(
    Family=="Cyclobacteriaceae"~"yes",
    Family=="Xanthobacteraceae"~"yes",
    Family=="Flavobacteriaceae"~"yes",
    Family=="Burkholderiaceae"~"yes",
    Family=="Puniceicoccaceae"~"yes",
    Family=="Order_Cytophagales"~"yes",
    Family=="AEGEAN-169 marine group"~"yes",
    Family=="Cyanobiaceae"~"yes",
    Family=="Clade I"~"yes",
    .default="no"))

V(ig.sid.pre.copy)$alf <- c(tax.sid.pre$alf)

V(ig.sid.pre.copy)$special <- c(tax.sid.pre$special)
# 
# pal.fam <- c("#201158","#00784C","#003E5F","#E89E6B","#FFADC1","#005E5E","#578B21","#FFCEF4","#A89800","lightgray")
                      
# names(pal.fam) <- c("Cyclobacteriaceae","Xanthobacteraceae","Flavobacteriaceae","Burkholderiaceae","Puniceicoccaceae","Order_Cytophagales","AEGEAN-169 marine group","Cyanobiaceae","Clade I","unique")

cen.sid.all$gen_lab <- substr(cen.sid.all$Genus,0,4)
tax.sid.pre$sqs <- row.names(tax.sid.pre)
tax.sid.pre2 <- merge(tax.sid.pre,cen.sid.all,sort=F,by="Genus")
row.names(tax.sid.pre2) <- tax.sid.pre2$sqs

row.names(tax.sid.pre2) == c(igraph::get.vertex.attribute(ig.sid.pre.copy)$name)

V(ig.sid.pre.copy)$gen_lab <- c(tax.sid.pre$special)


#tax.sid.pre$gen_lab <- substr(tax.sid.pre$Genus,0,4)
#V(ig.sid.pre.copy)$gen_lab <- c(tax.sid.pre$gen_lab)

ggnet2(ig.sid.pre.copy,alpha="alf",color="lightgray",size="degree",size.cut=5,max_size=2,label="gen_lab")+
  scale_alpha_manual(values=c(0.5,1))+
  ggtitle('Pre')

ggnet2(ig.sid.pre.copy,alpha=0.5,color="special",palette=pal.fam,size="degree",size.cut = )+
  ggtitle('Pre')




```

# Plotting nets

## Sids

```{r}
E(ig.sid.pre)$color2 <- sub("forestgreen","#008400",E(ig.sid.pre)$color)
E(ig.sid.pre)$color3 <- sub("red","#BB4386",E(ig.sid.pre)$color2)
#68001D
#CBCBCB gray 
# gray

gg.sid.pre <- ggnet2(ig.sid.pre,color="grey",alpha=0.5,size="degree",size.cut=T,label.color="black",max_size=5,label.size=2,edge.color="color3",edge.size=0.75,edge.alpha=0.6) #size="degree" before, #size.cut=5 before
gg.sid.pre

# col <- hcl.colors(12, "RedGreen")
# show_col(col)

#ggnet2(ig.sid.irm,size="degree",max_size=5,size.cut=3,edge.color="color",edge.size="width")
#cvdPlot(gg.sid.pre)

E(ig.sid.irm)$color2 <- sub("forestgreen","#008400",E(ig.sid.irm)$color)
E(ig.sid.irm)$color3 <- sub("red","#BB4386",E(ig.sid.irm)$color2)
#68001D
#CBCBCB gray 
# gray

gg.sid.irm <- ggnet2(ig.sid.irm,color="grey",alpha=0.5,size="degree",size.cut=T,label.color="black",max_size=5,label.size=2,edge.color="color3",edge.size=0.75,edge.alpha=0.6) #size="degree" before, #size.cut=5 before
gg.sid.irm

E(ig.sid.pos)$color2 <- sub("forestgreen","#008400",E(ig.sid.pos)$color)
E(ig.sid.pos)$color3 <- sub("red","#BB4386",E(ig.sid.pos)$color2)
#68001D
#CBCBCB gray 
# gray

gg.sid.pos <- ggnet2(ig.sid.pos,color="grey",alpha=0.5,size="degree",size.cut=T,label.color="black",max_size=5,label.size=2,edge.color="color3",edge.size=0.75,edge.alpha=0.6) #size="degree" before, #size.cut=5 before
gg.sid.pos

ggarrange(gg.sid.pre,gg.sid.irm,gg.sid.pos,nrow=1,align="hv")

#ggsave("gg.sid.nets.simple.png",width=12,height=3)
```

## Older iterations:

Simpler alternative

```{r simple alt sids}
###pre
cen.sid.pre <- eigen_centrality(ig.sid.pre)$vector
cen.sid.pre.sorted <- sort(cen.sid.pre,decreasing=TRUE)
cen.sid.pre.sorted.top10 <- cen.sid.pre.sorted[1:10]

cen.sid.pre.sorted.top10.df <- data.frame(cen.sid.pre.sorted.top10)
cen.sid.pre.sorted.top10.df$sqs <- row.names(cen.sid.pre.sorted.top10.df)

tax.sid.pre <- as.data.frame(ps.sid.pre@tax_table)
tax.sid.pre$sqs <- row.names(tax.sid.pre)

cen.sid.pre.tax <- merge(tax.sid.pre,cen.sid.pre.sorted.top10.df,by="sqs")

###irm
cen.sid.irm <- eigen_centrality(ig.sid.irm)$vector
cen.sid.irm.sorted <- sort(cen.sid.irm,decreasing=TRUE)
cen.sid.irm.sorted.top10 <- cen.sid.irm.sorted[1:10]

cen.sid.irm.sorted.top10.df <- data.frame(cen.sid.irm.sorted.top10)
cen.sid.irm.sorted.top10.df$sqs <- row.names(cen.sid.irm.sorted.top10.df)

tax.sid.irm <- as.data.frame(ps.sid.irm@tax_table)
tax.sid.irm$sqs <- row.names(tax.sid.irm)

cen.sid.irm.tax <- merge(tax.sid.irm,cen.sid.irm.sorted.top10.df,by="sqs")

###pos
cen.sid.pos <- eigen_centrality(ig.sid.pos)$vector
cen.sid.pos.sorted <- sort(cen.sid.pos,decreasing=TRUE)
cen.sid.pos.sorted.top10 <- cen.sid.pos.sorted[1:10]

cen.sid.pos.sorted.top10.df <- data.frame(cen.sid.pos.sorted.top10)
cen.sid.pos.sorted.top10.df$sqs <- row.names(cen.sid.pos.sorted.top10.df)

tax.sid.pos <- as.data.frame(ps.sid.pos@tax_table)
tax.sid.pos$sqs <- row.names(tax.sid.pos)

cen.sid.pos.tax <- merge(tax.sid.pos,cen.sid.pos.sorted.top10.df,by="sqs")

colnames(cen.sid.pre.tax) <- sub("cen.sid.pre.sorted.top10","cent",colnames(cen.sid.pre.tax))
colnames(cen.sid.irm.tax) <- sub("cen.sid.irm.sorted.top10","cent",colnames(cen.sid.irm.tax))
colnames(cen.sid.pos.tax) <- sub("cen.sid.pos.sorted.top10","cent",colnames(cen.sid.pos.tax))

cen.sid.all.tax <- rbind(cen.sid.pre.tax,cen.sid.irm.tax,cen.sid.pos.tax)
cen.sid.all.tax[duplicated(cen.sid.all.tax$Genus),]
cen.sid.all.tax[duplicated(cen.sid.all.tax$Family),]

##plotting
#making a new variable
# cen.sid.pre.tax <- cen.sid.pre.tax %>%
#   mutate(special=case_when(
#     Family=="Pirellulaceae"~"Pre-Disturb.",
#     Family=="Order_Rhizobiales"~"Pre-Post",
#     Family=="Order_SAR86 clade"~"Pre-Post",
#     Family=="Flavobacteriaceae"~"Pre-Post",
#     Family=="Woeseiaceae"~"All",
#     .default="Unique"))

cen.sid.pre.tax2 <- cen.sid.pre.tax %>% 
  mutate(Genus = fct_reorder(.f = Genus, .x = cen.sid.pre.sorted.top10, .fun=sum,.desc=T))

stats::reorder(Family,cent)

ggplot(cen.sid.pre.tax,aes(x=reorder(Genus,-cen.sid.pre.sorted.top10),y=cen.sid.pre.sorted.top10))+
  geom_bar(stat="identity",color="black")+
  theme_cowplot()+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  ylab("Eigen. cent.")+
  xlab("Genus")+
  #scale_fill_manual(values=c("black","grey","lightblue","white"),name="")+
  ggtitle("Pre")
#gg.bar.simple.sid.pre

# gg.bar.simple.sid.pre <- ggplot(cen.sid.pre.tax2,aes(x=Genus,y=cen.sid.pre.sorted.top10,fill=special))+
#   geom_bar(stat="identity",color="black")+
#   theme_cowplot()+
#   theme(axis.text.x=element_text(angle=45,hjust=1))+
#   ylab("Eigen. cent.")+
#   scale_fill_manual(values=c("black","grey","lightblue","white"),name="")+
#   ggtitle("Pre")
# gg.bar.simple.sid.pre

cen.sid.irm.tax <- cen.sid.irm.tax %>%
  mutate(special=case_when(
    Family=="Pirellulaceae"~"Pre-Disturb.",
    Family=="Order_Rhizobiales"~"Pre-Post",
    Family=="Order_SAR86 clade"~"Pre-Post",
    Family=="Flavobacteriaceae"~"Pre-Post",
    Family=="Woeseiaceae"~"All",
    .default="Unique"))

cen.sid.irm.tax$Genus <- sub("Burkholderia-Caballeronia-Paraburkholderia","Burkh.Cabal.Parab",cen.sid.irm.tax$Genus)

cen.sid.irm.tax2 <- cen.sid.irm.tax %>% 
  mutate(Genus = fct_reorder(.f = Genus, .x = cen.sid.irm.sorted.top10, .fun=sum,.desc=T))

gg.bar.simple.sid.irm <- ggplot(cen.sid.irm.tax2,aes(x=Genus,y=cen.sid.irm.sorted.top10,fill=special))+
  geom_bar(stat="identity",color="black")+
  theme_cowplot()+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  ylab("Eigen. cent.")+
  scale_fill_manual(values=c("black","grey","white"),name="")+
  ggtitle("Disturb.")
gg.bar.simple.sid.irm

cen.sid.pos.tax <- cen.sid.pos.tax %>%
  mutate(special=case_when(
    Family=="Pirellulaceae"~"Pre-Disturb.",
    Family=="Order_Rhizobiales"~"Pre-Post",
    Family=="Order_SAR86 clade"~"Pre-Post",
    Family=="Flavobacteriaceae"~"Pre-Post",
    Family=="Woeseiaceae"~"All",
    .default="Unique"))

cen.sid.pos.tax2 <- cen.sid.pos.tax %>% 
  mutate(Genus = fct_reorder(.f = Genus, .x = cen.sid.pos.sorted.top10, .fun=sum,.desc=T))

gg.bar.simple.sid.pos <- ggplot(cen.sid.pos.tax2,aes(x=Genus,y=cen.sid.pos.sorted.top10,fill=special))+
  geom_bar(stat="identity",color="black")+
  theme_cowplot()+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  ylab("Eigen. cent.")+
  scale_fill_manual(values=c("black","lightblue","white"),name="")+
  ggtitle("Post")
gg.bar.simple.sid.pos

gg.bar.simple.sid <- ggarrange(gg.bar.simple.sid.pre,gg.bar.simple.sid.irm,gg.bar.simple.sid.pos,nrow=1,align="h",common.legend=TRUE,legend="right")

annotate_figure(gg.bar.simple.sid,top=text_grob("S. siderea",face="italic",size=16))

ggsave("gg.sid.bar.simple.png",width=11)

##for network plotting
row.names(cen.sid.pos.tax2) <- cen.sid.pos.tax2$sqs

cen.sid.pos.tax2$Family <- sub("^[^_]*_", "", cen.sid.pos.tax2$Family)

cen.sid.pos.tax2$fam.new <- substr(cen.sid.pos.tax2$Family,1,3)

pos.sqs <- cen.sid.pos.tax2$sqs
for (sq in pos.sqs){
  print(sq)
}

ifelse(igraph::get.vertex.attribute(ig.sid.pos)$name %in% cen.sid.pos.tax2$sqs, print(cen.sid.pos.tax2$fam.new[,]),"")

V(ig.sid.pre)$fam <- c(cen.sid.pos.tax2$fam.new)
V(ig.sid.irm)$fam <- c(v.sid.names.info$fam)
V(ig.sid.pos)$fam <- c(v.sid.names.info$fam)
```

### Radians

Simpler alternative

```{r simple alt rads}
cen.rad.pre <- eigen_centrality(ig.rad.pre)$vector
cen.rad.pre.sorted <- sort(cen.rad.pre,decreasing=TRUE)
cen.rad.pre.sorted.top10 <- cen.rad.pre.sorted[1:10]

cen.rad.pre.sorted.top10.df <- data.frame(cen.rad.pre.sorted.top10)
cen.rad.pre.sorted.top10.df$sqs <- row.names(cen.rad.pre.sorted.top10.df)

tax.rad.pre <- as.data.frame(ps.rad.pre.no0@tax_table)
tax.rad.pre$sqs <- row.names(tax.rad.pre)

cen.rad.pre.tax <- merge(tax.rad.pre,cen.rad.pre.sorted.top10.df,by="sqs")

cen.rad.irm <- eigen_centrality(ig.rad.irm)$vector
cen.rad.irm.sorted <- sort(cen.rad.irm,decreasing=TRUE)
cen.rad.irm.sorted.top10 <- cen.rad.irm.sorted[1:10]

cen.rad.irm.sorted.top10.df <- data.frame(cen.rad.irm.sorted.top10)
cen.rad.irm.sorted.top10.df$sqs <- row.names(cen.rad.irm.sorted.top10.df)

tax.rad.irm <- as.data.frame(ps.rad.irm.no0@tax_table)
tax.rad.irm$sqs <- row.names(tax.rad.irm)

cen.rad.irm.tax <- merge(tax.rad.irm,cen.rad.irm.sorted.top10.df,by="sqs")

cen.rad.pos <- eigen_centrality(ig.rad.pos)$vector
cen.rad.pos.sorted <- sort(cen.rad.pos,decreasing=TRUE)
cen.rad.pos.sorted.top10 <- cen.rad.pos.sorted[1:10]

cen.rad.pos.sorted.top10.df <- data.frame(cen.rad.pos.sorted.top10)
cen.rad.pos.sorted.top10.df$sqs <- row.names(cen.rad.pos.sorted.top10.df)

tax.rad.pos <- as.data.frame(ps.rad.pos.no0@tax_table)
tax.rad.pos$sqs <- row.names(tax.rad.pos)

cen.rad.pos.tax <- merge(tax.rad.pos,cen.rad.pos.sorted.top10.df,by="sqs")

##plotting
#making a new variable
cen.rad.pre.tax <- cen.rad.pre.tax %>%
  mutate(special=case_when(
    Family=="Clade I"~"Disturb.-Post",
    Family=="Cyanobiaceae"~"Disturb.-Post",
    Family=="Flavobacteriaceae"~"Disturb.-Post",
    Family=="Order_Dadabacteriales"~"Pre-Post",
    Family=="Order_SAR86 clade"~"Disturb.-Post",
    Family=="Xanthobacteraceae"~"Disturb.-Post",
    .default="Unique"))

cen.rad.pre.tax2 <- cen.rad.pre.tax %>% 
  mutate(Genus = fct_reorder(.f = Genus, .x = cen.rad.pre.sorted.top10, .fun=sum,.desc=T))

gg.bar.simple.rad.pre <- ggplot(cen.rad.pre.tax2,aes(x=Genus,y=cen.rad.pre.sorted.top10,fill=special))+
  geom_bar(stat="identity",color="black")+
  theme_cowplot()+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  ylab("Eigen. cent.")+
  scale_fill_manual(values=c("lightblue","white"),name="")+
  ggtitle("Pre")
gg.bar.simple.rad.pre

cen.rad.irm.tax <- cen.rad.irm.tax %>%
  mutate(special=case_when(
    Family=="Clade I"~"Disturb.-Post",
    Family=="Cyanobiaceae"~"Disturb.-Post",
    Family=="Flavobacteriaceae"~"Disturb.-Post",
    Family=="Order_Dadabacteriales"~"Pre-Post",
    Family=="Order_SAR86 clade"~"Disturb.-Post",
    Family=="Xanthobacteraceae"~"Disturb.-Post",
    .default="Unique"))

#cen.rad.irm.tax$Genus <- sub("Burkholderia-Caballeronia-Paraburkholderia","Burkh.Cabal.Parab",cen.rad.irm.tax$Genus)

cen.rad.irm.tax2 <- cen.rad.irm.tax %>% 
  mutate(Genus = fct_reorder(.f = Genus, .x = cen.rad.irm.sorted.top10, .fun=sum,.desc=T))

gg.bar.simple.rad.irm <- ggplot(cen.rad.irm.tax2,aes(x=Genus,y=cen.rad.irm.sorted.top10,fill=special))+
  geom_bar(stat="identity",color="black")+
  theme_cowplot()+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  ylab("Eigen. cent.")+
  scale_fill_manual(values=c("lightgrey","white"),name="")+
  ggtitle("Disturb.")
gg.bar.simple.rad.irm

cen.rad.pos.tax <- cen.rad.pos.tax %>%
  mutate(special=case_when(
    Family=="Clade I"~"Disturb.-Post",
    Family=="Cyanobiaceae"~"Disturb.-Post",
    Family=="Flavobacteriaceae"~"Disturb.-Post",
    Family=="Order_Dadabacteriales"~"Pre-Post",
    Family=="Order_SAR86 clade"~"Disturb.-Post",
    Family=="Xanthobacteraceae"~"Disturb.-Post",
    .default="Unique"))

cen.rad.pos.tax2 <- cen.rad.pos.tax %>% 
  mutate(Genus = fct_reorder(.f = Genus, .x = cen.rad.pos.sorted.top10, .fun=sum,.desc=T))

gg.bar.simple.rad.pos <- ggplot(cen.rad.pos.tax2,aes(x=Genus,y=cen.rad.pos.sorted.top10,fill=special))+
  geom_bar(stat="identity",color="black")+
  theme_cowplot()+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  ylab("Eigen. cent.")+
  scale_fill_manual(values=c("lightgrey","lightblue","white"),name="")+
  ggtitle("Post")
gg.bar.simple.rad.pos

gg.bar.simple.rad <- ggarrange(gg.bar.simple.rad.pre,gg.bar.simple.rad.irm,gg.bar.simple.rad.pos,nrow=1,align="h",common.legend=TRUE,legend="right")

annotate_figure(gg.bar.simple.rad,top=text_grob("S. radians",face="italic",size=16))

ggsave("gg.rad.bar.simple.png",width=11)

justleg <- get_legend(gg.bar.simple.rad.pos)
grid.draw(justleg)
ggsave("just.rad.legend.png")
```

```{r}
###pre
cen.sid.pre <- eigen_centrality(ig.sid.pre)$vector
cen.sid.pre.sorted <- sort(cen.sid.pre,decreasing=TRUE)
cen.sid.pre.sorted.top10 <- cen.sid.pre.sorted[1:10]

cen.sid.pre.sorted.top10.df <- data.frame(cen.sid.pre.sorted.top10)
cen.sid.pre.sorted.top10.df$sqs <- row.names(cen.sid.pre.sorted.top10.df)

cen.sid.pre.sorted.top10.df$time <- rep("Pre",nrow(cen.sid.pre.sorted.top10.df))

names(cen.sid.pre.sorted.top10.df)[names(cen.sid.pre.sorted.top10.df) == 'cen.sid.pre.sorted.top10'] <- 'cent'

##put the info into the 'time' part of the networks for coloring
cen.sid.pre.sqs <- c(cen.sid.pre.sorted.top10.df$sqs)
#V(ig.sid.pre)$fam <- ifelse(igraph::get.vertex.attribute(ig.sid.pre)$name %in% cen.sid.pre.sqs, ig.sid.pre$fam,"other")
V(ig.sid.pre)$cent <- ifelse(igraph::get.vertex.attribute(ig.sid.pre)$name %in% cen.sid.pre.sqs, "Pre","other")

##irm
cen.sid.irm <- eigen_centrality(ig.sid.irm)$vector
cen.sid.irm.sorted <- sort(cen.sid.irm,decreasing=TRUE)
cen.sid.irm.sorted.top10 <- cen.sid.irm.sorted[1:10]

cen.sid.irm.sorted.top10.df <- data.frame(cen.sid.irm.sorted.top10)
cen.sid.irm.sorted.top10.df$sqs <- row.names(cen.sid.irm.sorted.top10.df)

cen.sid.irm.sorted.top10.df$time <- rep("Irma",nrow(cen.sid.irm.sorted.top10.df))

names(cen.sid.irm.sorted.top10.df)[names(cen.sid.irm.sorted.top10.df) == 'cen.sid.irm.sorted.top10'] <- 'cent'

cen.sid.irm.sqs <- c(cen.sid.irm.sorted.top10.df$sqs)
V(ig.sid.irm)$cent <- ifelse(igraph::get.vertex.attribute(ig.sid.irm)$name %in% cen.sid.irm.sqs, "Irma","other")

##pos
cen.sid.pos <- eigen_centrality(ig.sid.pos)$vector
cen.sid.pos.sorted <- sort(cen.sid.pos,decreasing=TRUE)
cen.sid.pos.sorted.top10 <- cen.sid.pos.sorted[1:10]

cen.sid.pos.sorted.top10.df <- data.frame(cen.sid.pos.sorted.top10)
cen.sid.pos.sorted.top10.df$sqs <- row.names(cen.sid.pos.sorted.top10.df)

cen.sid.pos.sorted.top10.df$time <- rep("Post",nrow(cen.sid.pos.sorted.top10.df))

names(cen.sid.pos.sorted.top10.df)[names(cen.sid.pos.sorted.top10.df) == 'cen.sid.pos.sorted.top10'] <- 'cent'

cen.sid.pos.sqs <- c(cen.sid.pos.sorted.top10.df$sqs)
V(ig.sid.pos)$cent <- ifelse(igraph::get.vertex.attribute(ig.sid.pos)$name %in% cen.sid.pos.sqs, "Post","other")

##putting them all together, going to name the families specific things
cen.sid <- rbind(cen.sid.pre.sorted.top10.df,cen.sid.irm.sorted.top10.df,cen.sid.pos.sorted.top10.df)

row.names(cen.sid) <- 1:nrow(cen.sid)

tax.sid <- as.data.frame(ps.sid.pos.no0@tax_table)
tax.sid$sqs <- row.names(tax.sid)

cen.sid.tax <- merge(tax.sid,cen.sid,by="sqs")

cen.sid.tax[duplicated(cen.sid.tax$sqs),]
##by genus:
sort(cen.sid.tax$sqs)
##dups
# sq2 = irma & post, burk
# sq287 = irma & post, flavo
# sq41 = irma & post, clade
# sq56 = pre & irma, woe
# sq8 = irma & post, xanth

# cen.sid.tax[7:8,]$time <- c("Irma & Post") #sq2
# cen.sid.tax[13:14,]$time <- c("Irma & Post") #sq287
# cen.sid.tax[18:19,]$time <- c("Irma & Post") #sq41
# cen.sid.tax[23:24,]$time <- c("Pre & Irma") #sq56
# cen.sid.tax[28:29,]$time <- c("Irma & Post") #sq8

table(cen.sid.tax$Family)
table(cen.sid.tax$Family)>1

cen.sid.tax$fam <- paste0(substr(cen.sid.tax$Family,1,3))
table(cen.sid.tax$fam)
#cen.sid.tax$fam <- c("Com","Kil","Cya","Cla3","Met","Spi","SAR","Phy","Bur","Bur","Chi","Hyd","AEG","Cla2","Alc","She","Cau","Rho","Sum","NS9","Cla1","Sap","Par","MBA","Woe","Vib","SB-","Rhi","Xan","Mor")
cen.sid.tax$fam1==cen.sid.tax$fam

#saveRDS(cen.sid.tax,file="./nets_revised/eigen.centrality.sid.rds")
# 
# pre.sid.sqs <- c(cen.sid.pre.sorted.top10.df$sqs)
# irm.sid.sqs <- c(cen.sid.irm.sorted.top10.df$sqs)
# pos.sid.sqs <- c(cen.sid.pos.sorted.top10.df$sqs)

cen.sid.sub <- data.frame(cen.sid.tax$sqs,cen.sid.tax$fam)
cen.sid.sub.uni <- unique(cen.sid.sub)
v.sid.names <- data.frame(igraph::get.vertex.attribute(ig.sid.pre)$name)
names(v.sid.names) <- "sqs"
names(cen.sid.sub.uni) <- c("sqs","fam")

v.sid.names.info <- join(v.sid.names,cen.sid.sub.uni,by="sqs")
v.sid.names.info$sqs==v.sid.names$sqs

#v.sid.names.info$time <- replace_na(v.sid.names.info$fam,"other")
igraph::get.vertex.attribute(ig.sid.pos)$name == igraph::get.vertex.attribute(ig.sid.pre)$name

V(ig.sid.pre)$fam <- c(v.sid.names.info$fam)
V(ig.sid.irm)$fam <- c(v.sid.names.info$fam)
V(ig.sid.pos)$fam <- c(v.sid.names.info$fam)
```

### Radians

```{r}
###pre
cen.rad.pre <- eigen_centrality(ig.rad.pre)$vector
cen.rad.pre.sorted <- sort(cen.rad.pre,decreasing=TRUE)
cen.rad.pre.sorted.top10 <- cen.rad.pre.sorted[1:10]

cen.rad.pre.sorted.top10.df <- data.frame(cen.rad.pre.sorted.top10)
cen.rad.pre.sorted.top10.df$sqs <- row.names(cen.rad.pre.sorted.top10.df)

cen.rad.pre.sorted.top10.df$time <- rep("Pre",nrow(cen.rad.pre.sorted.top10.df))

names(cen.rad.pre.sorted.top10.df)[names(cen.rad.pre.sorted.top10.df) == 'cen.rad.pre.sorted.top10'] <- 'cent'

##put the info into the 'time' part of the networks for coloring
cen.rad.pre.sqs <- c(cen.rad.pre.sorted.top10.df$sqs)
V(ig.rad.pre)$cent <- ifelse(igraph::get.vertex.attribute(ig.rad.pre)$name %in% cen.rad.pre.sqs, "Pre","other")

##irm
cen.rad.irm <- eigen_centrality(ig.rad.irm)$vector
cen.rad.irm.sorted <- sort(cen.rad.irm,decreasing=TRUE)
cen.rad.irm.sorted.top10 <- cen.rad.irm.sorted[1:10]

cen.rad.irm.sorted.top10.df <- data.frame(cen.rad.irm.sorted.top10)
cen.rad.irm.sorted.top10.df$sqs <- row.names(cen.rad.irm.sorted.top10.df)

cen.rad.irm.sorted.top10.df$time <- rep("Irma",nrow(cen.rad.irm.sorted.top10.df))

names(cen.rad.irm.sorted.top10.df)[names(cen.rad.irm.sorted.top10.df) == 'cen.rad.irm.sorted.top10'] <- 'cent'

cen.rad.irm.sqs <- c(cen.rad.irm.sorted.top10.df$sqs)
V(ig.rad.irm)$cent <- ifelse(igraph::get.vertex.attribute(ig.rad.irm)$name %in% cen.rad.irm.sqs, "Irma","other")

##pos
cen.rad.pos <- eigen_centrality(ig.rad.pos)$vector
cen.rad.pos.sorted <- sort(cen.rad.pos,decreasing=TRUE)
cen.rad.pos.sorted.top10 <- cen.rad.pos.sorted[1:10]

cen.rad.pos.sorted.top10.df <- data.frame(cen.rad.pos.sorted.top10)
cen.rad.pos.sorted.top10.df$sqs <- row.names(cen.rad.pos.sorted.top10.df)

cen.rad.pos.sorted.top10.df$time <- rep("Post",nrow(cen.rad.pos.sorted.top10.df))

names(cen.rad.pos.sorted.top10.df)[names(cen.rad.pos.sorted.top10.df) == 'cen.rad.pos.sorted.top10'] <- 'cent'

cen.rad.pos.sqs <- c(cen.rad.pos.sorted.top10.df$sqs)
V(ig.rad.pos)$cent <- ifelse(igraph::get.vertex.attribute(ig.rad.pos)$name %in% cen.rad.pos.sqs, "Post","other")

##putting them all together, going to name the families specific things
cen.rad <- rbind(cen.rad.pre.sorted.top10.df,cen.rad.irm.sorted.top10.df,cen.rad.pos.sorted.top10.df)

row.names(cen.rad) <- 1:nrow(cen.rad)

tax.rad <- as.data.frame(ps.rad.pos@tax_table)
tax.rad$sqs <- row.names(tax.rad)

cen.rad.tax <- merge(tax.rad,cen.rad,by="sqs")

cen.rad.tax[duplicated(cen.rad.tax$sqs),]
##by genus:
#sort(cen.rad$sqs)
##dups
# sq2 = irma & post, burk
# sq287 = irma & post, flavo
# sq41 = irma & post, clade
# sq56 = pre & irma, woe
# sq8 = irma & post, xanth

# cen.rad.tax[7:8,]$time <- c("Irma & Post") #sq2
# cen.rad.tax[13:14,]$time <- c("Irma & Post") #sq287
# cen.rad.tax[18:19,]$time <- c("Irma & Post") #sq41
# cen.rad.tax[23:24,]$time <- c("Pre & Irma") #sq56
# cen.rad.tax[28:29,]$time <- c("Irma & Post") #sq8

table(cen.rad.tax$Family)
table(cen.rad.tax$Family)>1
##had more when done by genus
#Burk = 3 
#Clade I = 2 
#Pirell = 2 
#Hali = 2
#Flavo = 5
#Woes = 2 #in two diff points
#Xanth = 3 #2 in irma/post, 1 in irma

cen.rad.tax$fam1 <- paste0(substr(cen.rad.tax$Family,1,3))
table(cen.rad.tax$fam1)
cen.rad.tax$fam <- c("Com","Kil","Cya","Cla3","Met","Spi","SAR","Phy","Bur","Bur","Chi","Hyd","AEG","Cla2","Alc","She","Cau","Rho","Sum","NS9","Cla1","Sap","Par","MBA","Woe","Vib","SB-","Rhi","Xan","Mor")
cen.rad.tax$fam1==cen.rad.tax$fam

#saveRDS(cen.rad.tax,file="./nets_revised/eigen.centrality.rad.rds")
# 
# pre.rad.sqs <- c(cen.rad.pre.sorted.top10.df$sqs)
# irm.rad.sqs <- c(cen.rad.irm.sorted.top10.df$sqs)
# pos.rad.sqs <- c(cen.rad.pos.sorted.top10.df$sqs)

cen.rad.sub <- data.frame(cen.rad.tax$sqs,cen.rad.tax$fam)
cen.rad.sub.uni <- unique(cen.rad.sub)
v.rad.names <- data.frame(igraph::get.vertex.attribute(ig.rad.pre)$name)
names(v.rad.names) <- "sqs"
names(cen.rad.sub.uni) <- c("sqs","fam")

v.rad.names.info <- join(v.rad.names,cen.rad.sub.uni,by="sqs")
v.rad.names.info$sqs==v.rad.names$sqs

#v.rad.names.info$time <- replace_na(v.rad.names.info$fam,"other")

V(ig.rad.pre)$fam <- c(v.rad.names.info$fam)
V(ig.rad.irm)$fam <- c(v.rad.names.info$fam)
V(ig.rad.pos)$fam <- c(v.rad.names.info$fam)
```

### Save processed igraph objects

```{r}
# saveRDS(ig.sid.pre,file="./nets_revised/ig.sid.pre.fam.2.more.rds")
# saveRDS(ig.sid.irm,file="./nets_revised/ig.sid.irm.fam.2.more.rds")
# saveRDS(ig.sid.pos,file="./nets_revised/ig.sid.pos.fam.2.more.rds")
# 
# saveRDS(ig.rad.pre,file="./nets_revised/ig.rad.pre.fam.2.more.rds")
# saveRDS(ig.rad.irm,file="./nets_revised/ig.rad.irm.fam.2.more.rds")
# saveRDS(ig.rad.pos,file="./nets_revised/ig.rad.pos.fam.2.more.rds")
```

## Plotting!{.tabset}

### Sids

```{r}
E(ig.sid.pre)$color2 <- sub("forestgreen","#008400",E(ig.sid.pre)$color)
E(ig.sid.pre)$color3 <- sub("red","#BB4386",E(ig.sid.pre)$color2)
#68001D
#CBCBCB gray 
# gray

gg.sid.pre <- ggnet2(ig.sid.pre,color="grey",alpha=0.5,size="degree",size.cut=T,label.color="black",max_size=5,label.size=2,edge.color="color3",edge.size=0.75,edge.alpha=0.6) #size="degree" before, #size.cut=5 before
gg.sid.pre

# col <- hcl.colors(12, "RedGreen")
# show_col(col)

#ggnet2(ig.sid.irm,size="degree",max_size=5,size.cut=3,edge.color="color",edge.size="width")
#cvdPlot(gg.sid.pre)

E(ig.sid.irm)$color2 <- sub("forestgreen","#008400",E(ig.sid.irm)$color)
E(ig.sid.irm)$color3 <- sub("red","#BB4386",E(ig.sid.irm)$color2)
#68001D
#CBCBCB gray 
# gray

gg.sid.irm <- ggnet2(ig.sid.irm,color="grey",alpha=0.5,size="degree",size.cut=T,label.color="black",max_size=5,label.size=2,edge.color="color3",edge.size=0.75,edge.alpha=0.6) #size="degree" before, #size.cut=5 before
gg.sid.irm

E(ig.sid.pos)$color2 <- sub("forestgreen","#008400",E(ig.sid.pos)$color)
E(ig.sid.pos)$color3 <- sub("red","#BB4386",E(ig.sid.pos)$color2)
#68001D
#CBCBCB gray 
# gray

gg.sid.pos <- ggnet2(ig.sid.pos,color="grey",alpha=0.5,size="degree",size.cut=T,label.color="black",max_size=5,label.size=2,edge.color="color3",edge.size=0.75,edge.alpha=0.6) #size="degree" before, #size.cut=5 before
gg.sid.pos

ggarrange(gg.sid.pre,gg.sid.irm,gg.sid.pos,nrow=1,align="hv")

#ggsave("gg.sid.nets.simple.png",width=12,height=3)
```

### Rads

```{r}
E(ig.rad.pre)$color2 <- sub("forestgreen","#008400",E(ig.rad.pre)$color)
E(ig.rad.pre)$color3 <- sub("red","#BB4386",E(ig.rad.pre)$color2)
#68001D
#CBCBCB gray 
# gray

gg.rad.pre <- ggnet2(ig.rad.pre,color="grey",alpha=0.5,size="degree",size.cut=T,label.color="black",max_size=5,label.size=2,edge.color="color3",edge.size=0.75,edge.alpha=0.6) #size="degree" before, #size.cut=5 before
gg.rad.pre

# col <- hcl.colors(12, "RedGreen")
# show_col(col)

#ggnet2(ig.rad.irm,size="degree",max_size=5,size.cut=3,edge.color="color",edge.size="width")
#cvdPlot(gg.rad.pre)

E(ig.rad.irm)$color2 <- sub("forestgreen","#008400",E(ig.rad.irm)$color)
E(ig.rad.irm)$color3 <- sub("red","#BB4386",E(ig.rad.irm)$color2)
#68001D
#CBCBCB gray 
# gray

gg.rad.irm <- ggnet2(ig.rad.irm,color="grey",alpha=0.5,size="degree",size.cut=T,label.color="black",max_size=5,label.size=2,edge.color="color3",edge.size=0.75,edge.alpha=0.6) #size="degree" before, #size.cut=5 before
gg.rad.irm

E(ig.rad.pos)$color2 <- sub("forestgreen","#008400",E(ig.rad.pos)$color)
E(ig.rad.pos)$color3 <- sub("red","#BB4386",E(ig.rad.pos)$color2)
#68001D
#CBCBCB gray 
# gray

gg.rad.pos <- ggnet2(ig.rad.pos,color="grey",alpha=0.5,size="degree",size.cut=T,label.color="black",max_size=5,label.size=2,edge.color="color3",edge.size=0.75,edge.alpha=0.6) #size="degree" before, #size.cut=5 before
gg.rad.pos

ggarrange(gg.rad.pre,gg.rad.irm,gg.rad.pos,nrow=1,align="hv")

#ggsave("gg.rad.nets.simple.png",width=12,height=3)
```

# Eigen bar graphs

## Siderea

```{r}
##we want the centrality info of all 25 unique sqs
cen.sid.pre.df <- data.frame(cen.sid.pre)
cen.sid.pre.df$sqs <- rownames(cen.sid.pre.df)

cen.sid.pre.sub <- cen.sid.pre.df[cen.sid.pre.df$sqs %in% c(cen.sid.tax$sqs),]
cen.sid.pre.sub$time <- rep("Pre",nrow(cen.sid.pre.sub))
names(cen.sid.pre.sub) <- c("cent","sqs","time")

cen.sid.irm.df <- data.frame(cen.sid.irm)
cen.sid.irm.df$sqs <- rownames(cen.sid.irm.df)

cen.sid.irm.sub <- cen.sid.irm.df[cen.sid.irm.df$sqs %in% c(cen.sid.tax$sqs),]
cen.sid.irm.sub$time <- rep("Irma",nrow(cen.sid.irm.sub))
names(cen.sid.irm.sub) <- c("cent","sqs","time")

cen.sid.pos.df <- data.frame(cen.sid.pos)
cen.sid.pos.df$sqs <- rownames(cen.sid.pos.df)

cen.sid.pos.sub <- cen.sid.pos.df[cen.sid.pos.df$sqs %in% c(cen.sid.tax$sqs),]
cen.sid.pos.sub$time <- rep("Post",nrow(cen.sid.pos.sub))
names(cen.sid.pos.sub) <- c("cent","sqs","time")

#cen.sid.sub <- rbind(cen.sid.pre.sub,cen.sid.irm.sub,cen.sid.pos.sub)
#cen.sid.sub[duplicated(cen.sid.sub$sqs),]

cen.sid.tax.less <- cen.sid.tax %>%
  select(sqs,Family) %>%
  unique()

cen.sid.pre.sub.fam <- merge(cen.sid.pre.sub, cen.sid.tax.less, by="sqs",all.x=F)

cen.sid.pre.sub.fam2 <- cen.sid.pre.sub.fam %>% 
  mutate(Family = fct_reorder(.f = Family, .x = cent, .fun=sum))

gg.bar.pre <- ggplot(data=cen.sid.pre.sub.fam2,aes(x=cent,y=Family))+
  geom_bar(stat="identity")+
  theme_bw()+
  ylab("Family")+
  xlab("Eigen. cent.")+
  theme(axis.text.x=element_text(angle=45,hjust=1))
gg.bar.pre

cen.sid.irm.sub.fam <- merge(cen.sid.irm.sub, cen.sid.tax.less, by="sqs",all.x=F)

gg.bar.irm <- ggplot(data=cen.sid.irm.sub.fam,aes(x=cent,y=reorder(Family,cent)))+
  geom_bar(stat="identity")+
  theme_bw()+
  ylab("Family")+
  xlab("Eigen. cent.")+
  theme(axis.text.x=element_text(angle=45,hjust=1))
gg.bar.irm

cen.sid.pos.sub.fam <- merge(cen.sid.pos.sub, cen.sid.tax.less, by="sqs",all.x=F)

cen.sid.pos.sub.fam$Family <- reorder(cen.sid.pos.sub.fam$Family,cen.sid.pos.sub.fam$cent)

penguins %>% 
  mutate(species = fct_reorder(.f = species, .x = bill_length_mm, .fun = median, na.rm = T)) %>% 
  ggplot(aes(x = species, y = bill_length_mm)) +
  geom_boxplot()

gg.bar.pos <- ggplot(data=cen.sid.pos.sub.fam,aes(x=cent,y=stats::reorder(Family,cent)))+
  geom_bar(stat="identity")+
  theme_bw()+
  ylab("Family")+
  xlab("Eigen. cent.")+
  theme(axis.text.x=element_text(angle=45,hjust=1))
gg.bar.pos

#ggarrange(gg.sid.pre,gg.sid.irm,gg.sid.pos,gg.bar.pre,gg.bar.irm,gg.bar.pos,nrow=2,ncol=3,widths=c(1,1,1,0.5,0.5,0.5))

net.rev.sid <- ggarrange(gg.sid.pre,gg.bar.pre,gg.sid.irm,gg.bar.irm,gg.sid.pos,gg.bar.pos,nrow=3,ncol=2,widths=c(1.5,1),labels=c("(a) Pre","(b)","(c) Disturb.","(d)","(e) Post","(f)"),align="hv")
net.rev.sid
annotate_figure(net.rev.sid,top=text_grob("S. siderea",face="italic",size=16))


```

## Radians

```{r}
##we want the centrality info of all 25 unique sqs
cen.rad.pre.df <- data.frame(cen.rad.pre)
cen.rad.pre.df$sqs <- rownames(cen.rad.pre.df)

cen.rad.pre.sub <- cen.rad.pre.df[cen.rad.pre.df$sqs %in% c(cen.rad.tax$sqs),]
cen.rad.pre.sub$time <- rep("Pre",nrow(cen.rad.pre.sub))
names(cen.rad.pre.sub) <- c("cent","sqs","time")

cen.rad.irm.df <- data.frame(cen.rad.irm)
cen.rad.irm.df$sqs <- rownames(cen.rad.irm.df)

cen.rad.irm.sub <- cen.rad.irm.df[cen.rad.irm.df$sqs %in% c(cen.rad.tax$sqs),]
cen.rad.irm.sub$time <- rep("Irma",nrow(cen.rad.irm.sub))
names(cen.rad.irm.sub) <- c("cent","sqs","time")

cen.rad.pos.df <- data.frame(cen.rad.pos)
cen.rad.pos.df$sqs <- rownames(cen.rad.pos.df)

cen.rad.pos.sub <- cen.rad.pos.df[cen.rad.pos.df$sqs %in% c(cen.rad.tax$sqs),]
cen.rad.pos.sub$time <- rep("Post",nrow(cen.rad.pos.sub))
names(cen.rad.pos.sub) <- c("cent","sqs","time")

#cen.rad.sub <- rbind(cen.rad.pre.sub,cen.rad.irm.sub,cen.rad.pos.sub)
#cen.rad.sub[duplicated(cen.rad.sub$sqs),]

cen.rad.tax.less <- cen.rad.tax %>%
  select(sqs,Family) %>%
  unique()

cen.rad.pre.sub.fam <- merge(cen.rad.pre.sub, cen.rad.tax.less, by="sqs",all.x=F)

gg.bar.pre <- ggplot(data=cen.rad.pre.sub.fam,aes(x=cent,y=reorder(Family,cent)))+
  geom_bar(stat="identity")+
  theme_bw()+
  ylab("Family")+
  xlab("Eigen. cent.")+
  theme(axis.text.x=element_text(angle=45,hjust=1))

cen.rad.irm.sub.fam <- merge(cen.rad.irm.sub, cen.rad.tax.less, by="sqs",all.x=F)

gg.bar.irm <- ggplot(data=cen.rad.irm.sub.fam,aes(x=cent,y=reorder(Family,cent)))+
  geom_bar(stat="identity")+
  theme_bw()+
  ylab("Family")+
  xlab("Eigen. cent.")+
  theme(axis.text.x=element_text(angle=45,hjust=1))

cen.rad.pos.sub.fam <- merge(cen.rad.pos.sub, cen.rad.tax.less, by="sqs",all.x=F)

gg.bar.pos <- ggplot(data=cen.rad.pos.sub.fam,aes(x=cent,y=reorder(Family,cent)))+
  geom_bar(stat="identity")+
  theme_bw()+
  ylab("Family")+
  xlab("Eigen. cent.")+
  theme(axis.text.x=element_text(angle=45,hjust=1))
gg.bar.pos

#ggarrange(gg.rad.pre,gg.rad.irm,gg.rad.pos,gg.bar.pre,gg.bar.irm,gg.bar.pos,nrow=2,ncol=3,widths=c(1,1,1,0.5,0.5,0.5))

net.rev.rad <- ggarrange(gg.rad.pre,gg.bar.pre,gg.rad.irm,gg.bar.irm,gg.rad.pos,gg.bar.pos,nrow=3,ncol=2,widths=c(1.5,1),labels=c("(a) Pre","(b)","(c) Disturb.","(d)","(e) Post","(f)"))
annotate_figure(net.rev.rad,top=text_grob("S. radians",face="italic",size=16))

#widths=c(1.5,0.5)

#all of 'em
#cen.rad.sub <- rbind(cen.rad.pre.sub,cen.rad.irm.sub,cen.rad.pos.sub)



ggplot(data=cen.rad.irm.sub,aes(x=cent,y=reorder(sqs,cent)))+
  geom_bar(stat="identity")

ggplot(data=cen.rad.pos.sub,aes(x=cent,y=reorder(sqs,cent)))+
  geom_bar(stat="identity")

##scraps:

ggplot(data=cen.rad.sub,aes(x=reorder(sqs,cent),y=cent,fill=time))+
  geom_bar(stat="identity",position="dodge")

library(dplyr)

cen.rad.sub <- cen.rad.sub %>%
  #select(time) %>%
  mutate(
    time.num = case_when(
      time == "Pre" ~ 1,
      time == "Irma" ~ 2,
      time == "Post" ~ 3))

##reorder?
cen.rad.sub <- cen.rad.sub[order(cen.rad.sub$time.num,-cen.rad.sub$cent),]

#cen.rad.sub$sqs <- factor(cen.rad.sub$sqs, levels = cen.rad.sub$sqs)

cen.rad.sub %>% 
  mutate(row = row_number()) %>%
  ggplot(aes(x=cent,y=reorder(sqs,row)))+
  geom_bar(stat="identity")+
  #facet_wrap(time~.)+
  theme_bw()

cen.rad.sub %>%
  mutate(name = fct_reorder(sqs, desc(row))) %>%
  ggplot(aes(x=cent, y=name)) +
    geom_bar(stat="identity", fill="#f68060", alpha=.6, width=.4) +
    coord_flip() +
    xlab("") +
    theme_bw()

library(tidyverse)

ggplot(dat, aes(y = fct_inorder(sqs), x = cent)) +
  geom_bar(stat = "identity")+
  facet_wrap(~time)

ggplot(dat)

#ggplot(df,aes(x=reorder(V1,row),y=V2))+geom_bar()



```

# ggnetwork?

```{r}
#install.packages("ggnetwork")
library("ggnetwork")

ggplot(ig.rad.pre2)
```

# Checking table stats

```{r}
#shannon diversity divided by species richness
#df.div$even <- df.div$Shannon/(log(df.div$Observed))
#write.csv(df.div,file="fl16s.df.diversity.csv")
#write.csv(df.div,file="fl16s.df.diversity_rare.csv")

##reorder the time points
df.div$time <- factor(df.div$time, levels = c("Pre","Irma","Post"))
df.div$zone <- as.factor(df.div$zone)

#separate species
df.div.rad <- subset(df.div,spp=="srad")
df.div.sid <- subset(df.div,spp=="ssid")

ps.cleanest.rel.ord <- ordinate(ps.cleanest.rel, method="PCoA",distance="bray")
plot_ordination(ps.cleanest.rel,ps.cleanest.rel.ord,color="year")

ps.rad.pre <- subset_samples(ps.clean.rad.no0,time=="Pre")
ps.rad.irm <- subset_samples(ps.clean.rad.no0,time=="Irma")
ps.rad.pos <- subset_samples(ps.clean.rad.no0,time=="Post")



ord.clean.sid <- ordinate(ps.clean.sid, "PCoA", "euclidean")

gg.clean.sid <- plot_ordination(ps.clean.sid, ord.clean.sid,color="time",shape="zone",axes=c(1,2))+
  stat_ellipse()+
  scale_color_manual(values=c("#FA7F53","#A8327D","#3B0F70"))+
  theme_cowplot()+
  scale_alpha_manual(breaks=c("Inshore","Offshore"),values=c(0.45,0.75),name="Reef zone")+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))+
  #xlab("Axis 1 (44.1%)")+
  #ylab("Axis 2 (23%)")+
  #ggtitle("S. siderea")+
  facet_wrap(~site_zone)
gg.clean.sid


```

# Read in & process data

Checking out diversity of taxa tables

Will need to update this for the reduced dataset

```{r}
#ps.clean.rad.rel = transform_sample_counts(ps.clean.rad.no0, function(x) x / sum(x))

samdf.rad <- data.frame(ps.clean.rad.no0@sam_data)
df.rad <- data.frame(estimate_richness(ps.clean.rad.no0, split=TRUE, measures=c("Shannon","InvSimpson","Observed")))

df.rad$sample_num <- rownames(df.rad)
df.rad$sample_num <- sub("X","",df.rad$sample_num)
rownames(df.rad) <- df.rad$sample_num
df.div.rad <- merge(df.rad,samdf.rad,by="sample_num") #add sample data

df.div.rad$time <- factor(df.div.rad$time, levels = c("Pre","Irma","Post"))

ggplot(df.div.rad,aes(x=time,y=Shannon))+
  geom_boxplot()

a1 <- aov(Shannon~time,data=df.div.rad)
summary(a1)

samdf.sid <- data.frame(ps.clean.sid.no0@sam_data)
df.sid <- data.frame(estimate_richness(ps.clean.sid.no0, split=TRUE, measures=c("Shannon","InvSimpson","Observed")))

df.sid$sample_num <- rownames(df.sid)
df.sid$sample_num <- sub("X","",df.sid$sample_num)
rownames(df.sid) <- df.sid$sample_num
df.div.sid <- merge(df.sid,samdf.sid,by="sample_num") #add sample data

df.div.sid$time <- factor(df.div.sid$time, levels = c("Pre","Irma","Post"))

ggplot(df.div.sid,aes(x=time,y=Shannon))+
  geom_boxplot()

a1 <- aov(Shannon~time,data=df.div.sid)
summary(a1)
```

# Not needed

## More plots

```{r}
# #v.rad.names.irm <- data.frame(igraph::get.vertex.attribute(ig.rad.irm2)$name)
# #names(v.rad.names.irm) <- "sqs"
# #v.rad.names.irm$sqs==v.rad.names$sqs
# V(ig.rad.irm2)$time <- c(v.rad.names.info$time)
# V(ig.rad.irm2)$fam <- c(v.rad.names.info$fam)
# 
# V(ig.rad.pos2)$time <- c(v.rad.names.info$time)
# V(ig.rad.pos2)$fam <- c(v.rad.names.info$fam)

#scale_color_manual(values=c("#3B0F70","#FA7F53","#A8327D"))+
#size.pal.pre = c("Pre"=10,"Irma"=1,"Post"=1,"Irma & Post"=1,"Pre & Irma"=1,"NA"=1)
#size="time",size.palette=size.pal.pre
##didn't really work
#lab.pal=c(cen.rad.sub.uni$fam)

#Pre & Irma = 
#colorRampPalette(c("#3B0F70", "#FA7F53"))(16)
#palette(c("#3B0F70","#FA7F53"))

#pal=c("Pre"="#3B0F70","Irma"="#FA7F53","Post"="#A8327D","Irma & Post"="goldenrod","Pre & Irma"="pink","other"="slategray")


# V(ig.rad.pre2)$cent <- ifelse(igraph::get.vertex.attribute(ig.rad.pre2)$name %in% pre.rad.sqs, "Pre","other")
# V(ig.rad.irm2)$cent <- ifelse(igraph::get.vertex.attribute(ig.rad.irm2)$name %in% irm.rad.sqs, "Irma","other")
# V(ig.rad.pos2)$cent <- ifelse(igraph::get.vertex.attribute(ig.rad.pos2)$name %in% pos.rad.sqs, "Post","other")
# 
# ggnet2(ig.rad.pre2,alpha=0.5,color="cent",size="degree",size.cut=5)+
#   ggtitle('Post')
# 
# ggnet2(ig.rad.pre2,alpha=0.5,color="cent",size="degree",size.cut=5)+
#   ggtitle('Post')

#alpha.pal.pre = c("Pre"=0.5,"Irma"=0.5,"Post"=0.5,"Irma & Post"=0.5,"Pre & Irma"=0.5,"other"=0.2)
```

## Lots of plot iterations

```{r}
ig.rad.pos2 <- adj2igraph(getRefit(se.rad.pos), vertex.attr=list(name=taxa_names(ps.rad.pos)))
plot_network(ig.rad.pos2, ps.rad.pos, type='taxa', color="Phylum")

ig.rad.pre2 <- adj2igraph(getRefit(se.rad.pre), vertex.attr=list(name=taxa_names(ps.rad.pre)))
plot_network(ig.rad.pre2, ps.rad.pre, type='taxa', color="Phylum")

ig.rad.irm2 <- adj2igraph(getRefit(se.rad.irm), vertex.attr=list(name=taxa_names(ps.rad.irm)))
plot_network(ig.rad.irm2, ps.rad.irm, type='taxa', color="Phylum")

set.seed(111)
coords <- layout_with_fr(ig.rad.pre)
#coords <- layout_in_circle(ig.rad.pos)

tigr.rad.pre <- as_tbl_graph(ig.rad.pre)
tigr.rad.irm <- as_tbl_graph(ig.rad.irm)
tigr.rad.pos <- as_tbl_graph(ig.rad.pos)

ggraph(tigr.rad.pre,layout=coords)+ 
  geom_edge_link(alpha=0.5) +
  geom_node_point(aes(color="Phylum"))+
  theme_graph()

ggraph(tigr.rad.irm,layout=coords)+ 
  geom_edge_link() +
  geom_node_point(aes(color="Phylum"))+
  theme_graph()

ggraph(tigr.rad.pos,layout=coords)+ 
  geom_edge_link() +
  geom_node_point(aes(color="Phylum"))+
  theme_graph()

##how I did it last time
##excellent walkthrough here: https://briatte.github.io/ggnet/

##pre
tax.rad.pre <- data.frame(ps.rad.pre@tax_table)
row.names(tax.rad.pre) == c(igraph::get.vertex.attribute(ig.rad.pre2)$name)
V(ig.rad.pre2)$phylum <- c(tax.rad.pre$Phylum)

##irm
tax.rad.irm <- data.frame(ps.rad.irm@tax_table)
row.names(tax.rad.irm) == c(igraph::get.vertex.attribute(ig.rad.irm2)$name)
V(ig.rad.irm2)$phylum <- c(tax.rad.irm$Phylum)

##pos
tax.rad.pos <- data.frame(ps.rad.pos@tax_table)
row.names(tax.rad.pos) == c(igraph::get.vertex.attribute(ig.rad.pos2)$name)
V(ig.rad.pos2)$phylum <- c(tax.rad.pos$Phylum)

ggnet2(ig.rad.pre2,alpha=0.5,color="phylum",size="degree",size.cut=5)+
  ggtitle('Pre')

ggnet2(ig.rad.irm2,alpha=0.5,color="phylum",size="degree",size.cut=5)+
  ggtitle('Disturb.')

ggnet2(ig.rad.pos2,alpha=0.5,color="phylum",size="degree",size.cut=5)+
  ggtitle('Post')

ig.rad.pre2 %v% "phono" = ifelse(letters[1:10] %in% c("a", "e", "i"), "vowel", "consonant")
igraph::get.vertex.attribute(ig.rad.pre2)
igraph::set_vertex_attr(ig.rad.pre2,name="phylum",index)
```

Igraph plots, fixed layout of nodes

```{r}
## Create igraph objects
ig.rad.pre <- adj2igraph(getRefit(se.rad.pre))
ig.rad.irm <- adj2igraph(getRefit(se.rad.irm))
ig.rad.pos <- adj2igraph(getRefit(se.rad.pos))

## set size of vertex proportional to clr-mean
#vsize.rad.pre    <- rowMeans(clr(otu.rad.pre.trim, 1))+6
coords <- igraph::layout.fruchterman.reingold(ig.rad.pre)

par(mfrow=c(1,3))
#plot(ig.rad.pre, layout=coord.rad.pre, vertex.size=vsize.rad.pre, vertex.label=NA, main="MB")

plot.igraph(ig.rad.pre, layout = coords, main = "pre")
plot.igraph(ig.rad.irm, layout = coords, main = "irma")
plot.igraph(ig.rad.pos, layout = coords, main = "post")
```

```{r}
# nums <- 1:nrow(otu.rad.cut) 
# samples <- rownames(otu.rad.cut)
# 
# int <- cbind(sample = 0, otu.rad.cut)
# otu.rad.cut.mcmc <- cbind(X = 0, int)
# 
# otu.rad.cut.mcmc$X <- nums
# otu.rad.cut.mcmc$sample <- samples #105 samples
# 
# seq.rad.mcmc.allinfo <- purgeOutliers(otu.rad.cut.mcmc,count.columns=3:67,sampleZcut=-2.5,otu.cut=0,zero.cut=0.05) 
# #leaves 63
# 
# seq.rad.trim <- seq.rad.mcmc.allinfo[,3:65]
# 
# 
# ps.rad.pre <- subset_samples(ps.rad,time=="Pre")
```

Network things from [SpiecEasi github](https://github.com/zdk123/SpiecEasi/)

```{r}
data(amgut1.filt)
depths <- rowSums(amgut1.filt)
amgut1.filt.n  <- t(apply(amgut1.filt, 1, norm_to_total))
amgut1.filt.cs <- round(amgut1.filt.n * min(depths))

d <- ncol(amgut1.filt.cs) #number of taxa
n <- nrow(amgut1.filt.cs) #number of samples
e <- d #I don't understand why these are the same

set.seed(10010)
graph <- make_graph('cluster', d, e)
#seems like binary yes or no
Prec  <- graph2prec(graph)
Cor   <- cov2cor(prec2cov(Prec))

X <- synth_comm_from_counts(amgut1.filt.cs, mar=2, distr='zinegbin', Sigma=Cor, n=n)
##I guess above was just generating fake data?
##I don't really understand because why not use the real one above?

se <- spiec.easi(amgut1.filt.cs, method='mb', lambda.min.ratio=1e-2, nlambda=15)
##method options = 'mb' or 'glasso'
##meinshausen-buhlmann's neighborhood selection
##this here: https://github.com/zdk123/SpiecEasi/issues/70 says either doesn't really matter? different performance somewhat

huge::huge.roc(se$est$path, graph, verbose=FALSE)
stars.pr(getOptMerge(se), graph, verbose=FALSE)
# stars selected final network under: getRefit(se)

##notes: The above example does not cover all possible options and parameters. For example, 
#other generative network models are available, the lambda.min.ratio (the scaling factor that 
#determines the minimum sparsity/lambda parameter) shown here might not be right for your 
#dataset, and its possible that youll want more repetitions (number of subsamples) for StARS.


```


