---
title: "Florida map & env. variables"
author: "Nicola Kriefall"
date: "8/27/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Kd490

## Setup

### Libraries

```{r packages}
library("ggplot2")
library("Rmisc")
library("cowplot")
library("ggpubr")
library("readr")
library("car")
library("lubridate")
library("dplyr")
library("tidyverse")
```

### Kd490 data

```{r kd490 data}
setwd("~/Library/CloudStorage/GoogleDrive-nicfall@bu.edu/My Drive/Flirma/fl_env/kd490")

kd490.lk1i <- read_csv("kd490_raw_lk1i_erdMH1kd4901day_10ff_0584_ad18.csv", skip = 1)
kd490.lk1o <- read_csv("kd490_raw_lk1o_erdMH1kd4901day_cefe_e0de_053a.csv", skip = 1)

kd490.uk1i <- read_csv("kd490_raw_uk1i_erdMH1kd4901day_0de0_5067_fcf5.csv", skip = 1)
kd490.uk1o <- read_csv("kd490_raw_uk1o_erdMH1kd4901day_cd9b_5837_f774.csv", skip = 1)

kd490.uk2i <- read_csv("kd490_raw_uk2i_erdMH1kd4901day_c963_e917_7fd7.csv", skip = 1)
kd490.uk2o <- read_csv("kd490_raw_uk2o_erdMH1kd4901day_580f_71f4_dabf.csv", skip = 1)
```

### Adding variable info

```{r kd490 process}
kd490.lk1i$site_zone <- rep("LK1-I",nrow(kd490.lk1i))
kd490.lk1i$site <- rep("LK1",nrow(kd490.lk1i))
kd490.lk1i$zone <- rep("Inshore",nrow(kd490.lk1i))

kd490.lk1o$site_zone <- rep("LK1-O",nrow(kd490.lk1o))
kd490.lk1o$site <- rep("LK1",nrow(kd490.lk1o))
kd490.lk1o$zone <- rep("Offshore",nrow(kd490.lk1o))

kd490.uk1i$site_zone <- rep("UK1-I",nrow(kd490.uk1i))
kd490.uk1i$site <- rep("UK1",nrow(kd490.uk1i))
kd490.uk1i$zone <- rep("Inshore",nrow(kd490.uk1i))

kd490.uk1o$site_zone <- rep("UK1-O",nrow(kd490.uk1o))
kd490.uk1o$site <- rep("UK1",nrow(kd490.uk1o))
kd490.uk1o$zone <- rep("Offshore",nrow(kd490.uk1o))

kd490.uk2i$site_zone <- rep("UK2-I",nrow(kd490.uk2i))
kd490.uk2i$site <- rep("UK2",nrow(kd490.uk2i))
kd490.uk2i$zone <- rep("Inshore",nrow(kd490.uk2i))

kd490.uk2o$site_zone <- rep("UK2-O",nrow(kd490.uk2o))
kd490.uk2o$site <- rep("UK2",nrow(kd490.uk2o))
kd490.uk2o$zone <- rep("Offshore",nrow(kd490.uk2o))

kd490.all <- rbind(kd490.lk1i,kd490.lk1o,kd490.uk1i,kd490.uk1o,kd490.uk2i,kd490.uk2o)

colnames(kd490.all) <- c("date","lat","lon","kd","site_zone","site","zone")

kd490.lk1 <- subset(kd490.all,site=="LK1")
kd490.uk1 <- subset(kd490.all,site=="UK1")
kd490.uk2 <- subset(kd490.all,site=="UK2")
```

## Plot - all

```{r}
kd490.all.com <- kd490.all[complete.cases(kd490.all),]
kd490.all.se <- summarySE(kd490.all.com,measurevar="kd",groupvars=c("site","zone"))
kd490.all.se

ggplot(kd490.all,aes(x=date,y=kd,color=zone,linetype=site,shape=zone,fill=zone))+
  theme_cowplot()+
  geom_point(alpha=0.4)+
  geom_smooth(se=FALSE)+
  scale_color_manual(name="Reef zone",values=c("#3BBA76","#453882"))+
  scale_fill_manual(name="Reef zone",values=c("#3BBA76","#453882"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  scale_linetype_manual(name="Site",values=c("solid","longdash","twodash"))+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="dotted",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dotted")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dotted")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dotted")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotted")+
  guides(linetype=guide_legend(keywidth = 3, keyheight = 1))+
  xlab("")+
  ylab("Kd490")

#ggsave("gg.kd490.all.pdf",width=5,height=2.5) 
```

## Plots by site{.tabset}

### LK1 kd490

```{r}
gg.kd490.lk1 <- ggplot(kd490.lk1,aes(x=date,y=kd,color=zone,shape=zone))+
  theme_cowplot()+
  geom_point(alpha=0.5)+
  #geom_hline(yintercept=0.11162019,color="#3BBA76",linetype="dashed")+
  #geom_hline(yintercept=0.06183251,color="#453882",linetype="longdash")+
  scale_color_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_fill_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_shape_manual(values=c(16,18),name="Reef zone")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotdash",alpha=0.7)+
  geom_smooth(aes(fill=zone))+
  ylim(0,0.3702)+
  xlab("")+
  facet_grid(vars(site))+
  ylab("")

gg.kd490.lk1
```

### UK1 kd490

```{r}
gg.kd490.uk1 <- ggplot(kd490.uk1,aes(x=date,y=kd,color=zone,shape=zone))+
  theme_cowplot()+
  geom_point(alpha=0.5)+
  #geom_hline(yintercept=0.11162019,color="#3BBA76",linetype="dashed")+
  #geom_hline(yintercept=0.06183251,color="#453882",linetype="longdash")+
  scale_color_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_fill_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_shape_manual(values=c(16,18),name="Reef zone")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotdash",alpha=0.7)+
  geom_smooth(aes(fill=zone))+
  ylim(0,0.3702)+
  xlab("")+
  facet_grid(vars(site))+
  ylab("Kd490")
gg.kd490.uk1
```

### UK2 kd490

```{r}
gg.kd490.uk2 <- ggplot(kd490.uk2,aes(x=date,y=kd,color=zone,shape=zone))+
  theme_cowplot()+
  geom_point(alpha=0.5)+
  #geom_hline(yintercept=0.11162019,color="#3BBA76",linetype="dashed")+
  #geom_hline(yintercept=0.06183251,color="#453882",linetype="longdash")+
  scale_color_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_fill_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_shape_manual(values=c(16,18),name="Reef zone")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotdash",alpha=0.7)+
  geom_smooth(aes(fill=zone))+
  ylim(0,0.3702)+
  xlab("")+
  facet_grid(vars(site))+
  ylab("")
gg.kd490.uk2
```

## Multi-panel plot

```{r}
gg.kd490 <- ggarrange(gg.kd490.uk2,gg.kd490.uk1,gg.kd490.lk1,nrow=3,ncol=1,common.legend=TRUE,legend="right")
gg.kd490

#ggsave("kd490.pdf",width=4.99,height=6.21) #4.99 x 6.21
```

## Kd490 stats

```{r}
kd490.lk1i <- subset(kd490.all.com,site_zone=="LK1-I")
kd490.lk1o <- subset(kd490.all.com,site_zone=="LK1-O")

var(kd490.lk1i$kd) #0.002345926
var(kd490.lk1o$kd) #0.000556887

leveneTest(kd~zone,data=kd490.lk1) #sig
#        Df F value    Pr(>F)    
# group   1   185.1 < 2.2e-16 ***
#       678                      
wilcox.test(kd~zone,data=kd490.lk1) #sig
# data:  kd by zone
# W = 95162, p-value < 2.2e-16

kd490.uk1i <- subset(kd490.all.com,site_zone=="UK1-I")
kd490.uk1o <- subset(kd490.all.com,site_zone=="UK1-O")

var(kd490.uk1i$kd) #0.00284924
var(kd490.uk1o$kd) #0.001324837

leveneTest(kd~zone,data=kd490.uk1) #sig p < 0.001***
#        Df F value    Pr(>F)    
# group   1  42.465 1.875e-10 ***
#       465                      
wilcox.test(kd~zone,data=kd490.uk1) #sig p < 0.001***
#W = 37540, p-value < 2.2e-16

kd490.uk2i <- subset(kd490.all.com,site_zone=="UK2-I")
kd490.uk2o <- subset(kd490.all.com,site_zone=="UK2-O")

var(kd490.uk2i$kd) #0.001563182
var(kd490.uk2o$kd) #0.001175876

leveneTest(kd~zone,data=kd490.uk2) #ns!
#        Df F value Pr(>F)
# group   1   0.047 0.8284
wilcox.test(kd~zone,data=kd490.uk2) #sig p < 0.001***
#W = 37172, p-value < 2.2e-16
```

## Outliers during Irma plot

```{r}
kd490.all.com.irm <- mutate(kd490.all.com, Conditions = case_when(
         date <= "2017-09-09" ~ "Ambient",
         date >= "2017-09-30" ~ "Ambient",
         TRUE ~ "Irma"))
       
ggplot(kd490.all.com.irm,aes(x=site_zone,y=kd,alpha=Conditions))+
  #geom_boxplot(outlier.shape=NA,alpha=0.2,width=0.4)+
  geom_boxplot(aes(x=site_zone,y=kd),color="black",alpha=1,width=0.4,outlier.shape=NA)+
  geom_jitter(aes(color=Conditions,size=Conditions),width=0.2)+
  theme_bw()+
  ylab("Kd490")+
  xlab("Site-zone")+
  scale_color_manual(values=c("grey","red"))+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  scale_alpha_manual(values=c(0.1,1))+
  scale_size_manual(values=c(1,2))

#ggsave("gg.kd490.disturb.pdf",height=3)  
```

### Who are the outliers

Outliers = 1.5*IQR

```{r kd490 outliers}
##lower keys 1 inshore
kd490.lk1i <- subset(kd490.all.com.irm,site_zone=="LK1-I")

quartiles <- quantile(kd490.lk1i$kd, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(kd490.lk1i$kd)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
kd490.lk1i.outs <- subset(kd490.lk1i, kd490.lk1i$kd > Upper)
kd490.lk1i.outs #2/2 is Irma
# 1 2017-09-15 12:00:00  24.5 -81.6 0.358 LK1-I     LK1   Inshore Irma      
# 2 2017-09-17 12:00:00  24.5 -81.6 0.292 LK1-I     LK1   Inshore Irma     

##lower keys 1 offshore
kd490.lk1o <- subset(kd490.all.com.irm,site_zone=="LK1-O")

quartiles <- quantile(kd490.lk1o$kd, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(kd490.lk1o$kd)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
kd490.lk1o.outs <- subset(kd490.lk1o, kd490.lk1o$kd > Upper)
kd490.lk1o.outs #1/24 is Irma

##upper keys 1 inshore
kd490.uk1i <- subset(kd490.all.com.irm,site_zone=="UK1-I")

quartiles <- quantile(kd490.uk1i$kd, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(kd490.uk1i$kd)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
kd490.uk1i.outs <- subset(kd490.uk1i, kd490.uk1i$kd > Upper)
kd490.uk1i.outs #2/3 is Irma

##upper keys 1 offshore
kd490.uk1o <- subset(kd490.all.com.irm,site_zone=="UK1-O")

quartiles <- quantile(kd490.uk1o$kd, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(kd490.uk1o$kd)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
kd490.uk1o.outs <- subset(kd490.uk1o, kd490.uk1o$kd > Upper)
kd490.uk1o.outs #1/4 is Irma [the highest one]

##upper keys 2 inshore
kd490.uk2i <- subset(kd490.all.com.irm,site_zone=="UK2-I")

quartiles <- quantile(kd490.uk2i$kd, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(kd490.uk2i$kd)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
kd490.uk2i.outs <- subset(kd490.uk2i, kd490.uk2i$kd > Upper)
kd490.uk2i.outs #1/2 is Irma [highest one]

##upper keys 2 offshore
kd490.uk2o <- subset(kd490.all.com.irm,site_zone=="UK2-O")

quartiles <- quantile(kd490.uk2o$kd, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(kd490.uk2o$kd)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
kd490.uk2o.outs <- subset(kd490.uk2o, kd490.uk2o$kd > Upper)
kd490.uk2o.outs #no irma
```

## Saving summary stats for RDA

```{r}
kd490.all.com$year <- year(kd490.all.com$date)

kd.sum <- kd490.all.com %>% 
  group_by(site_zone,year) %>%
  dplyr::summarise(mean.kd=mean(kd),
                   min.kd=min(kd),max.kd=max(kd),.groups='drop') %>%
  as.data.frame()

#write.csv(kd.sum,file="kd.for.rda.csv")

kd490.all.com$year <- year(kd490.all.com$date)
kd490.all.com$month <- month(kd490.all.com$date)

#monthly mean, max, min
kd.sum1 <- kd490.all.com %>% 
  group_by(site_zone,year,month) %>%
  dplyr::summarise(mean.kd1=mean(kd),min.kd1=min(kd),max.kd1=max(kd))

kd.sum <- kd.sum1 %>% 
  group_by(site_zone,year) %>%
  dplyr::summarise(mean.kd=mean(mean.kd1),
                   min.kd=mean(min.kd1),max.kd=mean(max.kd1))              

#write.csv(kd.sum,file="kd.for.rda.csv")
```

# SST

## Setup

### Data

```{r sst data}
setwd("~/Library/CloudStorage/GoogleDrive-nicfall@bu.edu/My Drive/Flirma/fl_env")

sst.lk1i <- read_csv("./sst/sst_lk1i_jplMURSST41_d238_b840_1199.csv", skip = 1)
sst.lk1o <- read_csv("./sst/sst_lk1o_jplMURSST41_001d_fbac_764f.csv", skip = 1)

sst.uk1i <- read_csv("./sst/sst_uk1i_jplMURSST41_55fe_e4dd_25da.csv", skip = 1)
sst.uk1o <- read_csv("./sst/sst_uk1o_jplMURSST41_8533_a86a_7e07.csv", skip = 1)

sst.uk2i <- read_csv("./sst/sst_uk2i_jplMURSST41_6185_eb06_e596.csv", skip = 1)
sst.uk2o <- read_csv("./sst/sst_uk2o_jplMURSST41_96cd_3ead_95a9.csv", skip = 1)
```

### Adding variable info

```{r sst process}
sst.lk1i$site_zone <- rep("LK1-I",nrow(sst.lk1i))
sst.lk1i$site <- rep("LK1",nrow(sst.lk1i))
sst.lk1i$zone <- rep("Inshore",nrow(sst.lk1i))

sst.lk1o$site_zone <- rep("LK1-O",nrow(sst.lk1o))
sst.lk1o$site <- rep("LK1",nrow(sst.lk1o))
sst.lk1o$zone <- rep("Offshore",nrow(sst.lk1o))

sst.uk1i$site_zone <- rep("UK1-I",nrow(sst.uk1i))
sst.uk1i$site <- rep("UK1",nrow(sst.uk1i))
sst.uk1i$zone <- rep("Inshore",nrow(sst.uk1i))

sst.uk1o$site_zone <- rep("UK1-O",nrow(sst.uk1o))
sst.uk1o$site <- rep("UK1",nrow(sst.uk1o))
sst.uk1o$zone <- rep("Offshore",nrow(sst.uk1o))

sst.uk2i$site_zone <- rep("UK2-I",nrow(sst.uk2i))
sst.uk2i$site <- rep("UK2",nrow(sst.uk2i))
sst.uk2i$zone <- rep("Inshore",nrow(sst.uk2i))

sst.uk2o$site_zone <- rep("UK2-O",nrow(sst.uk2o))
sst.uk2o$site <- rep("UK2",nrow(sst.uk2o))
sst.uk2o$zone <- rep("Offshore",nrow(sst.uk2o))

sst.all <- rbind(sst.lk1i,sst.lk1o,sst.uk1i,sst.uk1o,sst.uk2i,sst.uk2o)

colnames(sst.all) <- c("date","lat","lon","sst","error","mask","ice","site_zone","site","zone")

sst.lk1 <- subset(sst.all,site=="LK1")
sst.uk1 <- subset(sst.all,site=="UK1")
sst.uk2 <- subset(sst.all,site=="UK2")
```

## Plot - all

```{r}
sst.all.se <- summarySE(sst.all,measurevar="sst",groupvars=c("site","zone"))
sst.all.se

ggplot(sst.all,aes(x=date,y=sst,color=zone,linetype=site,shape=zone,fill=zone))+
  theme_cowplot()+
  geom_point(alpha=0.4)+
  geom_smooth(se=FALSE)+
  scale_color_manual(name="Reef zone",values=c("#3BBA76","#453882"))+
  scale_fill_manual(name="Reef zone",values=c("#3BBA76","#453882"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  scale_linetype_manual(name="Site",values=c("solid","longdash","twodash"))+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="dotted",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dotted")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dotted")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dotted")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotted")+
  guides(linetype=guide_legend(keywidth = 3, keyheight = 1))+
  xlab("")+
  ylab("sst")

#ggsave("gg.sst.all.pdf",width=5,height=2.5) 
```

## Plots by site{.tabset}

### LK1 sst

```{r}
gg.sst.lk1 <- ggplot(sst.lk1,aes(x=date,y=sst,color=zone,shape=zone))+
  theme_cowplot()+
  geom_point(alpha=0.5)+
  #geom_hline(yintercept=0.11162019,color="#3BBA76",linetype="dashed")+
  #geom_hline(yintercept=0.06183251,color="#453882",linetype="longdash")+
  scale_color_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_fill_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_shape_manual(values=c(16,18),name="Reef zone")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotdash",alpha=0.7)+
  geom_smooth(aes(fill=zone))+
  #ylim(0,0.3702)+
  xlab("")+
  facet_grid(vars(site))+
  ylab("")

gg.sst.lk1
```

### UK1 sst

```{r}
gg.sst.uk1 <- ggplot(sst.uk1,aes(x=date,y=sst,color=zone,shape=zone))+
  theme_cowplot()+
  geom_point(alpha=0.5)+
  #geom_hline(yintercept=0.11162019,color="#3BBA76",linetype="dashed")+
  #geom_hline(yintercept=0.06183251,color="#453882",linetype="longdash")+
  scale_color_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_fill_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_shape_manual(values=c(16,18),name="Reef zone")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotdash",alpha=0.7)+
  geom_smooth(aes(fill=zone))+
  #ylim(0,0.3702)+
  xlab("")+
  facet_grid(vars(site))+
  ylab("SST (˚C)")
gg.sst.uk1
```

### UK2 sst

```{r}
gg.sst.uk2 <- ggplot(sst.uk2,aes(x=date,y=sst,color=zone,shape=zone))+
  theme_cowplot()+
  geom_point(alpha=0.5)+
  #geom_hline(yintercept=0.11162019,color="#3BBA76",linetype="dashed")+
  #geom_hline(yintercept=0.06183251,color="#453882",linetype="longdash")+
  scale_color_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_fill_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_shape_manual(values=c(16,18),name="Reef zone")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotdash",alpha=0.7)+
  geom_smooth(aes(fill=zone))+
  #ylim(0,0.3702)+
  xlab("")+
  facet_grid(vars(site))+
  ylab("")
gg.sst.uk2
```

## Multi-panel plot

```{r}
gg.sst <- ggarrange(gg.sst.uk2,gg.sst.uk1,gg.sst.lk1,nrow=3,ncol=1,common.legend=TRUE,legend="right")
gg.sst

#ggsave("sst.pdf") #4.99 x 6.21
```

## Stats

```{r}
sst.all$zone <- as.factor(sst.all$zone)

sst.lk1i <- subset(sst.all,site_zone=="LK1-I")
sst.lk1o <- subset(sst.all,site_zone=="LK1-O")

var(sst.lk1i$sst) #7.37
var(sst.lk1o$sst) #6.34

leveneTest(sst~zone,data=sst.lk1) #sig
# Levene's Test for Homogeneity of Variance (center = median)
#         Df F value    Pr(>F)    
# group    1  13.067 0.0003057 ***
#       2922                      
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
wilcox.test(sst~zone,data=sst.lk1) #ns

sst.uk1i <- subset(sst.all,site_zone=="UK1-I")
sst.uk1o <- subset(sst.all,site_zone=="UK1-O")

var(sst.uk1i$sst) #6.55
var(sst.uk1o$sst) #5.91

leveneTest(sst~zone,data=sst.uk1) #sig p < 0.05*
# Levene's Test for Homogeneity of Variance (center = median)
#         Df F value  Pr(>F)  
# group    1  6.0814 0.01372 *
#       2922                  
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
wilcox.test(sst~zone,data=sst.uk1) #ns

sst.uk2i <- subset(sst.all,site_zone=="UK2-I")
sst.uk2o <- subset(sst.all,site_zone=="UK2-O")

var(sst.uk2i$sst) #5.91
var(sst.uk2o$sst) #4.98

leveneTest(sst~zone,data=sst.uk2) 
# Levene's Test for Homogeneity of Variance (center = median)
#         Df F value    Pr(>F)    
# group    1  17.338 3.219e-05 ***
#       2922                      
wilcox.test(sst~zone,data=sst.uk2) #ns
```

## SST during Irma plot

```{r}
sst.all.irm <- subset(sst.all,date>="2017-08-31"&date<="2017-10-01")

sst.all.irm$site <- factor(sst.all.irm$site,levels=c("UK2","UK1","LK1"))

#library("colorBlindness")
sst.irm <- ggplot(sst.all.irm,aes(x=date,y=sst,color=zone,shape=zone))+
  facet_grid(site~.)+
  theme_cowplot()+
  geom_point()+
  geom_line()+
  xlab("")+
  ylab("Sea surface temperature (˚C)")+
  scale_color_manual(values=c("#6BBE99","#14505C"))+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  ylim(28.5,31.5)
#cvdPlot(sst.check)
sst.irm

#ggsave("sst.irm.pdf")
```

## Outliers?

```{r}
sst.all.irm <- mutate(sst.all, Conditions = case_when(
         date <= "2017-09-09" ~ "Ambient",
         date >= "2017-09-30" ~ "Ambient",
         TRUE ~ "Irma"))
       
ggplot(sst.all.irm,aes(x=site_zone,y=sst,alpha=Conditions))+
  geom_boxplot()+
  #geom_boxplot(aes(x=site_zone,y=sst),color="black",alpha=1,width=0.4)+
  geom_jitter(aes(color=Conditions,size=Conditions),width=0.2)+
  theme_bw()+
  ylab("Chlorophyll a (mg*m-3)")+
  xlab("Site-zone")+
  scale_color_manual(values=c("grey","red"))+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  scale_alpha_manual(values=c(0.1,1))+
  scale_size_manual(values=c(1,2))

#ggsave("gg.sst.disturb.pdf",height=3)  
```

### Who are the outliers

Outliers = 1.5*IQR

```{r sst490 outliers}
##lower keys 1 inshore
sst.lk1i <- subset(sst.all,site_zone=="LK1-I")

quartiles <- quantile(sst.lk1i$sst, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(sst.lk1i$sst)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
sst.lk1i <- subset(sst.lk1i, sst.lk1i$sst > Upper)
sst.lk1i #none

##lower keys 1 offshore
sst.lk1o <- subset(sst.all,site_zone=="LK1-O")

quartiles <- quantile(sst.lk1o$sst, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(sst.lk1o$sst)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
sst.lk1o.outs <- subset(sst.lk1o, sst.lk1o$sst > Upper)
sst.lk1o.outs 

#Nada
```

## Saving summary stats for RDA

```{r}
sst.all$year <- year(sst.all$date)

sst.sum <- sst.all %>% 
  group_by(site_zone,year) %>%
  dplyr::summarise(mean.sst=mean(sst),
                   min.sst=min(sst),max.sst=max(sst),.groups='drop')

#write.csv(sst.sum,file="sst.for.rda.csv")

sst.all$year <- year(sst.all$date)
sst.all$month <- month(sst.all$date)

#monthly mean, max, min
sst.sum1 <- sst.all %>% 
  group_by(site_zone,year,month) %>%
  dplyr::summarise(mean.sst1=mean(sst),min.sst1=min(sst),max.sst1=max(sst))

sst.sum <- sst.sum1 %>% 
  group_by(site_zone,year) %>%
  dplyr::summarise(mean.sst=mean(mean.sst1),
                   min.sst=mean(min.sst1),max.sst=mean(max.sst1))              

#write.csv(sst.sum,file="sst.for.rda.csv")
```

# Chlorophyll a

## Setup

### Data

```{r chla data}
setwd("~/Library/CloudStorage/GoogleDrive-nicfall@bu.edu/My Drive/Flirma/fl_env")

chla.lk1i <- read_csv("./chla/chla_lk1i_erdMH1chla1day_fe38_e834_e4ff.csv", skip = 1)
chla.lk1o <- read_csv("./chla/chla_lk1o_erdMH1chla1day_8ec0_5ab7_9903.csv", skip = 1)

chla.uk1i <- read_csv("./chla/chla_uk1i_erdMH1chla1day_f196_3b14_0596.csv", skip = 1)
chla.uk1o <- read_csv("./chla/chla_uk1o_erdMH1chla1day_b2a5_06bd_6178.csv", skip = 1)

chla.uk2i <- read_csv("./chla/chla_uk2i_erdMH1chla1day_81c7_7691_902c.csv", skip = 1)
chla.uk2o <- read_csv("./chla/chla_uk2o_erdMH1chla1day_f92d_65cc_2509.csv", skip = 1)
```

### Adding variable info

```{r chla process}
chla.lk1i$site_zone <- rep("LK1-I",nrow(chla.lk1i))
chla.lk1i$site <- rep("LK1",nrow(chla.lk1i))
chla.lk1i$zone <- rep("Inshore",nrow(chla.lk1i))

chla.lk1o$site_zone <- rep("LK1-O",nrow(chla.lk1o))
chla.lk1o$site <- rep("LK1",nrow(chla.lk1o))
chla.lk1o$zone <- rep("Offshore",nrow(chla.lk1o))

chla.uk1i$site_zone <- rep("UK1-I",nrow(chla.uk1i))
chla.uk1i$site <- rep("UK1",nrow(chla.uk1i))
chla.uk1i$zone <- rep("Inshore",nrow(chla.uk1i))

chla.uk1o$site_zone <- rep("UK1-O",nrow(chla.uk1o))
chla.uk1o$site <- rep("UK1",nrow(chla.uk1o))
chla.uk1o$zone <- rep("Offshore",nrow(chla.uk1o))

chla.uk2i$site_zone <- rep("UK2-I",nrow(chla.uk2i))
chla.uk2i$site <- rep("UK2",nrow(chla.uk2i))
chla.uk2i$zone <- rep("Inshore",nrow(chla.uk2i))

chla.uk2o$site_zone <- rep("UK2-O",nrow(chla.uk2o))
chla.uk2o$site <- rep("UK2",nrow(chla.uk2o))
chla.uk2o$zone <- rep("Offshore",nrow(chla.uk2o))

chla.all1 <- rbind(chla.lk1i,chla.lk1o,chla.uk1i,chla.uk1o,chla.uk2i,chla.uk2o)

colnames(chla.all1) <- c("date","lat","lon","chla","site_zone","site","zone")

chla.all <- chla.all1[complete.cases(chla.all1),]

chla.lk1 <- subset(chla.all,site=="LK1")
chla.uk1 <- subset(chla.all,site=="UK1")
chla.uk2 <- subset(chla.all,site=="UK2")
```

## Plot - all

```{r}
chla.all.se <- summarySE(chla.all,measurevar="chla",groupvars=c("site","zone"))
chla.all.se

ggplot(chla.all,aes(x=date,y=chla,color=zone,linetype=site,shape=zone,fill=zone))+
  theme_cowplot()+
  geom_point(alpha=0.4)+
  geom_smooth(se=FALSE)+
  scale_color_manual(name="Reef zone",values=c("#3BBA76","#453882"))+
  scale_fill_manual(name="Reef zone",values=c("#3BBA76","#453882"))+
  scale_shape_manual(values=c(21,23),name="Reef zone")+
  scale_linetype_manual(name="Site",values=c("solid","longdash","twodash"))+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="dotted",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dotted")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dotted")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dotted")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotted")+
  guides(linetype=guide_legend(keywidth = 3, keyheight = 1))+
  xlab("")+
  ylab("chla")

#ggsave("gg.chla.all.pdf",width=5,height=2.5) 
```

## Plots by site{.tabset}

### LK1 chla

```{r}
gg.chla.lk1 <- ggplot(chla.lk1,aes(x=date,y=chla,color=zone,shape=zone))+
  theme_cowplot()+
  geom_point(alpha=0.5)+
  #geom_hline(yintercept=0.11162019,color="#3BBA76",linetype="dashed")+
  #geom_hline(yintercept=0.06183251,color="#453882",linetype="longdash")+
  scale_color_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_fill_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_shape_manual(values=c(16,18),name="Reef zone")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotdash",alpha=0.7)+
  geom_smooth(aes(fill=zone))+
  #ylim(0,0.3702)+
  xlab("")+
  facet_grid(vars(site))+
  ylab("")

gg.chla.lk1
```

### UK1 chla

```{r}
gg.chla.uk1 <- ggplot(chla.uk1,aes(x=date,y=chla,color=zone,shape=zone))+
  theme_cowplot()+
  geom_point(alpha=0.5)+
  #geom_hline(yintercept=0.11162019,color="#3BBA76",linetype="dashed")+
  #geom_hline(yintercept=0.06183251,color="#453882",linetype="longdash")+
  scale_color_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_fill_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_shape_manual(values=c(16,18),name="Reef zone")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotdash",alpha=0.7)+
  geom_smooth(aes(fill=zone))+
  #ylim(0,0.3702)+
  xlab("")+
  facet_grid(vars(site))+
  ylab("Chl-a (mg*m-3)")
gg.chla.uk1
```

### UK2 chla

```{r}
gg.chla.uk2 <- ggplot(chla.uk2,aes(x=date,y=chla,color=zone,shape=zone))+
  theme_cowplot()+
  geom_point(alpha=0.5)+
  #geom_hline(yintercept=0.11162019,color="#3BBA76",linetype="dashed")+
  #geom_hline(yintercept=0.06183251,color="#453882",linetype="longdash")+
  scale_color_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_fill_manual(name="Reef zone",values=c("#6BBE99","#14505C"))+
  scale_shape_manual(values=c(16,18),name="Reef zone")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")+
  geom_vline(xintercept=as.numeric(as.POSIXct("2015-04-28 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-10-26 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2018-10-16 12:00:00")),linetype="dashed",alpha=0.7)+
  geom_vline(xintercept=as.numeric(as.POSIXct("2016-04-10 12:00:00")),linetype="dotdash",alpha=0.7)+
  geom_smooth(aes(fill=zone))+
  #ylim(0,0.3702)+
  xlab("")+
  facet_grid(vars(site))+
  ylab("")
gg.chla.uk2
```

## Multi-panel plot

```{r}
gg.chla <- ggarrange(gg.chla.uk2,gg.chla.uk1,gg.chla.lk1,nrow=3,ncol=1,common.legend=TRUE,legend="right")
gg.chla

#ggsave("chla.pdf") #4.99 x 6.21
```

## Chla stats

```{r}
chla.all$zone <- as.factor(chla.all$zone)

chla.lk1i <- subset(chla.all,site_zone=="LK1-I")
chla.lk1o <- subset(chla.all,site_zone=="LK1-O")

var(chla.lk1i$chla) #0.604
var(chla.lk1o$chla) #0.112

leveneTest(chla~zone,data=chla.lk1) #sig
# Levene's Test for Homogeneity of Variance (center = median)
#        Df F value    Pr(>F)    
# group   1  234.45 < 2.2e-16 ***
#       676                      
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
wilcox.test(chla~zone,data=chla.lk1) #W = 94605, p-value < 2.2e-16

chla.uk1i <- subset(chla.all,site_zone=="UK1-I")
chla.uk1o <- subset(chla.all,site_zone=="UK1-O")

var(chla.uk1i$chla) #0.750
var(chla.uk1o$chla) #0.308

leveneTest(chla~zone,data=chla.uk1) #sig 
# Levene's Test for Homogeneity of Variance (center = median)
#        Df F value    Pr(>F)    
# group   1  48.506 1.132e-11 ***
#       464                      
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
wilcox.test(chla~zone,data=chla.uk1) #W = 37442, p-value < 2.2e-16

chla.uk2i <- subset(chla.all,site_zone=="UK2-I")
chla.uk2o <- subset(chla.all,site_zone=="UK2-O")

var(chla.uk2i$chla) #0.4236998
var(chla.uk2o$chla) #0.2791436

leveneTest(chla~zone,data=chla.uk2) #ns
wilcox.test(chla~zone,data=chla.uk2) #sig
#W = 37090, p-value < 2.2e-16
```

## Plots during Irma

Ugly plot

```{r}
chla.all.irm <- subset(chla.all,date>="2017-08-31"&date<="2017-10-01")

chla.all.irm$site <- factor(chla.all.irm$site,levels=c("UK2","UK1","LK1"))

#library("colorBlindness")
chla.irm <- ggplot(chla.all.irm,aes(x=date,y=chla,color=zone,shape=zone))+
  facet_grid(site~.)+
  theme_cowplot()+
  geom_point()+
  geom_line()+
  xlab("")+
  #ylab("Sea surface temperature (˚C)")+
  scale_color_manual(values=c("#6BBE99","#14505C"))+
  geom_vline(xintercept=as.numeric(as.POSIXct("2017-09-10 12:00:00")),linetype="longdash",color="#8b5107")
  #ylim(28.5,31.5)
#cvdPlot(chla.check)
chla.irm

#14505C
#6BBE99

#ggsave("chla.irm.pdf")
```

Different plot

```{r}
chla.all.irm <- mutate(chla.all, Conditions = case_when(
         date <= "2017-09-09" ~ "Ambient",
         date >= "2017-09-30" ~ "Ambient",
         TRUE ~ "Irma"))
       
ggplot(chla.all.irm,aes(x=site_zone,y=chla,alpha=Conditions))+
  geom_boxplot(outlier.shape=NA,alpha=0.2,width=0.4)+
  #geom_boxplot(aes(x=site_zone,y=chla),color="black",alpha=1,width=0.4)+
  geom_jitter(aes(color=Conditions,size=Conditions),width=0.2)+
  theme_bw()+
  ylab("Chlorophyll a (mg*m-3)")+
  xlab("Site-zone")+
  scale_color_manual(values=c("grey","red"))+
  theme(axis.text.x=element_text(angle=45,hjust=1))+
  scale_alpha_manual(values=c(0.1,1))+
  scale_size_manual(values=c(1,2))

#ggsave("gg.chla.disturb.pdf",height=3)  
```

### Who are the outliers

Outliers = 1.5*IQR

```{r chla outliers}
##lower keys 1 inshore
chla.lk1i  <- subset(chla.all.irm,site_zone=="LK1-I")

quartiles <- quantile(chla.lk1i$chla, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(chla.lk1i$chla)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
chla.lk1i.outs <- subset(chla.lk1i, chla.lk1i$chla > Upper)
chla.lk1i.outs #2/2 is Irma
# 1 2017-09-15 12:00:00  24.5 -81.6  5.41 LK1-I     LK1   Inshore Irma      
# 2 2017-09-17 12:00:00  24.5 -81.6  4.29 LK1-I     LK1   Inshore Irma   

##lower keys 1 offshore
chla.lk1o <- subset(chla.all.irm,site_zone=="LK1-O")

quartiles <- quantile(chla.lk1o$chla, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(chla.lk1o$chla)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
chla.lk1o.outs <- subset(chla.lk1o, chla.lk1o$chla > Upper)
chla.lk1o.outs #1/32 is Irma, not highest

##upper keys 1 inshore
chla.uk1i <- subset(chla.all.irm,site_zone=="UK1-I")

quartiles <- quantile(chla.uk1i$chla, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(chla.uk1i$chla)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
chla.uk1i.outs <- subset(chla.uk1i, chla.uk1i$chla > Upper)
chla.uk1i.outs #2/4 is Irma, highest one

##upper keys 1 offshore
chla.uk1o <- subset(chla.all.irm,site_zone=="UK1-O")

quartiles <- quantile(chla.uk1o$chla, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(chla.uk1o$chla)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
chla.uk1o.outs <- subset(chla.uk1o, chla.uk1o$chla > Upper)
chla.uk1o.outs #1/7 is Irma [the highest one]

##upper keys 2 inshore
chla.uk2i <- subset(chla.all.irm,site_zone=="UK2-I")

quartiles <- quantile(chla.uk2i$chla, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(chla.uk2i$chla)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
chla.uk2i.outs <- subset(chla.uk2i, chla.uk2i$chla > Upper)
chla.uk2i.outs #1/2 is Irma [highest one]

##upper keys 2 offshore
chla.uk2o <- subset(chla.all.irm,site_zone=="UK2-O")

quartiles <- quantile(chla.uk2o$chla, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(chla.uk2o$chla)
 
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
 
chla.uk2o.outs <- subset(chla.uk2o, chla.uk2o$chla > Upper)
chla.uk2o.outs #no irma
```

## Saving summary things for RDA

```{r}
chla.all$year <- year(chla.all$date)
chla.all$month <- month(chla.all$date)

#monthly mean, max, min
chla.sum1 <- chla.all %>% 
  group_by(site_zone,year,month) %>%
  dplyr::summarise(mean.chla1=mean(chla),min.chla1=min(chla),max.chla1=max(chla))

chla.sum <- chla.sum1 %>% 
  group_by(site_zone,year) %>%
  dplyr::summarise(mean.chla=mean(mean.chla1),
                   min.chla=mean(min.chla1),max.chla=mean(max.chla1))              

#write.csv(chla.sum,file="chla.for.rda.csv")
```

